\documentclass[english,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
  \ifthenelse{\equal{\string man}{\string man}}{%
   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
  }{}%



% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}


\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Outrageous observations: The redheaded stepchild of data analysis},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

\ifxetex
  \usepackage{polyglossia}
  \setmainlanguage{}
\else
  \usepackage[english]{babel}
\fi

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}

 % Line numbering
  \usepackage{lineno}
  \linenumbers


\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{Outrageous observations: The redheaded stepchild of data analysis}

  \shorttitle{Title}


  \author{Erin M. Buchanan\textsuperscript{1}~\& Ernst-August Doelle\textsuperscript{1,2}}

  % \def\affdep{{"", ""}}%
  % \def\affcity{{"", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Wilhelm-Wundt-University\\
          \textsuperscript{2} Konstanz Business School  }

  \authornote{
    Add complete departmental affiliations for each author here. Each new
    line herein must be indented, like this line.
    
    Enter author note here.
    
    Correspondence concerning this article should be addressed to Erin M.
    Buchanan, Postal address. E-mail:
    \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
  }


  \abstract{Enter abstract here. Each new line herein must be indented, like this
line.}
  \keywords{keywords \\

    \indent Word count: X
  }





\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}



\emph{What are outliers.} Throughout psychology's assessments of
experimental procedures, participant observations have intrigued,
inspired, and confused experimenters world wide. Some of these
observations exist in such extremes that we begin to think of them as
outliers, influential observations, or fringliers (Osborne and Overbay
(2004); Wainer (1976)). Since they were first commented on in 1777 by
Bernoulli, outliers have been defined as many things. Muñoz-Garcia,
Moreno-Rebollo, and Pascual-Acosta (1990) have synthesized their own
definition that we feel is concurrent with our work: \enquote{An outlier
is an observation which being atypical and/or erroneous deviates
decidedly from the general behavior of experimental data with respect to
the criteria which is to be analyzed on it.} (pg 217)

Outliers can be observed in many forms, which should be outlined to
ensure proper understanding and handling of such observations.
Researchers have separated outliers into categories in many different
ways over the years (Beckman and Cook (1983a); Hodge and Austin (2004);
Muñoz-Garcia et al. (1990); ORR, SACKETT, and DUBOIS (1991); Osborne and
Overbay (2004)). Many of the categories used to describe outliers have
noticeable overlap. For instance, Muñoz-Garcia et al. (1990) stated that
outliers come about by errors in the way we gather data (inappropriate
techniques, or experimenter error), errors in preparation (improper
hypothesis, planning, or methods), or natural variability. Shortly
after, ORR et al. (1991) described outliers as consisting of people
being included in an experiment who aren't part of the population,
legitimate datapoints that are interesting because they do not fit the
expected scheme, extreme datapoints on error components, human error in
observation/coding, and errors in data preparation. Similarly, Hodge and
Austin (2004) state that outliers arise, \enquote{due to mechanical
faults, changes in system behaviour, fraudulent behaviour, human error,
instrument error or simply through natural deviations in populations.}
Osborne and Overbay (2004) have also specified that outliers follow from
data errors, intentional or motivated mis-reporting, sampling error,
standardization failure, bad assumptions about distributions, or
legitimate data points. Taken together, we have delineated the following
4 types of outliers for the purpose of this paper. 1. Data entry error,
experimenter error in processing, coding, or preparing data, as well as
motivated misreporting. 2. Participants who do not represent the
intended population. For example, a participant who uses a DVORAK or
ergonomic keyboard will not be appropriate in a study investigating the
typing speeds of typical QWERTY keyboard users. 3. Valid data points
which bring to light interesting phenomena the study was not aimed at
capturing. For instance, the 1854 cholera epidemic in London was found
by Dr.~John Snow to stem from a specific water well on Broad Street.
While the majority of individuals infected lived very close to the
contaminated well, Dr.~Snow also found an instance of cholera far away
from the well. When he rode out to investigate this outlying case, he
found that the woman in question had someone ride to that specific well
to draw water for her because she liked the taste (Vinten-Johansen,
Brody, Paneth, Rachman, \& Rip, 2003). 4. Natural deviations in the
population.

\emph{Effects of outliers} These outliers can have serious effects on
data, which can lead to imprecise data analysis (Osborne and Overbay
(2004)), confusing results (Stevens (1984); Yuan and Bentler (2001)),
and inappropriate conclusions (Coin (2008); Stevens (1984)). By keeping
outliers in a dataset, analyses are more likely to have increased error
variance (depending on sample size, ORR et al. (1991)) and biased
estimates (Osborne and Overbay (2004)) as well as reduced effect size
and power (ORR et al. (1991); Osborne and Overbay (2004)) which can
alter the results of the analysis and lead to falsely supporting (Type I
error) or denying a claim (Type II error). Additionally, incorrect
estimates of effect lead to misleading meta-analyses or sample size
estimates for study planning. Beyond these effects on analyses and
conclusions these outliers can be inspirational to researchers and to
their research models as they can encourage the diagnosis, change, and
evolution of a research model (Beckman and Cook (1983b)). All together,
these issues caused by outliers can lead to furthering unwarranted
avenues of research, ignoring important information, and creating
erroneous theories, all of which serve to weaken the sciences.

\emph{Determination of outliers}

\emph{Report of outliers} For these reasons, we aim to stress the
importance of properly identifying outliers, their potential cause(s),
and ways to handle the extreme responses.

Further, as outlined by the APA (American Psychological Association,
2010), one should acknowledge these steps not only at the time of
analysis, but also at the time of publication. As Kruskal, Ferguson,
Tukey, and Gumbel (1960) stated, no matter how we treat outlying
observations, \enquote{It is very important to say something about such
observations in any but the most summary report. At least how many
observations were excluded from the formal analysis, and why, should be
given.} (pg. 1)

However, outlier report rates in studies have indicated that researchers
either fail to acknowledge outliers or fail to report their
acknowledgment of outliers (Huffcutt and Arthur (1995); ORR et al.
(1991)). Huffcutt and Arthur (1995) looked at Organizational
Behavior/Human Resource Management meta-analytic literature since 1987.
As they were dealing with meta-analyses, the outliers they were
identifying consisted of study coefficients, or correlations, not
individual data points, as outliers are usually thought of. In their
study they found only six of fifty meta-analyses used any outlier
treatment for study coefficients. Also, in most of these, highly
subjective means were used to determine which study coefficients were
outliers. Similarly, ORR et al. (1991) inspected 100
Industrial/Organizational Psychology personnel studies and found no
mention of outliers.

Although the APA and many researchers (ORR et al. (1991), \ldots{}) have
instructed researchers to outline their data cleaning, there has been a
dearth in recent literature investigating if these instructions are
actually being followed. Therefore, the authors felt that the current
study examined the results in 27 journals and 672 articles across 13
psychological disciplines to assess if outliers are being reported.
Given previous report rates (Huffcutt and Arthur (1995); ORR et al.
(1991)) we expect to find little to no reporting of outliers in these
articles. Further, we will examine how outlier reports relate to field,
journal, analysis, and sample size. We will also investigate the methods
and rational of outlier detection and removal.

\section{Method}\label{method}

\subsection{Fields}\label{fields}

A list of psychological field areas was created to begin the search for
appropriate journals to include. The authors brainstormed the list of
topics (shown in Table XX) by first listing major research areas in
psychology (i.e.~cognitive, clinical, social). Second, a list of common
courses offered at large universities was consulted to add to the list
of fields. Lastly, the American Psychological Association's list of
divisions was examined for any potential missed fields. The topic list
was created to capture large fields of psychology with small overlaps
(i.e.~cognition and neuropsychology) while avoiding specific subfields
of topics (i.e.~cognition, perception, and memory).

\subsection{Journals}\label{journals}

Once these topic areas were decided, researchers used various search
sources (Google, EBSCO host databases) to find journals that were
dedicated to each broad topic. Journals were included if they appeared
to publish a wide range of articles within the selected fields. A list
of journals, publishers, and impact factors (as noted by the journal
website) was created for each field. Two journals from each field were
selected based on the following criteria: 1) high impact factors, 2)
impact factors over one a minimum, 3) a mix of publishers if possible,
and 4) availability due to university resources. These journals are
shown in Table XX.

\subsection{Articles}\label{articles}

Fifty articles from each journal were examined for data analysis. Data
collection of articles started at the last volume publication from 2012
and progressed backwards until fifty articles had been found. We
excluded online first publications and started in 2012 to ensure time
for errata and retraction of articles. Articles were including if they
met the following criteria: 1) included data analyses, 2) included
multiple participants or data-points, and 3) analyses were based on
human subjects or stimuli. Therefore, we excluded theory articles,
animal populations, and single subject designs. Based on article review,
three fields were excluded. Applied behavior analysis articles
predominantly included single-subject designs, evolutionary psychology
articles were primarily theory articles, and statistics related journal
articles were based on user created data with specific set
characteristics. Since none of these themes fit into our analysis of
understanding data screening with human subject samples, we excluded
those two fields from analyses.

\subsection{Data Processing}\label{data-processing}

Each article was then reviewed for key components of data analyses. Each
experiment in an article was treated separately. For each experiment,
the type of analysis, number of participants/stimuli, and if they
indicated outliers were coded. Types of analyses were broadly coded into
basic statistics (descriptive statistics, z-scores, t-tests, and
correlations), ANOVAs, regressions, chi-squares, nonparametric
statistics, modeling, and Bayesian/other analyses. First, we coded if
outliers were mentioned at all in article. If so, we coded outliers into
four types: 1) people, 2) data, 3) both, and 4) none found. We found
that a separate coding for data was important for analyses with response
time studies where individual participants were not omitted but rather
specific data trials were eliminated. Then, the author decision on what
to do with the outliers was coded into whether they removed
participants/stimuli or left these outliers in the analysis, as well as
if they tested the analyses with and without these outliers for
determination of their effect on the study. If they removed outliers, a
new sample size was recorded. Lastly, we coded the reasoning for outlier
detection as either participant based (i.e.~3-month old infants were too
fussy to be included), experimenter based (i.e.~the experimental session
was interrupted), statistical based (i.e.~three SD from the mean), and
no listed reason.

Table XX \#\#List of Fields, Journals, and Impact Factors 2012

\begin{tabular}{l|l|l|l}
\hline
Field & Journal & Publisher & Impact Factor\\
\hline
Applied Behavior Analysis & Journal of Experimental Analysis of Behavior & Wiley & 1.39\\
\hline
Applied Behavior Analysis & Journal of Applied Behavior Analysis & Wiley & 1.19\\
\hline
Clinical & Journal of Consulting and Clinical Psychology & APA & 4.85\\
\hline
Clinical & Journal of Clinical Psychology & Wiley & 2.12\\
\hline
Cognitive & Cognitive Psychology & Elsevier & 4.27\\
\hline
Cognitive & Journal of Experimental Psychology: Learning, Memory, and Cognition & APA & 2.85\\
\hline
Counseling & Journal of Counseling & APA & 3.23\\
\hline
Counseling & The Counseling Psychologist & Sage & 1.82\\
\hline
Developmental & Journal of Experimental Child Psychology & Elsevier & 3.23\\
\hline
Developmental & Journal of Youth and Adolescence & Springer & 2.72\\
\hline
Educational & Journal of Educational Psychology & APA & 3.08\\
\hline
Educational & Contemporary Educational Psychology & Elsevier & 2.2\\
\hline
Environmental & Journal of Environmental Psychology & Elsevier & 2.93\\
\hline
Environmental & Environment and Behavior & Sage & 1.27\\
\hline
Evolutionary & Evolution and Human Behavior & Elsevier & 3.11\\
\hline
Evolutionary & Evolutionary Psychology & Open Access & 1.06\\
\hline
Forensics & Psychology, Public Policy, and Law & APA & 1.93\\
\hline
Forensics & Law and Human Bevhavior & Spring & 2.16\\
\hline
Industrial Organization & Organizational Behavior and Human Decision Process & Elsevier & 3.94\\
\hline
Industrial Organization & Personnel Psychology & Wiley & 2.93\\
\hline
Neurological/Physiological & Neuropsychology & APA & 3.82\\
\hline
Neurological/Physiological & Cognitive, Affective, and Behavioral Neuroscience & Springer & 3.57\\
\hline
Social & Journal of Personality and Social Psychology & APA & 5.08\\
\hline
Social & Journal of Experimental Social Psychology & Elsevier & 2.31\\
\hline
Sports & Journal of Sport \& Exercise Psychology & Human Kinetics & 2.66\\
\hline
Sports & Sociology of Sport Journal & Human Kinetics & 1\\
\hline
Statistics & Special Section of the Psychological Bulletin & APA & 14.46\\
\hline
Statistics & Structural Equation Modeling & Taylor \& Francis & 4.71\\
\hline
Overview & Psychonomic Bulletin \& Review & Springer & 2.25\\
\hline
Overview & Psychonomic Science & Sage & 4.43\\
\hline
Overview & Psychological Assessment & APA & 2.99\\
\hline
\end{tabular}

\emph{Note.} Impact factors as of tme of data collection (Spring 2013).

\subsection{Participants}\label{participants}

\subsection{Material}\label{material}

\subsection{Procedure}\label{procedure}

\subsection{Data analysis}\label{data-analysis}

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\newpage

\section{References}\label{references}

\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-Beckman1983a}{}
Beckman, R. J., \& Cook, R. D. (1983a). Outlier..........s.
\emph{Technometrics}, \emph{25}(2), 119.
doi:\href{https://doi.org/10.2307/1268541}{10.2307/1268541}

\hypertarget{ref-Beckman1983}{}
Beckman, R. J., \& Cook, R. D. (1983b). {[}Outlier..........s{]}:
Response. \emph{Technometrics}, \emph{25}(2), 161.
doi:\href{https://doi.org/10.2307/1268548}{10.2307/1268548}

\hypertarget{ref-Coin2008}{}
Coin, D. (2008). Testing normality in the presence of outliers.
\emph{Statistical Methods and Applications}, \emph{17}(1), 3--12.
doi:\href{https://doi.org/10.1007/s10260-007-0046-8}{10.1007/s10260-007-0046-8}

\hypertarget{ref-Hodge2004}{}
Hodge, V. J., \& Austin, J. (2004). A survey of outlier detection
methodologies. \emph{Artificial Intelligence Review}, \emph{22}(2),
85--126.
doi:\href{https://doi.org/10.1007/s10462-004-4304-y}{10.1007/s10462-004-4304-y}

\hypertarget{ref-Huffcutt1995}{}
Huffcutt, A. I., \& Arthur, W. (1995). Development of a new outlier
statistic for meta-analytic data. \emph{Journal of Applied Psychology},
\emph{80}(2), 327--334.
doi:\href{https://doi.org/10.1037//0021-9010.80.2.327}{10.1037//0021-9010.80.2.327}

\hypertarget{ref-Kruskal1960a}{}
Kruskal, W., Ferguson, T. S., Tukey, J. W., \& Gumbel, E. J. (1960).
Discussion of the Papers of Messrs. Anscombe and Daniel.
\emph{Technometrics}, \emph{2}(2), 157--166.
doi:\href{https://doi.org/10.1080/00401706.1960.10489890}{10.1080/00401706.1960.10489890}

\hypertarget{ref-Munoz-Garcia1990}{}
Muñoz-Garcia, J., Moreno-Rebollo, J. L., \& Pascual-Acosta, A. (1990).
Outliers: A formal approach. \emph{International Statistical Review /
Revue Internationale de Statistique}, \emph{58}(3), 215--226.
doi:\href{https://doi.org/10.2307/1403805}{10.2307/1403805}

\hypertarget{ref-ORR1991}{}
ORR, J. M., SACKETT, P. R., \& DUBOIS, C. L. Z. (1991). Outlier
detection and treatment in I / O psychology: A survey of researcher
beliefs and empirical illustration. \emph{Personnel Psychology},
\emph{44}(3), 473--486.
doi:\href{https://doi.org/10.1111/j.1744-6570.1991.tb02401.x}{10.1111/j.1744-6570.1991.tb02401.x}

\hypertarget{ref-Osborne2004}{}
Osborne, J. W., \& Overbay, A. (2004). The power of outliers (and why
researchers should always check for them). \emph{Practical Assessment,
Research \& Evaluation}, \emph{9}(6), 1--12.

\hypertarget{ref-Stevens1984}{}
Stevens, J. P. (1984). Outliers and influential data points in
regression analysis. \emph{Psychological Bulletin}, \emph{95}(2),
334--344.
doi:\href{https://doi.org/10.1037/0033-2909.95.2.334}{10.1037/0033-2909.95.2.334}

\hypertarget{ref-Wainer1976}{}
Wainer, H. (1976). Robust statistics: A survey and some prescriptions.
\emph{Journal of Educational Statistics}, \emph{1}(4), 285.
doi:\href{https://doi.org/10.2307/1164985}{10.2307/1164985}

\hypertarget{ref-Yuan2001}{}
Yuan, K. H., \& Bentler, P. M. (2001). Effect of outliers on estimators
and tests in covariance structure analysis. \emph{British Journal of
Mathematical and Statistical Psychology}, \emph{54}(1), 161--175.
doi:\href{https://doi.org/10.1348/000711001159366}{10.1348/000711001159366}






\end{document}
