\documentclass[english,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
  \ifthenelse{\equal{\string man}{\string man}}{%
   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
  }{}%



% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}


\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Reference List for Articles Used in Manuscript},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

\ifxetex
  \usepackage{polyglossia}
  \setmainlanguage{}
\else
  \usepackage[english]{babel}
\fi

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}



\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{Reference List for Articles Used in Manuscript}

  \shorttitle{Outlier reporting}


  \author{First Author\textsuperscript{1}~\& Ernst-August Doelle\textsuperscript{1,2}}

  % \def\affdep{{"", ""}}%
  % \def\affcity{{"", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Wilhelm-Wundt-University\\
          \textsuperscript{2} Konstanz Business School  }

  \authornote{
    Add complete departmental affiliations for each author here. Each new
    line herein must be indented, like this line.
    
    Enter author note here.
    
    Correspondence concerning this article should be addressed to First
    Author, Postal address. E-mail:
    \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
  }


  \abstract{Enter abstract here. Each new line herein must be indented, like this
line.}
  \keywords{keywords \\

    \indent Word count: X
  }





\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}



\section{Clinical}\label{clinical}

\subsection{Journal of Clinical
Psychology}\label{journal-of-clinical-psychology}

\subsubsection{2012}\label{section}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Anderson, Crowley, Patterson, and Heckman (2012)
\item
  Britton, Conner, and Maisto (2012)
\item
  Brown, Bell, Jason, Christos, and Bell (2012)
\item
  Dempsey, Karver, Labouliere, Zesiewicz, and De Nadai (2012)
\item
  Giromini, Velotti, De Campora, Bonalume, and Cesare Zavattini (2012)
\item
  Hamm et al. (2012)
\item
  Harris et al. (2012)
\item
  Jazaieri, Goldin, Werner, Ziv, and Gross (2012)
\item
  Kapson, Leddy, and Haaga (2012)
\item
  Kim, Zane, and Blozis (2012)
\item
  Leith and Stein (2012)
\item
  Marty, Segal, Coolidge, and Klebe (2012)
\item
  Meinzer, Pettit, Leventhal, and Hill (2012)
\item
  Nel, Pezzolesi, and Stott (2012)
\item
  Osman et al. (2012)
\item
  Park and Kim (2012)
\item
  Quek, Sofronoff, Sheffield, White, and Kelly (2012)
\item
  Skopp et al. (2012b)
\item
  Skopp et al. (2012a)
\item
  Tanner, Gray, and Haaga (2012)
\item
  Troister and Holden (2012)
\item
  Vanderveen, Reddy, Veilleux, January, and Dilillo (2012)
\item
  Viana and Gratz (2012)
\item
  Yu-Hsin Liao, Wei, Russell, and Abraham (2012)
\item
  Zhang, Lamis, and Yuanyuan (2012)
\end{enumerate}

\subsubsection{2017}\label{section-1}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Allan, Gros, Myers, Korte, and Acierno (2017)
\item
  Arrieta et al. (2017)
\item
  Busscher and Spinhoven (2017)
\item
  Silva, Vasco, and Watson (2017)
\item
  Elliott et al. (2017)
\item
  Finlay-Jones, Kane, and Rees (2017)
\item
  Flannery, Luebbe, and Becker (2017)
\item
  Fleming and Burns (2017)
\item
  Glickman, Shear, and Wall (2017)
\item
  Hazlett-Stevens and Oren (2017)
\item
  Johnson et al. (2017a)
\item
  Locke et al. (2017)
\item
  Lutz and Fiske (2017)
\item
  Maguen et al. (2017)
\item
  Miguel, Giromini, Colombarolli, Zuanazzi, and Zennaro (2017)
\item
  Nicolai, Zerach, and Solomon (2017)
\item
  Resnik, Ekerholm, Johnson, Ellison, and O'Toole (2017)
\item
  Richtberg, Jakob, Höfling, and Weck (2017)
\item
  Romano, Arambasic, and Peters (2017)
\item
  Shaw, Campbell, Runions, and Zubrick (2017)
\item
  Shigemoto, Low, Borowa, and Robitschek (2017)
\item
  Ung, Dozier, Bratiotis, and Ayers (2017)
\item
  Vissers et al. (2017)
\item
  Westbrook and Berenbaum (2017)
\item
  Wilson, Miller, Leheney, Ballman, and Scarpa (2017)
\end{enumerate}

\subsection{Journal of Consulting and Clinical
Psychology}\label{journal-of-consulting-and-clinical-psychology}

\subsubsection{2012}\label{section-2}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Applebaum et al. (2012)
\item
  Arch et al. (2012)
\item
  Best et al. (2012)
\item
  Borsari et al. (2012)
\item
  Bowler et al. (2012)
\item
  Brown, Lewis, Lamb, and Stephens (2012)
\item
  Cook et al. (2012)
\item
  Cullen et al. (2012)
\item
  Elbogen et al. (2012)
\item
  Galovski, Blain, Mott, Elwood, and Houle (2012)
\item
  Grilo, Crosby, Wilson, and Masheb (2012)
\item
  Guan, Fox, and Prinstein (2012)
\item
  Hinshaw et al. (2012)
\item
  Levenson, Wallace, Fournier, Rucci, and Frank (2012)
\item
  Lewin, Peris, De Nadai, McCracken, and Piacentini (2012)
\item
  Liverant, Suvak, Pineles, and Resick (2012)
\item
  Manne, Kashy, Rubin, Hernandez, and Bergman (2012)
\item
  McManus, Surawy, Muse, Vazquez-Montes, and Williams (2012)
\item
  Meuret, Seidel, Rosenfield, Hofmann, and Rosenfield (2012)
\item
  Pistorello, Fruzzetti, MacLane, Gallop, and Iverson (2012)
\item
  Sheeber et al. (2012)
\item
  Sibley et al. (2012)
\item
  Siddique, Chung, Brown, and Miranda (2012)
\item
  Strunk, Cooper, Ryan, DeRubeis, and Hollon (2012)
\item
  Wolitzky-Taylor, Arch, Rosenfield, and Craske (2012)
\end{enumerate}

\subsubsection{2017}\label{section-3}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Andover, Schatten, Morris, Holman, and Miller (2017)
\item
  Baumann et al. (2017)
\item
  Bennebroek Evertsz' et al. (2017)
\item
  Bentley, Nock, Sauer-Zavala, Gorman, and Barlow (2017)
\item
  Berman et al. (2017)
\item
  Boswell, Cain, Oswald, McAleavey, and Adelman (2017)
\item
  Chambless et al. (2017)
\item
  Comer et al. (2017)
\item
  Cooper, Zoellner, Roy-Byrne, Mavissakalian, and Feeny (2017)
\item
  Crits-Christoph, Gallop, Diehl, Yin, and Gibbons (2017)
\item
  Driessen et al. (2017)
\item
  Felder et al. (2017)
\item
  Foa et al. (2017)
\item
  Hill, Oosterhoff, and Kaplow (2017)
\item
  Lau et al. (2017)
\item
  Leykin, Dunn, and Muñoz (2017)
\item
  MacDonald, McFarlane, Dionne, David, and Olmsted (2017)
\item
  Miller et al. (2017)
\item
  Muehlenkamp, Brausch, and Washburn (2017)
\item
  Owens, Zalecki, Gillette, and Hinshaw (2017)
\item
  Puspitasari et al. (2017)
\item
  Schacht, Brooner, King, Kidorf, and Peirce (2017)
\item
  Schmidt, Norr, Allan, Raines, and Capron (2017)
\item
  Stephens, Cantor, Goodwill, and Seto (2017)
\item
  Stice, Rohde, Shaw, and Gau (2017)
\end{enumerate}

\section{Cognitive}\label{cognitive}

\subsection{Cognitive Psychology}\label{cognitive-psychology}

\subsubsection{2012}\label{section-4}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Austerweil and Griffiths (2011)
\item
  Bonawitz, Schijndel, Friel, and Schulz (2012)
\item
  Cimpian and Erickson (2012)
\item
  Clifton and Frazier (2012)
\item
  Cohn, Paczynski, Jackendoff, Holcomb, and Kuperberg (2012)
\item
  Creel (2012)
\item
  Endress and Wood (2011)
\item
  Frank, Fedorenko, Lai, Saxe, and Gibson (2012)
\item
  Gennari, Mirković, and MacDonald (2012)
\item
  Goodwin and Johnson-Laird (2011)
\item
  Goschke and Bolte (2012)
\item
  Hay, Pelucchi, Estes, and Saffran (2011)
\item
  Kemp, Shafto, and Tenenbaum (2012)
\item
  Leslie and Gelman (2012)
\item
  Lombrozo and Rehder (2012)
\item
  Pachur and Olsson (2012)
\item
  Reingold, Reichle, Glaholt, and Sheridan (2012)
\item
  Rottman and Keil (2012)
\item
  Schneider and Anderson (2012)
\item
  Snedeker, Geren, and Shafto (2012)
\item
  Taylor and Ahn (2012)
\item
  Thompson, Prowse Turner, and Pennycook (2011)
\item
  Van den Broeck and Geudens (2012)
\item
  Vandierendonck, Demanet, Liefooghe, and Verbruggen (2012)
\item
  White, Ratcliff, and Starns (2011)
\end{enumerate}

\subsubsection{2017}\label{section-5}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Baker, Leslie, Gallistel, and Hood (2016)
\item
  Chang, Welbourne, and Lee (2016)
\item
  Chen, McNamara, Kelly, and Wolbers (2017)
\item
  Cheung, Rubenson, and Barner (2017)
\item
  Cohen and Quinlan (2016)
\item
  Coley, Arenson, Xu, and Tanner (2017)
\item
  Dasgupta, Schulz, and Gershman (2017)
\item
  Endress and Langus (2017)
\item
  Heck, Hilbig, and Moshagen (2017)
\item
  Herbort, Mathew, and Kunde (2017)
\item
  Khodadadi, Fakhari, and Busemeyer (2017)
\item
  Kılıç, Criss, Malmberg, and Shiffrin (2017)
\item
  MacDonald, Yurovsky, and Frank (2017)
\item
  Meder and Mayrhofer (2017)
\item
  Molouki and Bartels (2017)
\item
  Ojalehto, Medin, and García (2017)
\item
  Pachur, Suter, and Hertwig (2017)
\item
  Park and Casasola (2017)
\item
  Plonsky and Erev (2017)
\item
  Rieth and Huber (2017)
\item
  Samara, Smith, Brown, and Wonnacott (2017)
\item
  Sexton and Cooper (2017)
\item
  Tardiff, Bascandziev, Sandor, Carey, and Zaitchik (2017)
\item
  Tillman, Marghetis, Barner, and Srinivasan (2017)
\item
  Xu, Malt, and Srinivasan (2017)
\end{enumerate}

\subsection{Journal of Experimental Psychology: Learning, Memory, and
Cognition}\label{journal-of-experimental-psychology-learning-memory-and-cognition}

\subsubsection{2012}\label{section-6}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Atalay and Misirlisoy (2012)
\item
  Bell, Buchner, Kroneisen, and Giang (2012)
\item
  Bell, Röer, Dentale, and Buchner (2012)
\item
  Bodner and Taikh (2012)
\item
  Bonin, Roux, Barry, and Canell (2012)
\item
  Chuderski and Necka (2012)
\item
  Clapper (2012)
\item
  Coelho, Nusbaum, Rosenbaum, and Fenn (2012)
\item
  Farrell and Lelièvre (2012)
\item
  Huff, Coane, Hutchison, Grasser, and Blais (2012)
\item
  Hutchison et al. (2012)
\item
  Johnson, Staub, and Fleri (2012)
\item
  Miller and Roodenrys (2012)
\item
  Pansky (2012)
\item
  Perfect and Weber (2012)
\item
  Peterson and Mulligan (2012)
\item
  Potts and Shanks (2012)
\item
  Pratte and Rouder (2012)
\item
  Read and Scholten (2012)
\item
  Renkewitz and Jahn (2012)
\item
  Sutton, Twyman, Joanisse, and Newcombe (2012)
\item
  Unsworth, McMillan, Brewer, and Spillers (2012)
\item
  Witzel and Forster (2012)
\item
  Worthy, Otto, and Maddox (2012)
\item
  Yang, Staub, Li, Wang, and Rayner (2012)
\end{enumerate}

\subsubsection{2017}\label{section-7}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Bhatia (2017)
\item
  Boone and Hegarty (2017)
\item
  Bosker (2017)
\item
  Busler and Lazarte (2017)
\item
  Davies, Arnell, Birchenough, Grimmond, and Houlson (2017)
\item
  De Freitas, DeScioli, Nemirow, Massenkoff, and Pinker (2017)
\item
  Faber and Gennari (2017)
\item
  Flores, Bailey, Eisenberg, and Zacks (2017)
\item
  Hintz, Meyer, and Huettig (2017)
\item
  Kenett, Levi, Anaki, and Faust (2017)
\item
  Khateb, Shamshoum, and Prior (2017)
\item
  Kowalski and Huang (2017)
\item
  Ostarek and Huettig (2017)
\item
  Peterson and Naveh-benjamin (2017)
\item
  Pierce, Gallo, and McCain (2017)
\item
  Rajsic, Swan, Wilson, and Pratt (2017)
\item
  Rummel, Smeekens, and Kane (2017)
\item
  Selmeczy and Dobbins (2017)
\item
  Silva, Inácio, Folia, and Petersson (2017)
\item
  Whiffen and Karpicke (2017)
\item
  Wiese, Komes, Tüttenberg, Leidinger, and Schweinberger (2017)
\item
  Wu, Meder, Filimon, and Nelson (2017)
\item
  Yamaguchi and Logan (2016)
\item
  Yang, Potts, and Shanks (2017)
\item
  Zhao and B?lthoff (2017)
\end{enumerate}

\section{Counseling}\label{counseling}

\subsection{Journal of Counseling
Psychology}\label{journal-of-counseling-psychology}

\subsubsection{2012}\label{section-8}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Anders, Frazier, and Shallcross (2012)
\item
  Bailey, Chung, Williams, Singh, and Terrell (2011)
\item
  Boswell, McAleavey, Castonguay, Hayes, and Locke (2012)
\item
  Cheng, Kwan, and Sevig (2013)
\item
  Cragun and Friedlander (2012)
\item
  Cramer, Miller, Amacker, and Burks (2013)
\item
  Peña, Friedlander, Escudero, and Heatherington (2012)
\item
  Duffy, Bott, Allan, and Torrey (2013)
\item
  Duffy, Allan, Autin, and Bott (2013)
\item
  Hammer and Vogel (2013)
\item
  Laska, Smith, Wislocki, Minami, and Wampold (2013)
\item
  Lin and Israel (2012)
\item
  Marmarosh and Kivlighan (2012)
\item
  McDermott and Lopez (2013)
\item
  Mercer, Zeigler-Hill, Wallace, and Hayes (2011)
\item
  Mohr, Selterman, and Fassinger (2013)
\item
  Nadal (2011)
\item
  Poteat, Mereish, DiGiovanni, and Koenig (2011)
\item
  Salahuddin and O'Brien (2011)
\item
  Sherry, Mackinnon, Macneil, and Fitzpatrick (2013)
\item
  Tylka and Kroon Van Diest (2013)
\item
  Velez and Moradi (2012)
\item
  Wang et al. (2012)
\item
  Wei, Tsai, Chao, Du, and Lin (2012)
\item
  Wong and Mak (2013)
\end{enumerate}

\subsubsection{2017}\label{section-9}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Altenstein-Yamanaka, Zimmermann, Krieger, Dörig, and \{grosse
  Holtforth\} (2017)
\item
  Arczynski and Morrow (2017)
\item
  Bernard, Lige, Willis, Sosoo, and Neblett (2017)
\item
  Budge, Chin, and Minero (2017)
\item
  Carrera and Wei (2017)
\item
  Cheng, Tran, Miyake, and Kim (2017)
\item
  Cobb, Meca, Xie, Schwartz, and Moise (2017)
\item
  Cokley et al. (2017)
\item
  Cornish, Lannin, Wade, and Martinez (2017)
\item
  Dorociak, Rupert, Bryant, and Zahniser (2017)
\item
  Douglass, Conlin, Duffy, and Allan (2017)
\item
  Duffy et al. (2017)
\item
  Garcia, Acosta, Pirani, Edwards, and Osman (2017)
\item
  Garriott, Raque-Bogdan, Yalango, Ziemer, and Utley (2017)
\item
  Hu, Creed, and Hood (2017)
\item
  Kahn, Wei, Su, Han, and Strojewska (2017)
\item
  Katz-Wise et al. (2017)
\item
  Keum and Miller (2017)
\item
  Kivlighan, Kline, Gelso, and Hill (2017)
\item
  Lannin, Vogel, and Heath (2017)
\item
  McClintock, Perlman, McCarrick, Anderson, and Himawan (2017)
\item
  Okun, Chang, Kanhai, Dunn, and Easley (2017)
\item
  Rappaport, Moskowitz, and D'Antono (2017)
\item
  Xiao et al. (2017)
\item
  Xu and Tracey (2017)
\end{enumerate}

\subsection{The Counseling
Psychologist}\label{the-counseling-psychologist}

\subsubsection{2012}\label{section-10}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Baskin, Wampold, Quintana, and Enright (2010)
\item
  Baskin, Rhody, Schoolmeesters, and Ellingson (2011)
\item
  Carr and Szymanski (2011)
\item
  Chavez-Korell and Vandiver (2012)
\item
  Duffy, Diemer, and Jadidian (2012)
\item
  Gati, Asulin-Peretz, and Fisher (2012)
\item
  Kaplan, Vogel, Gentile, and Wade (2012)
\item
  Klinger, Ladany, and Kulp (2012)
\item
  Latta and Goodman (2011)
\item
  Lee and Park (2011)
\item
  Owen, Tao, and Rodolfa (2010)
\item
  Perry and Calhoun-Butts (2012)
\item
  Pruitt, Johnson, Catlin, and Knox (2010)
\item
  Rice, Choi, Zhang, Morero, and Anderson (2012)
\item
  Seo (2010)
\item
  Shen-Miller, Forrest, and Burt (2012)
\item
  Smith, Vogel, Madon, and Edwards (2011)
\item
  Smith et al. (2012b)
\item
  Szymanski and Sung (2010)
\item
  Szymanski and Obiri (2011)
\item
  Thompson and Subich (2011)
\item
  Todd and Abrams (2011)
\item
  Valdez, Dvorscek, Budge, and Esmond (2011)
\item
  Vogel, Shechtman, and Wade (2010)
\item
  Wu and Mak (2012)
\end{enumerate}

\subsubsection{2017}\label{section-11}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Allan, Duffy, and Blustein (2016)
\item
  Budge, Thai, Tebbe, and Howard (2016)
\item
  Cheng, Hitter, Adams, and Williams (2016)
\item
  Conover, Israel, and Nylund-Gibson (2017)
\item
  Drob, Tasso, and Griffo (2016)
\item
  Frankfurt, Frazier, Syed, and Jung (2016)
\item
  Gattamorta, McCabe, Mena, and Santisteban (2016)
\item
  Goldberg, Sweeney, Black, and Moyer (2016)
\item
  Heath, Vogel, and Al-Darmaki (2016)
\item
  Hermannsdóttir and Ægisdóttir (2016)
\item
  Lefevor, Janis, and Park (2017)
\item
  Liao, Hong, and Rounds (2016)
\item
  Liao, Spanierman, Harlow, and Neville (2017)
\item
  Liu, Wong, and Tsai (2016)
\item
  McDermott et al. (2017)
\item
  Santos, Goldstein, and Tracey (2017)
\item
  Shea, Wong, Nguyen, and Baghdasarian (2017)
\item
  Shin, Smith, Welch, and Ezeofor (2016)
\item
  Silva, Dillon, Verdejo, Sanchez, and De La Rosa (2017)
\item
  Szymanski, Mikorski, and Carretta (2017)
\item
  Tuliao, Velasquez, Bello, and Pinson (2016)
\item
  VanDaalen and Santos (2017)
\item
  Velez and Moradi (2016)
\item
  Vogel et al. (2017)
\item
  Watson, Velez, Brownfield, and Flores (2016)
\end{enumerate}

\section{Developmental}\label{developmental}

\subsection{Journal of Experimental Child
Psychology}\label{journal-of-experimental-child-psychology}

\subsubsection{2012}\label{section-12}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Bailey, Hoard, Nugent, and Geary (2012)
\item
  Bauer et al. (2012)
\item
  Benenson, Quinn, and Stella (2012)
\item
  Boulton (2012)
\item
  Creel and Jimenez (2012)
\item
  DeCaro and Rittle-Johnson (2012)
\item
  Fu, Evans, Xu, and Lee (2012)
\item
  Geary, Hoard, and Nugent (2012)
\item
  Gurland, Grolnick, and Friendly (2012)
\item
  Hallett, Nunes, Bryant, and Thorpe (2012)
\item
  Joh and Spivey (2012)
\item
  Kirkham, Richardson, Wu, and Johnson (2012)
\item
  Kuwabara and Smith (2012)
\item
  Macchi Cassia, Pisacane, and Gava (2012)
\item
  Mann, Moeller, Pixner, Kaufmann, and Nuerk (2012)
\item
  Morita et al. (2012)
\item
  Neuenschwander, Röthlisberger, Cimeli, and Roebers (2012)
\item
  Poarch and Hell (2012)
\item
  Principe, Cherson, DiPuppo, and Schindewolf (2012)
\item
  Rat-Fischer, O'Regan, and Fagard (2012)
\item
  Sigelman (2012)
\item
  Takahashi (2012)
\item
  Valentin and Chanquoy (2012)
\item
  Von Holzen and Mani (2012)
\item
  Zosh and Feigenson (2012)
\end{enumerate}

\subsubsection{2017}\label{section-13}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Altani et al. (2017)
\item
  Atkinson, Slade, Powell, and Levy (2017)
\item
  Austin and Sweller (2017)
\item
  Blakely-McClure and Ostrov (2018)
\item
  Buckler, Oczak-Arsic, Siddiqui, and Johnson (2017)
\item
  Cottini, Basso, and Palladino (2018)
\item
  DeJesus, Hwang, Dautel, and Kinzler (2017)
\item
  Doebel, Dickerson, Hoover, and Munakata (2018)
\item
  Friend, DeAnda, Arias-Trejo, Poulin-Dubois, and Zesiger (2017)
\item
  Göbel, McCrink, Fischer, and Shaki (2018)
\item
  Hakvoort, Boer, Leenaars, Bos, and Tijms (2017)
\item
  Hasni, Adamson, Williamson, and Robins (2017)
\item
  Kim, Shimomaeda, Giuliano, and Skowron (2017)
\item
  Lipowski, Ariel, Tauber, and Dunlosky (2017)
\item
  Liu and Kager (2017)
\item
  Liu, Su, Xu, and Pei (2018)
\item
  Michaelides and Avraamides (2017)
\item
  Needham, Wiesen, Hejazi, Libertus, and Christopher (2017)
\item
  Russo, Kates, and Wyble (2017)
\item
  Schmidt, Gonzalez-Cabrera, and Tomasello (2017)
\item
  Simms, Frausel, and Richland (2018)
\item
  Van de Vondervoort and Hamlin (2017)
\item
  Westley, Kohút, and Rueschemeyer (2017)
\item
  White, Alexander, and Greenfield (2017)
\item
  Wong (2017)
\end{enumerate}

\subsection{Journal of Youth and
Adolescence}\label{journal-of-youth-and-adolescence}

\subsubsection{2012}\label{section-14}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Al-Yagon (2012)
\item
  Bastaits, Ponnet, and Mortelmans (2012)
\item
  Bissell-Havran, Loken, and McHale (2012)
\item
  Boman, Krohn, Gibson, and Stogner (2012)
\item
  Caughy et al. (2012)
\item
  Chen, Balan, and Price (2012)
\item
  Chien and East (2012)
\item
  Chiu, Pong, Mori, and Chow (2012)
\item
  Estrada-Martínez, Caldwell, Bauermeister, and Zimmerman (2012)
\item
  Kiesner and Poulin (2012)
\item
  Kim-Spoon, Longo, and McCullough (2012)
\item
  Koning, Eijnden, Verdurmen, Engels, and Vollebergh (2012)
\item
  Lam, Solmeyer, and McHale (2012)
\item
  Larsen et al. (2012)
\item
  Leversen, Danielsen, Birkeland, and Samdal (2012)
\item
  López-Romero, Romero, and Luengo (2012)
\item
  Malmberg et al. (2012)
\item
  Maynard, Salas-Wright, Vaughn, and Peters (2012)
\item
  Nichols and Loper (2012)
\item
  Pisani et al. (2012)
\item
  Poulin and Denault (2012)
\item
  Salas-Wright, Vaughn, Hodge, and Perron (2012)
\item
  Stein, Gonzalez, and Huq (2012)
\item
  Wang, Chan, and Lin (2012)
\item
  Wickrama, Simons, and Baltimore (2012)
\end{enumerate}

\subsubsection{2017}\label{section-15}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Amemiya and Wang (2017)
\item
  Andrews, Hanish, and Santos (2017)
\item
  Bhargava, Bámaca-Colbert, Witherspoon, Pomerantz, and Robins (2017)
\item
  Bonache, Gonzalez-Mendez, and Krahé (2017)
\item
  Burke, Sticca, and Perren (2017)
\item
  Gommans, Müller, Stevens, Cillessen, and Ter Bogt (2017)
\item
  Hadiwijaya, Klimstra, Vermunt, Branje, and Meeus (2017)
\item
  Ja and Jose (2017)
\item
  Jensen, Chassin, and Gonzales (2017)
\item
  Kleemans, Schlindwein, and Dohmen (2017)
\item
  Luyckx, Duriez, Green, and Negru-Subtirica (2017)
\item
  Meisel and Colder (2017)
\item
  Meldrum and Barnes (2017)
\item
  Mundt, Antonaccio, French, and Zakletskaia (2017)
\item
  Nieuwenhuis et al. (2017)
\item
  Obsuth et al. (2017)
\item
  Racz, Putnick, Suwalsky, Hendricks, and Bornstein (2017)
\item
  Reyes, Foshee, Chen, and Ennett (2017)
\item
  Sentse, Kretschmer, Haan, and Prinzie (2017)
\item
  Shulman, Seiffge-Krenke, and Walsh (2017)
\item
  Silva, Patrianakos, Chein, and Steinberg (2017)
\item
  Slater, Halliwell, Jarman, and Gaskin (2017)
\item
  Wang, Chow, and Amemiya (2017)
\item
  Zapolski, Fisher, Banks, Hensel, and Barnes-Najor (2017)
\item
  Zimmerman and Kushner (2017)
\end{enumerate}

\section{Educational}\label{educational}

\subsection{Contemporary Educational
Psychology}\label{contemporary-educational-psychology}

\subsubsection{2012}\label{section-16}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Bernacki, Byrnes, and Cromley (2012)
\item
  Bol, Hacker, Walck, and Nunnery (2012)
\item
  Booth and Newton (2012)
\item
  Carr, Taasoobshirazi, Stroud, and Royer (2011)
\item
  Dumont et al. (2012)
\item
  Elmore and Oyserman (2012)
\item
  Faircloth (2012)
\item
  Germeijs, Luyckx, Notelaers, Goossens, and Verschueren (2012)
\item
  Gniewosz and Noack (2012)
\item
  Greene, Hutchison, Costa, and Crompton (2012)
\item
  Job and Klassen (2012)
\item
  Kauffman, Zhao, and Yang (2011)
\item
  Kercood, Zentall, Vinh, and Tom-Wright (2012)
\item
  Lerkkanen et al. (2012)
\item
  Madjar, Kaplan, and Weinstock (2011)
\item
  Martin (2012)
\item
  PytlikZillig et al. (2011)
\item
  Reeve and Tseng (2011)
\item
  Reznitskaya et al. (2012)
\item
  Rich and Schachter (2012)
\item
  Schwinger and Wild (2012)
\item
  Sinai, Kaplan, and Flum (2012)
\item
  Stupnisky, Perry, Hall, and Guay (2012)
\item
  Thoman, Sansone, Fraughton, and Pasupathi (2012)
\item
  Yeager, Bundick, and Johnson (2012)
\end{enumerate}

\subsubsection{2017}\label{section-17}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Baker et al. (2017)
\item
  Barzilai (2017)
\item
  Boehme, Goetz, and Preckel (2017)
\item
  Chan, Au, Lau, and Tang (2017)
\item
  Ching (2017)
\item
  Gilbert and Fuchs (2017)
\item
  Ho et al. (2017)
\item
  Korpipää et al. (2017)
\item
  Kostons and Koning (2017)
\item
  Lewis and Farkas (2017)
\item
  Litalien et al. (2017)
\item
  Litalien, Morin, and McInerney (2017)
\item
  Lösch et al. (2017)
\item
  Murphy et al. (2017)
\item
  Parong et al. (2017)
\item
  Paulick, Großschedl, Harms, and Möller (2017)
\item
  Riggs, Alibali, and Kalish (2017)
\item
  Robinson et al. (2017)
\item
  Ruiz-Alfonso and León (2017)
\item
  Rutherford, Long, and Farkas (2017)
\item
  Schnotz, Wagner, Ullrich, Horz, and McElvany (2017)
\item
  Silinskas, Pakarinen, Lerkkanen, Poikkeus, and Nurmi (2017)
\item
  Voss, Wagner, Klusmann, Trautwein, and Kunter (2017)
\item
  Warburton (2017)
\item
  Zee, Jong, and Koomen (2017)
\end{enumerate}

\subsection{Journal of Educational
Psychology}\label{journal-of-educational-psychology}

\subsubsection{2012}\label{section-18}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Arya and Maul (2012)
\item
  Bugg and McDaniel (2012)
\item
  Casillas et al. (2012)
\item
  Collie, Shapka, and Perry (2012)
\item
  Darwich, Hymel, and Waterhouse (2012)
\item
  De Naeghel, Van Keer, Vansteenkiste, and Rosseel (2012)
\item
  Engel de Abreu and Gathercole (2012)
\item
  Fiorella and Mayer (2012)
\item
  Hannon and Frias (2012)
\item
  Harber et al. (2012)
\item
  Hughes, Wu, Kwok, Villarreal, and Johnson (2012)
\item
  Jang, Kim, and Reeve (2012)
\item
  Li, McBride-Chang, Wong, and Shu (2012)
\item
  McNeil et al. (2012)
\item
  Papadopoulos, Kendeou, and Spanoudis (2012)
\item
  Piasta, Petscher, and Justice (2012)
\item
  Poteat, O'Dwyer, and Mereish (2012)
\item
  Ryan and Shim (2012)
\item
  Spinath and Steinmayr (2012)
\item
  Swanson, Orosco, and Lussier (2012)
\item
  Tolar et al. (2012)
\item
  Vadasy and Sanders (2012)
\item
  Kooy-Hofland, Kooy, Bus, IJzendoorn, and Bonsel (2012)
\item
  Vitaro, Boivin, Brendgen, Girard, and Dionne (2012)
\item
  Zhou, Lam, and Chan (2012)
\end{enumerate}

\subsubsection{2017}\label{section-19}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Arens et al. (2017)
\item
  Bailey, Hansen, and Jordan (2017)
\item
  Bottiani, Bradshaw, and Mendelson (2017)
\item
  Brandenburg et al. (2017)
\item
  Ching and Nunes (2017)
\item
  Cooc and Kim (2017)
\item
  Dumont, Protsch, Jansen, and Becker (2017)
\item
  Fiorella, Gog, Hoogerheide, and Mayer (2017)
\item
  Fishman and Husman (2017)
\item
  Geary, Nicholas, Li, and Sun (2017)
\item
  Goodrich and Lonigan (2017)
\item
  Hendrickx, Mainhard, Oudman, Boor-Klip, and Brekelmans (2017)
\item
  Hurst and Cordes (2017)
\item
  Kaiser, Südkamp, and Möller (2017)
\item
  Ladd, Ettekal, and Kochenderfer-Ladd (2017)
\item
  Language and Reading Research Consortium and Logan (2017)
\item
  Liu and Georgiou (2017)
\item
  Muenks, Wigfield, Yang, and O'Neal (2017)
\item
  Ramirez, McDonough, and Jin (2017)
\item
  Retnowati, Ayres, and Sweller (2017)
\item
  Schenke, Nguyen, Watts, Sarama, and Clements (2017)
\item
  Sticca, Goetz, Nett, Hubbard, and Haag (2017)
\item
  Vollet, Kindermann, and Skinner (2017)
\item
  Wijekumar, Meyer, and Lei (2017)
\item
  Wong and Ho (2017)
\end{enumerate}

\section{Environmental}\label{environmental}

\subsection{Environment and Behavior}\label{environment-and-behavior}

\subsubsection{2012}\label{section-20}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Asah, Bengston, and Westphal (2012)
\item
  Berry, Fournier, and Porter (2012)
\item
  Boarnet, Forsyth, Day, and Oakes (2011)
\item
  Botetzagias and Schuur (2012)
\item
  Bourque, Mileti, Kano, and Wood (2012)
\item
  Bramston, Pretty, and Zammit (2011)
\item
  Breetzke and Cohn (2012)
\item
  Caperello and Kurani (2012)
\item
  Cleland, Ball, King, and Crawford (2012)
\item
  Costa (2012)
\item
  Dazkir and Read (2012)
\item
  Montigny, Ling, and Zacharias (2012)
\item
  Dills, Rutt, and Mumford (2012)
\item
  Fritsche and Häfner (2012)
\item
  Hovardas and Korfiatis (2012)
\item
  Johnson and Scicchitano (2012)
\item
  Larco, Steiner, Stockard, and West (2012)
\item
  Long and Baran (2012)
\item
  Lu and Zimring (2012)
\item
  Misra and Stokols (2012)
\item
  Staiano, Baker, and Calvert (2012)
\item
  Sugiyama, Okely, Masters, and Moore (2012)
\item
  Ullán et al. (2012)
\item
  {\{}van Rompay\}, Tanja-Dijkstra, Verhoeven, \& \{van Es\} (2012)
\item
  Wilkerson, Carlson, Yen, and Michael (2012)
\end{enumerate}

\subsubsection{2017}\label{section-21}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Anderson, Ruggeri, Steemers, and Huppert (2017)
\item
  Appel-Meulenbroek, Vries, and Weggeman (2017)
\item
  Barrett, Davies, Zhang, and Barrett (2017)
\item
  Benjamin, Por, and Budescu (2017)
\item
  Byrka, Kaiser, and Olko (2017)
\item
  Crawford, Holder, and O'Connor (2017)
\item
  Davis, Ohman, and Weisbeck (2017)
\item
  Ecklund, Scheitle, Peifer, and Bolger (2017)
\item
  García-Mira et al. (2017)
\item
  Kabo (2017)
\item
  Kanakri, Shepley, Tassinary, Varni, and Fawaz (2017)
\item
  Klatte et al. (2017)
\item
  Lymeus, Lundgren, and Hartig (2017)
\item
  Rollings and Wells (2017)
\item
  Sachdeva (2017)
\item
  Scannell and Gifford (2017)
\item
  Seebauer, Fleiß, and Schweighart (2017)
\item
  Smalls, Gregory, Zoller, and Egede (2017)
\item
  Smith, Kinnafick, Cooley, and Sandal (2017)
\item
  Switzer and Vedlitz (2017)
\item
  Tifferet and Vilnai-Yavetz (2017)
\item
  Vaid and Evans (2017)
\item
  Berg, Wesselius, Maas, and Tanja-Dijkstra (2017)
\item
  Watkins, Mincey, Vogt, and Sweeney (2017)
\item
  Wyles, Pahl, Holland, and Thompson (2017)
\end{enumerate}

\subsection{Journal of Environmental
Psychology}\label{journal-of-environmental-psychology}

\subsubsection{2012}\label{section-22}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Alkhresheh (2012)
\item
  Belojevic, Evans, Paunovic, and Jakovljevic (2012)
\item
  Brunyé et al. (2012)
\item
  Francis, Giles-Corti, Wood, and Knuiman (2012)
\item
  Guéguen (2012)
\item
  Haans and Kort (2012)
\item
  Honold, Beyer, Lakes, and Meer (2012)
\item
  Hund, Schmettow, and Noordzij (2012)
\item
  Mahdjoubi and Akplotsyi (2012)
\item
  Matthies, Selge, and Kl??ckner (2012)
\item
  Milfont and Sibley (2012)
\item
  Monti et al. (2012)
\item
  Mourshed and Zhao (2012)
\item
  Murtagh, Gatersleben, and Uzzell (2012)
\item
  Ojala (2012)
\item
  Oshio and Urakawa (2012)
\item
  Richetin et al. (2012)
\item
  Smith et al. (2012a)
\item
  Tobler, Visschers, and Siegrist (2012)
\item
  Toet and Schaik (2012)
\item
  Truelove and Parks (2012)
\item
  Venables, Pidgeon, Parkhill, Henwood, and Simmons (2012)
\item
  Wells and Baldwin (2012)
\item
  Werner, Cook, Colby, and Lim (2012)
\item
  Wynveen, Kyle, and Sutton (2012)
\end{enumerate}

\subsubsection{2017}\label{section-23}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Andrade, Devlin, Pereira, and Lima (2017)
\item
  Carfora, Caso, Sparks, and Conner (2017)
\item
  Casado, Hidalgo, and García-Leiva (2017)
\item
  Collado, Evans, and Sorrel (2017)
\item
  Davydenko and Peetz (2017)
\item
  Ernst and Briegel (2017)
\item
  Grønhøj and Thøgersen (2017)
\item
  Hahn and Garrett (2017)
\item
  Jansen, Hoekstra, and Boumeester (2017)
\item
  Janssen and Baggio (2016)
\item
  Junot, Paquet, and Martin-Krumm (2017)
\item
  Kangur, Jager, Verbrugge, and Bockarjova (2017)
\item
  Klein, Hilbig, and Heck (2017)
\item
  Leygue, Ferguson, and Spence (2017)
\item
  Meleady and Crisp (2017)
\item
  Nordfjærn and Zavareh (2017)
\item
  Paundra, Rook, Dalen, and Ketter (2017)
\item
  Perez-Lopez, Aragonés, and Amérigo (2017)
\item
  Ro, Brauer, Kuntz, Shukla, and Bensch (2017)
\item
  Sporrel, Caljouw, and Withagen (2017)
\item
  Stefanelli and Seidl (2017)
\item
  Ulset, Vitaro, Brendgen, Bekkhus, and Borge (2017)
\item
  Broek, Bolderdijk, and Steg (2017)
\item
  Zerella, Treuer, and Albrecht (2017)
\item
  Zijlstra, Hagedoorn, Krijnen, Schans, and Mobach (2017)
\end{enumerate}

\section{Forensics}\label{forensics}

\subsection{Law and Human Behavior}\label{law-and-human-behavior}

\subsubsection{2012}\label{section-24}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Block et al. (2012)
\item
  Boccaccini, Turner, Murrie, and Rufino (2012)
\item
  Callahan, Steadman, Tillman, and Vesselinov (2013)
\item
  Dysart, Lawson, and Rainey (2012)
\item
  Eastwood and Snook (2012)
\item
  Eno Louden and Skeem (2013)
\item
  Gromet, Okimoto, Wenzel, and Darley (2012)
\item
  Kennealy, Skeem, Manchak, and Eno Louden (2012)
\item
  Levenson, Sandler, and Freeman (2012)
\item
  Madon, Yang, Smalarz, Guyll, and Scherr (2013)
\item
  Mansour et al. (2012)
\item
  Olver, Stockdale, and Wong (2012)
\item
  Palmer, Brewer, and Weber (2012)
\item
  Peters, Lampinen, and Malesky (2013)
\item
  Pezdek, O'Brien, and Wasson (2012)
\item
  Quinlivan, Neuschatz, Douglass, Wells, and Wetmore (2012)
\item
  Reidy, Sorensen, and Cunningham (2012)
\item
  Sauerland, Sagana, and Sporer (2012)
\item
  Scurich, Monahan, and John (2012)
\item
  Seto, Wood, Babchishin, and Flynn (2012)
\item
  Brinke and Porter (2012)
\item
  Thomas, Loughran, and Piquero (2013)
\item
  Knaap, Alberda, Oosterveld, and Born (2012)
\item
  Walters (2012a)
\item
  Walters (2012b)
\end{enumerate}

\subsubsection{2017}\label{section-25}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Cash and Lane (2017)
\item
  Dargis and Koenigs (2017)
\item
  Dawson, Hartwig, Brimbal, and Denisenkov (2017)
\item
  Fine et al. (2017a)
\item
  Fine and Rooij (2017)
\item
  Hein et al. (2017)
\item
  Holland and Cortina (2017)
\item
  Kassin, Kukucka, Lawson, and DeCarlo (2017)
\item
  King et al. (2017)
\item
  Kois, Wellbeloved-Stone, Chauhan, and Warren (2017)
\item
  Kubiak et al. (2017b)
\item
  Lavis and Brewer (2017)
\item
  Madon et al. (2017)
\item
  Nijdam-Jones, Rivera, Rosenfeld, and Arango-Lasprilla (2017)
\item
  Rosenfeld et al. (2017)
\item
  Ruva and Guenther (2017)
\item
  Sauer, Palmer, and Brewer (2017)
\item
  Schreiber Compo et al. (2017)
\item
  Seto and Eke (2017)
\item
  Silver and Silver (2017)
\item
  Stolzenberg, McWilliams, and Lyon (2017)
\item
  Sweet, Meissner, and Atkinson (2017)
\item
  Viljoen, Shaffer, Gray, and Douglas (2017)
\item
  Williams and Stansfield (2017)
\item
  Zebel, Schreurs, and Ufkes (2017)
\end{enumerate}

\subsection{Psychology, Public Policy, and
Law}\label{psychology-public-policy-and-law}

\subsubsection{2012}\label{section-26}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Aharoni and Fridlund (2012)
\item
  Ballard, Holtzworth-Munroe, Applegate, and Beck (2011)
\item
  Batastini, Hunt, Present-Koller, and DeMatteo (2011)
\item
  Bornstein, Tomkins, Neeley, Herian, and Hamm (2013)
\item
  Brank, Greene, and Hochevar (2011)
\item
  Braver, Ellman, Votruba, and Fabricius (2011)
\item
  Brubacher, Roberts, and Powell (2011)
\item
  Elliott, Thomas, and Ogloff (2011)
\item
  Haegerich, Salerno, and Bottoms (2013)
\item
  Hildebrand, Hol, and Bosker (2013)
\item
  Lee, Li, Lamade, Schuler, and Prentky (2012)
\item
  Lussier and Davies (2011)
\item
  McLawsen, Scalora, and Darrow (2012)
\item
  Mokros, Stadtland, Osterheider, and Nedopil (2010)
\item
  Nysse-Carris, Bottoms, and Salerno (2011)
\item
  Pickel, Warner, Miller, and Barnes (2013)
\item
  Piquero et al. (2012)
\item
  Redlich, Kulish, and Steadman (2011)
\item
  Redlich and Summers (2012)
\item
  Schweitzer et al. (2011)
\item
  Towfigh and Glöckner (2011)
\item
  Vincent, Paiva-Salisbury, Cook, Guy, and Perrault (2012)
\item
  Vrij, Mann, Jundi, Hope, and Leal (2012)
\item
  Watson and Angell (2013)
\item
  Wiener, Bennett, Cheloha, and Nicholson (2012)
\end{enumerate}

\subsubsection{2017}\label{section-27}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Alvarez and Miller (2016)
\item
  Cantone and Wiener (2017)
\item
  Cavanagh and Cauffman (2017)
\item
  Davidson and Beck (2017)
\item
  Dopp, Borduin, Willroth, and Sorg (2017)
\item
  Eisen, Smith, Olaguez, and Skerritt-Perta (2017)
\item
  Evans, Stolzenberg, and Lyon (2017)
\item
  Evans, Pimentel, Pena, and Michael (2017)
\item
  Fabricius and Suh (2017)
\item
  Fine et al. (2017b)
\item
  Gongola, Krauss, and Scurich (2017)
\item
  Helm and Reyna (2017)
\item
  Helmus and Ternes (2017)
\item
  Humphreys et al. (2017)
\item
  Jaeger, Levin, and Porter (2017)
\item
  Koehler, Schweitzer, Saks, and McQuiston (2016)
\item
  Kubiak et al. (2017a)
\item
  London, Hall, and Lytle (2017)
\item
  Nahari (2017)
\item
  Salerno (2017)
\item
  Schmittat and Englich (2016)
\item
  Socia and Harris (2016)
\item
  Szojka, Andrews, Lamb, Stolzenberg, and Lyon (2017)
\item
  Wachi et al. (2017)
\item
  Zottoli, Daftary-Kapur, Winters, and Hogan (2016)
\end{enumerate}

\section{Industrial-Organizational}\label{industrial-organizational}

\subsection{Organizational Behavior and Human Decision
Processes}\label{organizational-behavior-and-human-decision-processes}

\subsubsection{2012}\label{section-28}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Beck and Schmidt (2012)
\item
  Bilgin (2012)
\item
  Chua, Morris, and Mor (2012)
\item
  Conlon, Tinsley, Birk, Humphrey, and Ellis (2012)
\item
  Dane, Rockmann, and Pratt (2012)
\item
  Fishbach and Choi (2012)
\item
  Gino and Galinsky (2012)
\item
  Hannah, Avolio, Walumbwa, and Chan (2012)
\item
  Hsee, Shen, Zhang, Chen, and Zhang (2012)
\item
  Kraus, Ahearne, Lam, and Wieseke (2012)
\item
  Miles and Clenney (2012)
\item
  Milkman (2012)
\item
  Molinsky, Grant, and Margolis (2012)
\item
  Polman (2012)
\item
  Polman and Russo (2012)
\item
  Rolison, Evans, Dennis, and Walsh (2012)
\item
  Sluss and Thompson (2012)
\item
  Spranger, Colarelli, Dimotakis, Jacob, and Arvey (2012)
\item
  Staats, Milkman, and Fox (2012)
\item
  Unkelbach, Ostheimer, Fasold, and Memmert (2012)
\item
  Van Ittersum and Pennings (2012)
\item
  Wang, Northcraft, and Van Kleef (2012)
\item
  Welsh and Navarro (2012)
\item
  Whitman and Woodward (2012)
\item
  Young, Goodie, Hall, and Wu (2012)
\end{enumerate}

\subsubsection{2017}\label{section-29}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Basu and Savani (2017)
\item
  Chang, Chow, and Woolley (2017)
\item
  Chartier and Abele (2017)
\item
  Daniels, Neale, and Greer (2017)
\item
  Guarana and Barnes (2017)
\item
  Hershcovis et al. (2017)
\item
  Huang, Jin, and Zhang (2017)
\item
  Humphrey, Aime, Cushenbery, Hill, and Fairchild (2017)
\item
  Johnson et al. (2017b)
\item
  Kennedy and Anderson (2017)
\item
  Kim and Zhong (2017)
\item
  Lee and Ames (2017)
\item
  Lount, Pettit, and Doyle (2017)
\item
  Lu, Akinola, and Mason (2017)
\item
  Luan and Reb (2017)
\item
  Ma and Kay (2017)
\item
  Martin and Phillips (2017)
\item
  McCarthy et al. (2017)
\item
  Newark, Bohns, and Flynn (2017)
\item
  Park, Kim, and Sung (2017)
\item
  Rodell, Colquitt, and Baer (2017)
\item
  Sitzmann and Bell (2017)
\item
  Tang, Morewedge, Larrick, and Klein (2017)
\item
  Wiltermuth, Vincent, and Gino (2017)
\item
  Zingoni and Byron (2017)
\end{enumerate}

\subsection{Personnel Psychology}\label{personnel-psychology}

\subsubsection{2012}\label{section-30}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Avery, McKay, Tonidandel, Volpone, and Morris (2012)
\item
  Barnes, Wagner, and Ghumman (2012)
\item
  Carlson, Ferguson, Perrewé, and Whitten (2011)
\item
  Cucina, Caputo, Thibodeaux, and Maclane (2012)
\item
  Dierdorff and Ellington (2012)
\item
  Dobrow and Tosti-Kharas (2011)
\item
  Dragoni, Oh, Vankatwyk, and Tesluk (2011)
\item
  Griepentrog, Harold, Holtz, Klimoski, and Marsh (2012)
\item
  Hirschfeld and Thomas (2011)
\item
  Hoffman et al. (2012)
\item
  Huo, Lam, and Chen (2012)
\item
  Levashina, Morgeson, and Campoin (2012)
\item
  Mackenzie, Podsakoff, and Podsakoff (2011)
\item
  Mawritz, Mayer, Hoobler, Wayne, and Marinova (2012)
\item
  Moore, Detert, Klebe Treviño, Baker, and Mayer (2012)
\item
  O'Boyle and Aguinis (2012)
\item
  Oreg and Berson (2011)
\item
  Peterson, Galvin, and Lange (2012)
\item
  Ragins, Gonzalez, Ehrhardt, and Singh (2012)
\item
  Seo et al. (2012)
\item
  Sonnentag and Grant (2012)
\item
  Sumanth and Cable (2011)
\item
  Takeuchi, Chen, and Cheung (2012)
\item
  Tangirala and Ramanujam (2012)
\item
  Zhang, Waldman, and Wang (2012)
\end{enumerate}

\subsubsection{2017}\label{section-31}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Chao, Takeuchi, and Farh (2017)
\item
  Dahling, Taylor, Chau, and Dwight (2016)
\item
  Deng, Wu, Leung, and Guan (2016)
\item
  Deng, Walter, Lam, and Zhao (2017)
\item
  Dumas and Stanko (2017)
\item
  Fang, McAllister, and Duffy (2017)
\item
  Gonzalez-Mulé and Cockburn (2017)
\item
  Huang, Ford, and Ryan (2017)
\item
  Jansen, Shipp, and Michael (2016)
\item
  Kauppila (2016)
\item
  Mandeville, Halbesleben, and Whitman (2016)
\item
  Marcus, Weigelt, Hergert, Gurt, and Gelléri (2017)
\item
  Methot, Lepine, Podsakoff, and Christian (2016)
\item
  Ng (2016)
\item
  Pohler and Schmidt (2016)
\item
  Porter, Woo, and Campion (2016)
\item
  Quade, Greenbaum, and Petrenko (2017)
\item
  Raghuram, Gajendran, Liu, and Somaya (2017)
\item
  Ragins, Ehrhardt, Lyness, Murphy, and Capman (2017)
\item
  Seibert, Sargent, Kraimer, and Kiazad (2017)
\item
  Sui, Wang, Kirkman, and Li (2016)
\item
  Triana, Richard, and Yücel (2017)
\item
  Wayne, Butts, Casper, and Allen (2017)
\item
  Welbourne and Paterson (2017)
\item
  Zhan, Wang, and Shi (2016)
\end{enumerate}

\section{Methods}\label{methods}

\subsection{Behavior Research Methods}\label{behavior-research-methods}

\subsubsection{2012}\label{section-32}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Amsel, Urbach, and Kutas (2012)
\item
  Armstrong, Tokowicz, and Plaut (2012)
\item
  Bestgen and Vincze (2012)
\item
  Brodeur et al. (2012)
\item
  Clark, Parakh, Smilek, and Roy (2012)
\item
  Dahmani, Ledoux, Boyer, and Bohbot (2012)
\item
  Dennett et al. (2012)
\item
  Dewhurst et al. (2012)
\item
  Ellis-Davies, Sakkalou, Fowler, Hilbrink, and Gattis (2012)
\item
  Ferré, Guasch, Moldovan, and Sánchez-Casas (2012)
\item
  Izura and Playfoot (2012)
\item
  Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012)
\item
  Kusev, Tsaneva-Atanasova, Schaik, and Chater (2012)
\item
  Lemhöfer and Broersma (2012)
\item
  Leveau, Jhean-Larose, Denhière, and Nguyen (2012)
\item
  Liu and Pell (2012)
\item
  Nishimoto, Ueda, Miyawaki, Une, and Takahashi (2012)
\item
  Ross and Allen (2012)
\item
  Sathyan, Shuttleworth, Hedley, and Davids (2012)
\item
  Schock, Cortese, and Khanna (2012)
\item
  Schock, Cortese, Khanna, and Toppi (2012)
\item
  Schröder, Gemballa, Ruppin, and Wartenburger (2012)
\item
  Steenbergen et al. (2012)
\item
  Steiner and Ashcraft (2012)
\item
  Xiao and Treiman (2012)
\end{enumerate}

\subsubsection{2017}\label{section-33}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Brankaer, Ghesquière, and De Smedt (2017)
\item
  Brascamp and Naber (2017)
\item
  Brunet, Dagenais, Therrien, Gartenberg, and Forest (2017)
\item
  Brust-Renck et al. (2017)
\item
  Constantinescu, Wolters, Moore, and MacPherson (2017)
\item
  Dawel et al. (2017)
\item
  Chiusole, Stefanutti, and Spoto (2017)
\item
  Diedenhofen and Musch (2017)
\item
  Forsythe, Street, and Helmy (2017)
\item
  Garrido et al. (2017)
\item
  Grant, Honn, Layton, Riedy, and Van Dongen (2017)
\item
  Hoffmann, Waubert de Puiseau, Schmidt, and Musch (2017)
\item
  Keil et al. (2017)
\item
  Lou, Liu, Kaakinen, and Li (2017)
\item
  Meuwissen, Anderson, and Zelazo (2017)
\item
  Michałowski et al. (2017)
\item
  Nyström, Niehorster, Cornelissen, and Garde (2017)
\item
  Semmelmann and Weigelt (2017)
\item
  Sense, Morey, Prince, Heathcote, and Morey (2017)
\item
  Takano et al. (2017)
\item
  Tse et al. (2017)
\item
  Wen and Heuven (2016)
\item
  Wolsiefer, Westfall, and Judd (2017)
\item
  Yao, Wu, Zhang, and Wang (2017)
\item
  Yu, Van Gemmert, and Chang (2016)
\end{enumerate}

\subsection{Psychological Methods}\label{psychological-methods}

\subsubsection{2012}\label{section-34}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Bartels, Boomsma, Hudziak, Beijsterveldt, and Oord (2007)
\item
  Bauer and Hussong (2009)
\item
  Deboeck, Montpetit, Bergeman, and Boker (2009)
\item
  González, De Boeck, and Tuerlinckx (2008)
\item
  Harder, Stuart, and Anthony (2010)
\item
  Hong (2012)
\item
  Jahng, Wood, and Trull (2008)
\item
  Klein Entink, Kuhn, Hornke, and Fox (2009)
\item
  Linting, Meulman, Groenen, and Koojj (2007)
\item
  Lüdtke et al. (2008)
\item
  Lüdtke, Marsh, Robitzsch, and Trautwein (2011)
\item
  McArdle, Grimm, Hamagami, Bowles, and Meredith (2009)
\item
  Meade and Craig (2012)
\item
  Muthén and Asparouhov (2012)
\item
  Nahum-Shani et al. (2012b)
\item
  Nahum-Shani et al. (2012a)
\item
  Ozechowski, Turner, and Hops (2007)
\item
  Preacher and Kelley (2011)
\item
  Shadish, Galindo, Wong, Steiner, and Cook (2011)
\item
  Steiner, Cook, Shadish, and Clark (2010)
\item
  Tonidandel, LeBreton, and Johnson (2009)
\item
  Voelkle, Oud, Davidov, and Schmidt (2012)
\item
  Weijters, Geuens, and Schillewaert (2010)
\item
  Widaman et al. (2012)
\item
  Yuan and Hayashi (2010)
\end{enumerate}

\subsubsection{2017}\label{section-35}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Anders, Alario, and Van Maanen (2016)
\item
  Bauer (2017)
\item
  Beaton, Dunlop, Initiative, and Abdi (2016)
\item
  Böckenholt (2017)
\item
  Cham and West (2016)
\item
  Chapman et al. (2016)
\item
  Chiusole, Stefanutti, Anselmi, and Robusto (2015)
\item
  Dziak, Li, Tan, Shiffman, and Shiyko (2015)
\item
  Eid, Geiser, Koch, and Heene (2016)
\item
  Geiser et al. (2015)
\item
  Jones and Waller (2015)
\item
  Jones, Wojcik, Sweeting, and Silver (2016)
\item
  Kosinski, Wang, Lakkaraju, and Leskovec (2016)
\item
  Kuha and Moustaki (2015)
\item
  Landers, Brusso, Cavanaugh, and Collmus (2016)
\item
  Liu, Zhou, Palumbo, and Wang (2016)
\item
  Liu et al. (2017)
\item
  Miller, Lubke, McArtor, and Bergeman (2016)
\item
  Montoya and Hayes (2017)
\item
  Oberski, Hagenaars, and Saris (2015)
\item
  Preacher, Zhang, and Zyphur (2015)
\item
  Rodriguez, Reise, and Haviland (2016)
\item
  Schuurman, Ferrer, Boer-Sonnenschein, and Hamaker (2016)
\item
  Shrout and Yip-Bannicq (2017)
\item
  Stanley and Byrne (2016)
\end{enumerate}

\section{Neuro}\label{neuro}

\subsection{Cognitive, Affective, \& Behavioral
Neuroscience}\label{cognitive-affective-behavioral-neuroscience}

\subsubsection{2012}\label{section-36}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Anton, Baskin-Sommers, Vitale, Curtin, and Newman (2012)
\item
  Balconi and Ferrari (2012)
\item
  Basten, Stelzel, and Fiebach (2012)
\item
  Dunn, Evans, Makarova, White, and Clark (2012)
\item
  Elman, Klostermann, Marian, Verstaen, and Shimamura (2012)
\item
  Fuentes et al. (2012)
\item
  Fukunaga, Brown, and Bogg (2012)
\item
  Garcea, Almeida, and Mahon (2012)
\item
  Halsband, Ferdinand, Bridger, and Mecklinger (2012)
\item
  Hartley, Maquestiaux, Brooks, Festini, and Frazier (2012)
\item
  Heitland et al. (2012)
\item
  Jaeger and Rugg (2012)
\item
  Koban, Pourtois, Bediou, and Vuilleumier (2012)
\item
  Kunde, Augst, and Kleinsorge (2012)
\item
  Park, Moon, Kim, and Lee (2012)
\item
  Parvaz, MacNamara, Goldstein, and Hajcak (2012)
\item
  Plessow, Schade, Kirschbaum, and Fischer (2012)
\item
  Savine and Braver (2012)
\item
  Schroder, Moran, Moser, and Altmann (2012)
\item
  Stocco, Lebiere, O'Reilly, and Anderson (2012)
\item
  Well, Visser, Scholte, and Kindt (2012)
\item
  Vendetti, Knowlton, and Holyoak (2012)
\item
  Weinberg, Luhmann, Bress, and Hajcak (2012)
\item
  Whitmer and Gotlib (2012)
\item
  Whitmer and Banich (2012)
\end{enumerate}

\subsubsection{2017}\label{section-37}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Anderson et al. (2017)
\item
  Budhiraja et al. (2017)
\item
  Cui, Zhu, and Luo (2017)
\item
  Deak et al. (2017)
\item
  Debbané et al. (2017)
\item
  De Bellis, Trojano, Errico, Grossi, and Conson (2017)
\item
  Del Zotto and Pegna (2017)
\item
  Herron (2017)
\item
  Lusk, Carr, Ranson, and Felmingham (2017)
\item
  MacLeod, Stewart, Newman, and Arnell (2017)
\item
  Marrero, Urrutia, Beltrán, Gámez, and Díaz (2017)
\item
  Pornpattananangkul, Nadig, Heidinger, Walden, and Nusslock (2017)
\item
  Qi et al. (2017)
\item
  Reznik et al. (2017)
\item
  Riem et al. (2017)
\item
  Schutte, Kenemans, and Schutter (2017)
\item
  Soltanlou et al. (2017)
\item
  Stites, Payne, and Federmeier (2017)
\item
  Tomlin, Nedic, Prentice, Holmes, and Cohen (2017)
\item
  Toyama, Katahira, and Ohira (2017)
\item
  Umemoto, HajiHosseini, Yates, and Holroyd (2017)
\item
  Meulen et al. (2017)
\item
  Vergara-Martínez, Comesaña, and Perea (2017)
\item
  Vlaev, Crockett, Clark, Müller, and Robbins (2017)
\item
  Wylie, Genova, DeLuca, and Dobryakova (2017)
\end{enumerate}

\subsection{Neuropsychology}\label{neuropsychology}

\subsubsection{2012}\label{section-38}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Asp, Ramchandran, and Tranel (2012)
\item
  Bate and Cook (2012)
\item
  Butcher et al. (2012)
\item
  Buxbaum, Dawson, and Linsley (2012)
\item
  Gabay, Schiff, and Vakil (2012)
\item
  Greer, Vendemia, and Stancil (2012)
\item
  Guillaume, Guillem, Tiberghien, and Stip (2012)
\item
  Harakeh et al. (2012)
\item
  Janos, Grange, Steiner, and White (2012)
\item
  Karalunas, Huang-Pollock, and Nigg (2012)
\item
  Lane, Moore, Batchelor, Brew, and Cysique (2012)
\item
  Lee et al. (2012)
\item
  Levy-Gigi et al. (2012)
\item
  Libon et al. (2012)
\item
  Macé, Ergis, and Caza (2012)
\item
  Nicholls, Johnston, and Shields (2012)
\item
  Perri, Zannino, Caltagirone, and Carlesimo (2012)
\item
  Pontifex, Scudder, Drollette, and Hillman (2012)
\item
  Roberts, Milich, and Fillmore (2012)
\item
  Ronchi, Algeri, Chiapella, Spada, and Vallar (2012)
\item
  Schmitter-Edgecombe, McAlister, and Weakley (2012)
\item
  Serrien, Sovijärvi-Spapé, and Farnsworth (2012)
\item
  Smith, Mills, Epping, Westervelt, and Paulsen (2012)
\item
  Spitz, Ponsford, Rudzki, and Maller (2012)
\item
  Sutter, Zöllig, Allemand, and Martin (2012)
\end{enumerate}

\subsubsection{2017}\label{section-39}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Abreu-Mendoza and Arias-Trejo (2017)
\item
  Andruchow, Konishi, Shatenstein, and Bohbot (2017)
\item
  Benoit et al. (2017)
\item
  Bitan, Kaftory, Meiri-Leib, Eviatar, and Peleg (2017)
\item
  Christodoulou et al. (2016)
\item
  Dewar, Neroni, Zeman, Beschin, and Della Sala (2017)
\item
  Dissanayaka et al. (2017)
\item
  Durber et al. (2017)
\item
  Faulkner, Wilshire, Parker, and Cunningham (2017)
\item
  Gamond, Vecchi, Ferrari, Merabet, and Cattaneo (2017)
\item
  Gomez, Power, Gill, and Fujiwara (2017)
\item
  Goodwin, Conrad, Ansley, and Nopoulos (2017)
\item
  Heinrichs, Parlar, and Pinnock (2017)
\item
  Impairment, Case, and Kvavilashvili (2017)
\item
  Lundqvist, Svärd, Michelgård Palmquist, Fischer, and Svenningsson
  (2017)
\item
  Millar et al. (2017)
\item
  Parthasarathy et al. (2017)
\item
  Pluta, Gawron, Sobańska, Wójcik, and Łojek (2017)
\item
  Raimo et al. (2017)
\item
  Reynolds, Hanna, Neargarder, and Cronin-Golomb (2017)
\item
  Riva et al. (2017)
\item
  Salazar et al. (2017)
\item
  Segal, Shalev, and Mashal (2017)
\item
  Treble-Barna et al. (2017)
\item
  Uren, Cotton, Killackey, Saling, and Allott (2017)
\end{enumerate}

\section{Overview}\label{overview}

\subsection{Psychological Assessment}\label{psychological-assessment}

\subsubsection{2012}\label{section-40}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Allen, Thaler, Ringdahl, Barney, and Mayfield (2012)
\item
  Allen, Thaler, Barchard, Vertinski, and Mayfield (2012)
\item
  Arbisi et al. (2012)
\item
  Barbot et al. (2012)
\item
  Chiesi, Ciancaleoni, Galli, and Primi (2012)
\item
  Conrad et al. (2012)
\item
  DeMartini and Carey (2012)
\item
  Dibble, Levine, and Park (2012)
\item
  Ebesutani et al. (2012)
\item
  Fledderus, Oude Voshaar, Klooster, and Bohlmeijer (2012)
\item
  Hale-Smith, Park, and Edmondson (2012)
\item
  Herzberg et al. (2012)
\item
  Jayawickreme, Jayawickreme, Atanasov, Goonasekera, and Foa (2012)
\item
  Martins and Calheiros (2012)
\item
  Mattson, Powers, Halfaker, Akeson, and Ben-Porath (2012)
\item
  Melas, Zampetakis, Dimopoulou, and Moustakis (2012)
\item
  Miller et al. (2012)
\item
  Mossman, Wygant, and Gervais (2012)
\item
  Naragon-Gainey, Simpson, Moore, Varra, and Kaysen (2012)
\item
  Resendes and Lecci (2012)
\item
  Schry, Roberson-Nay, and White (2012)
\item
  Tonkin et al. (2012)
\item
  Waiyavutti, Johnson, and Deary (2012)
\item
  Wilson and Durbin (2012)
\item
  Woltz, Gardner, Kircher, and Burrow-Sanchez (2012)
\end{enumerate}

\subsubsection{2017}\label{section-41}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Boccaccini, Rice, Helmus, Murrie, and Harris (2017)
\item
  Burgess, DiBartolo, and Rendón (2017)
\item
  Carr, Catak, Pejsa-Reitz, Saules, and Gearhardt (2017)
\item
  Coates, Ayers, and Visser (2017)
\item
  Crenshaw, Christensen, Baucom, Epstein, and Baucom (2017)
\item
  Ellis, Galloway, Webb, and Martz (2017)
\item
  Evans, Thirlwall, Cooper, and Creswell (2017)
\item
  Garey et al. (2017)
\item
  Gomez, Vance, and Watson (2016)
\item
  Harris, Boccaccini, and Rice (2017)
\item
  Lawing, Childs, Frick, and Vincent (2017)
\item
  Marshall, Feinberg, Jones, and Chote (2017)
\item
  Morgan, Wells, Andretta, and McKay (2016)
\item
  Mowle et al. (2016)
\item
  Naragon-Gainey and DeMarree (2017)
\item
  Ng, Cao, Marsh, Tay, and Seligman (2016)
\item
  Perrault, Vincent, and Guy (2017)
\item
  Rettenberger, Rice, Harris, and Eher (2017)
\item
  Rogge, Fincham, Crasta, and Maniaci (2016)
\item
  Shiyko, Perkins, and Caldwell (2017)
\item
  Sleep, Sellbom, Campbell, and Miller (2016)
\item
  Sunderland et al. (2017)
\item
  Weiss and Rosenfeld (2017)
\item
  Young et al. (2017)
\item
  Zwaanswijk, Veen, Geel, Andershed, and Vedder (2017)
\end{enumerate}

\subsection{Psychological Science}\label{psychological-science}

\subsubsection{2012}\label{section-42}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Berntsen et al. (2012)
\item
  Borra, Hooge, and Verstraten (2012)
\item
  Buehner (2012)
\item
  Chabris et al. (2012)
\item
  Chow and Galak (2012)
\item
  Dennett, McKone, Edwards, and Susilo (2012)
\item
  DeSteno et al. (2012)
\item
  Galesic, Olsson, and Rieskamp (2012)
\item
  Korjoukov et al. (2012)
\item
  Leder, Bär, and Topolinski (2012)
\item
  Legault, Al-Khindi, and Inzlicht (2012)
\item
  Lin and He (2012)
\item
  McCabe and Fleeson (2012)
\item
  Oishi and Kesebir (2012)
\item
  Rink, Ryan, and Stoker (2012)
\item
  Riva, Romero Lauro, DeWall, and Bushman (2012)
\item
  Rodeheffer, Hill, and Lord (2012)
\item
  Rossano, Carpenter, and Tomasello (2012)
\item
  Sanders, Shirk, Burgin, and Martin (2012)
\item
  Sherman, Haidt, and Clore (2012)
\item
  Stallen, De Dreu, Shalvi, Smidts, and Sanfey (2012)
\item
  Thiruchselvam, Hajcak, and Gross (2012)
\item
  Thompson, Vinson, Woll, and Vigliocco (2012)
\item
  Weems, Scott, Banks, and Graham (2012)
\item
  Wu, Shimojo, Wang, and Camerer (2012)
\end{enumerate}

\subsubsection{2017}\label{section-43}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Baek, Scholz, O'Donnell, and Falk (2017)
\item
  Bannard, Rosner, and Matthews (2017)
\item
  Batterink (2017)
\item
  Borhani, Beck, and Haggard (2017)
\item
  Brod, Bunge, and Shing (2017)
\item
  Carr, Brady, and Winkielman (2017)
\item
  Caruso, Shapira, and Landy (2017)
\item
  Caselli and Pyers (2017)
\item
  Daly, Robinson, and Sutin (2017)
\item
  Dankner, Shalev, Carrasco, and Yuval-Greenberg (2017)
\item
  Farmer, Baron-Cohen, and Skylark (2017)
\item
  FeldmanHall, Dunsmoor, Kroes, Lackovic, and Phelps (2017)
\item
  Foster, Sutterer, Serences, Vogel, and Awh (2017)
\item
  Jenkins and Hsu (2017)
\item
  Lages, Boyle, and Jenkins (2017)
\item
  Lapate et al. (2017)
\item
  Lloyd, Hugenberg, McConnell, Kunstman, and Deska (2017)
\item
  López-Pérez, Howells, and Gummerum (2017)
\item
  Mathôt, Grainger, and Strijkers (2017)
\item
  McNulty, Olson, Jones, and Acosta (2017)
\item
  Middlebrooks, Kerr, and Castel (2017)
\item
  Nilsson, Lebedev, Rydström, and Lövdén (2017)
\item
  Ort, Fahrenfort, and Olivers (2017)
\item
  Ramscar, Sun, Hendrix, and Baayen (2017)
\item
  Shen and Hsee (2017)
\end{enumerate}

\subsection{Psychonomic Bulletin and
Review}\label{psychonomic-bulletin-and-review}

\subsubsection{2012}\label{section-44}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Apel, Henderson, and Ferreira (2012)
\item
  Campbell and Dowd (2012)
\item
  Darling, Logie, and Della Sala (2012)
\item
  Doi and Shinohara (2012)
\item
  Duncan, Schramm, Thompson, and Dumontheil (2012)
\item
  Finlayson and Corley (2012)
\item
  Henderson and Luke (2012)
\item
  Huff and Schwan (2012)
\item
  Kaushanskaya and Rechtzigel (2012)
\item
  Kiernan, Ray, and Welsh (2012)
\item
  Li, Zhao, and Pollatsek (2012)
\item
  Liu and Fox Tree (2012)
\item
  May, Owens, and Einstein (2012)
\item
  Murphy, Velzen, and Fockert (2012)
\item
  Papesh and Goldinger (2012)
\item
  Perea, Gatt, Moret-Tatay, and Fabri (2012)
\item
  Pohl and Hilbig (2012)
\item
  Reynolds, Mulatti, and Besner (2012)
\item
  Riès, Legou, Burle, Alario, and Malfait (2012)
\item
  Roper and Vecera (2012)
\item
  Trueblood (2012)
\item
  Vatterott and Vecera (2012)
\item
  Vaughn and Rawson (2012)
\item
  Wang and Yonelinas (2012)
\item
  Zentall and Morris (2012)
\end{enumerate}

\subsubsection{2017}\label{section-45}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Berggren, Curtis, and Derakshan (2017)
\item
  Brown and Maylor (2017)
\item
  Conaway and Kurtz (2017)
\item
  Denison, Heeger, and Carrasco (2017)
\item
  Valk, Wnuk, Huisman, and Majid (2017)
\item
  Dowd, Pearson, and Egner (2017)
\item
  Du and Clark (2017)
\item
  Eskenazi and Folk (2017)
\item
  Heuer and Schubö (2017)
\item
  Hoyos and Gentner (2017)
\item
  Jonas, Spiller, and Hibbard (2017)
\item
  Marcet and Perea (2017)
\item
  Rindal, Chrobak, Zaragoza, and Weihing (2017)
\item
  Röer, Körner, Buchner, and Bell (2017)
\item
  Rogers (2017)
\item
  Rubio-Fernández (2017)
\item
  Scholz, Krems, and Jahn (2017)
\item
  Searston and Tangen (2017)
\item
  Sheremata and Shomstein (2017)
\item
  Thibodeau, Crow, and Flusberg (2017)
\item
  Undorf and Zander (2017)
\item
  Wang, Yan, Wang, Olivers, and Theeuwes (2017)
\item
  Wang et al. (2017)
\item
  Weeks and Hasher (2017)
\item
  Zanini, Benavides-Varela, Lorusso, and Franzon (2017)
\end{enumerate}

\section{Social}\label{social}

\subsection{Journal of Experimental Social
Psychology}\label{journal-of-experimental-social-psychology}

\subsubsection{2012}\label{section-46}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Alós-Ferrer, Granić, Shi, and Wagner (2012)
\item
  Callan, Dawtry, and Olson (2012)
\item
  Chen, Jing, and Lee (2012)
\item
  Devine, Forscher, Austin, and Cox (2012)
\item
  Eibach and Mock (2012)
\item
  Fay and Maner (2012)
\item
  Ferreira et al. (2012)
\item
  Gollwitzer and Melzer (2012)
\item
  Hartson and Sherman (2012)
\item
  Hebl, Williams, Sundermann, Kell, and Davies (2012)
\item
  Hess, Adams, Simard, Stevenson, and Kleck (2012)
\item
  Kendrick and Olson (2012)
\item
  Kushlev, Dunn, and Ashton-James (2012)
\item
  Landau, Sullivan, Keefer, Rothschild, and Osman (2012)
\item
  Lelkes, Krosnick, Marx, Judd, and Park (2012)
\item
  O'Brien, Major, and Simon (2012)
\item
  Preston and Ritter (2012)
\item
  Ramos, Garcia-Marques, Hamilton, Ferreira, and Van Acker (2012)
\item
  Ratcliff, Bernstein, Cundiff, and Vescio (2012)
\item
  Rios, Wheeler, and Miller (2012)
\item
  Santos et al. (2012)
\item
  Stephens, Townsend, Markus, and Phillips (2012)
\item
  Todd and Galinsky (2012)
\item
  Leeuwen, Park, and Penton-Voak (2012)
\item
  Wakslak (2012)
\end{enumerate}

\subsubsection{2017}\label{section-47}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Bang, Zhou Koval, and Wade-Benzoni (2017)
\item
  Burns, Monteith, and Parker (2017)
\item
  Carter and Murphy (2017)
\item
  Cassidy et al. (2017)
\item
  Chatard, Bocage-Barthélémy, Selimbegović, and Guimond (2017)
\item
  Cowgill, Rios, and Simpson (2017)
\item
  Danbold and Huo (2017)
\item
  Dang, Liu, Ren, and Su (2018)
\item
  Deska and Hugenberg (2018)
\item
  Eller, Abrams, and Koschate (2017)
\item
  Evans and Beest (2017)
\item
  Frimer, Skitka, and Motyl (2017)
\item
  Grossmann and Nickta (2017)
\item
  Hunter et al. (2017)
\item
  Kirby and Greenwald (2017)
\item
  Leander and Chartrand (2017)
\item
  Parker, Monteith, Moss-Racusin, and Van Camp (2018)
\item
  Robinson, Page-Gould, and Plaks (2017)
\item
  Rocklage, Pietri, and Fazio (2017)
\item
  Roese, Smallman, and Epstude (2017)
\item
  Rom and Conway (2018)
\item
  Schaumberg and Mullen (2017)
\item
  Wenzel, Anvari, Vel-Palumbo, and Bury (2017)
\item
  Wilson, Young, Rule, and Hugenberg (2018)
\item
  Zhu, Ritter, Müller, and Dijksterhuis (2017)
\end{enumerate}

\subsection{Journal of Personality and Social
Psychology}\label{journal-of-personality-and-social-psychology}

\subsubsection{2012}\label{section-48}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Ainsworth and Maner (2012)
\item
  Anderson, Brion, Moore, and Kennedy (2012)
\item
  Becker (2012)
\item
  Blankenship, Wegener, and Murray (2012)
\item
  Chan et al. (2012)
\item
  Effron, Miller, and Monin (2012)
\item
  Gable, Gosnell, Maisel, and Strachman (2012)
\item
  Galak, LeBoeuf, Nelson, and Simmons (2012)
\item
  Granqvist, Mikulincer, Gewirtz, and Shaver (2012)
\item
  Kochanska, Kim, and Koenig Nordling (2012)
\item
  Lee and Schwarz (2012)
\item
  Leikas, Lönnqvist, and Verkasalo (2012)
\item
  Lemay, Overall, and Clark (2012)
\item
  Levine, Lench, Kaplan, and Safer (2012)
\item
  Locke, Craig, Baik, and Gohil (2012)
\item
  Ma-Kellams and Blascovich (2012)
\item
  Nestler, Egloff, Küfner, and Back (2012)
\item
  Paluck and Shepherd (2012)
\item
  Piff, Stancato, Martinez, Kraus, and Keltner (2012)
\item
  Rattan, Savani, Naidu, and Dweck (2012)
\item
  Schwartz et al. (2012)
\item
  Sullivan, Landau, Kay, and Rothschild (2012)
\item
  Tadmor, Hong, Chao, Wiruchnipawan, and Wang (2012)
\item
  Tormala, Jia, and Norton (2012)
\item
  Woodcock, Hernandez, Estrada, and Schultz (2012)
\end{enumerate}

\subsubsection{2017}\label{section-49}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Bai et al. (2017)
\item
  Bjornsdottir and Rule (2017)
\item
  Borghuis et al. (2017)
\item
  Chou, Halevy, Galinsky, and Murnighan (2017)
\item
  Cortland et al. (2017)
\item
  Gawronski, Armstrong, Conway, Friesdorf, and Hütter (2017)
\item
  Gebauer et al. (2017)
\item
  Gordon et al. (2017)
\item
  Hehman, Sutherland, Flake, and Slepian (2017)
\item
  Huang, Yeomans, Brooks, Minson, and Gino (2017)
\item
  Jones and Paulhus (2017)
\item
  Klein and O'Brien (2017)
\item
  Köber and Habermas (2017)
\item
  Landy, Walco, and Bartels (2017)
\item
  Miller, Akiyama, and Kapadia (2017)
\item
  Motyl et al. (2017)
\item
  Neal, Durbin, Gornik, and Lo (2017)
\item
  Savani and Job (2017)
\item
  Schriber, Chung, Sorensen, and Robins (2016)
\item
  Slepian, Chun, and Mason (2017)
\item
  Stanton, Campbell, and Pink (2017)
\item
  Thrash, Maruskin, Moldovan, Oleynick, and Belzak (2017)
\item
  White and Crandall (2017)
\item
  Wilson, Hugenberg, and Rule (2017)
\item
  Zeinoun, Daouk-Öyry, Choueiri, and Vijver (2017)
\end{enumerate}

\section{Sports}\label{sports}

\subsection{Journal of Sport and Exercise
Psychology}\label{journal-of-sport-and-exercise-psychology}

\subsubsection{2012}\label{section-50}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Aelterman et al. (2012)
\item
  Arthur, Woodman, Ong, Hardy, and Ntoumanis (2011)
\item
  Bartholomew, Ntoumanis, Ryan, and Thøgersen-Ntoumani (2011)
\item
  Boucard et al. (2012)
\item
  Brunet and Sabiston (2011)
\item
  Chan and Hagger (2012)
\item
  Chang et al. (2011)
\item
  Chang, Chu, Chen, and Wang (2011)
\item
  Cheng, Hardy, and Woodman (2011)
\item
  Conroy, Elavsky, Hyde, and Doerksen (2011)
\item
  Englert and Bertrams (2012)
\item
  Finez and Sherman (2012)
\item
  Flora, Strachan, Brawley, and Spink (2012)
\item
  Freeman, Coffee, and Rees (2011)
\item
  Hyde, Elavsky, Doerksen, and Conroy (2012)
\item
  Kavussanu, Willoughby, and Ring (2012)
\item
  Kee, Chatzisarantis, Kong, Chow, and Chen (2012)
\item
  Maltby, Wood, Vlaev, Taylor, and Brown (2012)
\item
  Mosewich, Kowalski, Sabiston, Sedgwick, and Tracy (2011)
\item
  Parry, Chinnasamy, and Micklewright (2012)
\item
  Quested et al. (2011)
\item
  Sapieja, Dunn, and Holt (2011)
\item
  Smith, Ntoumanis, Duda, and Vansteenkiste (2011)
\item
  Pol, Kavussanu, and Ring (2012)
\item
  Williams et al. (2012)
\end{enumerate}

\subsubsection{2017}\label{section-51}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Arnautovska, O'Callaghan, and Hamilton (2017)
\item
  Benson and Eys (2017)
\item
  Berry, Rodgers, Markland, and Hall (2016)
\item
  Brewer, Cornelius, Van Raalte, and Tennen (2017)
\item
  Callow, Jiang, Roberts, and Edwards (2017)
\item
  Crust, Swann, and Allen-Collinson (2016)
\item
  De Muynck et al. (2017)
\item
  Dimmock et al. (2016)
\item
  Furley and Schweizer (2016)
\item
  Gray, Orn, and Woodman (2017)
\item
  Huysmans and Clement (2017)
\item
  Kay and Grimm (2017)
\item
  Krinski et al. (2017)
\item
  Lebeau et al. (2016)
\item
  Matosic, Ntoumanis, Boardley, Stenling, and Sedikides (2016)
\item
  McDavid, McDonough, Blankenship, and LeBreton (2017)
\item
  Delli Paoli, Smith, and Pontifex (2017)
\item
  Riciputi, McDonough, and Ullrich-French (2016)
\item
  Sparks, Lonsdale, Dimmock, and Jackson (2017)
\item
  Stenling and Tafvelin (2016)
\item
  Sun, Zhang, Vine, and Wilson (2016)
\item
  Tamminen, Gaudreau, McEwen, and Crocker (2016)
\item
  Bavel et al. (2017)
\item
  Wang, Morin, Ryan, and Liu (2016)
\item
  Zestcott, Lifshin, Helm, and Greenberg (2016)
\end{enumerate}

\subsection{Sociology of Sport
Journal}\label{sociology-of-sport-journal}

\subsubsection{2012}\label{section-52}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Brown, Ruel, and Medley-Rath (2011)
\item
  Christensen (2009)
\item
  Comeaux (2010)
\item
  Cunningham and Sagas (2004)
\item
  Cunningham and Melton (2012)
\item
  Dagkas and Quarmby (2012)
\item
  Denham (2011)
\item
  Goldsmith (2003)
\item
  Hanold (2010)
\item
  Harrison, Lawrence, and Bukstein (2011)
\item
  May (2009)
\item
  McGrath and Chananie-Hill (2009)
\item
  Meier and Leinwather (2012)
\item
  Mennesson (2012)
\item
  Miller, Barnes, Sabo, Melnick, and Farrell (2002)
\item
  Miller and Hoffman (2009)
\item
  Nixon (2010)
\item
  Parsons and Stern (2012)
\item
  Pringle (2009)
\item
  Purdy and Jones (2011)
\item
  Shakib, Veliz, Dunbar, and Sabo (2011)
\item
  Tucker and Parks (2001)
\item
  Walk and Wiersma (2005)
\item
  Ward (2008)
\item
  White and McTeer (2012)
\end{enumerate}

\subsubsection{2017}\label{section-53}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Cohen and Hanold (2016)
\item
  Cooper, Davis, and Dougherty (2017)
\item
  Van der Meij, Darby, and Liston (2017)
\item
  Dzikus, Smith, and Evans (2017)
\item
  Fry and Bloyce (2017)
\item
  Hayton (2017)
\item
  Lawrence, Harrison, and Bukstein (2016)
\item
  Liechty, Willfong, and Sveinson (2016)
\item
  Love, Gonzalez-Sobrino, and Hughey (2017)
\item
  Lund and Söderström (2017)
\item
  MacArthur, Angelini, Billings, and Smith (2017)
\item
  Musto and McGann (2016)
\item
  Nakamura (2016)
\item
  Nieri and Hughes (2016)
\item
  Rankin-Wright, Hylton, and Norman (2016)
\item
  Renfrow, Wissick, and Guard (2016)
\item
  Safai, Johnson, and Bryans (2016)
\item
  Sanchez (2017)
\item
  Sanderson and Gramlich (2015)
\item
  Sandvik, Strandbu, and Loland (2017)
\item
  Scherer, Koch, and Holt (2016)
\item
  Sirna (2016)
\item
  Szto (2016)
\item
  Tajrobehkar (2016)
\item
  Wood and Garn (2016)
\end{enumerate}

\newpage

\section{References}\label{references}

\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-Abreu-Mendoza2017}{}
Abreu-Mendoza, R. A., \& Arias-Trejo, N. (2017). Counting ability in
Down syndrome: The comprehension of the one-to-one correspondence
principle and the role of receptive vocabulary. \emph{Neuropsychology},
\emph{31}(7), 750--758.
doi:\href{https://doi.org/10.1037/neu0000377}{10.1037/neu0000377}

\hypertarget{ref-Aelterman2012}{}
Aelterman, N., Vansteenkiste, M., Van Keer, H., Van den Berghe, L., De
Meyer, J., \& Haerens, L. (2012). Students' objectively measured
physical activity levels and engagement as a function of between-class
and between-student differences in motivation toward physical education.
\emph{Journal of Sport and Exercise Psychology}, \emph{34}(4), 457--480.
doi:\href{https://doi.org/10.1123/jsep.34.4.457}{10.1123/jsep.34.4.457}

\hypertarget{ref-Aharoni2012}{}
Aharoni, E., \& Fridlund, A. J. (2012). Punishment without reason:
Isolating retribution in lay punishment of criminal offenders.
\emph{Psychology, Public Policy, and Law}, \emph{18}(4), 599--625.
doi:\href{https://doi.org/10.1037/a0025821}{10.1037/a0025821}

\hypertarget{ref-Ainsworth}{}
Ainsworth, S. E., \& Maner, J. K. (2012). Sex begets violence: Mating
motives, social dominance, and physical aggression in men. \emph{Journal
of Personality and Social Psychology}, \emph{103}(5), 819--829.
doi:\href{https://doi.org/10.1037/a0029428}{10.1037/a0029428}

\hypertarget{ref-Al-Yagon2012}{}
Al-Yagon, M. (2012). Adolescents with learning disabilities:
Socioemotional and behavioral functioning and attachment relationships
with fathers, mothers, and teachers. \emph{Journal of Youth and
Adolescence}, \emph{41}(10), 1294--1311.
doi:\href{https://doi.org/10.1007/s10964-012-9767-6}{10.1007/s10964-012-9767-6}

\hypertarget{ref-Alkhresheh2012}{}
Alkhresheh, M. M. (2012). Preference for void-to-solid ratio in
residential facades. \emph{Journal of Environmental Psychology},
\emph{32}(3), 234--245.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.02.003}{10.1016/j.jenvp.2012.02.003}

\hypertarget{ref-Allan2016}{}
Allan, B. A., Duffy, R. D., \& Blustein, D. L. (2016). Under (and over)
employment: measurement and correlates of employment discrepancy.
\emph{The Counseling Psychologist}, \emph{44}(6), 815--840.
doi:\href{https://doi.org/10.1177/0011000016654766}{10.1177/0011000016654766}

\hypertarget{ref-Allan2017}{}
Allan, N. P., Gros, D. F., Myers, U. S., Korte, K. J., \& Acierno, R.
(2017). Predictors and outcomes of growth mixture modeled trajectories
across an exposure-based PTSD intervention with veterans. \emph{Journal
of Clinical Psychology}, \emph{73}(9), 1048--1063.
doi:\href{https://doi.org/10.1002/jclp.22408}{10.1002/jclp.22408}

\hypertarget{ref-Allen2012a}{}
Allen, D. N., Thaler, N. S., Barchard, K. A., Vertinski, M., \&
Mayfield, J. (2012). Factor structure of the Comprehensive Trail Making
Test in children and adolescents with brain dysfunction.
\emph{Psychological Assessment}, \emph{24}(4), 964--972.
doi:\href{https://doi.org/10.1037/a0028521}{10.1037/a0028521}

\hypertarget{ref-Allen2012}{}
Allen, D. N., Thaler, N. S., Ringdahl, E. N., Barney, S. J., \&
Mayfield, J. (2012). Comprehensive Trail Making Test performance in
children and adolescents with traumatic brain injury.
\emph{Psychological Assessment}, \emph{24}(3), 556--564.
doi:\href{https://doi.org/10.1037/a0026263}{10.1037/a0026263}

\hypertarget{ref-Alos-Ferrer2012}{}
Alós-Ferrer, C., Granić, D. G., Shi, F., \& Wagner, A. K. (2012).
Choices and preferences: Evidence from implicit choices and response
times. \emph{Journal of Experimental Social Psychology}, \emph{48}(6),
1336--1342.
doi:\href{https://doi.org/10.1016/j.jesp.2012.07.004}{10.1016/j.jesp.2012.07.004}

\hypertarget{ref-Altani2017}{}
Altani, A., Georgiou, G. K., Deng, C., Cho, J.-R., Katopodi, K., Wei,
W., \& Protopapas, A. (2017). Is processing of symbols and words
influenced by writing system? Evidence from Chinese, Korean, English,
and Greek. \emph{Journal of Experimental Child Psychology}, \emph{164},
117--135.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.006}{10.1016/j.jecp.2017.07.006}

\hypertarget{ref-Altenstein-Yamanaka2017}{}
Altenstein-Yamanaka, D., Zimmermann, J., Krieger, T., Dörig, N., \&
\{grosse Holtforth\}, M. (2017). Self-reported interpersonal problems
and impact messages as perceived by significant others are
differentially associated with the process and outcome of depression
therapy. \emph{Journal of Counseling Psychology}, \emph{64}(4),
410--423.
doi:\href{https://doi.org/10.1037/cou0000221}{10.1037/cou0000221}

\hypertarget{ref-Alvarez2016}{}
Alvarez, M. J., \& Miller, M. K. (2016). Counterfactual thinking about
crime control theater: Mock jurors' decision making in an AMBER Alert
trial. \emph{Psychology, Public Policy, and Law}, \emph{22}(4),
349--361.
doi:\href{https://doi.org/10.1037/law0000098}{10.1037/law0000098}

\hypertarget{ref-Amemiya2017}{}
Amemiya, J., \& Wang, M.-T. (2017). Transactional relations between
motivational beliefs and help seeking from teachers and peers across
adolescence. \emph{Journal of Youth and Adolescence}, \emph{46}(8),
1743--1757.
doi:\href{https://doi.org/10.1007/s10964-016-0623-y}{10.1007/s10964-016-0623-y}

\hypertarget{ref-Amsel2012}{}
Amsel, B. D., Urbach, T. P., \& Kutas, M. (2012). Perceptual and motor
attribute ratings for 559 object concepts. \emph{Behavior Research
Methods}, \emph{44}(4), 1028--1041.
doi:\href{https://doi.org/10.3758/s13428-012-0215-z}{10.3758/s13428-012-0215-z}

\hypertarget{ref-Anders2016}{}
Anders, R., Alario, F.-X., \& Van Maanen, L. (2016). The shifted Wald
distribution for response time data analysis. \emph{Psychological
Methods}, \emph{21}(3), 309--327.
doi:\href{https://doi.org/10.1037/met0000066}{10.1037/met0000066}

\hypertarget{ref-Anders2012}{}
Anders, S. L., Frazier, P. A., \& Shallcross, S. L. (2012). Prevalence
and effects of life event exposure among undergraduate and community
college students. \emph{Journal of Counseling Psychology}, \emph{59}(3),
449--457. doi:\href{https://doi.org/10.1037/a0027753}{10.1037/a0027753}

\hypertarget{ref-Anderson2012a}{}
Anderson, C., Brion, S., Moore, D. A., \& Kennedy, J. A. (2012). A
status-enhancement account of overconfidence. \emph{Journal of
Personality and Social Psychology}, \emph{103}(4), 718--735.
doi:\href{https://doi.org/10.1037/a0029395}{10.1037/a0029395}

\hypertarget{ref-Anderson2017}{}
Anderson, J., Ruggeri, K., Steemers, K., \& Huppert, F. (2017). Lively
social space, well-being activity, and urban design: Findings from a
low-cost community-led public space intervention. \emph{Environment and
Behavior}, \emph{49}(6), 685--716.
doi:\href{https://doi.org/10.1177/0013916516659108}{10.1177/0013916516659108}

\hypertarget{ref-Anderson2017a}{}
Anderson, N. E., Steele, V. R., Maurer, J. M., Rao, V., Koenigs, M. R.,
Decety, J., \ldots{} Kiehl, K. A. (2017). Differentiating emotional
processing and attention in psychopathy with functional neuroimaging.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{17}(3),
491--515.
doi:\href{https://doi.org/10.3758/s13415-016-0493-5}{10.3758/s13415-016-0493-5}

\hypertarget{ref-Anderson2012}{}
Anderson, T., Crowley, M. E. J., Patterson, C. L., \& Heckman, B. D.
(2012). The influence of supervision on manual adherence and therapeutic
processes. \emph{Journal of Clinical Psychology}, \emph{68}(9),
972--988.
doi:\href{https://doi.org/10.1002/jclp.21879}{10.1002/jclp.21879}

\hypertarget{ref-Andover2017}{}
Andover, M. S., Schatten, H. T., Morris, B. W., Holman, C. S., \&
Miller, I. W. (2017). An intervention for nonsuicidal self-injury in
young adults: A pilot randomized controlled trial. \emph{Journal of
Consulting and Clinical Psychology}, \emph{85}(6), 620--631.
doi:\href{https://doi.org/10.1037/ccp0000206}{10.1037/ccp0000206}

\hypertarget{ref-Andrade2017}{}
Andrade, C. C., Devlin, A. S., Pereira, C. R., \& Lima, M. L. (2017). Do
the hospital rooms make a difference for patients' stress? A multilevel
analysis of the role of perceived control, positive distraction, and
social support. \emph{Journal of Environmental Psychology}, \emph{53},
63--72.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.06.008}{10.1016/j.jenvp.2017.06.008}

\hypertarget{ref-Andrews2017}{}
Andrews, N. C. Z., Hanish, L. D., \& Santos, C. E. (2017). Reciprocal
associations between delinquent behavior and social network position
during middle school. \emph{Journal of Youth and Adolescence},
\emph{46}(9), 1918--1932.
doi:\href{https://doi.org/10.1007/s10964-017-0643-2}{10.1007/s10964-017-0643-2}

\hypertarget{ref-Andruchow2017}{}
Andruchow, N. D., Konishi, K., Shatenstein, B., \& Bohbot, V. D. (2017).
A lower ratio of omega-6 to omega-3 fatty acids predicts better
hippocampus-dependent spatial memory and cognitive status in older
adults. \emph{Neuropsychology}, \emph{31}(7), 724--734.
doi:\href{https://doi.org/10.1037/neu0000373}{10.1037/neu0000373}

\hypertarget{ref-Anton2012}{}
Anton, M. E., Baskin-Sommers, A. R., Vitale, J. E., Curtin, J. J., \&
Newman, J. P. (2012). Differential effects of psychopathy and antisocial
personality disorder symptoms on cognitive and fear processing in female
offenders. \emph{Cognitive, Affective, \& Behavioral Neuroscience},
\emph{12}(4), 761--776.
doi:\href{https://doi.org/10.3758/s13415-012-0114-x}{10.3758/s13415-012-0114-x}

\hypertarget{ref-Apel2012}{}
Apel, J. K., Henderson, J. M., \& Ferreira, F. (2012). Targeting
regressions: Do readers pay attention to the left? \emph{Psychonomic
Bulletin \& Review}, \emph{19}(6), 1108--1113.
doi:\href{https://doi.org/10.3758/s13423-012-0291-1}{10.3758/s13423-012-0291-1}

\hypertarget{ref-Appel-Meulenbroek2017}{}
Appel-Meulenbroek, R., Vries, B. de, \& Weggeman, M. (2017). Knowledge
sharing behavior: The role of spatial design in buildings.
\emph{Environment and Behavior}, \emph{49}(8), 874--903.
doi:\href{https://doi.org/10.1177/0013916516673405}{10.1177/0013916516673405}

\hypertarget{ref-Applebaum2012}{}
Applebaum, A. J., DuHamel, K. N., Winkel, G., Rini, C., Greene, P. B.,
Mosher, C. E., \& Redd, W. H. (2012). Therapeutic alliance in
telephone-administered cognitive--behavioral therapy for hematopoietic
stem cell transplant survivors. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(5), 811--816.
doi:\href{https://doi.org/10.1037/a0027956}{10.1037/a0027956}

\hypertarget{ref-Arbisi2012}{}
Arbisi, P. A., Kaler, M. E., Kehle-Forbes, S. M., Erbes, C. R., Polusny,
M. A., \& Thuras, P. (2012). The predictive validity of the PTSD
Checklist in a nonclinical sample of combat-exposed National Guard
troops. \emph{Psychological Assessment}, \emph{24}(4), 1034--1040.
doi:\href{https://doi.org/10.1037/a0028014}{10.1037/a0028014}

\hypertarget{ref-Arch2012}{}
Arch, J. J., Eifert, G. H., Davies, C., Vilardaga, J. C. P., Rose, R.
D., \& Craske, M. G. (2012). Randomized clinical trial of cognitive
behavioral therapy (CBT) versus acceptance and commitment therapy (ACT)
for mixed anxiety disorders. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(5), 750--765.
doi:\href{https://doi.org/10.1037/a0028310}{10.1037/a0028310}

\hypertarget{ref-Arczynski2017}{}
Arczynski, A. V., \& Morrow, S. L. (2017). The complexities of power in
feminist multicultural psychotherapy supervision. \emph{Journal of
Counseling Psychology}, \emph{64}(2), 192--205.
doi:\href{https://doi.org/10.1037/cou0000179}{10.1037/cou0000179}

\hypertarget{ref-Arens2017}{}
Arens, A. K., Marsh, H. W., Pekrun, R., Lichtenfeld, S., Murayama, K.,
\& Hofe, R. vom. (2017). Math self-concept, grades, and achievement test
scores: Long-term reciprocal effects across five waves and three
achievement tracks. \emph{Journal of Educational Psychology},
\emph{109}(5), 621--634.
doi:\href{https://doi.org/10.1037/edu0000163}{10.1037/edu0000163}

\hypertarget{ref-Armstrong2012}{}
Armstrong, B. C., Tokowicz, N., \& Plaut, D. C. (2012). eDom: Norming
software and relative meaning frequencies for 544 English homonyms.
\emph{Behavior Research Methods}, \emph{44}(4), 1015--1027.
doi:\href{https://doi.org/10.3758/s13428-012-0199-8}{10.3758/s13428-012-0199-8}

\hypertarget{ref-Arnautovska2017}{}
Arnautovska, U., O'Callaghan, F., \& Hamilton, K. (2017). Applying the
integrated behavior change model to understanding physical activity
among older adults: A qualitative study. \emph{Journal of Sport and
Exercise Psychology}, \emph{39}(1), 43--55.
doi:\href{https://doi.org/10.1123/jsep.2015-0330}{10.1123/jsep.2015-0330}

\hypertarget{ref-Arrieta2017}{}
Arrieta, J., Aguerrebere, M., Raviola, G., Flores, H., Elliott, P.,
Espinosa, A., \ldots{} Franke, M. F. (2017). Validity and utility of the
Patient Health Questionnaire (PHQ)-2 and PHQ-9 for screening and
diagnosis of depression in rural Chiapas, Mexico: A cross-sectional
study. \emph{Journal of Clinical Psychology}, \emph{73}(9), 1076--1090.
doi:\href{https://doi.org/10.1002/jclp.22390}{10.1002/jclp.22390}

\hypertarget{ref-Arthur2011}{}
Arthur, C. A., Woodman, T., Ong, C. W., Hardy, L., \& Ntoumanis, N.
(2011). The role of athlete narcissism in moderating the relationship
between coaches' transformational leader behaviors and athlete
motivation. \emph{Journal of Sport and Exercise Psychology},
\emph{33}(1), 3--19.
doi:\href{https://doi.org/10.1123/jsep.33.1.3}{10.1123/jsep.33.1.3}

\hypertarget{ref-Arya2012}{}
Arya, D. J., \& Maul, A. (2012). The role of the scientific discovery
narrative in middle school science education: An experimental study.
\emph{Journal of Educational Psychology}, \emph{104}(4), 1022--1032.
doi:\href{https://doi.org/10.1037/a0028108}{10.1037/a0028108}

\hypertarget{ref-Asah2012}{}
Asah, S. T., Bengston, D. N., \& Westphal, L. M. (2012). The influence
of childhood. \emph{Environment and Behavior}, \emph{44}(4), 545--569.
doi:\href{https://doi.org/10.1177/0013916510397757}{10.1177/0013916510397757}

\hypertarget{ref-Asp2012}{}
Asp, E., Ramchandran, K., \& Tranel, D. (2012). Authoritarianism,
religious fundamentalism, and the human prefrontal cortex.
\emph{Neuropsychology}, \emph{26}(4), 414--421.
doi:\href{https://doi.org/10.1037/a0028526}{10.1037/a0028526}

\hypertarget{ref-Atalay2012}{}
Atalay, N. B., \& Misirlisoy, M. (2012). Can contingency learning alone
account for item-specific control? Evidence from within- and
between-language ISPC effects. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{38}(6), 1578--1590.
doi:\href{https://doi.org/10.1037/a0028458}{10.1037/a0028458}

\hypertarget{ref-Atkinson2017}{}
Atkinson, L., Slade, L., Powell, D., \& Levy, J. P. (2017). Theory of
mind in emerging reading comprehension: A longitudinal study of early
indirect and direct effects. \emph{Journal of Experimental Child
Psychology}, \emph{164}, 225--238.
doi:\href{https://doi.org/10.1016/j.jecp.2017.04.007}{10.1016/j.jecp.2017.04.007}

\hypertarget{ref-Austerweil2011}{}
Austerweil, J. L., \& Griffiths, T. L. (2011). A rational model of the
effects of distributional information on feature learning.
\emph{Cognitive Psychology}, \emph{63}(4), 173--209.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.08.002}{10.1016/j.cogpsych.2011.08.002}

\hypertarget{ref-Austin2017}{}
Austin, E. E., \& Sweller, N. (2017). Getting to the elephants: Gesture
and preschoolers' comprehension of route direction information.
\emph{Journal of Experimental Child Psychology}, \emph{163}, 1--14.
doi:\href{https://doi.org/10.1016/j.jecp.2017.05.016}{10.1016/j.jecp.2017.05.016}

\hypertarget{ref-Avery2012}{}
Avery, D. R., McKay, P. F., Tonidandel, S., Volpone, S. D., \& Morris,
M. A. (2012). Is there method to the madness? Examining how racioethnic
matching influences retail store productivity. \emph{Personnel
Psychology}, \emph{65}(1), 167--199.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01241.x}{10.1111/j.1744-6570.2011.01241.x}

\hypertarget{ref-Baek2017}{}
Baek, E. C., Scholz, C., O'Donnell, M. B., \& Falk, E. B. (2017). The
value of sharing information: A neural account of information
transmission. \emph{Psychological Science}, \emph{28}(7), 851--861.
doi:\href{https://doi.org/10.1177/0956797617695073}{10.1177/0956797617695073}

\hypertarget{ref-Bai2017}{}
Bai, Y., Maruskin, L. A., Chen, S., Gordon, A. M., Stellar, J. E.,
McNeil, G. D., \ldots{} Keltner, D. (2017). Awe, the diminished self,
and collective engagement: Universals and cultural variations in the
small self. \emph{Journal of Personality and Social Psychology},
\emph{113}(2), 185--209.
doi:\href{https://doi.org/10.1037/pspa0000087}{10.1037/pspa0000087}

\hypertarget{ref-Bailey2017}{}
Bailey, D. H., Hansen, N., \& Jordan, N. C. (2017). The codevelopment of
children's fraction arithmetic skill and fraction magnitude
understanding. \emph{Journal of Educational Psychology}, \emph{109}(4),
509--519.
doi:\href{https://doi.org/10.1037/edu0000152}{10.1037/edu0000152}

\hypertarget{ref-Bailey2012}{}
Bailey, D. H., Hoard, M. K., Nugent, L., \& Geary, D. C. (2012).
Competence with fractions predicts gains in mathematics achievement.
\emph{Journal of Experimental Child Psychology}, \emph{113}(3),
447--455.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.004}{10.1016/j.jecp.2012.06.004}

\hypertarget{ref-Bailey2011}{}
Bailey, T.-K. M., Chung, Y. B., Williams, W. S., Singh, A. A., \&
Terrell, H. K. (2011). Development and validation of the Internalized
Racial Oppression Scale for Black individuals. \emph{Journal of
Counseling Psychology}, \emph{58}(4), 481--493.
doi:\href{https://doi.org/10.1037/a0023585}{10.1037/a0023585}

\hypertarget{ref-Baker2017}{}
Baker, A. R., Lin, T.-J., Chen, J., Paul, N., Anderson, R. C., \&
Nguyen-Jahiel, K. (2017). Effects of teacher framing on student
engagement during collaborative reasoning discussions.
\emph{Contemporary Educational Psychology}, \emph{51}, 253--266.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.08.007}{10.1016/j.cedpsych.2017.08.007}

\hypertarget{ref-Baker2016}{}
Baker, S. T., Leslie, A. M., Gallistel, C. R., \& Hood, B. M. (2016).
Bayesian change-point analysis reveals developmental change in a classic
theory of mind task. \emph{Cognitive Psychology}, \emph{91}, 124--149.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.08.001}{10.1016/j.cogpsych.2016.08.001}

\hypertarget{ref-Balconi2012}{}
Balconi, M., \& Ferrari, C. (2012). rTMS stimulation on left DLPFC
increases the correct recognition of memories for emotional target and
distractor words. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{12}(3), 589--598.
doi:\href{https://doi.org/10.3758/s13415-012-0090-1}{10.3758/s13415-012-0090-1}

\hypertarget{ref-Ballard2011}{}
Ballard, R. H., Holtzworth-Munroe, A., Applegate, A. G., \& Beck, C. J.
A. (2011). Detecting intimate partner violence in family and divorce
mediation: A randomized trial of intimate partner violence screening.
\emph{Psychology, Public Policy, and Law}, \emph{17}(2), 241--263.
doi:\href{https://doi.org/10.1037/a0022616}{10.1037/a0022616}

\hypertarget{ref-Bang2017}{}
Bang, H. M., Zhou Koval, C., \& Wade-Benzoni, K. A. (2017). It's the
thought that counts over time: The interplay of intent, outcome,
stewardship, and legacy motivations in intergenerational reciprocity.
\emph{Journal of Experimental Social Psychology}, \emph{73}, 197--210.
doi:\href{https://doi.org/10.1016/j.jesp.2017.07.006}{10.1016/j.jesp.2017.07.006}

\hypertarget{ref-Bannard2017}{}
Bannard, C., Rosner, M., \& Matthews, D. (2017). What's worth talking
about? Information theory reveals how children balance informativeness
and ease of production. \emph{Psychological Science}, \emph{28}(7),
954--966.
doi:\href{https://doi.org/10.1177/0956797617699848}{10.1177/0956797617699848}

\hypertarget{ref-Barbot2012}{}
Barbot, B., Haeffel, G. J., Macomber, D., Hart, L., Chapman, J., \&
Grigorenko, E. L. (2012). Development and validation of the Delinquency
Reduction Outcome Profile (DROP) in a sample of incarcerated juveniles:
A multiconstruct/multisituational scoring approach. \emph{Psychological
Assessment}, \emph{24}(4), 901--912.
doi:\href{https://doi.org/10.1037/a0028193}{10.1037/a0028193}

\hypertarget{ref-Barnes2012}{}
Barnes, C. M., Wagner, D. T., \& Ghumman, S. (2012). Borrowing from
sleep to pay work and family: Expanding time-based conflict to the
broader nonwork domain. \emph{Personnel Psychology}, \emph{65}(4),
789--819.
doi:\href{https://doi.org/10.1111/peps.12002}{10.1111/peps.12002}

\hypertarget{ref-Barrett2017}{}
Barrett, P., Davies, F., Zhang, Y., \& Barrett, L. (2017). The holistic
impact of classroom spaces on learning in specific subjects.
\emph{Environment and Behavior}, \emph{49}(4), 425--451.
doi:\href{https://doi.org/10.1177/0013916516648735}{10.1177/0013916516648735}

\hypertarget{ref-Bartels2007}{}
Bartels, M., Boomsma, D. I., Hudziak, J. J., Beijsterveldt, T. C. E. M.
van, \& Oord, E. J. C. G. van den. (2007). Twins and the study of rater
(dis)agreement. \emph{Psychological Methods}, \emph{12}(4), 451--66.
doi:\href{https://doi.org/10.1037/1082-989X.12.4.451}{10.1037/1082-989X.12.4.451}

\hypertarget{ref-Bartholomew2011}{}
Bartholomew, K. J., Ntoumanis, N., Ryan, R. M., \& Thøgersen-Ntoumani,
C. (2011). Psychological need thwarting in the sport context: Assessing
the darker side of athletic experience. \emph{Journal of Sport and
Exercise Psychology}, \emph{33}(1), 75--102.
doi:\href{https://doi.org/10.1123/jsep.33.1.75}{10.1123/jsep.33.1.75}

\hypertarget{ref-Barzilai2017}{}
Barzilai, S. (2017). ``Half-reliable'': A qualitative analysis of
epistemic thinking in and about a digital game. \emph{Contemporary
Educational Psychology}, \emph{51}, 51--66.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.06.004}{10.1016/j.cedpsych.2017.06.004}

\hypertarget{ref-Baskin2011}{}
Baskin, T. W., Rhody, M., Schoolmeesters, S., \& Ellingson, C. (2011).
Supporting special-needs adoptive couples. \emph{The Counseling
Psychologist}, \emph{39}(7), 933--955.
doi:\href{https://doi.org/10.1177/0011000010397554}{10.1177/0011000010397554}

\hypertarget{ref-Baskin2010}{}
Baskin, T. W., Wampold, B. E., Quintana, S. M., \& Enright, R. D.
(2010). Belongingness as a protective factor against loneliness and
potential depression in a multicultural middle school. \emph{The
Counseling Psychologist}, \emph{38}(5), 626--651.
doi:\href{https://doi.org/10.1177/0011000009358459}{10.1177/0011000009358459}

\hypertarget{ref-Bastaits2012}{}
Bastaits, K., Ponnet, K., \& Mortelmans, D. (2012). Parentingof divorced
fathers and the association with children's self-esteem. \emph{Journal
of Youth and Adolescence}, \emph{41}(12), 1643--1656.
doi:\href{https://doi.org/10.1007/s10964-012-9783-6}{10.1007/s10964-012-9783-6}

\hypertarget{ref-Basten2012}{}
Basten, U., Stelzel, C., \& Fiebach, C. J. (2012). Trait anxiety and the
neural efficiency of manipulation in working memory. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, \emph{12}(3), 571--588.
doi:\href{https://doi.org/10.3758/s13415-012-0100-3}{10.3758/s13415-012-0100-3}

\hypertarget{ref-Basu2017}{}
Basu, S., \& Savani, K. (2017). Choosing one at a time? Presenting
options simultaneously helps people make more optimal decisions than
presenting options sequentially. \emph{Organizational Behavior and Human
Decision Processes}, \emph{139}, 76--91.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.01.004}{10.1016/j.obhdp.2017.01.004}

\hypertarget{ref-Batastini2011}{}
Batastini, A. B., Hunt, E., Present-Koller, J., \& DeMatteo, D. (2011).
Federal standards for community registration of juvenile sex offenders:
An evaluation of risk prediction and future implications.
\emph{Psychology, Public Policy, and Law}, \emph{17}(3), 451--474.
doi:\href{https://doi.org/10.1037/a0023637}{10.1037/a0023637}

\hypertarget{ref-Bate2012}{}
Bate, S., \& Cook, S. J. (2012). Covert recognition relies on affective
valence in developmental prosopagnosia: evidence from the skin
conductance response. \emph{Neuropsychology}, \emph{26}(5), 670--4.
doi:\href{https://doi.org/10.1037/a0029443}{10.1037/a0029443}

\hypertarget{ref-Batterink2017}{}
Batterink, L. J. (2017). Rapid statistical learning supporting word
extraction from continuous speech. \emph{Psychological Science},
\emph{28}(7), 921--928.
doi:\href{https://doi.org/10.1177/0956797617698226}{10.1177/0956797617698226}

\hypertarget{ref-Bauer2016}{}
Bauer, D. J. (2017). A more general model for testing measurement
invariance and differential item functioning. \emph{Psychological
Methods}, \emph{22}(3), 507--526.
doi:\href{https://doi.org/10.1037/met0000077}{10.1037/met0000077}

\hypertarget{ref-Bauer2009}{}
Bauer, D. J., \& Hussong, A. M. (2009). Psychometric approaches for
developing commensurate measures across independent studies: Traditional
and new models. \emph{Psychological Methods}, \emph{14}(2), 101--125.
doi:\href{https://doi.org/10.1037/a0015583}{10.1037/a0015583}

\hypertarget{ref-Bauer2012}{}
Bauer, P. J., Doydum, A. O., Pathman, T., Larkina, M., Güler, O. E., \&
Burch, M. (2012). It's all about location, location, location:
Children's memory for the `` where'' of personally experienced events.
\emph{Journal of Experimental Child Psychology}, \emph{113}(4),
510--522.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.007}{10.1016/j.jecp.2012.06.007}

\hypertarget{ref-Baumann2017}{}
Baumann, S., Gaertner, B., Haberecht, K., Meyer, C., Rumpf, H.-J., John,
U., \& Freyer-Adam, J. (2017). Does impaired mental health interfere
with the outcome of brief alcohol intervention at general hospitals?
\emph{Journal of Consulting and Clinical Psychology}, \emph{85}(6),
562--573.
doi:\href{https://doi.org/10.1037/ccp0000201}{10.1037/ccp0000201}

\hypertarget{ref-VanBavel2017}{}
Bavel, R. V., Esposito, G., Baranowski, T., Duch-Brown, N., Bavel, R.
van, Esposito, G., \ldots{} Duch-Brown, N. (2017). Tracing How Normative
Messages May Influence Physical Activity Intention. \emph{Journal of
Sport and Exercise Psychology}, \emph{39}(2), 89--96.
doi:\href{https://doi.org/10.1123/jsep.2016-0149}{10.1123/jsep.2016-0149}

\hypertarget{ref-Beaton2016}{}
Beaton, D., Dunlop, J., Initiative, A. D. N., \& Abdi, H. (2016).
Partial least squares correspondence analysis: A framework to
simultaneously analyze behavioral and genetic data. \emph{Psychological
Methods}, \emph{21}(4), 621--651.
doi:\href{https://doi.org/10.1037/met0000053}{10.1037/met0000053}

\hypertarget{ref-Beck2012}{}
Beck, J. W., \& Schmidt, A. M. (2012). Taken out of context? Cross-level
effects of between-person self-efficacy and difficulty on the
within-person relationship of self-efficacy with resource allocation and
performance. \emph{Organizational Behavior and Human Decision
Processes}, \emph{119}(2), 195--208.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.06.009}{10.1016/j.obhdp.2012.06.009}

\hypertarget{ref-Becker2012}{}
Becker, J. C. (2012). The system-stabilizing role of identity management
strategies: Social creativity can undermine collective action for social
change. \emph{Journal of Personality and Social Psychology},
\emph{103}(4), 647--662.
doi:\href{https://doi.org/10.1037/a0029240}{10.1037/a0029240}

\hypertarget{ref-Bell2012}{}
Bell, R., Buchner, A., Kroneisen, M., \& Giang, T. (2012). On the
flexibility of social source memory: A test of the emotional incongruity
hypothesis. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{38}(6), 1512--1529.
doi:\href{https://doi.org/10.1037/a0028219}{10.1037/a0028219}

\hypertarget{ref-Bell2012a}{}
Bell, R., Röer, J. P., Dentale, S., \& Buchner, A. (2012). Habituation
of the irrelevant sound effect: Evidence for an attentional theory of
short-term memory disruption. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{38}(6), 1542--1557.
doi:\href{https://doi.org/10.1037/a0028459}{10.1037/a0028459}

\hypertarget{ref-Belojevic2012}{}
Belojevic, G., Evans, G. W., Paunovic, K., \& Jakovljevic, B. (2012).
Traffic noise and executive functioning in urban primary school
children: The moderating role of gender. \emph{Journal of Environmental
Psychology}, \emph{32}(4), 337--341.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.05.005}{10.1016/j.jenvp.2012.05.005}

\hypertarget{ref-Benenson2012}{}
Benenson, J. F., Quinn, A., \& Stella, S. (2012). Boys affiliate more
than girls with a familiar same-sex peer. \emph{Journal of Experimental
Child Psychology}, \emph{113}(4), 587--593.
doi:\href{https://doi.org/10.1016/j.jecp.2012.08.003}{10.1016/j.jecp.2012.08.003}

\hypertarget{ref-Benjamin2017}{}
Benjamin, D., Por, H.-H., \& Budescu, D. (2017). Climate change versus
global warming: Who is susceptible to the framing of climate change?
\emph{Environment and Behavior}, \emph{49}(7), 745--770.
doi:\href{https://doi.org/10.1177/0013916516664382}{10.1177/0013916516664382}

\hypertarget{ref-BennebroekEvertsz2017a}{}
Bennebroek Evertsz', F., Sprangers, M. A. G., Sitnikova, K., Stokkers,
P. C. F., Ponsioen, C. Y., Bartelsman, J. F. W. M., \ldots{} Bockting,
C. L. H. (2017). Effectiveness of cognitive--behavioral therapy on
quality of life, anxiety, and depressive symptoms among patients with
inflammatory bowel disease: A multicenter randomized controlled trial.
\emph{Journal of Consulting and Clinical Psychology}, \emph{85}(9),
918--925.
doi:\href{https://doi.org/10.1037/ccp0000227}{10.1037/ccp0000227}

\hypertarget{ref-Benoit2017}{}
Benoit, S., Rouleau, I., Langlois, R., Dostie, V., Kergoat, M.-j., \&
Joubert, S. (2017). The impact of time and repeated exposure on famous
person knowledge in amnestic mild cognitive impairment and Alzheimer's
Disease. \emph{Neuropsychology}, \emph{31}(7), 697--707.
doi:\href{https://doi.org/10.1037/neu0000387}{10.1037/neu0000387}

\hypertarget{ref-Benson2017}{}
Benson, A. J., \& Eys, M. (2017). Understanding the consequences of
newcomer integration processes: The sport team socialization tactics
questionnaire. \emph{Journal of Sport and Exercise Psychology},
\emph{39}(1), 13--28.
doi:\href{https://doi.org/10.1123/jsep.2016-0182}{10.1123/jsep.2016-0182}

\hypertarget{ref-Bentley2017}{}
Bentley, K. H., Nock, M. K., Sauer-Zavala, S., Gorman, B. S., \& Barlow,
D. H. (2017). A functional analysis of two transdiagnostic,
emotion-focused interventions on nonsuicidal self-injury. \emph{Journal
of Consulting and Clinical Psychology}, \emph{85}(6), 632--646.
doi:\href{https://doi.org/10.1037/ccp0000205}{10.1037/ccp0000205}

\hypertarget{ref-VandenBerg2017}{}
Berg, A. E. van den, Wesselius, J. E., Maas, J., \& Tanja-Dijkstra, K.
(2017). Green walls for a restorative classroom environment: A
controlled evaluation study. \emph{Environment and Behavior},
\emph{49}(7), 791--813.
doi:\href{https://doi.org/10.1177/0013916516667976}{10.1177/0013916516667976}

\hypertarget{ref-Berggren2016}{}
Berggren, N., Curtis, H. M., \& Derakshan, N. (2017). Interactions of
emotion and anxiety on visual working memory performance.
\emph{Psychonomic Bulletin \& Review}, \emph{24}(4), 1274--1281.
doi:\href{https://doi.org/10.3758/s13423-016-1213-4}{10.3758/s13423-016-1213-4}

\hypertarget{ref-Berman2017}{}
Berman, M. E., Fanning, J. R., Guillot, C. R., Marsic, A., Bullock, J.,
Nadorff, M. R., \& McCloskey, M. S. (2017). Effect of alcohol dose on
deliberate self-harm in men and women. \emph{Journal of Consulting and
Clinical Psychology}, \emph{85}(9), 854--861.
doi:\href{https://doi.org/10.1037/ccp0000222}{10.1037/ccp0000222}

\hypertarget{ref-Bernacki2012}{}
Bernacki, M. L., Byrnes, J. P., \& Cromley, J. G. (2012). The effects of
achievement goals and self-regulated learning behaviors on reading
comprehension in technology-enhanced learning environments.
\emph{Contemporary Educational Psychology}, \emph{37}(2), 148--161.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.12.001}{10.1016/j.cedpsych.2011.12.001}

\hypertarget{ref-Bernard2017}{}
Bernard, D. L., Lige, Q. M., Willis, H. A., Sosoo, E. E., \& Neblett, E.
W. (2017). Impostor phenomenon and mental health: The influence of
racial discrimination and gender. \emph{Journal of Counseling
Psychology}, \emph{64}(2), 155--166.
doi:\href{https://doi.org/10.1037/cou0000197}{10.1037/cou0000197}

\hypertarget{ref-Berntsen2012}{}
Berntsen, D., Johannessen, K. B., Thomsen, Y. D., Bertelsen, M., Hoyle,
R. H., \& Rubin, D. C. (2012). Peace and war. \emph{Psychological
Science}, \emph{23}(12), 1557--1565.
doi:\href{https://doi.org/10.1177/0956797612457389}{10.1177/0956797612457389}

\hypertarget{ref-Berry2012}{}
Berry, T. D., Fournier, A. K., \& Porter, B. E. (2012). Developing and
testing a touch-path model for hand hygiene and pathogen risk.
\emph{Environment and Behavior}, \emph{44}(4), 451--473.
doi:\href{https://doi.org/10.1177/0013916510395729}{10.1177/0013916510395729}

\hypertarget{ref-Berry2016}{}
Berry, T. R., Rodgers, W. M., Markland, D., \& Hall, C. R. (2016).
Moderators of implicit--explicit exercise cognition concordance.
\emph{Journal of Sport and Exercise Psychology}, \emph{38}(6), 579--589.
doi:\href{https://doi.org/10.1123/jsep.2016-0174}{10.1123/jsep.2016-0174}

\hypertarget{ref-Best2012}{}
Best, J. R., Theim, K. R., Gredysa, D. M., Stein, R. I., Welch, R. R.,
Saelens, B. E., \ldots{} Wilfley, D. E. (2012). Behavioral economic
predictors of overweight children's weight loss. \emph{Journal of
Consulting and Clinical Psychology}, \emph{80}(6), 1086--1096.
doi:\href{https://doi.org/10.1037/a0029827}{10.1037/a0029827}

\hypertarget{ref-Bestgen2012}{}
Bestgen, Y., \& Vincze, N. (2012). Checking and bootstrapping lexical
norms by means of word similarity indexes. \emph{Behavior Research
Methods}, \emph{44}(4), 998--1006.
doi:\href{https://doi.org/10.3758/s13428-012-0195-z}{10.3758/s13428-012-0195-z}

\hypertarget{ref-Bhargava2017}{}
Bhargava, S., Bámaca-Colbert, M. Y., Witherspoon, D. P., Pomerantz, E.
M., \& Robins, R. W. (2017). Examining socio-cultural and neighborhood
factors associated with trajectories of Mexican-origin mothers'
education-related involvement. \emph{Journal of Youth and Adolescence},
\emph{46}(8), 1789--1804.
doi:\href{https://doi.org/10.1007/s10964-016-0628-6}{10.1007/s10964-016-0628-6}

\hypertarget{ref-Bhatia2017}{}
Bhatia, S. (2017). Comparing theories of reference-dependent choice.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(9), 1490--1507.
doi:\href{https://doi.org/10.1037/xlm0000384}{10.1037/xlm0000384}

\hypertarget{ref-Bilgin2012}{}
Bilgin, B. (2012). Losses loom more likely than gains: Propensity to
imagine losses increases their subjective probability.
\emph{Organizational Behavior and Human Decision Processes},
\emph{118}(2), 203--215.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.03.008}{10.1016/j.obhdp.2012.03.008}

\hypertarget{ref-Bissell-Havran2012}{}
Bissell-Havran, J. M., Loken, E., \& McHale, S. M. (2012). Mothers'
differential treatment of adolescent siblings: Predicting college
attendance of sisters versus brothers. \emph{Journal of Youth and
Adolescence}, \emph{41}(10), 1267--1279.
doi:\href{https://doi.org/10.1007/s10964-011-9727-6}{10.1007/s10964-011-9727-6}

\hypertarget{ref-Bitan2017}{}
Bitan, T., Kaftory, A., Meiri-Leib, A., Eviatar, Z., \& Peleg, O.
(2017). Phonological ambiguity modulates resolution of semantic
ambiguity during reading: An fMRI study of Hebrew.
\emph{Neuropsychology}, \emph{31}(7), 759--777.
doi:\href{https://doi.org/10.1037/neu0000357}{10.1037/neu0000357}

\hypertarget{ref-Bjornsdottir2017}{}
Bjornsdottir, R. T., \& Rule, N. O. (2017). The visibility of social
class from facial cues. \emph{Journal of Personality and Social
Psychology}, \emph{113}(4), 530--546.
doi:\href{https://doi.org/10.1037/pspa0000091}{10.1037/pspa0000091}

\hypertarget{ref-Blakely-McClure2018}{}
Blakely-McClure, S. J., \& Ostrov, J. M. (2018). Examining co-occurring
and pure relational and physical victimization in early childhood.
\emph{Journal of Experimental Child Psychology}, \emph{166}, 1--16.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.011}{10.1016/j.jecp.2017.07.011}

\hypertarget{ref-Blankenship}{}
Blankenship, K. L., Wegener, D. T., \& Murray, R. A. (2012).
Circumventing resistance: Using values to indirectly change attitudes.
\emph{Journal of Personality and Social Psychology}, \emph{103}(4),
606--621. doi:\href{https://doi.org/10.1037/a0029226}{10.1037/a0029226}

\hypertarget{ref-Block}{}
Block, S. D., Shestowsky, D., Segovia, D. A., Goodman, G. S., Schaaf, J.
M., \& Alexander, K. W. (2012). ``That never happened'': Adults'
discernment of children's true and false memory reports. \emph{Law and
Human Behavior}, \emph{36}(5), 365--374.
doi:\href{https://doi.org/10.1037/h0093920}{10.1037/h0093920}

\hypertarget{ref-Boarnet2011}{}
Boarnet, M. G., Forsyth, A., Day, K., \& Oakes, J. M. (2011). The street
level built environment and physical activity and walking.
\emph{Environment and Behavior}, \emph{43}(6), 735--775.
doi:\href{https://doi.org/10.1177/0013916510379760}{10.1177/0013916510379760}

\hypertarget{ref-Boccaccini2017}{}
Boccaccini, M. T., Rice, A. K., Helmus, L. M., Murrie, D. C., \& Harris,
P. B. (2017). Field validity of Static-99/R scores in a statewide sample
of 34,687 convicted sexual offenders. \emph{Psychological Assessment},
\emph{29}(6), 611--623.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/pas0000377}{http://dx.doi.org/10.1037/pas0000377}

\hypertarget{ref-Boccaccini2011}{}
Boccaccini, M. T., Turner, D. B., Murrie, D. C., \& Rufino, K. A.
(2012). Do PCL-R scores from state or defense experts best predict
future misconduct among civilly committed sex offenders? \emph{Law and
Human Behavior}, \emph{36}(3), 159--169.
doi:\href{https://doi.org/10.1037/h0093949}{10.1037/h0093949}

\hypertarget{ref-Bodner2012}{}
Bodner, G. E., \& Taikh, A. (2012). Reassessing the basis of the
production effect in memory. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{38}(6), 1711--1719.
doi:\href{https://doi.org/10.1037/a0028466}{10.1037/a0028466}

\hypertarget{ref-Boehme2017}{}
Boehme, K. L., Goetz, T., \& Preckel, F. (2017). Is it good to value
math? Investigating mothers' impact on their children's test anxiety
based on control-value theory. \emph{Contemporary Educational
Psychology}, \emph{51}, 11--21.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.05.002}{10.1016/j.cedpsych.2017.05.002}

\hypertarget{ref-Bol2012}{}
Bol, L., Hacker, D. J., Walck, C. C., \& Nunnery, J. A. (2012). The
effects of individual or group guidelines on the calibration accuracy
and achievement of high school biology students. \emph{Contemporary
Educational Psychology}, \emph{37}(4), 280--287.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.02.004}{10.1016/j.cedpsych.2012.02.004}

\hypertarget{ref-BomanIV2012}{}
Boman, J. H., Krohn, M. D., Gibson, C. L., \& Stogner, J. M. (2012).
Investigating friendship quality: An exploration of self-control and
social control theories' friendship hypotheses. \emph{Journal of Youth
and Adolescence}, \emph{41}(11), 1526--1540.
doi:\href{https://doi.org/10.1007/s10964-012-9747-x}{10.1007/s10964-012-9747-x}

\hypertarget{ref-Bonache2017}{}
Bonache, H., Gonzalez-Mendez, R., \& Krahé, B. (2017). Romantic
attachment, conflict resolution styles, and teen dating violence
victimization. \emph{Journal of Youth and Adolescence}, \emph{46}(9),
1905--1917.
doi:\href{https://doi.org/10.1007/s10964-017-0635-2}{10.1007/s10964-017-0635-2}

\hypertarget{ref-Bonawitz2012}{}
Bonawitz, E. B., Schijndel, T. J. P. van, Friel, D., \& Schulz, L.
(2012). Children balance theories and evidence in exploration,
explanation, and learning. \emph{Cognitive Psychology}, \emph{64}(4),
215--234.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.12.002}{10.1016/j.cogpsych.2011.12.002}

\hypertarget{ref-Bonin2012}{}
Bonin, P., Roux, S., Barry, C., \& Canell, L. (2012). Evidence for a
limited-cascading account of written word naming. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{38}(6),
1741--1758.
doi:\href{https://doi.org/10.1037/a0028471}{10.1037/a0028471}

\hypertarget{ref-Boone2017}{}
Boone, A. P., \& Hegarty, M. (2017). Sex differences in mental rotation
tasks: Not just in the mental rotation process! \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{43}(7),
1005--1019.
doi:\href{https://doi.org/10.1037/xlm0000370}{10.1037/xlm0000370}

\hypertarget{ref-Booth2012}{}
Booth, J. L., \& Newton, K. J. (2012). Fractions: Could they really be
the gatekeeper's doorman? \emph{Contemporary Educational Psychology},
\emph{37}(4), 247--253.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.07.001}{10.1016/j.cedpsych.2012.07.001}

\hypertarget{ref-Borghuis2017}{}
Borghuis, J., Denissen, J. J. A., Oberski, D., Sijtsma, K., Meeus, W. H.
J., Branje, S., \ldots{} Bleidorn, W. (2017). Big Five personality
stability, change, and codevelopment across adolescence and early
adulthood. \emph{Journal of Personality and Social Psychology},
\emph{113}(4), 641--657.
doi:\href{https://doi.org/10.1037/pspp0000138}{10.1037/pspp0000138}

\hypertarget{ref-Borhani2017}{}
Borhani, K., Beck, B., \& Haggard, P. (2017). Choosing, doing, and
controlling: Implicit sense of agency over somatosensory events.
\emph{Psychological Science}, \emph{28}(7), 882--893.
doi:\href{https://doi.org/10.1177/0956797617697693}{10.1177/0956797617697693}

\hypertarget{ref-Bornstein2013}{}
Bornstein, B. H., Tomkins, A. J., Neeley, E. M., Herian, M. N., \& Hamm,
J. A. (2013). Reducing courts' failure-to-appear rate by written
reminders. \emph{Psychology, Public Policy, and Law}, \emph{19}(1),
70--80. doi:\href{https://doi.org/10.1037/a0026293}{10.1037/a0026293}

\hypertarget{ref-Borra2012}{}
Borra, T., Hooge, I. T. C., \& Verstraten, F. A. J. (2012). Orientation
perception of occluded objects is based on perceptually completed
objects. \emph{Psychological Science}, \emph{23}(11), 1303--1305.
doi:\href{https://doi.org/10.1177/0956797612446951}{10.1177/0956797612446951}

\hypertarget{ref-Borsari2012}{}
Borsari, B., Hustad, J. T. P., Mastroleo, N. R., Tevyaw, T. O., Barnett,
N. P., Kahler, C. W., \ldots{} Monti, P. M. (2012). Addressing alcohol
use and problems in mandated college students: A randomized clinical
trial using stepped care. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(6), 1062--1074.
doi:\href{https://doi.org/10.1037/a0029902}{10.1037/a0029902}

\hypertarget{ref-Bosker2017}{}
Bosker, H. R. (2017). How our own speech rate influences our perception
of others. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{43}(8), 1225--1238.
doi:\href{https://doi.org/10.1037/xlm0000381}{10.1037/xlm0000381}

\hypertarget{ref-Boswell2017a}{}
Boswell, J. F., Cain, N. M., Oswald, J. M., McAleavey, A. A., \&
Adelman, R. (2017). Interpersonal pathoplasticity and trajectories of
change in routine adolescent and young adult residential substance abuse
treatment. \emph{Journal of Consulting and Clinical Psychology},
\emph{85}(7), 676--688.
doi:\href{https://doi.org/10.1037/ccp0000219}{10.1037/ccp0000219}

\hypertarget{ref-Boswell2012}{}
Boswell, J. F., McAleavey, A. A., Castonguay, L. G., Hayes, J. A., \&
Locke, B. D. (2012). Previous mental health service utilization and
change in clients' depressive symptoms. \emph{Journal of Counseling
Psychology}, \emph{59}(3), 368--378.
doi:\href{https://doi.org/10.1037/a0028078}{10.1037/a0028078}

\hypertarget{ref-Botetzagias2012}{}
Botetzagias, I., \& Schuur, W. van. (2012). Active greens.
\emph{Environment and Behavior}, \emph{44}(4), 509--544.
doi:\href{https://doi.org/10.1177/0013916510393278}{10.1177/0013916510393278}

\hypertarget{ref-Bottiani2017}{}
Bottiani, J. H., Bradshaw, C. P., \& Mendelson, T. (2017). A multilevel
examination of racial disparities in high school discipline: Black and
white adolescents' perceived equity, school belonging, and adjustment
problems. \emph{Journal of Educational Psychology}, \emph{109}(4),
532--545.
doi:\href{https://doi.org/10.1037/edu0000155}{10.1037/edu0000155}

\hypertarget{ref-Boucard2012}{}
Boucard, G. K., Albinet, C. T., Bugaiska, A., Bouquet, C. a, Clarys, D.,
\& Audiffren, M. (2012). Impact of physical activity on executive
functions in aging: A selective effect on inhibition among old adults.
\emph{Journal of Sport and Exercise Psychology}, \emph{34}(6), 808--827.
doi:\href{https://doi.org/10.1123/jsep.34.6.808}{10.1123/jsep.34.6.808}

\hypertarget{ref-Boulton2012}{}
Boulton, M. J. (2012). Children's hostile attribution bias is reduced
after watching realistic playful fighting, and the effect is mediated by
prosocial thoughts. \emph{Journal of Experimental Child Psychology},
\emph{113}(1), 36--48.
doi:\href{https://doi.org/10.1016/j.jecp.2012.02.011}{10.1016/j.jecp.2012.02.011}

\hypertarget{ref-Bourque2012}{}
Bourque, L. B., Mileti, D. S., Kano, M., \& Wood, M. M. (2012). Who
prepares for terrorism? \emph{Environment and Behavior}, \emph{44}(3),
374--409.
doi:\href{https://doi.org/10.1177/0013916510390318}{10.1177/0013916510390318}

\hypertarget{ref-Bowler2012}{}
Bowler, J. O., Mackintosh, B., Dunn, B. D., Mathews, A., Dalgleish, T.,
\& Hoppitt, L. (2012). A comparison of cognitive bias modification for
interpretation and computerized cognitive behavior therapy: Effects on
anxiety, depression, attentional control, and interpretive bias.
\emph{Journal of Consulting and Clinical Psychology}, \emph{80}(6),
1021--1033.
doi:\href{https://doi.org/10.1037/a0029932}{10.1037/a0029932}

\hypertarget{ref-Bockenholt2017}{}
Böckenholt, U. (2017). Measuring response styles in Likert items.
\emph{Psychological Methods}, \emph{22}(1), 69--83.
doi:\href{https://doi.org/10.1037/met0000106}{10.1037/met0000106}

\hypertarget{ref-Bramston2011}{}
Bramston, P., Pretty, G., \& Zammit, C. (2011). Assessing Environmental
Stewardship Motivation. \emph{Environment and Behavior}, \emph{43}(6),
776--788.
doi:\href{https://doi.org/10.1177/0013916510382875}{10.1177/0013916510382875}

\hypertarget{ref-Brandenburg2017}{}
Brandenburg, J., Klesczewski, J., Schuchardt, K., Fischbach, A.,
Büttner, G., \& Hasselhorn, M. (2017). Phonological processing in
children with specific reading disorder versus typical learners: Factor
structure and measurement invariance in a transparent orthography.
\emph{Journal of Educational Psychology}, \emph{109}(5), 709--726.
doi:\href{https://doi.org/10.1037/edu0000162}{10.1037/edu0000162}

\hypertarget{ref-Brank2011}{}
Brank, E. M., Greene, E., \& Hochevar, K. (2011). Holding parents
responsible: Is vicarious responsibility the public's answer to juvenile
crime? \emph{Psychology, Public Policy, and Law}, \emph{17}(4),
507--529. doi:\href{https://doi.org/10.1037/a0024566}{10.1037/a0024566}

\hypertarget{ref-Brankaer2016}{}
Brankaer, C., Ghesquière, P., \& De Smedt, B. (2017). Symbolic magnitude
processing in elementary school children: A group administered
paper-and-pencil measure (SYMP Test). \emph{Behavior Research Methods},
\emph{49}(4), 1361--1373.
doi:\href{https://doi.org/10.3758/s13428-016-0792-3}{10.3758/s13428-016-0792-3}

\hypertarget{ref-Brascamp2017a}{}
Brascamp, J. W., \& Naber, M. (2017). Eye tracking under dichoptic
viewing conditions: a practical solution. \emph{Behavior Research
Methods}, \emph{49}(4), 1303--1309.
doi:\href{https://doi.org/10.3758/s13428-016-0805-2}{10.3758/s13428-016-0805-2}

\hypertarget{ref-Braver2011}{}
Braver, S. L., Ellman, I. M., Votruba, A. M., \& Fabricius, W. V.
(2011). Lay judgments about child custody after divorce.
\emph{Psychology, Public Policy, and Law}, \emph{17}(2), 212--240.
doi:\href{https://doi.org/10.1037/a0023194}{10.1037/a0023194}

\hypertarget{ref-Breetzke2012}{}
Breetzke, G. D., \& Cohn, E. G. (2012). Seasonal assault and
neighborhood deprivation in South Africa. \emph{Environment and
Behavior}, \emph{44}(5), 641--667.
doi:\href{https://doi.org/10.1177/0013916510397758}{10.1177/0013916510397758}

\hypertarget{ref-Brewer2017}{}
Brewer, B. W., Cornelius, A. E., Van Raalte, J. L., \& Tennen, H.
(2017). Adversarial growth after anterior cruciate ligament
reconstruction. \emph{Journal of Sport and Exercise Psychology},
\emph{39}(2), 134--144.
doi:\href{https://doi.org/10.1123/jsep.2016-0210}{10.1123/jsep.2016-0210}

\hypertarget{ref-TenBrinke2012}{}
Brinke, L. ten, \& Porter, S. (2012). Cry me a river: Identifying the
behavioral consequences of extremely high-stakes interpersonal
deception. \emph{Law and Human Behavior}, \emph{36}(6), 469--477.
doi:\href{https://doi.org/10.1037/h0093929}{10.1037/h0093929}

\hypertarget{ref-Britton2012}{}
Britton, P. C., Conner, K. R., \& Maisto, S. A. (2012). An open trial of
motivational interviewing to address suicidal ideation with hospitalized
veterans. \emph{Journal of Clinical Psychology}, \emph{68}(9), 961--971.
doi:\href{https://doi.org/10.1002/jclp.21885}{10.1002/jclp.21885}

\hypertarget{ref-Brod2017}{}
Brod, G., Bunge, S. A., \& Shing, Y. L. (2017). Does one year of
schooling improve children's cognitive control and alter associated
brain activation? \emph{Psychological Science}, \emph{28}(7), 967--978.
doi:\href{https://doi.org/10.1177/0956797617699838}{10.1177/0956797617699838}

\hypertarget{ref-Brodeur2012}{}
Brodeur, M. B., Kehayia, E., Dion-Lessard, G., Chauret, M., Montreuil,
T., Dionne-Dostie, E., \& Lepage, M. (2012). The bank of standardized
stimuli (BOSS): comparison between French and English norms.
\emph{Behavior Research Methods}, \emph{44}(4), 961--970.
doi:\href{https://doi.org/10.3758/s13428-011-0184-7}{10.3758/s13428-011-0184-7}

\hypertarget{ref-VandenBroek2017}{}
Broek, K. van den, Bolderdijk, J. W., \& Steg, L. (2017). Individual
differences in values determine the relative persuasiveness of
biospheric, economic and combined appeals. \emph{Journal of
Environmental Psychology}, \emph{53}, 145--156.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.07.009}{10.1016/j.jenvp.2017.07.009}

\hypertarget{ref-Brown2012}{}
Brown, D. A., Lewis, C. N., Lamb, M. E., \& Stephens, E. (2012). The
influences of delay and severity of intellectual disability on event
memory in children. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(5), 829--841.
doi:\href{https://doi.org/10.1037/a0029388}{10.1037/a0029388}

\hypertarget{ref-Brown2016}{}
Brown, H., \& Maylor, E. A. (2017). Memory consolidation effects on
memory stabilization and item integration in older adults.
\emph{Psychonomic Bulletin \& Review}, \emph{24}(4), 1032--1039.
doi:\href{https://doi.org/10.3758/s13423-016-1197-0}{10.3758/s13423-016-1197-0}

\hypertarget{ref-Brown2012a}{}
Brown, M. M., Bell, D. S., Jason, L. A., Christos, C., \& Bell, D. E.
(2012). Understanding long-term outcomes of chronic fatigue syndrome.
\emph{Journal of Clinical Psychology}, \emph{68}(9), 1028--1035.
doi:\href{https://doi.org/10.1002/jclp.21880}{10.1002/jclp.21880}

\hypertarget{ref-Brown2011}{}
Brown, M., Ruel, E., \& Medley-Rath, S. (2011). High school students'
attitudes toward providing girls opportunities to participate in sport.
\emph{Sociology of Sport Journal}, \emph{28}(2), 239--253.
doi:\href{https://doi.org/10.1123/ssj.28.2.239}{10.1123/ssj.28.2.239}

\hypertarget{ref-Brubacher2011}{}
Brubacher, S. P., Roberts, K. P., \& Powell, M. (2011). Effects of
practicing episodic versus scripted recall on children's subsequent
narratives of a repeated event. \emph{Psychology, Public Policy, and
Law}, \emph{17}(2), 286--314.
doi:\href{https://doi.org/10.1037/a0022793}{10.1037/a0022793}

\hypertarget{ref-Brunet2011}{}
Brunet, J., \& Sabiston, C. M. (2011). Self-presentation and physical
activity in breast cancer survivors: the moderating effect of social
cognitive constructs. \emph{J Sport Exerc Psychol}, \emph{33}(6),
759--778. Retrieved from
\url{http://www.ncbi.nlm.nih.gov/pubmed/22262704}

\hypertarget{ref-Brunet2016}{}
Brunet, J.-F., Dagenais, D., Therrien, M., Gartenberg, D., \& Forest, G.
(2017). Validation of sleep-2-Peak: A smartphone application that can
detect fatigue-related changes in reaction times during sleep
deprivation. \emph{Behavior Research Methods}, \emph{49}(4), 1460--1469.
doi:\href{https://doi.org/10.3758/s13428-016-0802-5}{10.3758/s13428-016-0802-5}

\hypertarget{ref-Brunye2012}{}
Brunyé, T. T., Andonova, E., Meneghetti, C., Noordzij, M. L., Pazzaglia,
F., Wienemann, R., \ldots{} Taylor, H. A. (2012). Planning routes around
the world: International evidence for southern route preferences.
\emph{Journal of Environmental Psychology}, \emph{32}(4), 297--304.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.05.003}{10.1016/j.jenvp.2012.05.003}

\hypertarget{ref-Brust-Renck2016}{}
Brust-Renck, P. G., Reyna, V. F., Wilhelms, E. A., Wolfe, C. R., Widmer,
C. L., Cedillos-Whynott, E. M., \& Morant, A. K. (2017). Active
engagement in a web-based tutorial to prevent obesity grounded in
Fuzzy-Trace Theory predicts higher knowledge and gist comprehension.
\emph{Behavior Research Methods}, \emph{49}(4), 1386--1398.
doi:\href{https://doi.org/10.3758/s13428-016-0794-1}{10.3758/s13428-016-0794-1}

\hypertarget{ref-Buckler2017}{}
Buckler, H., Oczak-Arsic, S., Siddiqui, N., \& Johnson, E. K. (2017).
Input matters: Speed of word recognition in 2-year-olds exposed to
multiple accents. \emph{Journal of Experimental Child Psychology},
\emph{164}, 87--100.
doi:\href{https://doi.org/10.1016/j.jecp.2017.06.017}{10.1016/j.jecp.2017.06.017}

\hypertarget{ref-Budge2017}{}
Budge, S. L., Chin, M. Y., \& Minero, L. P. (2017). Trans individuals'
facilitative coping: An analysis of internal and external processes.
\emph{Journal of Counseling Psychology}, \emph{64}(1), 12--25.
doi:\href{https://doi.org/10.1037/cou0000178}{10.1037/cou0000178}

\hypertarget{ref-Budge2016}{}
Budge, S. L., Thai, J. L., Tebbe, E. A., \& Howard, K. A. S. (2016). The
intersection of race, sexual orientation, socioeconomic status, trans
identity, and mental health outcomes. \emph{The Counseling
Psychologist}, \emph{44}(7), 1025--1049.
doi:\href{https://doi.org/10.1177/0011000015609046}{10.1177/0011000015609046}

\hypertarget{ref-Budhiraja2017}{}
Budhiraja, M., Savic, I., Lindner, P., Jokinen, J., Tiihonen, J., \&
Hodgins, S. (2017). Brain structure abnormalities in young women who
presented conduct disorder in childhood/adolescence. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, 869--885.
doi:\href{https://doi.org/10.3758/s13415-017-0519-7}{10.3758/s13415-017-0519-7}

\hypertarget{ref-Buehner2012}{}
Buehner, M. J. (2012). Understanding the past, predicting the future.
\emph{Psychological Science}, \emph{23}(12), 1490--1497.
doi:\href{https://doi.org/10.1177/0956797612444612}{10.1177/0956797612444612}

\hypertarget{ref-Bugg2012}{}
Bugg, J. M., \& McDaniel, M. A. (2012). Selective benefits of question
self-generation and answering for remembering expository text.
\emph{Journal of Educational Psychology}, \emph{104}(4), 922--931.
doi:\href{https://doi.org/10.1037/a0028661}{10.1037/a0028661}

\hypertarget{ref-Burgess2017}{}
Burgess, A. M., DiBartolo, P. M., \& Rendón, M. J. (2017). Can the Frost
Multidimensional Perfectionism Scale assess perfeccionismo?
\emph{Psychological Assessment}, \emph{29}(7), 857--867.
doi:\href{https://doi.org/10.1037/pas0000374}{10.1037/pas0000374}

\hypertarget{ref-Burke2017}{}
Burke, T., Sticca, F., \& Perren, S. (2017). Everything's gonna be
alright! The longitudinal interplay among social support, peer
victimization, and depressive symptoms. \emph{Journal of Youth and
Adolescence}, \emph{46}(9), 1999--2014.
doi:\href{https://doi.org/10.1007/s10964-017-0653-0}{10.1007/s10964-017-0653-0}

\hypertarget{ref-Burns2017}{}
Burns, M. D., Monteith, M. J., \& Parker, L. R. (2017). Training away
bias: The differential effects of counterstereotype training and
self-regulation on stereotype activation and application. \emph{Journal
of Experimental Social Psychology}, \emph{73}, 97--110.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.003}{10.1016/j.jesp.2017.06.003}

\hypertarget{ref-Busler2017}{}
Busler, J. N., \& Lazarte, A. A. (2017). Reading time allocation
strategies and working memory using rapid serial visual presentation.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(9), 1375--1386.
doi:\href{https://doi.org/10.1037/xlm0000392}{10.1037/xlm0000392}

\hypertarget{ref-Busscher2017}{}
Busscher, B., \& Spinhoven, P. (2017). Cognitive coping as a mechanism
of change in cognitive-behavioral therapy for fear of flying: A
longitudinal study with 3-year follow-up. \emph{Journal of Clinical
Psychology}, \emph{73}(9), 1064--1075.
doi:\href{https://doi.org/10.1002/jclp.22424}{10.1002/jclp.22424}

\hypertarget{ref-Butcher2012}{}
Butcher, P. R., Bouma, A., Stremmelaar, E. F., Bos, A. F., Smithson, M.,
\& Van Braeckel, K. N. J. A. (2012). Visuospatial perception in children
born preterm with no major neurological disorders.
\emph{Neuropsychology}, \emph{26}(6), 723--734.
doi:\href{https://doi.org/10.1037/a0029298}{10.1037/a0029298}

\hypertarget{ref-Buxbaum}{}
Buxbaum, L. J., Dawson, A. M., \& Linsley, D. (2012). Reliability and
validity of the Virtual Reality Lateralized Attention Test in assessing
hemispatial neglect in right-hemisphere stroke. \emph{Neuropsychology},
\emph{26}(4), 430--441.
doi:\href{https://doi.org/10.1037/a0028674}{10.1037/a0028674}

\hypertarget{ref-Byrka2017}{}
Byrka, K., Kaiser, F. G., \& Olko, J. (2017). Understanding the
acceptance of nature-preservation-related restrictions as the result of
the compensatory effects of environmental attitude and behavioral costs.
\emph{Environment and Behavior}, \emph{49}(5), 487--508.
doi:\href{https://doi.org/10.1177/0013916516653638}{10.1177/0013916516653638}

\hypertarget{ref-Callahan2013}{}
Callahan, L., Steadman, H. J., Tillman, S., \& Vesselinov, R. (2013). A
multi-site study of the use of sanctions and incentives in mental health
courts. \emph{Law and Human Behavior}, \emph{37}(1), 1--9.
doi:\href{https://doi.org/10.1037/h0093989}{10.1037/h0093989}

\hypertarget{ref-Callan2012}{}
Callan, M. J., Dawtry, R. J., \& Olson, J. M. (2012). Justice motive
effects in ageism: The effects of a victim's age on observer perceptions
of injustice and punishment judgments. \emph{Journal of Experimental
Social Psychology}, \emph{48}(6), 1343--1349.
doi:\href{https://doi.org/10.1016/j.jesp.2012.07.003}{10.1016/j.jesp.2012.07.003}

\hypertarget{ref-Callow2017a}{}
Callow, N., Jiang, D., Roberts, R., \& Edwards, M. G. (2017).
Kinesthetic imagery provides additive benefits to internal visual
imagery on slalom task performance. \emph{Journal of Sport and Exercise
Psychology}, \emph{39}(1), 81--86.
doi:\href{https://doi.org/10.1123/jsep.2016-0168}{10.1123/jsep.2016-0168}

\hypertarget{ref-Campbell2012}{}
Campbell, J. I. D., \& Dowd, R. R. (2012). Interoperation transfer in
Chinese--English bilinguals' arithmetic. \emph{Psychonomic Bulletin \&
Review}, \emph{19}(5), 948--954.
doi:\href{https://doi.org/10.3758/s13423-012-0277-z}{10.3758/s13423-012-0277-z}

\hypertarget{ref-Cantone2017}{}
Cantone, J. A., \& Wiener, R. L. (2017). Religion at work: Evaluating
hostile work environment religious discrimination claims.
\emph{Psychology, Public Policy, and Law}, \emph{23}(3), 351--366.
doi:\href{https://doi.org/10.1037/law0000132}{10.1037/law0000132}

\hypertarget{ref-Caperello2012}{}
Caperello, N. D., \& Kurani, K. S. (2012). Households' stories of their
encounters with a plug-in hybrid electric vehicle. \emph{Environment and
Behavior}, \emph{44}(4), 493--508.
doi:\href{https://doi.org/10.1177/0013916511402057}{10.1177/0013916511402057}

\hypertarget{ref-Carfora2017}{}
Carfora, V., Caso, D., Sparks, P., \& Conner, M. (2017). Moderating
effects of pro-environmental self-identity on pro-environmental
intentions and behaviour: A multi-behaviour study. \emph{Journal of
Environmental Psychology}, \emph{53}, 92--99.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.07.001}{10.1016/j.jenvp.2017.07.001}

\hypertarget{ref-Carlson2011}{}
Carlson, D. S., Ferguson, M., Perrewé, P. L., \& Whitten, D. (2011). The
fallout from abusive supervision: An examination of subordinates and
their partners. \emph{Personnel Psychology}, \emph{64}(4), 937--961.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01232.x}{10.1111/j.1744-6570.2011.01232.x}

\hypertarget{ref-Carr2011a}{}
Carr, E. R., \& Szymanski, D. M. (2011). Sexual objectification and
substance abuse in young adult women. \emph{The Counseling
Psychologist}, \emph{39}(1), 39--66.
doi:\href{https://doi.org/10.1177/0011000010378449}{10.1177/0011000010378449}

\hypertarget{ref-Carr2017}{}
Carr, E. W., Brady, T. F., \& Winkielman, P. (2017). Are you smiling, or
have I seen you before? Familiarity makes faces look happier.
\emph{Psychological Science}, \emph{28}(8), 1087--1102.
doi:\href{https://doi.org/10.1177/0956797617702003}{10.1177/0956797617702003}

\hypertarget{ref-Carr2016}{}
Carr, M. M., Catak, P. D., Pejsa-Reitz, M. C., Saules, K. K., \&
Gearhardt, A. N. (2017). Measurement invariance of the Yale Food
Addiction Scale 2.0 across gender and racial groups. \emph{Psychological
Assessment}, \emph{29}(8), 1044--1052.
doi:\href{https://doi.org/10.1037/pas0000403}{10.1037/pas0000403}

\hypertarget{ref-Carr2011}{}
Carr, M., Taasoobshirazi, G., Stroud, R., \& Royer, J. M. (2011).
Combined fluency and cognitive strategies instruction improves
mathematics achievement in early elementary school. \emph{Contemporary
Educational Psychology}, \emph{36}(4), 323--333.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.04.002}{10.1016/j.cedpsych.2011.04.002}

\hypertarget{ref-Carrera2017}{}
Carrera, S. G., \& Wei, M. (2017). Thwarted belongingness, perceived
burdensomeness, and depression among asian americans: A longitudinal
study of interpersonal shame as a mediator and perfectionistic family
discrepancy as a moderator. \emph{Journal of Counseling Psychology},
\emph{64}(3), 280--291.
doi:\href{https://doi.org/10.1037/cou0000199}{10.1037/cou0000199}

\hypertarget{ref-Carter2017}{}
Carter, E. R., \& Murphy, M. C. (2017). Consensus and consistency:
Exposure to multiple discrimination claims shapes whites' intergroup
attitudes. \emph{Journal of Experimental Social Psychology}, \emph{73},
24--33.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.001}{10.1016/j.jesp.2017.06.001}

\hypertarget{ref-Caruso2017}{}
Caruso, E. M., Shapira, O., \& Landy, J. F. (2017). Show me the money: A
systematic exploration of manipulations, moderators, and mechanisms of
priming effects. \emph{Psychological Science}, \emph{28}(8), 1148--1159.
doi:\href{https://doi.org/10.1177/0956797617706161}{10.1177/0956797617706161}

\hypertarget{ref-Casado2017}{}
Casado, F., Hidalgo, M. C., \& García-Leiva, P. (2017). Energy
efficiency in households: The effectiveness of different types of
messages in advertising campaigns. \emph{Journal of Environmental
Psychology}, \emph{53}, 198--205.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.08.003}{10.1016/j.jenvp.2017.08.003}

\hypertarget{ref-Caselli2017}{}
Caselli, N. K., \& Pyers, J. E. (2017). The road to language learning is
not entirely iconic: Iconicity, neighborhood density, and frequency
facilitate sign language acquisition. \emph{Psychological Science},
\emph{28}(7), 979--987.
doi:\href{https://doi.org/10.1177/0956797617700498}{10.1177/0956797617700498}

\hypertarget{ref-Cash2017}{}
Cash, D. K., \& Lane, S. M. (2017). Context influences interpretation of
eyewitness confidence statements. \emph{Law and Human Behavior},
\emph{41}(2), 180--190.
doi:\href{https://doi.org/10.1037/lhb0000216}{10.1037/lhb0000216}

\hypertarget{ref-Casillas2012}{}
Casillas, A., Robbins, S., Allen, J., Kuo, Y.-L., Hanson, M. A., \&
Schmeiser, C. (2012). Predicting early academic failure in high school
from prior academic achievement, psychosocial characteristics, and
behavior. \emph{Journal of Educational Psychology}, \emph{104}(2),
407--420. doi:\href{https://doi.org/10.1037/a0027180}{10.1037/a0027180}

\hypertarget{ref-Cassidy2017}{}
Cassidy, B. S., Krendl, A. C., Stanko, K. A., Rydell, R. J., Young, S.
G., \& Hugenberg, K. (2017). Configural face processing impacts race
disparities in humanization and trust. \emph{Journal of Experimental
Social Psychology}, \emph{73}, 111--124.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.018}{10.1016/j.jesp.2017.06.018}

\hypertarget{ref-Caughy2012}{}
Caughy, M. O., Franzini, L., Windle, M., Dittus, P., Cuccaro, P.,
Elliott, M. N., \& Schuster, M. A. (2012). Social competence in late
elementary school: Relationships to parenting and neighborhood context.
\emph{Journal of Youth and Adolescence}, \emph{41}(12), 1613--1627.
doi:\href{https://doi.org/10.1007/s10964-012-9779-2}{10.1007/s10964-012-9779-2}

\hypertarget{ref-Cavanagh2017}{}
Cavanagh, C., \& Cauffman, E. (2017). What they don't know can hurt
them: Mothers' legal knowledge and youth re-offending. \emph{Psychology,
Public Policy, and Law}, \emph{23}(2), 141--153.
doi:\href{https://doi.org/10.1037/law0000112}{10.1037/law0000112}

\hypertarget{ref-Chabris2012}{}
Chabris, C. F., Hebert, B. M., Benjamin, D. J., Beauchamp, J., Cesarini,
D., Loos, M. van der, \ldots{} Laibson, D. (2012). Most reported genetic
associations with general intelligence are probably false positives.
\emph{Psychological Science}, \emph{23}(11), 1314--1323.
doi:\href{https://doi.org/10.1177/0956797611435528}{10.1177/0956797611435528}

\hypertarget{ref-Cham2016}{}
Cham, H., \& West, S. G. (2016). Propensity score analysis with missing
data. \emph{Psychological Methods}, \emph{21}(3), 427--445.
doi:\href{https://doi.org/10.1037/met0000076}{10.1037/met0000076}

\hypertarget{ref-Chambless2017a}{}
Chambless, D. L., Milrod, B., Porter, E., Gallop, R., McCarthy, K. S.,
Graf, E., \ldots{} Barber, J. P. (2017). Prediction and moderation of
improvement in cognitive-behavioral and psychodynamic psychotherapy for
panic disorder. \emph{Journal of Consulting and Clinical Psychology},
\emph{85}(8), 803--813.
doi:\href{https://doi.org/10.1037/ccp0000224}{10.1037/ccp0000224}

\hypertarget{ref-Chan2012a}{}
Chan, D. K.-C., \& Hagger, M. S. (2012). Transcontextual development of
motivation in sport injury prevention among elite athletes.
\emph{Journal of Sport and Exercise Psychology}, \emph{34}(5), 661--682.
doi:\href{https://doi.org/10.1123/jsep.34.5.661}{10.1123/jsep.34.5.661}

\hypertarget{ref-Chan2017}{}
Chan, W. W. L., Au, T. K., Lau, N. T., \& Tang, J. (2017). Counting
errors as a window onto children's place-value concept.
\emph{Contemporary Educational Psychology}, \emph{51}, 123--130.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.07.001}{10.1016/j.cedpsych.2017.07.001}

\hypertarget{ref-Chan2012}{}
Chan, W., McCrae, R. R., De Fruyt, F., Jussim, L., Löckenhoff, C. E., De
Bolle, M., \ldots{} Terracciano, A. (2012). Stereotypes of age
differences in personality traits: Universal and accurate? \emph{Journal
of Personality and Social Psychology}, \emph{103}(6), 1050--1066.
doi:\href{https://doi.org/10.1037/a0029712}{10.1037/a0029712}

\hypertarget{ref-Chang2017}{}
Chang, J. W., Chow, R. M., \& Woolley, A. W. (2017). Effects of
inter-group status on the pursuit of intra-group status.
\emph{Organizational Behavior and Human Decision Processes}, \emph{139},
1--17.
doi:\href{https://doi.org/10.1016/j.obhdp.2016.12.001}{10.1016/j.obhdp.2016.12.001}

\hypertarget{ref-Chang2016}{}
Chang, Y. N., Welbourne, S., \& Lee, C. Y. (2016). Exploring
orthographic neighborhood size effects in a computational model of
Chinese character naming. \emph{Cognitive Psychology}, \emph{91}, 1--23.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.09.001}{10.1016/j.cogpsych.2016.09.001}

\hypertarget{ref-Chang2011a}{}
Chang, Y.-K., Chu, I.-H., Chen, F.-T., \& Wang, C.-C. (2011).
Dose-response effect of acute resistance Exercise on tower of London in
middle-aged adults. \emph{Journal of Sport and Exercise Psychology},
\emph{33}(6), 866--883.
doi:\href{https://doi.org/10.1123/jsep.33.6.866}{10.1123/jsep.33.6.866}

\hypertarget{ref-Chang2011}{}
Chang, Y.-K., Tsai, C.-L., Hung, T.-M., So, E. C., Chen, F.-T., \&
Etnier, J. L. (2011). Effects of acute exercise on executive function: A
study with a tower of London task. \emph{Journal of Sport and Exercise
Psychology}, \emph{33}(6), 847--865.
doi:\href{https://doi.org/10.1123/jsep.33.6.847}{10.1123/jsep.33.6.847}

\hypertarget{ref-Chao2017}{}
Chao, M. M., Takeuchi, R., \& Farh, J. L. (2017). Enhancing cultural
intelligence: The roles of implicit culture beliefs and adjustment.
\emph{Personnel Psychology}, \emph{70}(1), 257--292.
doi:\href{https://doi.org/10.1111/peps.12142}{10.1111/peps.12142}

\hypertarget{ref-Chapman2016}{}
Chapman, B. P., Weiss, A., Duberstein, P. R., Chapman, B. P., Weiss, A.,
\& Duberstein, P. R. (2016). Statistical learning theory for high
dimensional prediction: Application to criterion-keyed scale
development. \emph{Psychological Methods}, \emph{21}(4), 603--620.
doi:\href{https://doi.org/10.1037/met0000088}{10.1037/met0000088}

\hypertarget{ref-Chartier2017}{}
Chartier, C. R., \& Abele, S. (2017). Groups outperform individuals in
tacit coordination by using consensual and disjunctive salience.
\emph{Organizational Behavior and Human Decision Processes}, \emph{141},
74--81.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.06.001}{10.1016/j.obhdp.2017.06.001}

\hypertarget{ref-Chatard2017}{}
Chatard, A., Bocage-Barthélémy, Y., Selimbegović, L., \& Guimond, S.
(2017). The woman who wasn't there: Converging evidence that subliminal
social comparison affects self-evaluation. \emph{Journal of Experimental
Social Psychology}, \emph{73}, 1--13.
doi:\href{https://doi.org/10.1016/j.jesp.2017.05.005}{10.1016/j.jesp.2017.05.005}

\hypertarget{ref-Chavez-Korell2012}{}
Chavez-Korell, S., \& Vandiver, B. J. (2012). Are CRIS cluster patterns
differentially associated with African American enculturation and social
distance? \emph{The Counseling Psychologist}, \emph{40}(5), 755--788.
doi:\href{https://doi.org/10.1177/0011000011418839}{10.1177/0011000011418839}

\hypertarget{ref-Chen2012a}{}
Chen, F. F., Jing, Y., \& Lee, J. M. (2012). ``I'' value competence but
``we'' value social competence: The moderating role of voters'
individualistic and collectivistic orientation in political elections.
\emph{Journal of Experimental Social Psychology}, \emph{48}(6),
1350--1355.
doi:\href{https://doi.org/10.1016/j.jesp.2012.07.006}{10.1016/j.jesp.2012.07.006}

\hypertarget{ref-Chen2012}{}
Chen, H.-J., Balan, S., \& Price, R. K. (2012). Association of
contextual factors with drug use and binge drinking among white, Native
American, and mixed-race adolescents in the general population.
\emph{Journal of Youth and Adolescence}, \emph{41}(11), 1426--1441.
doi:\href{https://doi.org/10.1007/s10964-012-9789-0}{10.1007/s10964-012-9789-0}

\hypertarget{ref-Chen2017}{}
Chen, X., McNamara, T. P., Kelly, J. W., \& Wolbers, T. (2017). Cue
combination in human spatial navigation. \emph{Cognitive Psychology},
\emph{95}, 105--144.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.04.003}{10.1016/j.cogpsych.2017.04.003}

\hypertarget{ref-Cheng2016}{}
Cheng, H.-L., Hitter, T. L., Adams, E. M., \& Williams, C. (2016).
Minority stress and depressive symptoms. \emph{The Counseling
Psychologist}, \emph{44}(6), 841--870.
doi:\href{https://doi.org/10.1177/0011000016660377}{10.1177/0011000016660377}

\hypertarget{ref-Cheng2013}{}
Cheng, H.-L., Kwan, K.-L. K., \& Sevig, T. (2013). Racial and ethnic
minority college students' stigma associated with seeking psychological
help: Examining psychocultural correlates. \emph{Journal of Counseling
Psychology}, \emph{60}(1), 98--111.
doi:\href{https://doi.org/10.1037/a0031169}{10.1037/a0031169}

\hypertarget{ref-Cheng2017}{}
Cheng, H.-L., Tran, A. G. T. T., Miyake, E. R., \& Kim, H. Y. (2017).
Disordered eating among Asian American college women: A racially
expanded model of objectification theory. \emph{Journal of Counseling
Psychology}, \emph{64}(2), 179--191.
doi:\href{https://doi.org/10.1037/cou0000195}{10.1037/cou0000195}

\hypertarget{ref-Cheng2011}{}
Cheng, W.-N. K., Hardy, L., \& Woodman, T. (2011). Predictive validity
of a three-dimensional model of performance anxiety in the context of
Tae-Kwon-Do. \emph{Journal of Sport and Exercise Psychology},
\emph{33}(1), 40--53.
doi:\href{https://doi.org/10.1123/jsep.33.1.40}{10.1123/jsep.33.1.40}

\hypertarget{ref-Cheung2017}{}
Cheung, P., Rubenson, M., \& Barner, D. (2017). To infinity and beyond:
Children generalize the successor function to all possible numbers years
after learning to count. \emph{Cognitive Psychology}, \emph{92}, 22--36.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.11.002}{10.1016/j.cogpsych.2016.11.002}

\hypertarget{ref-Chien2012}{}
Chien, N. C., \& East, P. L. (2012). The younger siblings of
childbearing adolescents: Parenting influences on their academic and
social-emotional adjustment. \emph{Journal of Youth and Adolescence},
\emph{41}(10), 1280--1293.
doi:\href{https://doi.org/10.1007/s10964-011-9715-x}{10.1007/s10964-011-9715-x}

\hypertarget{ref-Chiesi2012}{}
Chiesi, F., Ciancaleoni, M., Galli, S., \& Primi, C. (2012). Using the
Advanced Progressive Matrices (Set I) to assess fluid ability in a short
time frame: An item response theory--based analysis. \emph{Psychological
Assessment}, \emph{24}(4), 892--900.
doi:\href{https://doi.org/10.1037/a0027830}{10.1037/a0027830}

\hypertarget{ref-Ching2017}{}
Ching, B. H.-H. (2017). Mathematics anxiety and working memory:
Longitudinal associations with mathematical performance in Chinese
children. \emph{Contemporary Educational Psychology}, \emph{51},
99--113.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.06.006}{10.1016/j.cedpsych.2017.06.006}

\hypertarget{ref-Ching2017a}{}
Ching, B. H.-h., \& Nunes, T. (2017). The importance of additive
reasoning in children's mathematical achievement: A longitudinal study.
\emph{Journal of Educational Psychology}, \emph{109}(4), 477--508.
doi:\href{https://doi.org/10.1037/edu0000154}{10.1037/edu0000154}

\hypertarget{ref-Chiu2012}{}
Chiu, M. M., Pong, S.-l., Mori, I., \& Chow, B. W.-Y. (2012). Immigrant
students' emotional and cognitive engagement at school: a multilevel
analysis of students in 41 countries. \emph{Journal of Youth and
Adolescence}, \emph{41}(11), 1409--1425.
doi:\href{https://doi.org/10.1007/s10964-012-9763-x}{10.1007/s10964-012-9763-x}

\hypertarget{ref-DeChiusole2016}{}
Chiusole, D. de, Stefanutti, L., \& Spoto, A. (2017). A class of k-modes
algorithms for extracting knowledge structures from data. \emph{Behavior
Research Methods}, \emph{49}(4), 1212--1226.
doi:\href{https://doi.org/10.3758/s13428-016-0780-7}{10.3758/s13428-016-0780-7}

\hypertarget{ref-Chiusole2015}{}
Chiusole, D. de, Stefanutti, L., Anselmi, P., \& Robusto, E. (2015).
Modeling missing data in knowledge space theory. \emph{Psychological
Methods}, \emph{20}(4), 506--522.
doi:\href{https://doi.org/10.1037/met0000050}{10.1037/met0000050}

\hypertarget{ref-Chou2017}{}
Chou, E. Y., Halevy, N., Galinsky, A. D., \& Murnighan, J. K. (2017).
The Goldilocks contract: The synergistic benefits of combining structure
and autonomy for persistence, creativity, and cooperation. \emph{Journal
of Personality and Social Psychology}, \emph{113}(3), 393--412.
doi:\href{https://doi.org/10.1037/pspi0000096}{10.1037/pspi0000096}

\hypertarget{ref-Chow2012}{}
Chow, R. M., \& Galak, J. (2012). The effect of inequality frames on
support for redistributive tax policies. \emph{Psychological Science},
\emph{23}(12), 1467--1469.
doi:\href{https://doi.org/10.1177/0956797612450035}{10.1177/0956797612450035}

\hypertarget{ref-Christensen2009}{}
Christensen, M. K. (2009). ``An eye for talent'': Talent identification
and the ``practical sense'' of top-level soccer coaches. \emph{Sociology
of Sport Journal}, \emph{26}(3), 365--382.
doi:\href{https://doi.org/10.1123/ssj.26.3.365}{10.1123/ssj.26.3.365}

\hypertarget{ref-Christodoulou2016}{}
Christodoulou, J. A., Murtagh, J., Cyr, A., Perrachione, T. K., Chang,
P., Halverson, K., \ldots{} Gabrieli, J. D. E. (2016). Relation of
white-matter microstructure to reading ability and disability in
beginning readers. \emph{Neuropsychology}, \emph{31}(5), 508--515.
doi:\href{https://doi.org/10.1037/neu0000243}{10.1037/neu0000243}

\hypertarget{ref-Chua2012}{}
Chua, R. Y., Morris, M. W., \& Mor, S. (2012). Collaborating across
cultures: Cultural metacognition and affect-based trust in creative
collaboration. \emph{Organizational Behavior and Human Decision
Processes}, \emph{118}(2), 116--131.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.03.009}{10.1016/j.obhdp.2012.03.009}

\hypertarget{ref-Chuderski2012}{}
Chuderski, A., \& Necka, E. (2012). The contribution of working memory
to fluid reasoning: Capacity, control, or both? \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{38}(6),
1689--1710.
doi:\href{https://doi.org/10.1037/a0028465}{10.1037/a0028465}

\hypertarget{ref-Cimpian2012}{}
Cimpian, A., \& Erickson, L. C. (2012). Remembering kinds: New evidence
that categories are privileged in children's thinking. \emph{Cognitive
Psychology}, \emph{64}(3), 161--185.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.11.002}{10.1016/j.cogpsych.2011.11.002}

\hypertarget{ref-Clapper2012}{}
Clapper, J. P. (2012). The effects of prior knowledge on incidental
category learning. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{38}(6), 1558--1577.
doi:\href{https://doi.org/10.1037/a0028457}{10.1037/a0028457}

\hypertarget{ref-Clark2012}{}
Clark, A. J., Parakh, R., Smilek, D., \& Roy, E. A. (2012). The Slip
Induction Task: Creating a window into cognitive control failures.
\emph{Behavior Research Methods}, \emph{44}(2), 558--574.
doi:\href{https://doi.org/10.3758/s13428-011-0154-0}{10.3758/s13428-011-0154-0}

\hypertarget{ref-Cleland2012}{}
Cleland, V. J., Ball, K., King, A. C., \& Crawford, D. (2012). Do the
individual, social, and environmental correlates of physical activity
differ between urban and rural women? \emph{Environment and Behavior},
\emph{44}(3), 350--373.
doi:\href{https://doi.org/10.1177/0013916510393275}{10.1177/0013916510393275}

\hypertarget{ref-Clifton2012}{}
Clifton, C., \& Frazier, L. (2012). Discourse integration guided by the
`Question under Discussion'. \emph{Cognitive Psychology}, \emph{65}(2),
352--379.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.04.001}{10.1016/j.cogpsych.2012.04.001}

\hypertarget{ref-Coates2016}{}
Coates, R., Ayers, S., \& Visser, R. de. (2017). Factor structure of the
Edinburgh Postnatal Depression Scale in a population-based sample.
\emph{Psychological Assessment}, \emph{29}(8), 1016--1027.
doi:\href{https://doi.org/10.1037/pas0000397}{10.1037/pas0000397}

\hypertarget{ref-Cobb2017}{}
Cobb, C. L., Meca, A., Xie, D., Schwartz, S. J., \& Moise, R. K. (2017).
Perceptions of legal status: Associations with psychosocial experiences
among undocumented Latino/a immigrants. \emph{Journal of Counseling
Psychology}, \emph{64}(2), 167--178.
doi:\href{https://doi.org/10.1037/cou0000189}{10.1037/cou0000189}

\hypertarget{ref-Coelho2012}{}
Coelho, C. J., Nusbaum, H. C., Rosenbaum, D. A., \& Fenn, K. M. (2012).
Imagined actions aren't just weak actions: Task variability promotes
skill learning in physical practice but not in mental practice.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{38}(6), 1759--1764.
doi:\href{https://doi.org/10.1037/a0028065}{10.1037/a0028065}

\hypertarget{ref-Cohen2016}{}
Cohen, D. J., \& Quinlan, P. T. (2016). How numbers mean: Comparing
random walk models of numerical cognition varying both encoding
processes and underlying quantity representations. \emph{Cognitive
Psychology}, \emph{91}, 63--81.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.10.002}{10.1016/j.cogpsych.2016.10.002}

\hypertarget{ref-Cohen2016a}{}
Cohen, D. T., \& Hanold, M. T. (2016). Finish lines, not finish times:
Making meaning of the ``Marathon Maniacs.'' \emph{Sociology of Sport
Journal}, \emph{33}(4), 347--356.
doi:\href{https://doi.org/10.1123/ssj.2016-0016}{10.1123/ssj.2016-0016}

\hypertarget{ref-Cohn2012}{}
Cohn, N., Paczynski, M., Jackendoff, R., Holcomb, P. J., \& Kuperberg,
G. R. (2012). (Pea)nuts and bolts of visual narrative: Structure and
meaning in sequential image comprehension. \emph{Cognitive Psychology},
\emph{65}(1), 1--38.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.01.003}{10.1016/j.cogpsych.2012.01.003}

\hypertarget{ref-Cokley2017}{}
Cokley, K., Smith, L., Bernard, D., Hurst, A., Jackson, S., Stone, S.,
\ldots{} Roberts, D. (2017). Impostor feelings as a moderator and
mediator of the relationship between perceived discrimination and mental
health among racial/ethnic minority college students. \emph{Journal of
Counseling Psychology}, \emph{64}(2), 141--154.
doi:\href{https://doi.org/10.1037/cou0000198}{10.1037/cou0000198}

\hypertarget{ref-Coley2017}{}
Coley, J. D., Arenson, M., Xu, Y., \& Tanner, K. D. (2017). Intuitive
biological thought: Developmental changes and effects of biology
education in late adolescence. \emph{Cognitive Psychology}, \emph{92},
1--21.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.11.001}{10.1016/j.cogpsych.2016.11.001}

\hypertarget{ref-Collado2017}{}
Collado, S., Evans, G. W., \& Sorrel, M. A. (2017). The role of parents
and best friends in children's pro-environmentalism: Differences
according to age and gender. \emph{Journal of Environmental Psychology},
\emph{54}, 27--37.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.09.007}{10.1016/j.jenvp.2017.09.007}

\hypertarget{ref-Collie2012}{}
Collie, R. J., Shapka, J. D., \& Perry, N. E. (2012). School climate and
social--emotional learning: Predicting teacher stress, job satisfaction,
and teaching efficacy. \emph{Journal of Educational Psychology},
\emph{104}(4), 1189--1204.
doi:\href{https://doi.org/10.1037/a0029356}{10.1037/a0029356}

\hypertarget{ref-Comeaux2010}{}
Comeaux, E. (2010). Racial differences in faculty perceptions of
collegiate student-athletes' academic and post-undergraduate
achievements. \emph{Sociology of Sport Journal}, \emph{27}(4), 390--412.
doi:\href{https://doi.org/10.1123/ssj.27.4.390}{10.1123/ssj.27.4.390}

\hypertarget{ref-Comer2017a}{}
Comer, J. S., Furr, J. M., Miguel, E. M., Cooper-Vince, C. E.,
Carpenter, A. L., Elkins, R. M., \ldots{} Chase, R. (2017). Remotely
delivering real-time parent training to the home: An initial randomized
trial of Internet-delivered parent--child interaction therapy (I-PCIT).
\emph{Journal of Consulting and Clinical Psychology}, \emph{85}(9),
909--917.
doi:\href{https://doi.org/10.1037/ccp0000230}{10.1037/ccp0000230}

\hypertarget{ref-Conaway2016}{}
Conaway, N., \& Kurtz, K. J. (2017). Similar to the category, but not
the exemplars: A study of generalization. \emph{Psychonomic Bulletin \&
Review}, \emph{24}(4), 1312--1323.
doi:\href{https://doi.org/10.3758/s13423-016-1208-1}{10.3758/s13423-016-1208-1}

\hypertarget{ref-Conlon2012}{}
Conlon, D. E., Tinsley, C. H., Birk, S. J., Humphrey, S. E., \& Ellis,
A. P. J. (2012). Is it sometimes better to receive than to give?
Preferences for receiver roles over proposer roles in consumer behavior
ultimatums. \emph{Organizational Behavior and Human Decision Processes},
\emph{119}(1), 64--77.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.05.003}{10.1016/j.obhdp.2012.05.003}

\hypertarget{ref-Conover2017}{}
Conover, K. J., Israel, T., \& Nylund-Gibson, K. (2017). Development and
validation of the ableist microaggressions scale. \emph{The Counseling
Psychologist}, \emph{45}(4), 570--599.
doi:\href{https://doi.org/10.1177/0011000017715317}{10.1177/0011000017715317}

\hypertarget{ref-Conrad2012}{}
Conrad, K. J., Conrad, K. M., Mazza, J., Riley, B. B., Funk, R., Stein,
M. A., \& Dennis, M. L. (2012). Dimensionality, hierarchical structure,
age generalizability, and criterion validity of the GAIN's Behavioral
Complexity Scale. \emph{Psychological Assessment}, \emph{24}(4),
913--924. doi:\href{https://doi.org/10.1037/a0028196}{10.1037/a0028196}

\hypertarget{ref-Conroy2011}{}
Conroy, D. E., Elavsky, S., Hyde, A. L., \& Doerksen, S. E. (2011). The
dynamic nature of physical activity intentions: A within-person
perspective on intention-behavior coupling. \emph{Journal of Sport and
Exercise Psychology}, \emph{33}(6), 807--827.
doi:\href{https://doi.org/10.1123/jsep.33.6.807}{10.1123/jsep.33.6.807}

\hypertarget{ref-Constantinescu2017}{}
Constantinescu, A. C., Wolters, M., Moore, A., \& MacPherson, S. E.
(2017). A cluster-based approach to selecting representative stimuli
from the International Affective Picture System (IAPS) database.
\emph{Behavior Research Methods}, \emph{49}(3), 896--912.
doi:\href{https://doi.org/10.3758/s13428-016-0750-0}{10.3758/s13428-016-0750-0}

\hypertarget{ref-Cooc2017}{}
Cooc, N., \& Kim, J. S. (2017). Peer influence on children's reading
skills: A social network analysis of elementary school classrooms.
\emph{Journal of Educational Psychology}, \emph{109}(5), 727--740.
doi:\href{https://doi.org/10.1037/edu0000166}{10.1037/edu0000166}

\hypertarget{ref-Cook2012}{}
Cook, J. W., Fucito, L. M., Piasecki, T. M., Piper, M. E., Schlam, T.
R., Berg, K. M., \& Baker, T. B. (2012). Relations of alcohol
consumption with smoking cessation milestones and tobacco dependence.
\emph{Journal of Consulting and Clinical Psychology}, \emph{80}(6),
1075--1085.
doi:\href{https://doi.org/10.1037/a0029931}{10.1037/a0029931}

\hypertarget{ref-Cooper2017a}{}
Cooper, A. A., Zoellner, L. A., Roy-Byrne, P., Mavissakalian, M. R., \&
Feeny, N. C. (2017). Do changes in trauma-related beliefs predict PTSD
symptom improvement in prolonged exposure and sertraline? \emph{Journal
of Consulting and Clinical Psychology}, \emph{85}(9), 873--882.
doi:\href{https://doi.org/10.1037/ccp0000220}{10.1037/ccp0000220}

\hypertarget{ref-Cooper2017}{}
Cooper, J. N., Davis, T. J., \& Dougherty, S. (2017). Not so black and
white : A multi-divisional exploratory analysis of male
student-athletes' experiences at National Collegiate Athletic
Association ( NCAA ) Institutions. \emph{Sociology of Sport Journal},
\emph{34}, 59--78.
doi:\href{https://doi.org/10.1123/ssj.2016-0015}{10.1123/ssj.2016-0015}

\hypertarget{ref-Cornish2017}{}
Cornish, M. A., Lannin, D. G., Wade, N. G., \& Martinez, M. (2017). Can
use of positive religious coping predict greater distress? An
examination of Army soldiers on deployment. \emph{Journal of Counseling
Psychology}, \emph{64}(3), 302--309.
doi:\href{https://doi.org/10.1037/cou0000200}{10.1037/cou0000200}

\hypertarget{ref-Cortland2017}{}
Cortland, C. I., Craig, M. A., Shapiro, J. R., Richeson, J. A., Neel,
R., \& Goldstein, N. J. (2017). Solidarity through shared disadvantage:
Highlighting shared experiences of discrimination improves relations
between stigmatized groups. \emph{Journal of Personality and Social
Psychology}, \emph{113}(4), 547--567.
doi:\href{https://doi.org/10.1037/pspi0000100}{10.1037/pspi0000100}

\hypertarget{ref-Costa2012}{}
Costa, M. (2012). Territorial behavior in public settings.
\emph{Environment and Behavior}, \emph{44}(5), 713--721.
doi:\href{https://doi.org/10.1177/0013916511403803}{10.1177/0013916511403803}

\hypertarget{ref-Cottini2018}{}
Cottini, M., Basso, D., \& Palladino, P. (2018). The role of declarative
and procedural metamemory in event-based prospective memory in
school-aged children. \emph{Journal of Experimental Child Psychology},
\emph{166}, 17--33.
doi:\href{https://doi.org/10.1016/j.jecp.2017.08.002}{10.1016/j.jecp.2017.08.002}

\hypertarget{ref-Cowgill2017}{}
Cowgill, C. M., Rios, K., \& Simpson, A. (2017). Generous heathens?
Reputational concerns and atheists' behavior toward Christians in
economic games. \emph{Journal of Experimental Social Psychology},
\emph{73}, 169--179.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.015}{10.1016/j.jesp.2017.06.015}

\hypertarget{ref-Cragun2012}{}
Cragun, C. L., \& Friedlander, M. L. (2012). Experiences of Christian
clients in secular psychotherapy: A mixed-methods investigation.
\emph{Journal of Counseling Psychology}, \emph{59}(3), 379--391.
doi:\href{https://doi.org/10.1037/a0028283}{10.1037/a0028283}

\hypertarget{ref-Cramer2013}{}
Cramer, R. J., Miller, A. K., Amacker, A. M., \& Burks, A. C. (2013).
Openness, right-wing authoritarianism, and antigay prejudice in college
students: A mediational model. \emph{Journal of Counseling Psychology},
\emph{60}(1), 64--71.
doi:\href{https://doi.org/10.1037/a0031090}{10.1037/a0031090}

\hypertarget{ref-Crawford2017}{}
Crawford, M. R., Holder, M. D., \& O'Connor, B. P. (2017). Using mobile
technology to engage children with nature. \emph{Environment and
Behavior}, \emph{49}(9), 959--984.
doi:\href{https://doi.org/10.1177/0013916516673870}{10.1177/0013916516673870}

\hypertarget{ref-Creel2012a}{}
Creel, S. C. (2012). Similarity-based restoration of metrical
information: Different listening experiences result in different
perceptual inferences. \emph{Cognitive Psychology}, \emph{65}(2),
321--351.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.04.004}{10.1016/j.cogpsych.2012.04.004}

\hypertarget{ref-Creel2012}{}
Creel, S. C., \& Jimenez, S. R. (2012). Differences in talker
recognition by preschoolers and adults. \emph{Journal of Experimental
Child Psychology}, \emph{113}(4), 487--509.
doi:\href{https://doi.org/10.1016/j.jecp.2012.07.007}{10.1016/j.jecp.2012.07.007}

\hypertarget{ref-Crenshaw2016}{}
Crenshaw, A. O., Christensen, A., Baucom, D. H., Epstein, N. B., \&
Baucom, B. R. W. (2017). Revised scoring and improved reliability for
the Communication Patterns Questionnaire. \emph{Psychological
Assessment}, \emph{29}(7), 913--925.
doi:\href{https://doi.org/10.1037/pas0000385}{10.1037/pas0000385}

\hypertarget{ref-Crits-Christoph2017a}{}
Crits-Christoph, P., Gallop, R., Diehl, C. K., Yin, S., \& Gibbons, M.
B. C. (2017). Mechanisms of change in cognitive therapy for major
depressive disorder in the community mental health setting.
\emph{Journal of Consulting and Clinical Psychology}, \emph{85}(6),
550--561.
doi:\href{https://doi.org/10.1037/ccp0000198}{10.1037/ccp0000198}

\hypertarget{ref-Crust2016}{}
Crust, L., Swann, C., \& Allen-Collinson, J. (2016). The thin line: A
phenomenological study of mental toughness and decision making in elite
high-altitude mountaineers. \emph{Journal of Sport and Exercise
Psychology}, \emph{38}(6), 598--611.
doi:\href{https://doi.org/10.1123/jsep.2016-0109}{10.1123/jsep.2016-0109}

\hypertarget{ref-Cucina2012}{}
Cucina, J. M., Caputo, P. M., Thibodeaux, H. F., \& Maclane, C. N.
(2012). Unlocking the key to biodata scoring: A comparison of empirical,
rational, and hybrid approaches at different sample sizes.
\emph{Personnel Psychology}, \emph{65}(2), 385--428.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01244.x}{10.1111/j.1744-6570.2012.01244.x}

\hypertarget{ref-Cui2017}{}
Cui, F., Zhu, X., \& Luo, Y. (2017). Social contexts modulate neural
responses in the processing of others' pain: An event-related potential
study. \emph{Cognitive, Affective, \& Behavioral Neuroscience},
\emph{17}(4), 850--857.
doi:\href{https://doi.org/10.3758/s13415-017-0517-9}{10.3758/s13415-017-0517-9}

\hypertarget{ref-Cullen2012}{}
Cullen, A. E., Clarke, A. Y., Kuipers, E., Hodgins, S., Dean, K., \&
Fahy, T. (2012). A multisite randomized trial of a cognitive skills
program for male mentally disordered offenders: Violence and antisocial
behavior outcomes. \emph{Journal of Consulting and Clinical Psychology},
\emph{80}(6), 1114--1120.
doi:\href{https://doi.org/10.1037/a0030291}{10.1037/a0030291}

\hypertarget{ref-Cunningham2012}{}
Cunningham, G. B., \& Melton, N. (2012). Prejudice against lesbian, gay,
and bisexual coaches: The influence of race, religious fundamentalism,
modern sexism, and contact with sexual minorities. \emph{Sociology of
Sport Journal}, \emph{29}(3), 283--305.
doi:\href{https://doi.org/10.1123/ssj.29.3.283}{10.1123/ssj.29.3.283}

\hypertarget{ref-Cunningham2004}{}
Cunningham, G. B., \& Sagas, M. (2004). Racial differences in
occupational turnover intent among NCAA Division IA assistant football
coaches. \emph{Sociology of Sport Journal}, \emph{21}(1), 84--92.
doi:\href{https://doi.org/10.1123/ssj.21.1.84}{10.1123/ssj.21.1.84}

\hypertarget{ref-Dagkas2012}{}
Dagkas, S., \& Quarmby, T. (2012). Young people's embodiment of physical
activity: The role of the ``pedagogized'' family. \emph{Sociology of
Sport Journal}, \emph{29}(2), 210--226.
doi:\href{https://doi.org/10.1123/ssj.29.2.210}{10.1123/ssj.29.2.210}

\hypertarget{ref-Dahling2016}{}
Dahling, J. J., Taylor, S. R., Chau, S. L., \& Dwight, S. A. (2016).
Does coaching matter? A multilevel model linking managerial coaching
skill and frequency to sales goal attainment. \emph{Personnel
Psychology}, \emph{69}(4), 863--894.
doi:\href{https://doi.org/10.1111/peps.12123}{10.1111/peps.12123}

\hypertarget{ref-Dahmani2012}{}
Dahmani, L., Ledoux, A.-A., Boyer, P., \& Bohbot, V. D. (2012).
Wayfinding: The effects of large displays and 3-D perception.
\emph{Behavior Research Methods}, \emph{44}(2), 447--454.
doi:\href{https://doi.org/10.3758/s13428-011-0158-9}{10.3758/s13428-011-0158-9}

\hypertarget{ref-Daly2017}{}
Daly, M., Robinson, E., \& Sutin, A. R. (2017). Does knowing hurt?
Perceiving oneself as overweight predicts future physical health and
well-being. \emph{Psychological Science}, \emph{28}(7), 872--881.
doi:\href{https://doi.org/10.1177/0956797617696311}{10.1177/0956797617696311}

\hypertarget{ref-Danbold2017}{}
Danbold, F., \& Huo, Y. J. (2017). Men's defense of their
prototypicality undermines the success of women in STEM initiatives.
\emph{Journal of Experimental Social Psychology}, \emph{72}, 57--66.
doi:\href{https://doi.org/10.1016/j.jesp.2016.12.014}{10.1016/j.jesp.2016.12.014}

\hypertarget{ref-Dane2012}{}
Dane, E., Rockmann, K. W., \& Pratt, M. G. (2012). When should I trust
my gut? Linking domain expertise to intuitive decision-making
effectiveness. \emph{Organizational Behavior and Human Decision
Processes}, \emph{119}(2), 187--194.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.07.009}{10.1016/j.obhdp.2012.07.009}

\hypertarget{ref-Dang2018}{}
Dang, J., Liu, L., Ren, D., \& Su, Q. (2018). Polarization and
positivity effects: Divergent roles of group entitativity in warmth and
competence judgments. \emph{Journal of Experimental Social Psychology},
\emph{74}, 74--84.
doi:\href{https://doi.org/10.1016/j.jesp.2017.09.003}{10.1016/j.jesp.2017.09.003}

\hypertarget{ref-Daniels2017}{}
Daniels, D. P., Neale, M. A., \& Greer, L. L. (2017). Spillover bias in
diversity judgment. \emph{Organizational Behavior and Human Decision
Processes}, \emph{139}, 92--105.
doi:\href{https://doi.org/10.1016/j.obhdp.2016.12.005}{10.1016/j.obhdp.2016.12.005}

\hypertarget{ref-Dankner2017}{}
Dankner, Y., Shalev, L., Carrasco, M., \& Yuval-Greenberg, S. (2017).
Prestimulus inhibition of saccades in adults with and without
Attention-Deficit/Hyperactivity Disorder as an index of temporal
expectations. \emph{Psychological Science}, \emph{28}(7), 835--850.
doi:\href{https://doi.org/10.1177/0956797617694863}{10.1177/0956797617694863}

\hypertarget{ref-Dargis2017}{}
Dargis, M., \& Koenigs, M. (2017). Witnessing domestic violence during
childhood is associated with psychopathic traits in adult male criminal
offenders. \emph{Law and Human Behavior}, \emph{41}(2), 173--179.
doi:\href{https://doi.org/10.1037/lhb0000226}{10.1037/lhb0000226}

\hypertarget{ref-Darling2012}{}
Darling, S., Logie, R. H., \& Della Sala, S. (2012). Representational
pseudoneglect in line bisection. \emph{Psychonomic Bulletin \& Review},
\emph{19}(5), 879--883.
doi:\href{https://doi.org/10.3758/s13423-012-0285-z}{10.3758/s13423-012-0285-z}

\hypertarget{ref-Darwich2012}{}
Darwich, L., Hymel, S., \& Waterhouse, T. (2012). School avoidance and
substance use among lesbian, gay, bisexual, and questioning youths: The
impact of peer victimization and adult support. \emph{Journal of
Educational Psychology}, \emph{104}(2), 381--392.
doi:\href{https://doi.org/10.1037/a0026684}{10.1037/a0026684}

\hypertarget{ref-Dasgupta2017}{}
Dasgupta, I., Schulz, E., \& Gershman, S. J. (2017). Where do hypotheses
come from? \emph{Cognitive Psychology}, \emph{96}, 1--25.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.05.001}{10.1016/j.cogpsych.2017.05.001}

\hypertarget{ref-Davidson2017}{}
Davidson, R. D., \& Beck, C. J. A. (2017). Using couple-level patterns
of intimate partner violence to predict divorce outcomes.
\emph{Psychology, Public Policy, and Law}, \emph{23}(1), 85--95.
doi:\href{https://doi.org/10.1037/law0000106}{10.1037/law0000106}

\hypertarget{ref-Davies2017}{}
Davies, R. A. I., Arnell, R., Birchenough, J. M. H., Grimmond, D., \&
Houlson, S. (2017). Reading through the life span: Individual
differences in psycholinguistic effects. \emph{Journal of Experimental
Psychology: Learning, Memory, and Cognition}, \emph{43}(8), 1298--1338.
doi:\href{https://doi.org/10.1037/xlm0000366}{10.1037/xlm0000366}

\hypertarget{ref-Davis2017}{}
Davis, R., Ohman, J. M., \& Weisbeck, C. (2017). Salient cues and
wayfinding in Alzheimer's Disease within a virtual senior residence.
\emph{Environment and Behavior}, \emph{49}(9), 1038--1065.
doi:\href{https://doi.org/10.1177/0013916516677341}{10.1177/0013916516677341}

\hypertarget{ref-Davydenko2017}{}
Davydenko, M., \& Peetz, J. (2017). Time grows on trees: The effect of
nature settings on time perception. \emph{Journal of Environmental
Psychology}, \emph{54}, 20--26.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.09.003}{10.1016/j.jenvp.2017.09.003}

\hypertarget{ref-Dawel2017}{}
Dawel, A., Wright, L., Irons, J., Dumbleton, R., Palermo, R., O'Kearney,
R., \& McKone, E. (2017). Perceived emotion genuineness: normative
ratings for popular facial expression stimuli and the development of
perceived-as-genuine and perceived-as-fake sets. \emph{Behavior Research
Methods}, \emph{49}(4), 1539--1562.
doi:\href{https://doi.org/10.3758/s13428-016-0813-2}{10.3758/s13428-016-0813-2}

\hypertarget{ref-Dawson2017}{}
Dawson, E., Hartwig, M., Brimbal, L., \& Denisenkov, P. (2017). A room
with a view: Setting influences information disclosure in investigative
interviews. \emph{Law and Human Behavior}, \emph{41}(4), 333--343.
doi:\href{https://doi.org/10.1037/lhb0000244}{10.1037/lhb0000244}

\hypertarget{ref-Dazkir2012}{}
Dazkir, S. S., \& Read, M. A. (2012). Furniture forms and their
influence on our emotional responses toward interior environments.
\emph{Environment and Behavior}, \emph{44}(5), 722--732.
doi:\href{https://doi.org/10.1177/0013916511402063}{10.1177/0013916511402063}

\hypertarget{ref-DeBellis2017}{}
De Bellis, F., Trojano, L., Errico, D., Grossi, D., \& Conson, M.
(2017). Whose hand is this? Differential responses of right and left
extrastriate body areas to visual images of self and others' hands.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{17}(4),
826--837.
doi:\href{https://doi.org/10.3758/s13415-017-0514-z}{10.3758/s13415-017-0514-z}

\hypertarget{ref-DeFreitas2017}{}
De Freitas, J., DeScioli, P., Nemirow, J., Massenkoff, M., \& Pinker, S.
(2017). Kill or die: Moral judgment alters linguistic coding of
causality. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{43}(8), 1173--1182.
doi:\href{https://doi.org/10.1037/xlm0000369}{10.1037/xlm0000369}

\hypertarget{ref-DeMuynck2017a}{}
De Muynck, G.-J., Vansteenkiste, M., Delrue, J., Aelterman, N., Haerens,
L., \& Soenens, B. (2017). The effects of feedback valence and style on
need satisfaction, self-talk, and perseverance among tennis players: An
experimental study. \emph{Journal of Sport and Exercise Psychology},
\emph{39}(1), 67--80.
doi:\href{https://doi.org/10.1123/jsep.2015-0326}{10.1123/jsep.2015-0326}

\hypertarget{ref-DeNaeghel2012}{}
De Naeghel, J., Van Keer, H., Vansteenkiste, M., \& Rosseel, Y. (2012).
The relation between elementary students' recreational and academic
reading motivation, reading frequency, engagement, and comprehension: A
self-determination theory perspective. \emph{Journal of Educational
Psychology}, \emph{104}(4), 1006--1021.
doi:\href{https://doi.org/10.1037/a0027800}{10.1037/a0027800}

\hypertarget{ref-Deak2017}{}
Deak, A., Bodrogi, B., Biro, B., Perlaki, G., Orsi, G., \& Bereczkei, T.
(2017). Machiavellian emotion regulation in a cognitive reappraisal
task: An fMRI study. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{17}(3), 528--541.
doi:\href{https://doi.org/10.3758/s13415-016-0495-3}{10.3758/s13415-016-0495-3}

\hypertarget{ref-Debbane2017}{}
Debbané, M., Badoud, D., Sander, D., Eliez, S., Luyten, P., \& Vrtička,
P. (2017). Brain activity underlying negative self- and other-perception
in adolescents: The role of attachment-derived self-representations.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{17}(3),
554--576.
doi:\href{https://doi.org/10.3758/s13415-017-0497-9}{10.3758/s13415-017-0497-9}

\hypertarget{ref-Deboeck2009}{}
Deboeck, P. R., Montpetit, M. A., Bergeman, C. S., \& Boker, S. M.
(2009). Using derivative estimates to describe intraindividual
variability at multiple time scales. \emph{Psychological Methods},
\emph{14}(4), 367--386.
doi:\href{https://doi.org/10.1037/a0016622}{10.1037/a0016622}

\hypertarget{ref-DeCaro2012}{}
DeCaro, M. S., \& Rittle-Johnson, B. (2012). Exploring mathematics
problems prepares children to learn from instruction. \emph{Journal of
Experimental Child Psychology}, \emph{113}(4), 552--568.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.009}{10.1016/j.jecp.2012.06.009}

\hypertarget{ref-DeJesus2017}{}
DeJesus, J. M., Hwang, H. G., Dautel, J. B., \& Kinzler, K. D. (2017).
Bilingual children's social preferences hinge on accent. \emph{Journal
of Experimental Child Psychology}, \emph{164}, 178--191.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.005}{10.1016/j.jecp.2017.07.005}

\hypertarget{ref-DelZotto2017}{}
Del Zotto, M., \& Pegna, A. J. (2017). Electrophysiological evidence of
perceived sexual attractiveness for human female bodies varying in
waist-to-hip ratio. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{17}(3), 577--591.
doi:\href{https://doi.org/10.3758/s13415-017-0498-8}{10.3758/s13415-017-0498-8}

\hypertarget{ref-Paoli2017}{}
Delli Paoli, A. G., Smith, A. L., \& Pontifex, M. B. (2017). Does
walking mitigate affective and cognitive responses to social exclusion?
\emph{Journal of Sport and Exercise Psychology}, \emph{39}(2), 97--108.
doi:\href{https://doi.org/10.1123/jsep.2016-0202}{10.1123/jsep.2016-0202}

\hypertarget{ref-DeMartini2012}{}
DeMartini, K. S., \& Carey, K. B. (2012). Optimizing the use of the
AUDIT for alcohol screening in college students. \emph{Psychological
Assessment}, \emph{24}(4), 954--963.
doi:\href{https://doi.org/10.1037/a0028519}{10.1037/a0028519}

\hypertarget{ref-Dempsey2012}{}
Dempsey, L. E., Karver, M. S., Labouliere, C., Zesiewicz, T. A., \& De
Nadai, A. S. (2012). Self-perceived burden as a mediator of depression
symptoms amongst individuals living with a movement disorder.
\emph{Journal of Clinical Psychology}, \emph{68}(10), 1149--1160.
doi:\href{https://doi.org/10.1002/jclp.21901}{10.1002/jclp.21901}

\hypertarget{ref-Deng2017}{}
Deng, H., Walter, F., Lam, C. K., \& Zhao, H. H. (2017). Spillover
effects of emotional labor in customer service encounters toward
coworker harming: A resource depletion perspective. \emph{Personnel
Psychology}, \emph{70}(2), 469--502.
doi:\href{https://doi.org/10.1111/peps.12156}{10.1111/peps.12156}

\hypertarget{ref-Deng2016}{}
Deng, H., Wu, C. H., Leung, K., \& Guan, Y. (2016). Depletion from
self-regulation: A resource-based account of the effect of value
incongruence. \emph{Personnel Psychology}, \emph{69}(2), 431--465.
doi:\href{https://doi.org/10.1111/peps.12107}{10.1111/peps.12107}

\hypertarget{ref-Denham2011}{}
Denham, B. E. (2011). Alcohol and marijuana use among American high
school seniors: Empirical associations with competitive sports
participation. \emph{Sociology of Sport Journal}, \emph{28}(3),
362--379.
doi:\href{https://doi.org/10.1123/ssj.28.3.362}{10.1123/ssj.28.3.362}

\hypertarget{ref-Denison2017}{}
Denison, R. N., Heeger, D. J., \& Carrasco, M. (2017). Attention
flexibly trades off across points in time. \emph{Psychonomic Bulletin \&
Review}, \emph{24}(4), 1142--1151.
doi:\href{https://doi.org/10.3758/s13423-016-1216-1}{10.3758/s13423-016-1216-1}

\hypertarget{ref-Dennett2012a}{}
Dennett, H. W., McKone, E., Edwards, M., \& Susilo, T. (2012). Face
aftereffects predict individual differences in face recognition ability.
\emph{Psychological Science}, \emph{23}(11), 1279--1287.
doi:\href{https://doi.org/10.1177/0956797612446350}{10.1177/0956797612446350}

\hypertarget{ref-Dennett2012}{}
Dennett, H. W., McKone, E., Tavashmi, R., Hall, A., Pidcock, M.,
Edwards, M., \& Duchaine, B. (2012). The Cambridge Car Memory Test: A
task matched in format to the Cambridge Face Memory Test, with norms,
reliability, sex differences, dissociations from face memory, and
expertise effects. \emph{Behavior Research Methods}, \emph{44}(2),
587--605.
doi:\href{https://doi.org/10.3758/s13428-011-0160-2}{10.3758/s13428-011-0160-2}

\hypertarget{ref-Deska2018}{}
Deska, J. C., \& Hugenberg, K. (2018). Targets' facial width-to-height
ratio biases pain judgments. \emph{Journal of Experimental Social
Psychology}, \emph{74}, 56--64.
doi:\href{https://doi.org/10.1016/j.jesp.2017.08.004}{10.1016/j.jesp.2017.08.004}

\hypertarget{ref-DeSteno2012}{}
DeSteno, D., Breazeal, C., Frank, R. H., Pizarro, D., Baumann, J.,
Dickens, L., \& Lee, J. J. (2012). Detecting the trustworthiness of
novel partners in economic exchange. \emph{Psychological Science},
\emph{23}(12), 1549--1556.
doi:\href{https://doi.org/10.1177/0956797612448793}{10.1177/0956797612448793}

\hypertarget{ref-Devine2012}{}
Devine, P. G., Forscher, P. S., Austin, A. J., \& Cox, W. T. L. (2012).
Long-term reduction in implicit race bias: A prejudice habit-breaking
intervention. \emph{Journal of Experimental Social Psychology},
\emph{48}(6), 1267--1278.
doi:\href{https://doi.org/10.1016/j.jesp.2012.06.003}{10.1016/j.jesp.2012.06.003}

\hypertarget{ref-Dewar2017}{}
Dewar, M., Neroni, M. A., Zeman, A., Beschin, N., \& Della Sala, S.
(2017). Visual complexity accentuates picture-description deficit in
amnesia. \emph{Neuropsychology}, \emph{31}(6), 689--696.
doi:\href{https://doi.org/10.1037/neu0000310}{10.1037/neu0000310}

\hypertarget{ref-Dewhurst2012}{}
Dewhurst, R., Nyström, M., Jarodzka, H., Foulsham, T., Johansson, R., \&
Holmqvist, K. (2012). It depends on how you look at it: Scanpath
comparison in multiple dimensions with MultiMatch, a vector-based
approach. \emph{Behavior Research Methods}, \emph{44}(4), 1079--1100.
doi:\href{https://doi.org/10.3758/s13428-012-0212-2}{10.3758/s13428-012-0212-2}

\hypertarget{ref-Dibble2012}{}
Dibble, J. L., Levine, T. R., \& Park, H. S. (2012). The Unidimensional
Relationship Closeness Scale (URCS): Reliability and validity evidence
for a new measure of relationship closeness. \emph{Psychological
Assessment}, \emph{24}(3), 565--572.
doi:\href{https://doi.org/10.1037/a0026265}{10.1037/a0026265}

\hypertarget{ref-Diedenhofen2017}{}
Diedenhofen, B., \& Musch, J. (2017). PageFocus: Using paradata to
detect and prevent cheating on online achievement tests. \emph{Behavior
Research Methods}, \emph{49}(4), 1444--1459.
doi:\href{https://doi.org/10.3758/s13428-016-0800-7}{10.3758/s13428-016-0800-7}

\hypertarget{ref-Dierdorff2012}{}
Dierdorff, E. C., \& Ellington, J. K. (2012). Members matter in team
training: Multilevel and longitudinal relationships between goal
orientation, self-regulation, and team outcomes. \emph{Personnel
Psychology}, \emph{65}(3), 661--703.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01255.x}{10.1111/j.1744-6570.2012.01255.x}

\hypertarget{ref-Dills2012}{}
Dills, J. E., Rutt, C. D., \& Mumford, K. G. (2012). Objectively
measuring route-to-park walkability in Atlanta, Georgia.
\emph{Environment and Behavior}, \emph{44}(6), 841--860.
doi:\href{https://doi.org/10.1177/0013916511404409}{10.1177/0013916511404409}

\hypertarget{ref-Dimmock2016}{}
Dimmock, J. A., Gagné, M., Proud, L., Howle, T. C., Rebar, A. L., \&
Jackson, B. (2016). An Exercise in Resistance: Inoculation Messaging as
a Strategy for Protecting Motivation During a Monotonous and Controlling
Exercise Class. \emph{Journal of Sport and Exercise Psychology},
\emph{38}(6), 567--578.
doi:\href{https://doi.org/10.1123/jsep.2016-0146}{10.1123/jsep.2016-0146}

\hypertarget{ref-Dissanayaka2017}{}
Dissanayaka, N. N. W., Au, T. R., Angwin, A. J., O'Sullivan, J. D.,
Byrne, G. J., Silburn, P. A., \ldots{} Copland, D. A. (2017). N400 and
emotional word processing in Parkinson's Disease.
\emph{Neuropsychology}, \emph{31}(6), 585--595.
doi:\href{https://doi.org/10.1037/neu0000333}{10.1037/neu0000333}

\hypertarget{ref-Dobrow2011}{}
Dobrow, S. R., \& Tosti-Kharas, J. (2011). Calling: The development of a
scale measure. \emph{Personnel Psychology}, \emph{64}(4), 1001--1049.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01234.x}{10.1111/j.1744-6570.2011.01234.x}

\hypertarget{ref-Doebel2018}{}
Doebel, S., Dickerson, J. P., Hoover, J. D., \& Munakata, Y. (2018).
Using language to get ready: Familiar labels help children engage
proactive control. \emph{Journal of Experimental Child Psychology},
\emph{166}, 147--159.
doi:\href{https://doi.org/10.1016/j.jecp.2017.08.006}{10.1016/j.jecp.2017.08.006}

\hypertarget{ref-Doi2012}{}
Doi, H., \& Shinohara, K. (2012). Bodily movement of approach is
detected faster than that of receding. \emph{Psychonomic Bulletin \&
Review}, \emph{19}(5), 858--863.
doi:\href{https://doi.org/10.3758/s13423-012-0284-0}{10.3758/s13423-012-0284-0}

\hypertarget{ref-Dopp2017}{}
Dopp, A. R., Borduin, C. M., Willroth, E. C., \& Sorg, A. A. (2017).
Long-term economic benefits of psychological interventions for
criminality: Comparing and integrating estimation methods.
\emph{Psychology, Public Policy, and Law}, \emph{23}(3), 312--323.
doi:\href{https://doi.org/10.1037/law0000134}{10.1037/law0000134}

\hypertarget{ref-Dorociak2017}{}
Dorociak, K. E., Rupert, P. A., Bryant, F. B., \& Zahniser, E. (2017).
Development of the professional self-care scale. \emph{Journal of
Counseling Psychology}, \emph{64}(3), 325--334.
doi:\href{https://doi.org/10.1037/cou0000206}{10.1037/cou0000206}

\hypertarget{ref-Douglass2017}{}
Douglass, R. P., Conlin, S. E., Duffy, R. D., \& Allan, B. A. (2017).
Examining moderators of discrimination and subjective well-being among
LGB individuals. \emph{Journal of Counseling Psychology}, \emph{64}(1),
1--11. doi:\href{https://doi.org/10.1037/cou0000187}{10.1037/cou0000187}

\hypertarget{ref-Dowd2017}{}
Dowd, E. W., Pearson, J. M., \& Egner, T. (2017). Decoding working
memory content from attentional biases. \emph{Psychonomic Bulletin \&
Review}, \emph{24}(4), 1252--1260.
doi:\href{https://doi.org/10.3758/s13423-016-1204-5}{10.3758/s13423-016-1204-5}

\hypertarget{ref-Dragoni2011}{}
Dragoni, L., Oh, I.-S., Vankatwyk, P., \& Tesluk, P. E. (2011).
Developing executive leaders: The relative contribution of cognitive
ability, personality, and the accumulation of work experience in
predicting strategic thinking. \emph{Personnel Psychology},
\emph{64}(4), 829--864.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01229.x}{10.1111/j.1744-6570.2011.01229.x}

\hypertarget{ref-Driessen2017}{}
Driessen, E., Van, H. L., Peen, J., Don, F. J., Twisk, J. W. R.,
Cuijpers, P., \& Dekker, J. J. M. (2017). Cognitive-behavioral versus
psychodynamic therapy for major depression: Secondary outcomes of a
randomized clinical trial. \emph{Journal of Consulting and Clinical
Psychology}, \emph{85}(7), 653--663.
doi:\href{https://doi.org/10.1037/ccp0000207}{10.1037/ccp0000207}

\hypertarget{ref-Drob2016}{}
Drob, V., Tasso, A. F., \& Griffo, R. (2016). Attitudes toward
psychotherapy among immigrant Russian-speaking Jews from the former
Soviet Union. \emph{The Counseling Psychologist}, \emph{44}(6),
921--941.
doi:\href{https://doi.org/10.1177/0011000016652690}{10.1177/0011000016652690}

\hypertarget{ref-Du2016}{}
Du, Y., \& Clark, J. E. (2017). New insights into statistical learning
and chunk learning in implicit sequence acquisition. \emph{Psychonomic
Bulletin \& Review}, \emph{24}(4), 1225--1233.
doi:\href{https://doi.org/10.3758/s13423-016-1193-4}{10.3758/s13423-016-1193-4}

\hypertarget{ref-Duffy2013a}{}
Duffy, R. D., Allan, B. A., Autin, K. L., \& Bott, E. M. (2013). Calling
and life satisfaction: It's not about having it, it's about living it.
\emph{Journal of Counseling Psychology}, \emph{60}(1), 42--52.
doi:\href{https://doi.org/10.1037/a0030635}{10.1037/a0030635}

\hypertarget{ref-Duffy2017}{}
Duffy, R. D., Allan, B. A., England, J. W., Blustein, D. L., Autin, K.
L., Douglass, R. P., \ldots{} Santos, E. J. R. (2017). The development
and initial validation of the decent wok scale. \emph{Journal of
Counseling Psychology}, \emph{64}(2), 206--221.
doi:\href{https://doi.org/10.1037/cou0000191}{10.1037/cou0000191}

\hypertarget{ref-Duffy2013}{}
Duffy, R. D., Bott, E. M., Allan, B. A., \& Torrey, C. L. (2013).
Examining a model of life satisfaction among unemployed adults.
\emph{Journal of Counseling Psychology}, \emph{60}(1), 53--63.
doi:\href{https://doi.org/10.1037/a0030771}{10.1037/a0030771}

\hypertarget{ref-Duffy2012}{}
Duffy, R. D., Diemer, M. A., \& Jadidian, A. (2012). The development and
initial validation of the work volition scale--student version.
\emph{The Counseling Psychologist}, \emph{40}(2), 291--319.
doi:\href{https://doi.org/10.1177/0011000011417147}{10.1177/0011000011417147}

\hypertarget{ref-Dumas2017}{}
Dumas, T. L., \& Stanko, T. L. (2017). Married with children: How family
role identification shapes leadership behaviors at work. \emph{Personnel
Psychology}, \emph{70}(3), 597--633.
doi:\href{https://doi.org/10.1111/peps.12182}{10.1111/peps.12182}

\hypertarget{ref-Dumont2017}{}
Dumont, H., Protsch, P., Jansen, M., \& Becker, M. (2017). Fish swimming
into the ocean: How tracking relates to students' self-beliefs and
school disengagement at the end of schooling. \emph{Journal of
Educational Psychology}, \emph{109}(6), 855--870.
doi:\href{https://doi.org/10.1037/edu0000175}{10.1037/edu0000175}

\hypertarget{ref-Dumont2012}{}
Dumont, H., Trautwein, U., Lüdtke, O., Neumann, M., Niggli, A., \&
Schnyder, I. (2012). Does parental homework involvement mediate the
relationship between family background and educational outcomes?
\emph{Contemporary Educational Psychology}, \emph{37}(1), 55--69.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.09.004}{10.1016/j.cedpsych.2011.09.004}

\hypertarget{ref-Duncan2012}{}
Duncan, J., Schramm, M., Thompson, R., \& Dumontheil, I. (2012). Task
rules, working memory, and fluid intelligence. \emph{Psychonomic
Bulletin \& Review}, \emph{19}(5), 864--870.
doi:\href{https://doi.org/10.3758/s13423-012-0225-y}{10.3758/s13423-012-0225-y}

\hypertarget{ref-Dunn2012}{}
Dunn, B. D., Evans, D., Makarova, D., White, J., \& Clark, L. (2012).
Gut feelings and the reaction to perceived inequity: The interplay
between bodily responses, regulation, and perception shapes the
rejection of unfair offers on the ultimatum game. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, \emph{12}(3), 419--429.
doi:\href{https://doi.org/10.3758/s13415-012-0092-z}{10.3758/s13415-012-0092-z}

\hypertarget{ref-Durber2017}{}
Durber, C. M., Yeates, K. O., Taylor, H. G., Walz, N. C., Stancin, T.,
\& Wade, S. L. (2017). The family environment predicts long-term
academic achievement and classroom behavior following traumatic brain
injury in early childhood. \emph{Neuropsychology}, \emph{31}(5),
499--507.
doi:\href{https://doi.org/10.1037/neu0000351}{10.1037/neu0000351}

\hypertarget{ref-Dysart2012}{}
Dysart, J. E., Lawson, V. Z., \& Rainey, A. (2012). Blind lineup
administration as a prophylactic against the postidentification feedback
effect. \emph{Law and Human Behavior}, \emph{36}(4), 312--319.
doi:\href{https://doi.org/10.1037/h0093921}{10.1037/h0093921}

\hypertarget{ref-Dziak2015}{}
Dziak, J. J., Li, R., Tan, X., Shiffman, S., \& Shiyko, M. P. (2015).
Modeling intensive longitudinal data with mixtures of nonparametric
trajectories and time-varying effects. \emph{Psychological Methods},
\emph{20}(4), 444--469.
doi:\href{https://doi.org/10.1037/met0000048}{10.1037/met0000048}

\hypertarget{ref-Dzikus2017}{}
Dzikus, L., Smith, A. B., \& Evans, J. (2017). ``What it means to be a
'lady''': Defending the ``Lady Vols'' nickname and logo. \emph{Sociology
of Sport Journal}, \emph{34}(1), 35--45.
doi:\href{https://doi.org/10.1123/ssj.2016-0060}{10.1123/ssj.2016-0060}

\hypertarget{ref-Eastwood2011}{}
Eastwood, J., \& Snook, B. (2012). The effect of listenability factors
on the comprehension of police cautions. \emph{Law and Human Behavior},
\emph{36}(3), 177--183.
doi:\href{https://doi.org/10.1037/h0093955}{10.1037/h0093955}

\hypertarget{ref-Ebesutani2012}{}
Ebesutani, C., Reise, S. P., Chorpita, B. F., Ale, C., Regan, J., Young,
J., \ldots{} Weisz, J. R. (2012). The Revised Child Anxiety and
Depression Scale-Short Version: Scale reduction via exploratory bifactor
modeling of the broad anxiety factor. \emph{Psychological Assessment},
\emph{24}(4), 833--845.
doi:\href{https://doi.org/10.1037/a0027283}{10.1037/a0027283}

\hypertarget{ref-Ecklund2017}{}
Ecklund, E. H., Scheitle, C. P., Peifer, J., \& Bolger, D. (2017).
Examining links between religion, evolution views, and climate change
skepticism. \emph{Environment and Behavior}, \emph{49}(9), 985--1006.
doi:\href{https://doi.org/10.1177/0013916516674246}{10.1177/0013916516674246}

\hypertarget{ref-Effron2012}{}
Effron, D. A., Miller, D. T., \& Monin, B. (2012). Inventing racist
roads not taken: The licensing effect of immoral counterfactual
behaviors. \emph{Journal of Personality and Social Psychology},
\emph{103}(6), 916--932.
doi:\href{https://doi.org/10.1037/a0030008}{10.1037/a0030008}

\hypertarget{ref-Eibach2012}{}
Eibach, R. P., \& Mock, S. E. (2012). System justifying functions of
myths that exaggerate the emotional rewards of parenthood. \emph{Journal
of Experimental Social Psychology}, \emph{48}(6), 1310--1315.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.010}{10.1016/j.jesp.2012.05.010}

\hypertarget{ref-Eid2016}{}
Eid, M., Geiser, C., Koch, T., \& Heene, M. (2016). Anomalous results in
G -Factor models: Explanations and alternatives. \emph{Psychological
Methods}, \emph{22}(3), 541--562.
doi:\href{https://doi.org/10.1037/met0000083}{10.1037/met0000083}

\hypertarget{ref-Eisen2017}{}
Eisen, M. L., Smith, A. M., Olaguez, A. P., \& Skerritt-Perta, A. S.
(2017). An examination of showups conducted by law enforcement using a
field-simulation paradigm. \emph{Psychology, Public Policy, and Law},
\emph{23}(1), 1--22.
doi:\href{https://doi.org/10.1037/law0000115}{10.1037/law0000115}

\hypertarget{ref-Elbogen2012}{}
Elbogen, E. B., Johnson, S. C., Newton, V. M., Straits-Troster, K.,
Vasterling, J. J., Wagner, H. R., \& Beckham, J. C. (2012). Criminal
justice involvement, trauma, and negative affect in Iraq and Afghanistan
war era veterans. \emph{Journal of Consulting and Clinical Psychology},
\emph{80}(6), 1097--1102.
doi:\href{https://doi.org/10.1037/a0029967}{10.1037/a0029967}

\hypertarget{ref-Eller2017}{}
Eller, A., Abrams, D., \& Koschate, M. (2017). Can stateways change
folkways? Longitudinal tests of the interactive effects of intergroup
contact and categorization on prejudice. \emph{Journal of Experimental
Social Psychology}, \emph{72}, 21--31.
doi:\href{https://doi.org/10.1016/j.jesp.2017.04.005}{10.1016/j.jesp.2017.04.005}

\hypertarget{ref-Elliott2011}{}
Elliott, I., Thomas, S. D. M., \& Ogloff, J. R. P. (2011). Procedural
justice in contacts with the police: Testing a relational model of
authority in a mixed methods study. \emph{Psychology, Public Policy, and
Law}, \emph{17}(4), 592--610.
doi:\href{https://doi.org/10.1037/a0024212}{10.1037/a0024212}

\hypertarget{ref-Elliott2017}{}
Elliott, T. R., Hsiao, Y.-Y., Kimbrel, N. A., Meyer, E., DeBeer, B. B.,
Gulliver, S. B., \ldots{} Morissette, S. B. (2017). Resilience and
traumatic brain injury among Iraq/Afghanistan war veterans: differential
patterns of adjustment and quality of life. \emph{Journal of Clinical
Psychology}, \emph{73}(9), 1160--1178.
doi:\href{https://doi.org/10.1002/jclp.22414}{10.1002/jclp.22414}

\hypertarget{ref-Ellis2017}{}
Ellis, J. M., Galloway, A. T., Webb, R. M., \& Martz, D. M. (2017).
Measuring adult picky eating: The development of a multidimensional
self-report instrument. \emph{Psychological Assessment}, \emph{29}(8),
955--966.
doi:\href{https://doi.org/10.1037/pas0000387}{10.1037/pas0000387}

\hypertarget{ref-Ellis-Davies2012}{}
Ellis-Davies, K., Sakkalou, E., Fowler, N. C., Hilbrink, E. E., \&
Gattis, M. (2012). CUE: The continuous unified electronic diary method.
\emph{Behavior Research Methods}, \emph{44}(4), 1063--1078.
doi:\href{https://doi.org/10.3758/s13428-012-0205-1}{10.3758/s13428-012-0205-1}

\hypertarget{ref-Elman2012}{}
Elman, J. A., Klostermann, E. C., Marian, D. E., Verstaen, A., \&
Shimamura, A. P. (2012). Neural correlates of metacognitive monitoring
during episodic and semantic retrieval. \emph{Cognitive, Affective, \&
Behavioral Neuroscience}, \emph{12}(3), 599--609.
doi:\href{https://doi.org/10.3758/s13415-012-0096-8}{10.3758/s13415-012-0096-8}

\hypertarget{ref-Elmore2012}{}
Elmore, K. C., \& Oyserman, D. (2012). If 'we' can succeed, 'I' can too:
Identity-based motivation and gender in the classroom.
\emph{Contemporary Educational Psychology}, \emph{37}(3), 176--185.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.05.003}{10.1016/j.cedpsych.2011.05.003}

\hypertarget{ref-Endress2017}{}
Endress, A. D., \& Langus, A. (2017). Transitional probabilities count
more than frequency, but might not be used for memorization.
\emph{Cognitive Psychology}, \emph{92}, 37--64.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.11.004}{10.1016/j.cogpsych.2016.11.004}

\hypertarget{ref-Endress2011}{}
Endress, A. D., \& Wood, J. N. (2011). From movements to actions: Two
mechanisms for learning action sequences. \emph{Cognitive Psychology},
\emph{63}(3), 141--171.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.07.001}{10.1016/j.cogpsych.2011.07.001}

\hypertarget{ref-EngeldeAbreu2012}{}
Engel de Abreu, P. M. J., \& Gathercole, S. E. (2012). Executive and
phonological processes in second-language acquisition. \emph{Journal of
Educational Psychology}, \emph{104}(4), 974--986.
doi:\href{https://doi.org/10.1037/a0028390}{10.1037/a0028390}

\hypertarget{ref-Englert2012}{}
Englert, C., \& Bertrams, A. (2012). Anxiety, ego depletion, and sports
performance. \emph{Journal of Sport and Exercise Psychology},
\emph{34}(5), 580--599.
doi:\href{https://doi.org/10.1123/jsep.34.5.580}{10.1123/jsep.34.5.580}

\hypertarget{ref-EnoLouden2013}{}
Eno Louden, J., \& Skeem, J. L. (2013). How do probation officers assess
and manage recidivism and violence risk for probationers with mental
disorder? An experimental investigation. \emph{Law and Human Behavior},
\emph{37}(1), 22--34.
doi:\href{https://doi.org/10.1037/h0093991}{10.1037/h0093991}

\hypertarget{ref-Ernst2017}{}
Ernst, A., \& Briegel, R. (2017). A dynamic and spatially explicit
psychological model of the diffusion of green electricity across
Germany. \emph{Journal of Environmental Psychology}, \emph{52},
183--193.
doi:\href{https://doi.org/10.1016/j.jenvp.2016.12.003}{10.1016/j.jenvp.2016.12.003}

\hypertarget{ref-Eskenazi2016}{}
Eskenazi, M. A., \& Folk, J. R. (2017). Regressions during reading: The
cost depends on the cause. \emph{Psychonomic Bulletin \& Review},
\emph{24}(4), 1211--1216.
doi:\href{https://doi.org/10.3758/s13423-016-1200-9}{10.3758/s13423-016-1200-9}

\hypertarget{ref-Estrada-Martinez2012}{}
Estrada-Martínez, L. M., Caldwell, C. H., Bauermeister, J. A., \&
Zimmerman, M. A. (2012). Stressors in multiple life-domains and the risk
for externalizing and internalizing behaviors among African Americans
during emerging adulthood. \emph{Journal of Youth and Adolescence},
\emph{41}(12), 1600--1612.
doi:\href{https://doi.org/10.1007/s10964-012-9778-3}{10.1007/s10964-012-9778-3}

\hypertarget{ref-Evans2017b}{}
Evans, A. D., Stolzenberg, S. N., \& Lyon, T. D. (2017). Pragmatic
failure and referential ambiguity when attorneys ask child witnesses
``do you know/remember'' questions. \emph{Psychology, Public Policy, and
Law}, \emph{23}(2), 191--199.
doi:\href{https://doi.org/10.1037/law0000116}{10.1037/law0000116}

\hypertarget{ref-Evans2017a}{}
Evans, A. M., \& Beest, I. van. (2017). Gain-loss framing effects in
dilemmas of trust and reciprocity. \emph{Journal of Experimental Social
Psychology}, \emph{73}, 151--163.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.012}{10.1016/j.jesp.2017.06.012}

\hypertarget{ref-Evans2017c}{}
Evans, J. R., Pimentel, P. S., Pena, M. M., \& Michael, S. W. (2017).
The ability to detect false statements as a function of the type of
statement and the language proficiency of the statement provider.
\emph{Psychology, Public Policy, and Law}, \emph{23}(3), 290--300.
doi:\href{https://doi.org/10.1037/law0000127}{10.1037/law0000127}

\hypertarget{ref-Evans2017}{}
Evans, R., Thirlwall, K., Cooper, P., \& Creswell, C. (2017). Using
symptom and interference questionnaires to identify recovery among
children with anxiety disorders. \emph{Psychological Assessment},
\emph{29}(7), 835--843.
doi:\href{https://doi.org/10.1037/pas0000375}{10.1037/pas0000375}

\hypertarget{ref-Faber2017}{}
Faber, M., \& Gennari, S. P. (2017). Effects of learned episodic event
structure on prospective duration judgments. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{43}(8),
1203--1214.
doi:\href{https://doi.org/10.1037/xlm0000378}{10.1037/xlm0000378}

\hypertarget{ref-Fabricius2017}{}
Fabricius, W. V., \& Suh, G. W. (2017). Should infants and toddlers have
frequent overnight parenting time with fathers? The policy debate and
new data. \emph{Psychology, Public Policy, and Law}, \emph{23}(1),
68--84.
doi:\href{https://doi.org/10.1037/law0000108}{10.1037/law0000108}

\hypertarget{ref-Faircloth2012}{}
Faircloth, B. S. (2012). `` Wearing a mask'' vs. connecting identity
with learning. \emph{Contemporary Educational Psychology}, \emph{37}(3),
186--194.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.12.003}{10.1016/j.cedpsych.2011.12.003}

\hypertarget{ref-Fang2017}{}
Fang, R., McAllister, D. J., \& Duffy, M. K. (2017). Down but not out:
Newcomers can compensate for low vertical access with strong horizontal
ties and favorable core self-evaluations. \emph{Personnel Psychology},
\emph{70}(3), 517--555.
doi:\href{https://doi.org/10.1111/peps.12177}{10.1111/peps.12177}

\hypertarget{ref-Farmer2017}{}
Farmer, G. D., Baron-Cohen, S., \& Skylark, W. J. (2017). People with
Autism Spectrum conditions make more consistent decisions.
\emph{Psychological Science}, \emph{28}(8), 1067--1076.
doi:\href{https://doi.org/10.1177/0956797617694867}{10.1177/0956797617694867}

\hypertarget{ref-Farrell2012}{}
Farrell, S., \& Lelièvre, A. (2012). The dynamics of access to groups in
working memory. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{38}(6), 1659--1674.
doi:\href{https://doi.org/10.1037/a0028469}{10.1037/a0028469}

\hypertarget{ref-Faulkner2017}{}
Faulkner, J. W., Wilshire, C. E., Parker, A. J., \& Cunningham, K.
(2017). An evaluation of language in brain tumor patients using a new
cognitively motivated testing protocol. \emph{Neuropsychology},
\emph{31}(6), 648--665.
doi:\href{https://doi.org/10.1037/neu0000374}{10.1037/neu0000374}

\hypertarget{ref-Fay2012}{}
Fay, A. J., \& Maner, J. K. (2012). Warmth, spatial proximity, and
social attachment: The embodied perception of a social metaphor.
\emph{Journal of Experimental Social Psychology}, \emph{48}(6),
1369--1372.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.017}{10.1016/j.jesp.2012.05.017}

\hypertarget{ref-Felder2017a}{}
Felder, J. N., Epel, E., Lewis, J. B., Cunningham, S. D., Tobin, J. N.,
Rising, S. S., \ldots{} Ickovics, J. R. (2017). Depressive symptoms and
gestational length among pregnant adolescents: Cluster randomized
control trial of CenteringPregnancy plus group prenatal care.
\emph{Journal of Consulting and Clinical Psychology}, \emph{85}(6),
574--584.
doi:\href{https://doi.org/10.1037/ccp0000191}{10.1037/ccp0000191}

\hypertarget{ref-FeldmanHall2017}{}
FeldmanHall, O., Dunsmoor, J. E., Kroes, M. C. W., Lackovic, S., \&
Phelps, E. A. (2017). Associative learning of social value in dynamic
groups. \emph{Psychological Science}, \emph{28}(8), 1160--1170.
doi:\href{https://doi.org/10.1177/0956797617706394}{10.1177/0956797617706394}

\hypertarget{ref-Ferreira2012}{}
Ferreira, M. B., Garcia-Marques, L., Hamilton, D., Ramos, T., Uleman, J.
S., \& Jeronimo, R. (2012). On the relation between spontaneous trait
inferences and intentional inferences: An inference monitoring
hypothesis. \emph{Journal of Experimental Social Psychology},
\emph{48}(1), 1--12.
doi:\href{https://doi.org/10.1016/j.jesp.2011.06.013}{10.1016/j.jesp.2011.06.013}

\hypertarget{ref-Ferre2012}{}
Ferré, P., Guasch, M., Moldovan, C., \& Sánchez-Casas, R. (2012).
Affective norms for 380 Spanish words belonging to three different
semantic categories. \emph{Behavior Research Methods}, \emph{44}(2),
395--403.
doi:\href{https://doi.org/10.3758/s13428-011-0165-x}{10.3758/s13428-011-0165-x}

\hypertarget{ref-Fine2017a}{}
Fine, A., \& Rooij, B. van. (2017). For whom does deterrence affect
behavior? Identifying key individual differences. \emph{Law and Human
Behavior}, \emph{41}(4), 354--360.
doi:\href{https://doi.org/10.1037/lhb0000246}{10.1037/lhb0000246}

\hypertarget{ref-Fine2017}{}
Fine, A., Cavanagh, C., Donley, S., Frick, P. J., Steinberg, L., \&
Cauffman, E. (2017a). Is the effect of justice system attitudes on
recidivism stable after youths' first arrest? Race and legal
socialization among first-time youth offenders. \emph{Law and Human
Behavior}, \emph{41}(2), 146--158.
doi:\href{https://doi.org/10.1037/lhb0000229}{10.1037/lhb0000229}

\hypertarget{ref-Fine2017b}{}
Fine, A., Donley, S., Cavanagh, C., Miltimore, S., Steinberg, L., Frick,
P. J., \& Cauffman, E. (2017b). And justice for all: Determinants and
effects of probation officers' processing decisions regarding first-time
juvenile offenders. \emph{Psychology, Public Policy, and Law},
\emph{23}(1), 105.
doi:\href{https://doi.org/10.1037/law0000113}{10.1037/law0000113}

\hypertarget{ref-Finez2012}{}
Finez, L., \& Sherman, D. K. (2012). Train in vain: The role of the self
in claimed self-handicapping strategies. \emph{Journal of Sport and
Exercise Psychology}, \emph{34}(5), 600--620.
doi:\href{https://doi.org/10.1123/jsep.34.5.600}{10.1123/jsep.34.5.600}

\hypertarget{ref-Finlay-Jones2017}{}
Finlay-Jones, A., Kane, R., \& Rees, C. (2017). Self-compassion online:
A pilot study of an internet-based self-compassion cultivation program
for psychology trainees. \emph{Journal of Clinical Psychology},
\emph{73}(7), 797--816.
doi:\href{https://doi.org/10.1002/jclp.22375}{10.1002/jclp.22375}

\hypertarget{ref-Finlayson2012}{}
Finlayson, I. R., \& Corley, M. (2012). Disfluency in dialogue: an
intentional signal from the speaker? \emph{Psychonomic Bulletin \&
Review}, \emph{19}(5), 921--928.
doi:\href{https://doi.org/10.3758/s13423-012-0279-x}{10.3758/s13423-012-0279-x}

\hypertarget{ref-Fiorella2012}{}
Fiorella, L., \& Mayer, R. E. (2012). Paper-based aids for learning with
a computer-based game. \emph{Journal of Educational Psychology},
\emph{104}(4), 1074--1082.
doi:\href{https://doi.org/10.1037/a0028088}{10.1037/a0028088}

\hypertarget{ref-Fiorella2017}{}
Fiorella, L., Gog, T. van, Hoogerheide, V., \& Mayer, R. E. (2017). It's
all a matter of perspective: Viewing first-person video modeling
examples promotes learning of an assembly task. \emph{Journal of
Educational Psychology}, \emph{109}(5), 653--665.
doi:\href{https://doi.org/10.1037/edu0000161}{10.1037/edu0000161}

\hypertarget{ref-Fishbach2012}{}
Fishbach, A., \& Choi, J. (2012). When thinking about goals undermines
goal pursuit. \emph{Organizational Behavior and Human Decision
Processes}, \emph{118}(2), 99--107.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.02.003}{10.1016/j.obhdp.2012.02.003}

\hypertarget{ref-Fishman2017}{}
Fishman, E. J., \& Husman, J. (2017). Extending attribution theory:
Considering students' perceived control of the attribution process.
\emph{Journal of Educational Psychology}, \emph{109}(4), 559--573.
doi:\href{https://doi.org/10.1037/edu0000158}{10.1037/edu0000158}

\hypertarget{ref-Flannery2017}{}
Flannery, A. J., Luebbe, A. M., \& Becker, S. P. (2017). Sluggish
cognitive tempo is associated with poorer study skills, more executive
functioning deficits, and greater impairment in college students.
\emph{Journal of Clinical Psychology}, \emph{73}(9), 1091--1113.
doi:\href{https://doi.org/10.1002/jclp.22406}{10.1002/jclp.22406}

\hypertarget{ref-Fledderus2012}{}
Fledderus, M., Oude Voshaar, M. A. H., Klooster, P. M. ten, \&
Bohlmeijer, E. T. (2012). Further evaluation of the psychometric
properties of the Acceptance and Action Questionnaire--II.
\emph{Psychological Assessment}, \emph{24}(4), 925--936.
doi:\href{https://doi.org/10.1037/a0028200}{10.1037/a0028200}

\hypertarget{ref-Fleming2017}{}
Fleming, J. B., \& Burns, M. N. (2017). Online evaluative conditioning
did not alter internalized homonegativity or self-esteem in gay men.
\emph{Journal of Clinical Psychology}, \emph{73}(9), 1013--1026.
doi:\href{https://doi.org/10.1002/jclp.22388}{10.1002/jclp.22388}

\hypertarget{ref-Flora2012}{}
Flora, P. K., Strachan, S. M., Brawley, L. R., \& Spink, K. S. (2012).
Exercise identity and attribution properties predict negative
self-conscious emotions for exercise relapse. \emph{Journal of Sport and
Exercise Psychology}, \emph{34}(5), 647--660.
doi:\href{https://doi.org/10.1123/jsep.34.5.647}{10.1123/jsep.34.5.647}

\hypertarget{ref-Flores2017}{}
Flores, S., Bailey, H. R., Eisenberg, M. L., \& Zacks, J. M. (2017).
Event segmentation improves event memory up to one month later.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(8), 1183--1202.
doi:\href{https://doi.org/10.1037/xlm0000367}{10.1037/xlm0000367}

\hypertarget{ref-Foa2017a}{}
Foa, E. B., Asnaani, A., Rosenfield, D., Zandberg, L. J., Gariti, P., \&
Imms, P. (2017). Concurrent varenicline and prolonged exposure for
patients with nicotine dependence and PTSD: A randomized controlled
trial. \emph{Journal of Consulting and Clinical Psychology},
\emph{85}(9), 862--872.
doi:\href{https://doi.org/10.1037/ccp0000213}{10.1037/ccp0000213}

\hypertarget{ref-Forsythe2016}{}
Forsythe, A., Street, N., \& Helmy, M. (2017). Revisiting Rossion and
Pourtois with new ratings for automated complexity, familiarity, beauty,
and encounter. \emph{Behavior Research Methods}, \emph{49}(4),
1484--1493.
doi:\href{https://doi.org/10.3758/s13428-016-0808-z}{10.3758/s13428-016-0808-z}

\hypertarget{ref-Foster2017}{}
Foster, J. J., Sutterer, D. W., Serences, J. T., Vogel, E. K., \& Awh,
E. (2017). Alpha-Band Oscillations enable spatially and temporally
resolved tracking of covert spatial attention. \emph{Psychological
Science}, \emph{28}(7), 929--941.
doi:\href{https://doi.org/10.1177/0956797617699167}{10.1177/0956797617699167}

\hypertarget{ref-Francis2012}{}
Francis, J., Giles-Corti, B., Wood, L., \& Knuiman, M. (2012). Creating
sense of community: The role of public space. \emph{Journal of
Environmental Psychology}, \emph{32}(4), 401--409.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.07.002}{10.1016/j.jenvp.2012.07.002}

\hypertarget{ref-Frank2012}{}
Frank, M. C., Fedorenko, E., Lai, P., Saxe, R., \& Gibson, E. (2012).
Verbal interference suppresses exact numerical representation.
\emph{Cognitive Psychology}, \emph{64}(1-2), 74--92.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.10.004}{10.1016/j.cogpsych.2011.10.004}

\hypertarget{ref-Frankfurt2016}{}
Frankfurt, S., Frazier, P., Syed, M., \& Jung, K. R. (2016). Using
group-based trajectory and growth mixture modeling to identify classes
of change trajectories. \emph{The Counseling Psychologist},
\emph{44}(5), 622--660.
doi:\href{https://doi.org/10.1177/0011000016658097}{10.1177/0011000016658097}

\hypertarget{ref-Freeman2011}{}
Freeman, P., Coffee, P., \& Rees, T. (2011). The PASS-Q: The perceived
available support in sport questionnaire. \emph{Journal of Sport and
Exercise Psychology}, \emph{33}(1), 54--74.
doi:\href{https://doi.org/10.1123/jsep.33.1.54}{10.1123/jsep.33.1.54}

\hypertarget{ref-Friend2017}{}
Friend, M., DeAnda, S., Arias-Trejo, N., Poulin-Dubois, D., \& Zesiger,
P. (2017). Developmental changes in maternal education and minimal
exposure effects on vocabulary in English- and Spanish-learning
toddlers. \emph{Journal of Experimental Child Psychology}, \emph{164},
250--259.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.003}{10.1016/j.jecp.2017.07.003}

\hypertarget{ref-Frimer2017}{}
Frimer, J. A., Skitka, L. J., \& Motyl, M. (2017). Liberals and
conservatives are similarly motivated to avoid exposure to one another's
opinions. \emph{Journal of Experimental Social Psychology}, \emph{72},
1--12.
doi:\href{https://doi.org/10.1016/j.jesp.2017.04.003}{10.1016/j.jesp.2017.04.003}

\hypertarget{ref-Fritsche2012}{}
Fritsche, I., \& Häfner, K. (2012). The malicious effects of existential
threat on motivation to protect the natural environment and the role of
environmental identity as a moderator. \emph{Environment and Behavior},
\emph{44}(4), 570--590.
doi:\href{https://doi.org/10.1177/0013916510397759}{10.1177/0013916510397759}

\hypertarget{ref-Fry2017}{}
Fry, J., \& Bloyce, D. (2017). `Life in the travelling circus': A study
of loneliness, work stress, and money issues in touring professional
golf. \emph{Sociology of Sport Journal}, \emph{34}(2), 148--159.
doi:\href{https://doi.org/10.1123/ssj.2017-0002}{10.1123/ssj.2017-0002}

\hypertarget{ref-Fu2012}{}
Fu, G., Evans, A. D., Xu, F., \& Lee, K. (2012). Young children can tell
strategic lies after committing a transgression. \emph{Journal of
Experimental Child Psychology}, \emph{113}(1), 147--158.
doi:\href{https://doi.org/10.1016/j.jecp.2012.04.003}{10.1016/j.jecp.2012.04.003}

\hypertarget{ref-Fuentes2012}{}
Fuentes, P., Barrós-Loscertales, A., Bustamante, J. C., Rosell, P.,
Costumero, V., \& Ávila, C. (2012). Individual differences in the
Behavioral Inhibition System are associated with orbitofrontal cortex
and precuneus gray matter volume. \emph{Cognitive, Affective, \&
Behavioral Neuroscience}, \emph{12}(3), 491--498.
doi:\href{https://doi.org/10.3758/s13415-012-0099-5}{10.3758/s13415-012-0099-5}

\hypertarget{ref-Fukunaga2012}{}
Fukunaga, R., Brown, J. W., \& Bogg, T. (2012). Decision making in the
Balloon Analogue Risk Task (BART): Anterior cingulate cortex signals
loss aversion but not the infrequency of risky choices. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, \emph{12}(3), 479--490.
doi:\href{https://doi.org/10.3758/s13415-012-0102-1}{10.3758/s13415-012-0102-1}

\hypertarget{ref-Furley2016}{}
Furley, P., \& Schweizer, G. (2016). Nonverbal communication of
confidence in soccer referees: An experimental test of Darwin's leakage
hypothesis. \emph{Journal of Sport and Exercise Psychology},
\emph{38}(6), 590--597.
doi:\href{https://doi.org/10.1123/jsep.2016-0192}{10.1123/jsep.2016-0192}

\hypertarget{ref-Gabay2012}{}
Gabay, Y., Schiff, R., \& Vakil, E. (2012). Attentional requirements
during acquisition and consolidation of a skill in normal readers and
developmental dyslexics. \emph{Neuropsychology}, \emph{26}(6), 744--757.
doi:\href{https://doi.org/10.1037/a0030235}{10.1037/a0030235}

\hypertarget{ref-Gable2012}{}
Gable, S. L., Gosnell, C. L., Maisel, N. C., \& Strachman, A. (2012).
Safely testing the alarm: Close others' responses to personal positive
events. \emph{Journal of Personality and Social Psychology},
\emph{103}(6), 963--981.
doi:\href{https://doi.org/10.1037/a0029488}{10.1037/a0029488}

\hypertarget{ref-Galak2012}{}
Galak, J., LeBoeuf, R. A., Nelson, L. D., \& Simmons, J. P. (2012).
Correcting the past: Failures to replicate psi. \emph{Journal of
Personality and Social Psychology}, \emph{103}(6), 933--948.
doi:\href{https://doi.org/10.1037/a0029709}{10.1037/a0029709}

\hypertarget{ref-Galesic2012}{}
Galesic, M., Olsson, H., \& Rieskamp, J. (2012). Social sampling
explains apparent biases in judgments of social environments.
\emph{Psychological Science}, \emph{23}(12), 1515--1523.
doi:\href{https://doi.org/10.1177/0956797612445313}{10.1177/0956797612445313}

\hypertarget{ref-Galovski2012}{}
Galovski, T. E., Blain, L. M., Mott, J. M., Elwood, L., \& Houle, T.
(2012). Manualized therapy for PTSD: Flexing the structure of cognitive
processing therapy. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(6), 968--981.
doi:\href{https://doi.org/10.1037/a0030600}{10.1037/a0030600}

\hypertarget{ref-Gamond2017}{}
Gamond, L., Vecchi, T., Ferrari, C., Merabet, L. B., \& Cattaneo, Z.
(2017). Emotion processing in early blind and sighted individuals.
\emph{Neuropsychology}, \emph{31}(5), 516--524.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/neu0000360}{http://dx.doi.org/10.1037/neu0000360}

\hypertarget{ref-Garcea2012}{}
Garcea, F. E., Almeida, J., \& Mahon, B. Z. (2012). A right visual field
advantage for visual processing of manipulable objects. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, \emph{12}(4), 813--825.
doi:\href{https://doi.org/10.3758/s13415-012-0106-x}{10.3758/s13415-012-0106-x}

\hypertarget{ref-Garcia2017}{}
Garcia, A. F., Acosta, M., Pirani, S., Edwards, D., \& Osman, A. (2017).
Factor structure, factorial invariance, and validity of the
multidimensional shame-related response inventory-21 (MSRI-21).
\emph{Journal of Counseling Psychology}, \emph{64}(2), 233--246.
doi:\href{https://doi.org/10.1037/cou0000192}{10.1037/cou0000192}

\hypertarget{ref-Garcia-Mira2017}{}
García-Mira, R., Dumitru, A., Alonso-Betanzos, A., Sánchez-Maroño, N.,
Fontenla-Romero, Ó., Craig, T., \& Polhill, J. G. (2017). Testing
scenarios to achieve workplace sustainability goals using backcasting
and agent-based modeling. \emph{Environment and Behavior}, \emph{49}(9),
1007--1037.
doi:\href{https://doi.org/10.1177/0013916516673869}{10.1177/0013916516673869}

\hypertarget{ref-Garey2017}{}
Garey, L., Jardin, C., Kauffman, B. Y., Sharp, C., Neighbors, C.,
Schmidt, N. B., \& Zvolensky, M. J. (2017). Psychometric evaluation of
the Barriers to Cessation Scale. \emph{Psychological Assessment},
\emph{29}(7), 844--856.
doi:\href{https://doi.org/10.1037/pas0000379}{10.1037/pas0000379}

\hypertarget{ref-Garrido2016}{}
Garrido, M. V., Lopes, D., Prada, M., Rodrigues, D., Jerónimo, R., \&
Mourão, R. P. (2017). The many faces of a face: Comparing stills and
videos of facial expressions in eight dimensions (SAVE database).
\emph{Behavior Research Methods}, \emph{49}(4), 1343--1360.
doi:\href{https://doi.org/10.3758/s13428-016-0790-5}{10.3758/s13428-016-0790-5}

\hypertarget{ref-Garriott2017}{}
Garriott, P. O., Raque-Bogdan, T. L., Yalango, K., Ziemer, K. S., \&
Utley, J. (2017). Intentions to seek counseling in first-generation and
continuing-generation college students. \emph{Journal of Counseling
Psychology}, \emph{64}(4), 432--442.
doi:\href{https://doi.org/10.1037/cou0000210}{10.1037/cou0000210}

\hypertarget{ref-Gati2012}{}
Gati, I., Asulin-Peretz, L., \& Fisher, A. (2012). Emotional and
personality-related career decision-making difficulties. \emph{The
Counseling Psychologist}, \emph{40}(1), 6--27.
doi:\href{https://doi.org/10.1177/0011000011398726}{10.1177/0011000011398726}

\hypertarget{ref-Gattamorta2016}{}
Gattamorta, K. A., McCabe, B. E., Mena, M. P., \& Santisteban, D. A.
(2016). A latent profile analysis investigating factors impacting Latino
adolescents' attendance in treatment. \emph{The Counseling
Psychologist}, \emph{44}(6), 871--894.
doi:\href{https://doi.org/10.1177/0011000016642843}{10.1177/0011000016642843}

\hypertarget{ref-Gawronski2017}{}
Gawronski, B., Armstrong, J., Conway, P., Friesdorf, R., \& Hütter, M.
(2017). Consequences, norms, and generalized inaction in moral dilemmas:
The CNI model of moral decision-making. \emph{Journal of Personality and
Social Psychology}, \emph{113}(3), 343--376.
doi:\href{https://doi.org/10.1037/pspa0000086}{10.1037/pspa0000086}

\hypertarget{ref-Geary2012}{}
Geary, D. C., Hoard, M. K., \& Nugent, L. (2012). Independent
contributions of the central executive, intelligence, and in-class
attentive behavior to developmental change in the strategies used to
solve addition problems. \emph{Journal of Experimental Child
Psychology}, \emph{113}(1), 49--65.
doi:\href{https://doi.org/10.1016/j.jecp.2012.03.003}{10.1016/j.jecp.2012.03.003}

\hypertarget{ref-Geary2017}{}
Geary, D. C., Nicholas, A., Li, Y., \& Sun, J. (2017). Developmental
change in the influence of domain-general abilities and domain-specific
knowledge on mathematics achievement: An eight-year longitudinal study.
\emph{Journal of Educational Psychology}, \emph{109}(5), 680--693.
doi:\href{https://doi.org/10.1037/edu0000159}{10.1037/edu0000159}

\hypertarget{ref-Gebauer2016}{}
Gebauer, J. E., Sedikides, C., Schönbrodt, F. D., Bleidorn, W.,
Rentfrow, P. J., Potter, J., \& Gosling, S. D. (2017). The religiosity
as social value hypothesis: A multi-method replication and extension
across 65 countries and three levels of spatial aggregation.
\emph{Journal of Personality and Social Psychology}, \emph{113}(3),
18--39.
doi:\href{https://doi.org/10.1037/pspp0000104}{10.1037/pspp0000104}

\hypertarget{ref-Geiser2015}{}
Geiser, C., Litson, K., Bishop, J., Keller, B. T., Burns, G. L.,
Servera, M., \& Shiffman, S. (2015). Analyzing person, situation and
person × situation interaction effects: Latent state-trait models for
the combination of random and fixed situations. \emph{Psychological
Methods}, \emph{20}(2), 165--192.
doi:\href{https://doi.org/10.1037/met0000026}{10.1037/met0000026}

\hypertarget{ref-Gennari2012}{}
Gennari, S. P., Mirković, J., \& MacDonald, M. C. (2012). Animacy and
competition in relative clause production: A cross-linguistic
investigation. \emph{Cognitive Psychology}, \emph{65}(2), 141--176.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.03.002}{10.1016/j.cogpsych.2012.03.002}

\hypertarget{ref-Germeijs2012}{}
Germeijs, V., Luyckx, K., Notelaers, G., Goossens, L., \& Verschueren,
K. (2012). Choosing a major in higher education: Profiles of students'
decision-making process. \emph{Contemporary Educational Psychology},
\emph{37}(3), 229--239.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.12.002}{10.1016/j.cedpsych.2011.12.002}

\hypertarget{ref-Gilbert2017}{}
Gilbert, J. K., \& Fuchs, L. S. (2017). Bivariate developmental
relations between calculations and word problems: A latent change
approach. \emph{Contemporary Educational Psychology}, \emph{51}, 83--98.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.06.008}{10.1016/j.cedpsych.2017.06.008}

\hypertarget{ref-Gino2012}{}
Gino, F., \& Galinsky, A. D. (2012). Vicarious dishonesty: When
psychological closeness creates distance from one's moral compass.
\emph{Organizational Behavior and Human Decision Processes},
\emph{119}(1), 15--26.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.03.011}{10.1016/j.obhdp.2012.03.011}

\hypertarget{ref-Giromini2012}{}
Giromini, L., Velotti, P., De Campora, G., Bonalume, L., \& Cesare
Zavattini, G. (2012). Cultural adaptation of the difficulties in emotion
regulation scale: Reliability and validity of an Italian version.
\emph{Journal of Clinical Psychology}, \emph{68}(9), 989--1007.
doi:\href{https://doi.org/10.1002/jclp.21876}{10.1002/jclp.21876}

\hypertarget{ref-Glickman2017}{}
Glickman, K., Shear, M. K., \& Wall, M. M. (2017). Mediators of outcome
in complicated grief treatment. \emph{Journal of Clinical Psychology},
\emph{73}(7), 817--828.
doi:\href{https://doi.org/10.1002/jclp.22384}{10.1002/jclp.22384}

\hypertarget{ref-Gniewosz2012}{}
Gniewosz, B., \& Noack, P. (2012). What you see is what you get: The
role of early adolescents' perceptions in the intergenerational
transmission of academic values. \emph{Contemporary Educational
Psychology}, \emph{37}(1), 70--79.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.10.002}{10.1016/j.cedpsych.2011.10.002}

\hypertarget{ref-Goldberg2016}{}
Goldberg, A. E., Sweeney, K., Black, K., \& Moyer, A. (2016). Lesbian,
gay, and heterosexual adoptive parents' socialization approaches to
children's minority statuses. \emph{The Counseling Psychologist},
\emph{44}(2), 267--299.
doi:\href{https://doi.org/10.1177/0011000015628055}{10.1177/0011000015628055}

\hypertarget{ref-Goldsmith2003}{}
Goldsmith, P. A. (2003). Race relations and racial patterns in school
sports participation. \emph{Sociology of Sport Journal}, \emph{20}(2),
147--171.
doi:\href{https://doi.org/10.1123/ssj.20.2.147}{10.1123/ssj.20.2.147}

\hypertarget{ref-Gollwitzer2012}{}
Gollwitzer, M., \& Melzer, A. (2012). Macbeth and the Joystick: Evidence
for moral cleansing after playing a violent video game. \emph{Journal of
Experimental Social Psychology}, \emph{48}(6), 1356--1360.
doi:\href{https://doi.org/10.1016/j.jesp.2012.07.001}{10.1016/j.jesp.2012.07.001}

\hypertarget{ref-Gomez2017}{}
Gomez, D., Power, C., Gill, M. J., \& Fujiwara, E. (2017). Determinants
of risk-taking in HIV-associated neurocognitive disorders.
\emph{Neuropsychology}, \emph{31}(7), 798--810.
doi:\href{https://doi.org/10.1037/neu0000366}{10.1037/neu0000366}

\hypertarget{ref-Gomez2017a}{}
Gomez, R., Vance, A., \& Watson, S. (2016). Bifactor Model of WISC-IV:
Applicability and Measurement Invariance in Low and Normal IQ Groups.
\emph{Psychological Assessment}, \emph{29}(7), 902--912.
doi:\href{https://doi.org/10.1037/pas0000369}{10.1037/pas0000369}

\hypertarget{ref-Gommans2017}{}
Gommans, R., Müller, C. M., Stevens, G. W. J. M., Cillessen, A. H. N.,
\& Ter Bogt, T. F. M. (2017). Individual popularity, peer group
popularity composition and adolescents' alcohol consumption.
\emph{Journal of Youth and Adolescence}, \emph{46}(8), 1716--1726.
doi:\href{https://doi.org/10.1007/s10964-016-0611-2}{10.1007/s10964-016-0611-2}

\hypertarget{ref-Gongola2017}{}
Gongola, J., Krauss, D. A., \& Scurich, N. (2017). Life without parole
for juvenile offenders: Public sentiments. \emph{Psychology, Public
Policy, and Law}, \emph{23}(1), 96--104.
doi:\href{https://doi.org/10.1037/law0000111}{10.1037/law0000111}

\hypertarget{ref-Gonzalez-Mule2017}{}
Gonzalez-Mulé, E., \& Cockburn, B. (2017). Worked to eeath: The
relationships of job demands and job control with mortality.
\emph{Personnel Psychology}, \emph{70}(1), 73--112.
doi:\href{https://doi.org/10.1111/peps.12206}{10.1111/peps.12206}

\hypertarget{ref-Gonzalez2008}{}
González, J., De Boeck, P., \& Tuerlinckx, F. (2008). A double-structure
structural equation model for three-mode data. \emph{Psychological
Methods}, \emph{13}(4), 337--353.
doi:\href{https://doi.org/10.1037/a0013269}{10.1037/a0013269}

\hypertarget{ref-Goodrich2017}{}
Goodrich, J. M., \& Lonigan, C. J. (2017). Language-independent and
language-specific aspects of early literacy: An evaluation of the common
underlying proficiency model. \emph{Journal of Educational Psychology},
\emph{109}(6), 782--793.
doi:\href{https://doi.org/10.1037/edu0000179}{10.1037/edu0000179}

\hypertarget{ref-Goodwin2011}{}
Goodwin, G. P., \& Johnson-Laird, P. N. (2011). Mental models of Boolean
concepts. \emph{Cognitive Psychology}, \emph{63}(1), 34--59.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.04.001}{10.1016/j.cogpsych.2011.04.001}

\hypertarget{ref-Goodwin2017}{}
Goodwin, J. W., Conrad, A. L., Ansley, T., \& Nopoulos, P. (2017).
Arithmetical calculation and related neuropsychological skills in
subjects with isolated oral clefts. \emph{Neuropsychology},
\emph{31}(7), 834--841.
doi:\href{https://doi.org/10.1037/neu0000381}{10.1037/neu0000381}

\hypertarget{ref-Gordon2017}{}
Gordon, A. M., Stellar, J. E., Anderson, C. L., McNeil, G. D., Loew, D.,
\& Keltner, D. (2017). The dark side of the sublime: Distinguishing a
threat-based variant of awe. \emph{Journal of Personality and Social
Psychology}, \emph{113}(2), 310--328.
doi:\href{https://doi.org/10.1037/pspp0000120}{10.1037/pspp0000120}

\hypertarget{ref-Goschke2012}{}
Goschke, T., \& Bolte, A. (2012). On the modularity of implicit sequence
learning: Independent acquisition of spatial, symbolic, and manual
sequences. \emph{Cognitive Psychology}, \emph{65}(2), 284--320.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.04.002}{10.1016/j.cogpsych.2012.04.002}

\hypertarget{ref-Gobel2018}{}
Göbel, S. M., McCrink, K., Fischer, M. H., \& Shaki, S. (2018).
Observation of directional storybook reading influences young children's
counting direction. \emph{Journal of Experimental Child Psychology},
\emph{166}, 49--66.
doi:\href{https://doi.org/10.1016/j.jecp.2017.08.001}{10.1016/j.jecp.2017.08.001}

\hypertarget{ref-Granqvist}{}
Granqvist, P., Mikulincer, M., Gewirtz, V., \& Shaver, P. R. (2012).
Experimental findings on God as an attachment figure: Normative
processes and moderating effects of internal working models.
\emph{Journal of Personality and Social Psychology}, \emph{103}(5),
804--818. doi:\href{https://doi.org/10.1037/a0029344}{10.1037/a0029344}

\hypertarget{ref-Grant2017a}{}
Grant, D. A., Honn, K. A., Layton, M. E., Riedy, S. M., \& Van Dongen,
H. P. A. (2017). 3-minute smartphone-based and tablet-based psychomotor
vigilance tests for the assessment of reduced alertness due to sleep
deprivation. \emph{Behavior Research Methods}, \emph{49}(3), 1020--1029.
doi:\href{https://doi.org/10.3758/s13428-016-0763-8}{10.3758/s13428-016-0763-8}

\hypertarget{ref-Gray2016}{}
Gray, R., Orn, A., \& Woodman, T. (2017). Ironic and Reinvestment
Effects in Baseball Pitching: How Information About an Opponent Can
Influence Performance Under Pressure. \emph{Journal of Sport and
Exercise Psychology}, \emph{39}(1), 3--12.
doi:\href{https://doi.org/10.1123/jsep.2016-0035}{10.1123/jsep.2016-0035}

\hypertarget{ref-Greene2012}{}
Greene, J. A., Hutchison, L. A., Costa, L. J., \& Crompton, H. (2012).
Investigating how college students' task definitions and plans relate to
self-regulated learning processing and understanding of a complex
science topic. \emph{Contemporary Educational Psychology}, \emph{37}(4),
307--320.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.02.002}{10.1016/j.cedpsych.2012.02.002}

\hypertarget{ref-Greer2012}{}
Greer, T. M., Vendemia, J. M. C., \& Stancil, M. (2012). Neural
correlates of race-related social evaluations for African Americans and
White Americans. \emph{Neuropsychology}, \emph{26}(6), 704--712.
doi:\href{https://doi.org/10.1037/a0030035}{10.1037/a0030035}

\hypertarget{ref-Griepentrog2012}{}
Griepentrog, B. K., Harold, C. M., Holtz, B. C., Klimoski, R. J., \&
Marsh, S. M. (2012). Integrating social identity and the theory of
planned behavior: Predicting withdrawal from an organizational
recruitment process. \emph{Personnel Psychology}, \emph{65}(4),
723--753.
doi:\href{https://doi.org/10.1111/peps.12000}{10.1111/peps.12000}

\hypertarget{ref-Grilo2012}{}
Grilo, C. M., Crosby, R. D., Wilson, G. T., \& Masheb, R. M. (2012).
12-month follow-up of fluoxetine and cognitive behavioral therapy for
binge eating disorder. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(6), 1108--1113.
doi:\href{https://doi.org/10.1037/a0030061}{10.1037/a0030061}

\hypertarget{ref-Gromet2012}{}
Gromet, D. M., Okimoto, T. G., Wenzel, M., \& Darley, J. M. (2012). A
victim-centered approach to justice? Victim satisfaction effects on
third-party punishments. \emph{Law and Human Behavior}, \emph{36}(5),
375--389. doi:\href{https://doi.org/10.1037/h0093922}{10.1037/h0093922}

\hypertarget{ref-Grossmann2017}{}
Grossmann, I., \& Nickta, J. (2017). Cognition and the self: Attempt of
an independent close replication of the effects of self-construal
priming on spatial memory recall. \emph{Journal of Experimental Social
Psychology}, \emph{74}, 65--73.
doi:\href{https://doi.org/10.17605/OSF.IO/T34KF}{10.17605/OSF.IO/T34KF}

\hypertarget{ref-Gruxf8nhuxf8j2017}{}
Grønhøj, A., \& Thøgersen, J. (2017). Why young people do things for the
environment: The role of parenting for adolescents' motivation to engage
in pro-environmental behaviour. \emph{Journal of Environmental
Psychology}, \emph{54}, 11--19.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.09.005}{10.1016/j.jenvp.2017.09.005}

\hypertarget{ref-Guan2012}{}
Guan, K., Fox, K. R., \& Prinstein, M. J. (2012). Nonsuicidal
self-injury as a time-invariant predictor of adolescent suicide ideation
and attempts in a diverse community sample. \emph{Journal of Consulting
and Clinical Psychology}, \emph{80}(5), 842--849.
doi:\href{https://doi.org/10.1037/a0029429}{10.1037/a0029429}

\hypertarget{ref-Guarana2017}{}
Guarana, C. L., \& Barnes, C. M. (2017). Lack of sleep and the
development of leader-follower relationships over time.
\emph{Organizational Behavior and Human Decision Processes}, \emph{141},
57--73.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.04.003}{10.1016/j.obhdp.2017.04.003}

\hypertarget{ref-Gueguen2012}{}
Guéguen, N. (2012). Dead indoor plants strengthen belief in global
warming. \emph{Journal of Environmental Psychology}, \emph{32}(2),
173--177.
doi:\href{https://doi.org/10.1016/j.jenvp.2011.12.002}{10.1016/j.jenvp.2011.12.002}

\hypertarget{ref-Guillaume2012}{}
Guillaume, F., Guillem, F., Tiberghien, G., \& Stip, E. (2012).
Mismatched expressions decrease face recognition and corresponding ERP
old/new effects in schizophrenia. \emph{Neuropsychology}, \emph{26}(5),
568--577. doi:\href{https://doi.org/10.1037/a0028924}{10.1037/a0028924}

\hypertarget{ref-Gurland2012}{}
Gurland, S. T., Grolnick, W. S., \& Friendly, R. W. (2012). The role of
expectations in children's experience of novel events. \emph{Journal of
Experimental Child Psychology}, \emph{113}(3), 305--321.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.010}{10.1016/j.jecp.2012.06.010}

\hypertarget{ref-Haans2012}{}
Haans, A., \& Kort, Y. A. W. de. (2012). Light distribution in dynamic
street lighting: Two experimental studies on its effects on perceived
safety, prospect, concealment, and escape. \emph{Journal of
Environmental Psychology}, \emph{32}(4), 342--352.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.05.006}{10.1016/j.jenvp.2012.05.006}

\hypertarget{ref-Hadiwijaya2017}{}
Hadiwijaya, H., Klimstra, T. A., Vermunt, J. K., Branje, S. J. T., \&
Meeus, W. H. J. (2017). On the development of harmony, turbulence, and
independence in parent--adolescent relationships: A five-wave
longitudinal study. \emph{Journal of Youth and Adolescence},
\emph{46}(8), 1772--1788.
doi:\href{https://doi.org/10.1007/s10964-016-0627-7}{10.1007/s10964-016-0627-7}

\hypertarget{ref-Haegerich2013}{}
Haegerich, T. M., Salerno, J. M., \& Bottoms, B. L. (2013). Are the
effects of juvenile offender stereotypes maximized or minimized by jury
deliberation? \emph{Psychology, Public Policy, and Law}, \emph{19}(1),
81--97. doi:\href{https://doi.org/10.1037/a0027808}{10.1037/a0027808}

\hypertarget{ref-Hahn2017}{}
Hahn, E. R., \& Garrett, M. K. (2017). Preschoolers' moral judgments of
environmental harm and the influence of perspective taking.
\emph{Journal of Environmental Psychology}, \emph{53}, 11--19.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.05.004}{10.1016/j.jenvp.2017.05.004}

\hypertarget{ref-Hakvoort2017}{}
Hakvoort, B., Boer, M. van den, Leenaars, T., Bos, P., \& Tijms, J.
(2017). Improvements in reading accuracy as a result of increased
interletter spacing are not specific to children with dyslexia.
\emph{Journal of Experimental Child Psychology}, \emph{164}, 101--116.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.010}{10.1016/j.jecp.2017.07.010}

\hypertarget{ref-Hale-Smith2012}{}
Hale-Smith, A., Park, C. L., \& Edmondson, D. (2012). Measuring beliefs
about suffering: Development of the Views of Suffering Scale.
\emph{Psychological Assessment}, \emph{24}(4), 855--866.
doi:\href{https://doi.org/10.1037/a0027399}{10.1037/a0027399}

\hypertarget{ref-Hallett2012}{}
Hallett, D., Nunes, T., Bryant, P., \& Thorpe, C. M. (2012). Individual
differences in conceptual and procedural fraction understanding: The
role of abilities and school experience. \emph{Journal of Experimental
Child Psychology}, \emph{113}(4), 469--486.
doi:\href{https://doi.org/10.1016/j.jecp.2012.07.009}{10.1016/j.jecp.2012.07.009}

\hypertarget{ref-Halsband2012}{}
Halsband, T. M., Ferdinand, N. K., Bridger, E. K., \& Mecklinger, A.
(2012). Monetary rewards influence retrieval orientations.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{12}(3),
430--445.
doi:\href{https://doi.org/10.3758/s13415-012-0093-y}{10.3758/s13415-012-0093-y}

\hypertarget{ref-Hamm2012}{}
Hamm, J. A., Renard, S. B., Fogley, R. L., Leonhardt, B. L., Dimaggio,
G., Buck, K. D., \& Lysaker, P. H. (2012). Metacognition and social
cognition in schizophrenia: Stability and relationship to concurrent and
prospective symptom assessments. \emph{Journal of Clinical Psychology},
\emph{68}(12), 1303--1312.
doi:\href{https://doi.org/10.1002/jclp.21906}{10.1002/jclp.21906}

\hypertarget{ref-Hammer2013}{}
Hammer, J. H., \& Vogel, D. L. (2013). Assessing the utility of the
willingness/prototype model in predicting help-seeking decisions.
\emph{Journal of Counseling Psychology}, \emph{60}(1), 83--97.
doi:\href{https://doi.org/10.1037/a0030449}{10.1037/a0030449}

\hypertarget{ref-Hannah2012}{}
Hannah, S. T., Avolio, B. J., Walumbwa, F. O., \& Chan, A. (2012).
Leader self and means efficacy: A multi-component approach.
\emph{Organizational Behavior and Human Decision Processes},
\emph{118}(2), 143--161.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.03.007}{10.1016/j.obhdp.2012.03.007}

\hypertarget{ref-Hannon2012}{}
Hannon, B., \& Frias, S. (2012). A new measure for assessing the
contributions of higher level processes to language comprehension
performance in preschoolers. \emph{Journal of Educational Psychology},
\emph{104}(4), 897--921.
doi:\href{https://doi.org/10.1037/a0029156}{10.1037/a0029156}

\hypertarget{ref-Hanold2010}{}
Hanold, M. T. (2010). Beyond the marathon: (De)construction of female
ultrarunning bodies. \emph{Sociology of Sport Journal}, \emph{27}(2),
160--177.
doi:\href{https://doi.org/10.1123/ssj.27.2.160}{10.1123/ssj.27.2.160}

\hypertarget{ref-Harakeh2012}{}
Harakeh, Z., Sonneville, L. de, Eijnden, R. J. J. M. van den, Huizink,
A. C., Reijneveld, S. A., Ormel, J., \ldots{} Vollebergh, W. A. M.
(2012). The association between neurocognitive functioning and smoking
in adolescence: The TRAILS study. \emph{Neuropsychology}, \emph{26}(5),
541--550. doi:\href{https://doi.org/10.1037/a0029217}{10.1037/a0029217}

\hypertarget{ref-Harber2012}{}
Harber, K. D., Gorman, J. L., Gengaro, F. P., Butisingh, S., Tsang, W.,
\& Ouellette, R. (2012). Students' race and teachers' social support
affect the positive feedback bias in public schools. \emph{Journal of
Educational Psychology}, \emph{104}(4), 1149--1161.
doi:\href{https://doi.org/10.1037/a0028110}{10.1037/a0028110}

\hypertarget{ref-Harder2010}{}
Harder, V. S., Stuart, E. A., \& Anthony, J. C. (2010). Propensity score
techniques and the assessment of measured covariate balance to test
causal associations in psychological research. \emph{Psychological
Methods}, \emph{15}(3), 234--249.
doi:\href{https://doi.org/10.1037/a0019623}{10.1037/a0019623}

\hypertarget{ref-Harris2012}{}
Harris, J. I., Erbes, C. R., Engdahl, B. E., Ogden, H., Olson, R. H.,
Winskowski, A. M. M., \ldots{} Mataas, S. (2012). Religious distress and
coping with stressful life events: A longitudinal study. \emph{Journal
of Clinical Psychology}, \emph{68}(12), 1276--1286.
doi:\href{https://doi.org/10.1002/jclp.21900}{10.1002/jclp.21900}

\hypertarget{ref-Harris2017}{}
Harris, P. B., Boccaccini, M. T., \& Rice, A. K. (2017). Field measures
of psychopathy and sexual deviance as predictors of recidivism among
sexual offenders. \emph{Psychological Assessment}, \emph{29}(6),
639--651.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/pas0000394}{http://dx.doi.org/10.1037/pas0000394}

\hypertarget{ref-Harrison2011}{}
Harrison, C. K., Lawrence, S. M., \& Bukstein, S. J. (2011). White
college students' explanations of white (and black) athletic
performance: a qualitative investigation of white college students.
\emph{Sociology of Sport Journal}, \emph{28}(3), 347--361.
doi:\href{https://doi.org/10.1123/ssj.28.3.347}{10.1123/ssj.28.3.347}

\hypertarget{ref-Hartley2012}{}
Hartley, A. A., Maquestiaux, F., Brooks, R. D., Festini, S. B., \&
Frazier, K. (2012). Electrodermal responses to sources of dual-task
interference. \emph{Cognitive, Affective, \& Behavioral Neuroscience},
\emph{12}(3), 543--556.
doi:\href{https://doi.org/10.3758/s13415-012-0094-x}{10.3758/s13415-012-0094-x}

\hypertarget{ref-Hartson2012}{}
Hartson, K. A., \& Sherman, D. K. (2012). Gradual escalation: The role
of continuous commitments in perceptions of guilt. \emph{Journal of
Experimental Social Psychology}, \emph{48}(6), 1279--1290.
doi:\href{https://doi.org/10.1016/j.jesp.2012.06.005}{10.1016/j.jesp.2012.06.005}

\hypertarget{ref-Hasni2017}{}
Hasni, A. A., Adamson, L. B., Williamson, R. A., \& Robins, D. L.
(2017). Adding sound to theory of mind: Comparing children's development
of mental-state understanding in the auditory and visual realms.
\emph{Journal of Experimental Child Psychology}, \emph{164}, 239--249.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.009}{10.1016/j.jecp.2017.07.009}

\hypertarget{ref-Hay2011}{}
Hay, J. F., Pelucchi, B., Estes, K. G., \& Saffran, J. R. (2011).
Linking sounds to meanings: Infant statistical learning in a natural
language. \emph{Cognitive Psychology}, \emph{63}(2), 93--106.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.06.002}{10.1016/j.cogpsych.2011.06.002}

\hypertarget{ref-Hayton2017}{}
Hayton, J. W. (2017). ``They need to learn to take it on the chin'':
Exploring the emotional labour of student volunteers in a sports-based
outreach project in the North East of England. \emph{Sociology of Sport
Journal}, \emph{34}(2), 136--147.
doi:\href{https://doi.org/10.1123/ssj.2016-0098}{10.1123/ssj.2016-0098}

\hypertarget{ref-Hazlett-Stevens2017}{}
Hazlett-Stevens, H., \& Oren, Y. (2017). Effectiveness of
mindfulness-based stress reduction bibliotherapy: A preliminary
randomized controlled trial. \emph{Journal of Clinical Psychology},
\emph{73}(6), 626--637.
doi:\href{https://doi.org/10.1002/jclp.22370}{10.1002/jclp.22370}

\hypertarget{ref-Heath2016}{}
Heath, P. J., Vogel, D. L., \& Al-Darmaki, F. R. (2016). Help-Seeking
attitudes of United Arab Emirates Students. \emph{The Counseling
Psychologist}, \emph{44}(3), 331--352.
doi:\href{https://doi.org/10.1177/0011000015621149}{10.1177/0011000015621149}

\hypertarget{ref-Hebl2012}{}
Hebl, M. R., Williams, M. J., Sundermann, J. M., Kell, H. J., \& Davies,
P. G. (2012). Selectively friending: Racial stereotypicality and social
rejection. \emph{Journal of Experimental Social Psychology},
\emph{48}(6), 1329--1335.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.019}{10.1016/j.jesp.2012.05.019}

\hypertarget{ref-Heck2017}{}
Heck, D. W., Hilbig, B. E., \& Moshagen, M. (2017). From information
processing to decisions: Formalizing and comparing psychologically
plausible choice models. \emph{Cognitive Psychology}, \emph{96}, 26--40.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.05.003}{10.1016/j.cogpsych.2017.05.003}

\hypertarget{ref-Hehman2017}{}
Hehman, E., Sutherland, C. A. M., Flake, J. K., \& Slepian, M. L.
(2017). The unique contributions of perceiver and target characteristics
in person perception. \emph{Journal of Personality and Social
Psychology}, \emph{113}(4), 513--529.
doi:\href{https://doi.org/10.1037/pspa0000090}{10.1037/pspa0000090}

\hypertarget{ref-Hein2017}{}
Hein, S., Barbot, B., Square, A., Chapman, J., Geib, C. F., \&
Grigorenko, E. L. (2017). Violent offending among juveniles: A 7-year
longitudinal study of recidivism, desistance, and associations with
mental health. \emph{Law and Human Behavior}, \emph{41}(3), 273--283.
doi:\href{https://doi.org/10.1037/lhb0000241}{10.1037/lhb0000241}

\hypertarget{ref-Heinrichs2017}{}
Heinrichs, R. W., Parlar, M., \& Pinnock, F. (2017). Normal-range
verbal-declarative memory in schizophrenia. \emph{Neuropsychology},
\emph{31}(7), 778--786.
doi:\href{https://doi.org/10.1037/neu0000365}{10.1037/neu0000365}

\hypertarget{ref-Heitland2012}{}
Heitland, I., Oosting, R. S., Baas, J. M. P., Massar, S. A. A.,
Kenemans, J. L., \& Böcker, K. B. E. (2012). Genetic polymorphisms of
the dopamine and serotonin systems modulate the neurophysiological
response to feedback and risk taking in healthy humans. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, \emph{12}(4), 678--691.
doi:\href{https://doi.org/10.3758/s13415-012-0108-8}{10.3758/s13415-012-0108-8}

\hypertarget{ref-Helm2017}{}
Helm, R. K., \& Reyna, V. F. (2017). Logical but incompetent plea
decisions: A new approach to plea bargaining grounded in cognitive
theory. \emph{Psychology, Public Policy, and Law}, \emph{23}(3),
367--380.
doi:\href{https://doi.org/10.1037/law0000125}{10.1037/law0000125}

\hypertarget{ref-Helmus2017}{}
Helmus, L. M., \& Ternes, M. (2017). Temporary absences from prison in
Canada reduce unemployment and reoffending: Evidence for dosage effects
from an exploratory study. \emph{Psychology, Public Policy, and Law},
\emph{23}(1), 23--38.
doi:\href{https://doi.org/10.1037/law0000104}{10.1037/law0000104}

\hypertarget{ref-Henderson2012}{}
Henderson, J. M., \& Luke, S. G. (2012). Oculomotor inhibition of return
in normal and mindless reading. \emph{Psychonomic Bulletin \& Review},
\emph{19}(6), 1101--1107.
doi:\href{https://doi.org/10.3758/s13423-012-0274-2}{10.3758/s13423-012-0274-2}

\hypertarget{ref-Hendrickx2017}{}
Hendrickx, M. M. H. G., Mainhard, T., Oudman, S., Boor-Klip, H. J., \&
Brekelmans, M. (2017). Teacher behavior and peer liking and disliking:
The teacher as a social referent for peer status. \emph{Journal of
Educational Psychology}, \emph{109}(4), 546--558.
doi:\href{https://doi.org/10.1037/edu0000157}{10.1037/edu0000157}

\hypertarget{ref-Herbort2017}{}
Herbort, O., Mathew, H., \& Kunde, W. (2017). Habit outweighs planning
in grasp selection for object manipulation. \emph{Cognitive Psychology},
\emph{92}, 127--140.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.11.008}{10.1016/j.cogpsych.2016.11.008}

\hypertarget{ref-Hermannsdottir2016}{}
Hermannsdóttir, B. S., \& Ægisdóttir, S. (2016). Spirituality,
connectedness, and beliefs about psychological services among Filipino
immigrants in Iceland. \emph{The Counseling Psychologist}, \emph{44}(4),
546--572.
doi:\href{https://doi.org/10.1177/0011000016639146}{10.1177/0011000016639146}

\hypertarget{ref-Herron2017}{}
Herron, J. E. (2017). ERP evidence for the control of emotional memories
during strategic retrieval. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, 737--753.
doi:\href{https://doi.org/10.3758/s13415-017-0509-9}{10.3758/s13415-017-0509-9}

\hypertarget{ref-Hershcovis2017}{}
Hershcovis, M. S., Neville, L., Reich, T. C., Christie, A. M., Cortina,
L. M., \& Shan, J. V. (2017). Witnessing wrongdoing: The effects of
observer power on incivility intervention in the workplace.
\emph{Organizational Behavior and Human Decision Processes},
\emph{142}(November 2015), 45--57.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.07.006}{10.1016/j.obhdp.2017.07.006}

\hypertarget{ref-Herzberg2012}{}
Herzberg, K. N., Sheppard, S. C., Forsyth, J. P., Credé, M., Earleywine,
M., \& Eifert, G. H. (2012). The Believability of Anxious Feelings and
Thoughts Questionnaire (BAFT): A psychometric evaluation of cognitive
fusion in a nonclinical and highly anxious community sample.
\emph{Psychological Assessment}, \emph{24}(4), 877--891.
doi:\href{https://doi.org/10.1037/a0027782}{10.1037/a0027782}

\hypertarget{ref-Hess2012}{}
Hess, U., Adams, R. B., Simard, A., Stevenson, M. T., \& Kleck, R. E.
(2012). Smiling and sad wrinkles: Age-related changes in the face and
the perception of emotions and intentions. \emph{Journal of Experimental
Social Psychology}, \emph{48}(6), 1377--1380.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.018}{10.1016/j.jesp.2012.05.018}

\hypertarget{ref-Heuer2016}{}
Heuer, A., \& Schubö, A. (2017). Selective weighting of action-related
feature dimensions in visual working memory. \emph{Psychonomic Bulletin
\& Review}, \emph{24}(4), 1129--1134.
doi:\href{https://doi.org/10.3758/s13423-016-1209-0}{10.3758/s13423-016-1209-0}

\hypertarget{ref-Hildebrand2013}{}
Hildebrand, M., Hol, A. M., \& Bosker, J. (2013). Predicting probation
supervision violations. \emph{Psychology, Public Policy, and Law},
\emph{19}(1), 114--125.
doi:\href{https://doi.org/10.1037/a0028179}{10.1037/a0028179}

\hypertarget{ref-Hill2017}{}
Hill, R. M., Oosterhoff, B., \& Kaplow, J. B. (2017). Prospective
identification of adolescent suicide ideation using classification tree
analysis: Models for community-based screening. \emph{Journal of
Consulting and Clinical Psychology}, \emph{85}(7), 702--711.
doi:\href{https://doi.org/10.1037/ccp0000218}{10.1037/ccp0000218}

\hypertarget{ref-Hinshaw2012}{}
Hinshaw, S. P., Owens, E. B., Zalecki, C., Huggins, S. P.,
Montenegro-Nevado, A. J., Schrodek, E., \& Swanson, E. N. (2012).
Prospective follow-up of girls with attention-deficit/hyperactivity
disorder into early adulthood: Continuing impairment includes elevated
risk for suicide attempts and self-injury. \emph{Journal of Consulting
and Clinical Psychology}, \emph{80}(6), 1041--1051.
doi:\href{https://doi.org/10.1037/a0029451}{10.1037/a0029451}

\hypertarget{ref-Hintz2017}{}
Hintz, F., Meyer, A. S., \& Huettig, F. (2017). Predictors of
verb-mediated anticipatory eye movements in the visual world.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(9), 1352--1374.
doi:\href{https://doi.org/10.1037/xlm0000388}{10.1037/xlm0000388}

\hypertarget{ref-Hirschfeld2011}{}
Hirschfeld, R. R., \& Thomas, C. H. (2011). Age- and gender-based role
incongruence: Implications for knowledge mastery and observed leadership
potential among personnel in a leadership development program.
\emph{Personnel Psychology}, \emph{64}(3), 661--692.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01222.x}{10.1111/j.1744-6570.2011.01222.x}

\hypertarget{ref-Ho2017}{}
Ho, C. S.-H., Zheng, M., McBride, C., Hsu, L. S. J., Waye, M. M., \&
Kwok, J. C.-Y. (2017). Examining an extended simple view of reading in
Chinese: The role of naming efficiency for reading comprehension.
\emph{Contemporary Educational Psychology}, \emph{51}, 293--302.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.08.009}{10.1016/j.cedpsych.2017.08.009}

\hypertarget{ref-Hoffman2012}{}
Hoffman, B. J., Gorman, C. A., Blair, C. A., Meriac, J. P., Overstreet,
B., \& Atchley, E. K. (2012). Evidence for the effectiveness of an
alternative multisource performance rating methodology. \emph{Personnel
Psychology}, \emph{65}(3), 531--563.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01252.x}{10.1111/j.1744-6570.2012.01252.x}

\hypertarget{ref-Hoffmann2016}{}
Hoffmann, A., Waubert de Puiseau, B., Schmidt, A. F., \& Musch, J.
(2017). On the comprehensibility and perceived privacy protection of
indirect questioning techniques. \emph{Behavior Research Methods},
\emph{49}(4), 1470--1483.
doi:\href{https://doi.org/10.3758/s13428-016-0804-3}{10.3758/s13428-016-0804-3}

\hypertarget{ref-Holland2017}{}
Holland, K. J., \& Cortina, L. M. (2017). The evolving landscape of
Title IX: Predicting mandatory reporters' responses to sexual assault
disclosures. \emph{Law and Human Behavior}, \emph{41}(5), 429--439.
doi:\href{https://doi.org/10.1037/lhb0000253}{10.1037/lhb0000253}

\hypertarget{ref-Hong2012}{}
Hong, G. (2012). Marginal mean weighting through stratification: A
generalized method for evaluating multivalued and multiple treatments
with nonexperimental data. \emph{Psychological Methods}, \emph{17}(1),
44--60. doi:\href{https://doi.org/10.1037/a0024918}{10.1037/a0024918}

\hypertarget{ref-Honold2012}{}
Honold, J., Beyer, R., Lakes, T., \& Meer, E. van der. (2012). Multiple
environmental burdens and neighborhood-related health of city residents.
\emph{Journal of Environmental Psychology}, \emph{32}(4), 305--317.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.05.002}{10.1016/j.jenvp.2012.05.002}

\hypertarget{ref-Hovardas2012}{}
Hovardas, T., \& Korfiatis, K. (2012). Effects of an environmental
education course on consensus estimates for proenvironmental intentions.
\emph{Environment and Behavior}, \emph{44}(6), 760--784.
doi:\href{https://doi.org/10.1177/0013916511407308}{10.1177/0013916511407308}

\hypertarget{ref-Hoyos2017}{}
Hoyos, C., \& Gentner, D. (2017). Generating explanations via analogical
comparison. \emph{Psychonomic Bulletin \& Review}, \emph{24}(5),
1364--1374.
doi:\href{https://doi.org/10.3758/s13423-017-1289-5}{10.3758/s13423-017-1289-5}

\hypertarget{ref-Hsee2012}{}
Hsee, C. K., Shen, L., Zhang, S., Chen, J., \& Zhang, L. (2012). Fate or
fight: Exploring the hedonic costs of competition. \emph{Organizational
Behavior and Human Decision Processes}, \emph{119}(2), 177--186.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.07.005}{10.1016/j.obhdp.2012.07.005}

\hypertarget{ref-Hu2017}{}
Hu, S., Creed, P. A., \& Hood, M. (2017). Career goal revision in
response to negative feedback: Testing a longitudinal cross-lagged
model. \emph{Journal of Counseling Psychology}, \emph{64}(3), 335--345.
doi:\href{https://doi.org/10.1037/cou0000193}{10.1037/cou0000193}

\hypertarget{ref-Huang2017}{}
Huang, S. chi, Jin, L., \& Zhang, Y. (2017). Step by step: Sub-goals as
a source of motivation. \emph{Organizational Behavior and Human Decision
Processes}, \emph{141}, 1--15.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.05.001}{10.1016/j.obhdp.2017.05.001}

\hypertarget{ref-Huang2017a}{}
Huang, J. L., Ford, J. K., \& Ryan, A. M. (2017). Ignored no more:
Within-person variability enables better understanding of training
transfer. \emph{Personnel Psychology}, \emph{70}(3), 557--596.
doi:\href{https://doi.org/10.1111/peps.12155}{10.1111/peps.12155}

\hypertarget{ref-Huang2017b}{}
Huang, K., Yeomans, M., Brooks, A. W., Minson, J., \& Gino, F. (2017).
It doesn't hurt to ask: Question-asking increases liking. \emph{Journal
of Personality and Social Psychology}, \emph{113}(3), 430--452.
doi:\href{https://doi.org/10.1037/pspi0000097}{10.1037/pspi0000097}

\hypertarget{ref-Huff2012}{}
Huff, M. J., Coane, J. H., Hutchison, K. A., Grasser, E. B., \& Blais,
J. E. (2012). Interpolated task effects on direct and mediated false
recognition: Effects of initial recall, recognition, and the ironic
effect of guessing. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{38}(6), 1720--1730.
doi:\href{https://doi.org/10.1037/a0028476}{10.1037/a0028476}

\hypertarget{ref-Huff2012a}{}
Huff, M., \& Schwan, S. (2012). Do not cross the line: Heuristic spatial
updating in dynamic scenes. \emph{Psychonomic Bulletin \& Review},
\emph{19}(6), 1065--1072.
doi:\href{https://doi.org/10.3758/s13423-012-0293-z}{10.3758/s13423-012-0293-z}

\hypertarget{ref-Hughes2012}{}
Hughes, J. N., Wu, J.-Y., Kwok, O.-m., Villarreal, V., \& Johnson, A. Y.
(2012). Indirect effects of child reports of teacher--student
relationship on achievement. \emph{Journal of Educational Psychology},
\emph{104}(2), 350--365.
doi:\href{https://doi.org/10.1037/a0026339}{10.1037/a0026339}

\hypertarget{ref-Humphrey2017}{}
Humphrey, S. E., Aime, F., Cushenbery, L., Hill, A. D., \& Fairchild, J.
(2017). Team conflict dynamics: Implications of a dyadic view of
conflict for team performance. \emph{Organizational Behavior and Human
Decision Processes}, \emph{142}, 58--70.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.08.002}{10.1016/j.obhdp.2017.08.002}

\hypertarget{ref-Humphreys2017}{}
Humphreys, M. S., McFarlane, K. A., Burt, J. S., Kelly, S. J.,
Weatherall, K. G., \& Burrell, R. G. (2017). How important is the name
in predicting false recognition for lookalike brands? \emph{Psychology,
Public Policy, and Law}, \emph{23}(3), 381--395.
doi:\href{https://doi.org/10.1037/law0000133}{10.1037/law0000133}

\hypertarget{ref-Hund2012}{}
Hund, A. M., Schmettow, M., \& Noordzij, M. L. (2012). The impact of
culture and recipient perspective on direction giving in the service of
wayfinding. \emph{Journal of Environmental Psychology}, \emph{32}(4),
327--336.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.05.007}{10.1016/j.jenvp.2012.05.007}

\hypertarget{ref-Hunter2017}{}
Hunter, J. A., Platow, M. J., Moradi, S., Banks, M., Hayhurst, J.,
Kafka, S., \ldots{} Ruffman, T. (2017). Subjective belonging and
in-group favoritism. \emph{Journal of Experimental Social Psychology},
\emph{73}, 136--146.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.010}{10.1016/j.jesp.2017.06.010}

\hypertarget{ref-Huo2012}{}
Huo, Y., Lam, W., \& Chen, Z. (2012). Am I the only one this supervisor
is laughing at? Effects of aggressive humor on employee strain and
addictive behaviors. \emph{Personnel Psychology}, \emph{65}(4),
859--885.
doi:\href{https://doi.org/10.1111/peps.12004}{10.1111/peps.12004}

\hypertarget{ref-Hurst2017}{}
Hurst, M., \& Cordes, S. (2017). Working memory strategies during
rational number magnitude processing. \emph{Journal of Educational
Psychology}, \emph{109}(5), 694--708.
doi:\href{https://doi.org/10.1037/edu0000169}{10.1037/edu0000169}

\hypertarget{ref-Hutchison2012}{}
Hutchison, J. L., Hubbard, T. L., Ferrandino, B., Brigante, R., Wright,
J. M., \& Rypma, B. (2012). Auditory memory distortion for spoken prose.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{38}(6), 1469--1489.
doi:\href{https://doi.org/10.1037/a0028464}{10.1037/a0028464}

\hypertarget{ref-Huysmans2017}{}
Huysmans, Z., \& Clement, D. (2017). A preliminary exploration of the
application of self-compassion within the context of sport injury.
\emph{Journal of Sport and Exercise Psychology}, \emph{39}(1), 56--66.
doi:\href{https://doi.org/10.1123/jsep.2016-0144}{10.1123/jsep.2016-0144}

\hypertarget{ref-Hyde2012}{}
Hyde, A. L., Elavsky, S., Doerksen, S. E., \& Conroy, D. E. (2012). The
stability of automatic evaluations of physical activity and their
relations with physical activity. \emph{Journal of Sport and Exercise
Psychology}, \emph{34}(6), 715--736.
doi:\href{https://doi.org/10.1123/jsep.34.6.715}{10.1123/jsep.34.6.715}

\hypertarget{ref-Impairment2017}{}
Impairment, C., Case, A., \& Kvavilashvili, L. (2017). Spontaneous
retrieval deficits in amnestic mild cognitive impairment : A case of
focal event-based prospective memory. \emph{Neuropsychology},
\emph{31}(7), 735--749.
doi:\href{https://doi.org/10.1037/neu0000378}{10.1037/neu0000378}

\hypertarget{ref-Izura2012}{}
Izura, C., \& Playfoot, D. (2012). A normative study of acronyms and
acronym naming. \emph{Behavior Research Methods}, \emph{44}(3),
862--889.
doi:\href{https://doi.org/10.3758/s13428-011-0175-8}{10.3758/s13428-011-0175-8}

\hypertarget{ref-Ja2017}{}
Ja, N. M., \& Jose, P. E. (2017). ``I can't take hold of some kind of a
life'': The role of social connectedness and confidence in engaging
``lost'' adolescents with their lives. \emph{Journal of Youth and
Adolescence}, \emph{46}(9), 2028--2046.
doi:\href{https://doi.org/10.1007/s10964-017-0656-x}{10.1007/s10964-017-0656-x}

\hypertarget{ref-Jaeger2012}{}
Jaeger, A., \& Rugg, M. D. (2012). Implicit effects of emotional
contexts: An ERP study. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{12}(4), 748--760.
doi:\href{https://doi.org/10.3758/s13415-012-0110-1}{10.3758/s13415-012-0110-1}

\hypertarget{ref-Jaeger2017}{}
Jaeger, C. B., Levin, D. T., \& Porter, E. (2017). Justice is (change)
blind: Applying research on visual metacognition in legal settings.
\emph{Psychology, Public Policy, and Law}, \emph{23}(2), 259--279.
doi:\href{https://doi.org/10.1037/law0000107}{10.1037/law0000107}

\hypertarget{ref-Jahng2008}{}
Jahng, S., Wood, P. K., \& Trull, T. J. (2008). Analysis of affective
instability in ecological momentary assessment: Indices using successive
difference and group comparison via multilevel modeling.
\emph{Psychological Methods}, \emph{13}(4), 354--375.
doi:\href{https://doi.org/10.1037/a0014173}{10.1037/a0014173}

\hypertarget{ref-Jang2012}{}
Jang, H., Kim, E. J., \& Reeve, J. (2012). Longitudinal test of
self-determination theory's motivation mediation model in a naturally
occurring classroom context. \emph{Journal of Educational Psychology},
\emph{104}(4), 1175--1188.
doi:\href{https://doi.org/10.1037/a0028089}{10.1037/a0028089}

\hypertarget{ref-Janos2012}{}
Janos, A. L., Grange, D. K., Steiner, R. D., \& White, D. A. (2012).
Processing speed and executive abilities in children with
phenylketonuria. \emph{Neuropsychology}, \emph{26}(6), 735--743.
doi:\href{https://doi.org/10.1037/a0029419}{10.1037/a0029419}

\hypertarget{ref-Jansen2016}{}
Jansen, K. J., Shipp, A. J., \& Michael, J. H. (2016). \emph{Champions,
converts, doubters, and defectors: The impact of shifting perceptions on
momentum for change.} (Vol. 69, pp. 673--707).
doi:\href{https://doi.org/10.1111/peps.12120}{10.1111/peps.12120}

\hypertarget{ref-Jansen2017}{}
Jansen, S. J., Hoekstra, J. S., \& Boumeester, H. J. (2017). The impact
of earthquakes on the intention to move: Fight or flight? \emph{Journal
of Environmental Psychology}, \emph{54}, 38--49.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.09.006}{10.1016/j.jenvp.2017.09.006}

\hypertarget{ref-Janssen2016}{}
Janssen, M. A., \& Baggio, J. A. (2016). Using agent-based models to
compare behavioral theories on experimental data: Application for
irrigation games. \emph{Journal of Environmental Psychology}, \emph{46},
106--115.
doi:\href{https://doi.org/10.1016/j.jenvp.2016.04.003}{10.1016/j.jenvp.2016.04.003}

\hypertarget{ref-Jayawickreme2012}{}
Jayawickreme, N., Jayawickreme, E., Atanasov, P., Goonasekera, M. A., \&
Foa, E. B. (2012). Are culturally specific measures of trauma-related
anxiety and depression needed? The case of Sri Lanka.
\emph{Psychological Assessment}, \emph{24}(4), 791--800.
doi:\href{https://doi.org/10.1037/a0027564}{10.1037/a0027564}

\hypertarget{ref-Jazaieri2012}{}
Jazaieri, H., Goldin, P. R., Werner, K., Ziv, M., \& Gross, J. J.
(2012). A randomized rrial of MBSR versus aerobic exercise for social
anxiety disorder. \emph{Journal of Clinical Psychology}, \emph{68}(7),
715--731.
doi:\href{https://doi.org/10.1002/jclp.21863}{10.1002/jclp.21863}

\hypertarget{ref-Jenkins2017}{}
Jenkins, A. C., \& Hsu, M. (2017). Dissociable contributions of
imagination and willpower to the malleability of human patience.
\emph{Psychological Science}, \emph{28}(7), 894--906.
doi:\href{https://doi.org/10.1177/0956797617698133}{10.1177/0956797617698133}

\hypertarget{ref-Jensen2017}{}
Jensen, M., Chassin, L., \& Gonzales, N. A. (2017). Neighborhood
moderation of sensation seeking effects on adolescent substance use
initiation. \emph{Journal of Youth and Adolescence}, \emph{46}(9),
1953--1967.
doi:\href{https://doi.org/10.1007/s10964-017-0647-y}{10.1007/s10964-017-0647-y}

\hypertarget{ref-Job2012}{}
Job, J. M., \& Klassen, R. M. (2012). Predicting performance on academic
and non-academic tasks: A comparison of adolescents with and without
learning disabilities. \emph{Contemporary Educational Psychology},
\emph{37}(2), 162--169.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.05.001}{10.1016/j.cedpsych.2011.05.001}

\hypertarget{ref-Joh2012}{}
Joh, A. S., \& Spivey, L. A. (2012). Colorful success: Preschoolers' use
of perceptual color cues to solve a spatial reasoning problem.
\emph{Journal of Experimental Child Psychology}, \emph{113}(4),
523--534.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.012}{10.1016/j.jecp.2012.06.012}

\hypertarget{ref-Johnson2017}{}
Johnson, L. R., Chin, E. G., Kajumba, M., Buchanan, E., Kizito, S., \&
Bangirana, P. (2017a). Do concepts of depression predict treatment
pathways? A closer look at explanatory models among clinical and
nonclinical samples in uganda. \emph{Journal of Clinical Psychology},
\emph{73}(7), 893--909.
doi:\href{https://doi.org/10.1002/jclp.22378}{10.1002/jclp.22378}

\hypertarget{ref-Johnson2017a}{}
Johnson, R. E., King, D. D., Joanna Lin, S. H., Scott, B. A., Jackson
Walker, E. M., \& Wang, M. (2017b). Regulatory focus trickle-down. How
leader regulatory focus and behavior shape follower regulatory focus.
\emph{Organizational Behavior and Human Decision Processes}, \emph{140},
29--45.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.03.002}{10.1016/j.obhdp.2017.03.002}

\hypertarget{ref-Johnson2012}{}
Johnson, R. J., \& Scicchitano, M. J. (2012). Don't call me NIMBY.
\emph{Environment and Behavior}, \emph{44}(3), 410--426.
doi:\href{https://doi.org/10.1177/0013916511435354}{10.1177/0013916511435354}

\hypertarget{ref-Johnson2012a}{}
Johnson, R. L., Staub, A., \& Fleri, A. M. (2012). Distributional
analysis of the transposed-letter neighborhood effect on naming latency.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{38}(6), 1773--1779.
doi:\href{https://doi.org/10.1037/a0028222}{10.1037/a0028222}

\hypertarget{ref-Jonas2017}{}
Jonas, C., Spiller, M. J., \& Hibbard, P. (2017). Summation of visual
attributes in auditory--visual crossmodal correspondences.
\emph{Psychonomic Bulletin \& Review}, \emph{24}(4), 1104--1112.
doi:\href{https://doi.org/10.3758/s13423-016-1215-2}{10.3758/s13423-016-1215-2}

\hypertarget{ref-Jones2017}{}
Jones, D. N., \& Paulhus, D. L. (2017). Duplicity among the dark triad:
Three faces of deceit. \emph{Journal of Personality and Social
Psychology}, \emph{113}(2), 329--342.
doi:\href{https://doi.org/10.1037/pspp0000139}{10.1037/pspp0000139}

\hypertarget{ref-Jones2015}{}
Jones, J. A., \& Waller, N. G. (2015). Fungible weights in logistic
regression. \emph{Psychological Methods}, \emph{21}(2), 241--260.
doi:\href{https://doi.org/10.1037/met0000060}{10.1037/met0000060}

\hypertarget{ref-Jones2016}{}
Jones, N. M., Wojcik, S. P., Sweeting, J., \& Silver, R. C. (2016).
Tweeting negative emotion: An investigation of Twitter data in the
aftermath of violence on college campuses. \emph{Psychological Methods},
\emph{21}(4), 526--541.
doi:\href{https://doi.org/10.1037/met0000099}{10.1037/met0000099}

\hypertarget{ref-Junot2017}{}
Junot, A., Paquet, Y., \& Martin-Krumm, C. (2017). Passion for outdoor
activities and environmental behaviors: A look at emotions related to
passionate activities. \emph{Journal of Environmental Psychology},
\emph{53}, 177--184.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.07.011}{10.1016/j.jenvp.2017.07.011}

\hypertarget{ref-Kabo2017}{}
Kabo, F. W. (2017). A model of potential encounters in the workplace:
The relationships of homophily, spatial distance, organizational
structure, and perceived networks. \emph{Environment and Behavior},
\emph{49}(6), 638--662.
doi:\href{https://doi.org/10.1177/0013916516658501}{10.1177/0013916516658501}

\hypertarget{ref-Kahn2017}{}
Kahn, J. H., Wei, M., Su, J. C., Han, S., \& Strojewska, A. (2017).
Distress disclosure and psychological functioning among Taiwanese
nationals and European Americans: The moderating roles of mindfulness
and nationality. \emph{Journal of Counseling Psychology}, \emph{64}(3),
292--301.
doi:\href{https://doi.org/10.1037/cou0000202}{10.1037/cou0000202}

\hypertarget{ref-Kaiser2017}{}
Kaiser, J., Südkamp, A., \& Möller, J. (2017). The effects of student
characteristics on teachers' judgment accuracy: Disentangling ethnicity,
minority status, and achievement. \emph{Journal of Educational
Psychology}, \emph{109}(6), 871--888.
doi:\href{https://doi.org/10.1037/edu0000156}{10.1037/edu0000156}

\hypertarget{ref-Kanakri2017}{}
Kanakri, S. M., Shepley, M., Tassinary, L. G., Varni, J. W., \& Fawaz,
H. M. (2017). An observational study of classroom acoustical design and
repetitive behaviors in children with Autism. \emph{Environment and
Behavior}, \emph{49}(8), 847--873.
doi:\href{https://doi.org/10.1177/0013916516669389}{10.1177/0013916516669389}

\hypertarget{ref-Kangur2017}{}
Kangur, A., Jager, W., Verbrugge, R., \& Bockarjova, M. (2017). An
agent-based model for diffusion of electric vehicles. \emph{Journal of
Environmental Psychology}, \emph{52}, 166--182.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.01.002}{10.1016/j.jenvp.2017.01.002}

\hypertarget{ref-Kaplan2012}{}
Kaplan, S. A., Vogel, D. L., Gentile, D. A., \& Wade, N. G. (2012).
Increasing positive perceptions of counseling. \emph{The Counseling
Psychologist}, \emph{40}(3), 409--442.
doi:\href{https://doi.org/10.1177/0011000011414211}{10.1177/0011000011414211}

\hypertarget{ref-Kapson2012}{}
Kapson, H. S., Leddy, M. A., \& Haaga, D. A. (2012). Specificity of
effects of cognitive behavior therapy on coping, acceptance, and
distress tolerance in a randomized controlled trial for smoking
cessation. \emph{Journal of Clinical Psychology}, \emph{68}(12),
1231--1240.
doi:\href{https://doi.org/10.1002/jclp.21903}{10.1002/jclp.21903}

\hypertarget{ref-Karalunas2012}{}
Karalunas, S. L., Huang-Pollock, C. L., \& Nigg, J. T. (2012).
Decomposing attention-deficit/hyperactivity disorder (ADHD)-related
effects in response speed and variability. \emph{Neuropsychology},
\emph{26}(6), 684--694.
doi:\href{https://doi.org/10.1037/a0029936}{10.1037/a0029936}

\hypertarget{ref-Kassin2017}{}
Kassin, S. M., Kukucka, J., Lawson, V. Z., \& DeCarlo, J. (2017). Police
reports of mock suspect interrogations: A test of accuracy and
perception. \emph{Law and Human Behavior}, \emph{41}(3), 230--243.
doi:\href{https://doi.org/10.1037/lhb0000225}{10.1037/lhb0000225}

\hypertarget{ref-Katz-Wise2017}{}
Katz-Wise, S. L., Budge, S. L., Orovecz, J. J., Nguyen, B.,
Nava-Coulter, B., \& Thomson, K. (2017). Imagining the future:
Perspectives among youth and caregivers in the trans youth family study.
\emph{Journal of Counseling Psychology}, \emph{64}(1), 26--40.
doi:\href{https://doi.org/10.1037/cou0000186}{10.1037/cou0000186}

\hypertarget{ref-Kauffman2011}{}
Kauffman, D. F., Zhao, R., \& Yang, Y. S. (2011). Effects of online note
taking formats and self-monitoring prompts on learning from online text:
Using technology to enhance self-regulated learning. \emph{Contemporary
Educational Psychology}, \emph{36}(4), 313--322.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.04.001}{10.1016/j.cedpsych.2011.04.001}

\hypertarget{ref-Kauppila2016}{}
Kauppila, O. P. (2016). When and how does LMX differentiation influence
followers' work outcomes? The interactive roles of one's own LMX status
and organizational context. \emph{Personnel Psychology}, \emph{69}(2),
357--393.
doi:\href{https://doi.org/10.1111/peps.12110}{10.1111/peps.12110}

\hypertarget{ref-Kaushanskaya2012}{}
Kaushanskaya, M., \& Rechtzigel, K. (2012). Concreteness effects in
bilingual and monolingual word learning. \emph{Psychonomic Bulletin \&
Review}, \emph{19}(5), 935--941.
doi:\href{https://doi.org/10.3758/s13423-012-0271-5}{10.3758/s13423-012-0271-5}

\hypertarget{ref-Kavussanu2012}{}
Kavussanu, M., Willoughby, A., \& Ring, C. (2012). Moral identity and
emotion in athletes. \emph{Journal of Sport and Exercise Psychology},
\emph{34}(6), 695--714.
doi:\href{https://doi.org/10.1123/jsep.34.6.695}{10.1123/jsep.34.6.695}

\hypertarget{ref-Kay2017}{}
Kay, S. A., \& Grimm, L. R. (2017). Regulatory fit improves fitness for
people with low exercise experience. \emph{Journal of Sport and Exercise
Psychology}, \emph{39}(2), 109--119.
doi:\href{https://doi.org/10.1123/jsep.2016-0274}{10.1123/jsep.2016-0274}

\hypertarget{ref-Kee2012}{}
Kee, Y. H., Chatzisarantis, N. N., Kong, P. W., Chow, J. Y., \& Chen, L.
H. (2012). Mindfulness, movement control, and attentional focus
strategies: Effects of mindfulness on a postural balance task.
\emph{Journal of Sport and Exercise Psychology}, \emph{34}(5), 561--579.
doi:\href{https://doi.org/10.1123/jsep.34.5.561}{10.1123/jsep.34.5.561}

\hypertarget{ref-Keil2017}{}
Keil, J., Michel, A., Sticca, F., Leipold, K., Klein, A. M., Sierau, S.,
\ldots{} White, L. O. (2017). The Pizzagame: A virtual public goods game
to assess cooperative behavior in children and adolescents.
\emph{Behavior Research Methods}, \emph{49}(4), 1432--1443.
doi:\href{https://doi.org/10.3758/s13428-016-0799-9}{10.3758/s13428-016-0799-9}

\hypertarget{ref-Kemp2012}{}
Kemp, C., Shafto, P., \& Tenenbaum, J. B. (2012). An integrated account
of generalization across objects and features. \emph{Cognitive
Psychology}, \emph{64}(1-2), 35--73.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.10.001}{10.1016/j.cogpsych.2011.10.001}

\hypertarget{ref-Kendrick2012}{}
Kendrick, R. V., \& Olson, M. A. (2012). When feeling right leads to
being right in the reporting of implicitly-formed attitudes, or how I
learned to stop worrying and trust my gut. \emph{Journal of Experimental
Social Psychology}, \emph{48}(6), 1316--1321.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.008}{10.1016/j.jesp.2012.05.008}

\hypertarget{ref-Kenett2017}{}
Kenett, Y. N., Levi, E., Anaki, D., \& Faust, M. (2017). The semantic
distance task: Quantifying semantic distance with semantic network path
length. \emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(9), 1470--1489.
doi:\href{https://doi.org/10.1037/xlm0000391}{10.1037/xlm0000391}

\hypertarget{ref-Kennealy2012}{}
Kennealy, P. J., Skeem, J. L., Manchak, S. M., \& Eno Louden, J. (2012).
Firm, fair, and caring officer-offender relationships protect against
supervision failure. \emph{Law and Human Behavior}, \emph{36}(6),
496--505. doi:\href{https://doi.org/10.2307/43586876}{10.2307/43586876}

\hypertarget{ref-Kennedy2017}{}
Kennedy, J. A., \& Anderson, C. (2017). Hierarchical rank and principled
dissent: How holding higher rank suppresses objection to unethical
practices. \emph{Organizational Behavior and Human Decision Processes},
\emph{139}, 30--49.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.01.002}{10.1016/j.obhdp.2017.01.002}

\hypertarget{ref-Kercood2012}{}
Kercood, S., Zentall, S. S., Vinh, M., \& Tom-Wright, K. (2012).
Attentional cuing in math word problems for girls at-risk for ADHD and
their peers in general education settings. \emph{Contemporary
Educational Psychology}, \emph{37}(2), 106--112.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.02.001}{10.1016/j.cedpsych.2012.02.001}

\hypertarget{ref-Keum2017}{}
Keum, B. T., \& Miller, M. J. (2017). Racism in digital era: Development
and initial validation of the perceived online racism scale (PORS v1.0).
\emph{Journal of Counseling Psychology}, \emph{64}(3), 310--324.
doi:\href{https://doi.org/10.1037/cou0000205}{10.1037/cou0000205}

\hypertarget{ref-Khateb2017}{}
Khateb, A., Shamshoum, R., \& Prior, A. (2017). Modulation of language
switching by cue timing: Implications for models of bilingual language
control. \emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(8), 1239--1253.
doi:\href{https://doi.org/10.1037/xlm0000382}{10.1037/xlm0000382}

\hypertarget{ref-Khodadadi2017}{}
Khodadadi, A., Fakhari, P., \& Busemeyer, J. R. (2017). Learning to
allocate limited time to decisions with different expected outcomes.
\emph{Cognitive Psychology}, \emph{95}, 17--49.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.03.002}{10.1016/j.cogpsych.2017.03.002}

\hypertarget{ref-Kiernan2012}{}
Kiernan, D., Ray, M., \& Welsh, T. N. (2012). Inverting the joint Simon
effect by intention. \emph{Psychonomic Bulletin \& Review}, \emph{19},
914--920.
doi:\href{https://doi.org/10.3758/s13423-012-0283-1}{10.3758/s13423-012-0283-1}

\hypertarget{ref-Kiesner2012}{}
Kiesner, J., \& Poulin, F. (2012). Developmental associations between
adolescent change in depressive symptoms and
menstrual-cycle-phase-specific negative affect during early adulthood.
\emph{Journal of Youth and Adolescence}, \emph{41}(10), 1325--1338.
doi:\href{https://doi.org/10.1007/s10964-011-9722-y}{10.1007/s10964-011-9722-y}

\hypertarget{ref-Klc2017}{}
Kılıç, A., Criss, A. H., Malmberg, K. J., \& Shiffrin, R. M. (2017).
Models that allow us to perceive the world more accurately also allow us
to remember past events more accurately via differentiation.
\emph{Cognitive Psychology}, \emph{92}, 65--86.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.11.005}{10.1016/j.cogpsych.2016.11.005}

\hypertarget{ref-Kim2012}{}
Kim, J. E., Zane, N. W., \& Blozis, S. A. (2012). Client predictors of
short-term psychotherapy outcomes among Asian and white American
outpatients. \emph{Journal of Clinical Psychology}, \emph{68}(12),
1287--1302.
doi:\href{https://doi.org/10.1002/jclp.21905}{10.1002/jclp.21905}

\hypertarget{ref-Kim2017}{}
Kim, M. H., Shimomaeda, L., Giuliano, R. J., \& Skowron, E. A. (2017).
Intergenerational associations in executive function between mothers and
children in the context of risk. \emph{Journal of Experimental Child
Psychology}, \emph{164}, 1--15.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.002}{10.1016/j.jecp.2017.07.002}

\hypertarget{ref-Kim2017a}{}
Kim, Y. J., \& Zhong, C. B. (2017). Ideas rise from chaos: Information
structure and creativity. \emph{Organizational Behavior and Human
Decision Processes}, \emph{138}, 15--27.
doi:\href{https://doi.org/10.1016/j.obhdp.2016.10.001}{10.1016/j.obhdp.2016.10.001}

\hypertarget{ref-Kim-Spoon2012}{}
Kim-Spoon, J., Longo, G. S., \& McCullough, M. E. (2012).
Parent--adolescent relationship quality as a moderator for the
influences of parents' religiousness on adolescents' religiousness and
adjustment. \emph{Journal of Youth and Adolescence}, \emph{41}(12),
1576--1587.
doi:\href{https://doi.org/10.1007/s10964-012-9796-1}{10.1007/s10964-012-9796-1}

\hypertarget{ref-King2017a}{}
King, C. M., Heilbrun, K., Kim, N. Y., McWilliams, K., Phillips, S.,
Barbera, J., \& Fretz, R. (2017). Tablet computers and forensic and
correctional psychological assessment: A randomized controlled study.
\emph{Law and Human Behavior}, \emph{41}(5), 468--477.
doi:\href{https://doi.org/10.1037/lhb0000245}{10.1037/lhb0000245}

\hypertarget{ref-Kirby2017}{}
Kirby, T. A., \& Greenwald, A. G. (2017). Mental ownership: Does mental
rehearsal transform novel stimuli into mental possessions? \emph{Journal
of Experimental Social Psychology}, \emph{73}, 125--135.
doi:\href{https://doi.org/10.1016/j.jesp.2017.05.004}{10.1016/j.jesp.2017.05.004}

\hypertarget{ref-Kirkham2012}{}
Kirkham, N. Z., Richardson, D. C., Wu, R., \& Johnson, S. P. (2012). The
importance of `` what'': Infants use featural information to index
events. \emph{Journal of Experimental Child Psychology}, \emph{113}(3),
430--439.
doi:\href{https://doi.org/10.1016/j.jecp.2012.07.001}{10.1016/j.jecp.2012.07.001}

\hypertarget{ref-Kivlighan2017}{}
Kivlighan, D. M., Kline, K., Gelso, C. J., \& Hill, C. E. (2017).
Congruence and discrepancy between working alliance and real
relationship: Variance decomposition and response surface analyses.
\emph{Journal of Counseling Psychology}, \emph{64}(4), 394--409.
doi:\href{https://doi.org/10.1037/cou0000216}{10.1037/cou0000216}

\hypertarget{ref-Klatte2017}{}
Klatte, M., Spilski, J., Mayerl, J., Möhler, U., Lachmann, T., \&
Bergström, K. (2017). Effects of aircraft noise on reading and quality
of life in primary school children in Germany: Results from the NORAH
study. \emph{Environment and Behavior}, \emph{49}(4), 390--424.
doi:\href{https://doi.org/10.1177/0013916516642580}{10.1177/0013916516642580}

\hypertarget{ref-Kleemans2017}{}
Kleemans, M., Schlindwein, L. F., \& Dohmen, R. (2017). Preadolescents'
emotional and prosocial responses to negative TV news: Investigating the
beneficial effects of constructive reporting and peer discussion.
\emph{Journal of Youth and Adolescence}, \emph{46}(9), 2060--2072.
doi:\href{https://doi.org/10.1007/s10964-017-0675-7}{10.1007/s10964-017-0675-7}

\hypertarget{ref-KleinEntink2009}{}
Klein Entink, R. H., Kuhn, J.-T., Hornke, L. F., \& Fox, J.-P. (2009).
Evaluating cognitive theory: a joint modeling approach using responses
and response times. \emph{Psychological Methods}, \emph{14}(1), 54--75.
doi:\href{https://doi.org/10.1037/a0014877}{10.1037/a0014877}

\hypertarget{ref-Klein2017a}{}
Klein, N., \& O'Brien, E. (2017). The power and limits of personal
change: When a bad past does (and does not) inspire in the present.
\emph{Journal of Personality and Social Psychology}, \emph{113}(2),
210--229.
doi:\href{https://doi.org/10.1037/pspa0000088}{10.1037/pspa0000088}

\hypertarget{ref-Klein2017}{}
Klein, S. A., Hilbig, B. E., \& Heck, D. W. (2017). Which is the greater
good? A social dilemma paradigm disentangling environmentalism and
cooperation. \emph{Journal of Environmental Psychology}, \emph{53},
40--49.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.06.001}{10.1016/j.jenvp.2017.06.001}

\hypertarget{ref-Klinger2012}{}
Klinger, R. S., Ladany, N., \& Kulp, L. E. (2012). It's too late to
apologize. \emph{The Counseling Psychologist}, \emph{40}(4), 554--574.
doi:\href{https://doi.org/10.1177/0011000011416372}{10.1177/0011000011416372}

\hypertarget{ref-VanderKnaap2012}{}
Knaap, L. M. van der, Alberda, D. L., Oosterveld, P., \& Born, M. P.
(2012). The predictive validity of criminogenic needs for male and
female offenders: Comparing the relative impact of needs in predicting
recidivism. \emph{Law and Human Behavior}, \emph{36}(5), 413--422.
doi:\href{https://doi.org/10.1037/h0093932}{10.1037/h0093932}

\hypertarget{ref-Koban2012}{}
Koban, L., Pourtois, G., Bediou, B., \& Vuilleumier, P. (2012). Effects
of social context and predictive relevance on action outcome monitoring.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{12}(3),
460--478.
doi:\href{https://doi.org/10.3758/s13415-012-0091-0}{10.3758/s13415-012-0091-0}

\hypertarget{ref-Kochanska2012}{}
Kochanska, G., Kim, S., \& Koenig Nordling, J. (2012). Challenging
circumstances moderate the links between mothers' personality traits and
their parenting in low-income families with young children.
\emph{Journal of Personality and Social Psychology}, \emph{103}(6),
1040--1049.
doi:\href{https://doi.org/10.1037/a0030386}{10.1037/a0030386}

\hypertarget{ref-Koehler2016}{}
Koehler, J. J., Schweitzer, N. J., Saks, M. J., \& McQuiston, D. E.
(2016). Science, technology, or the expert witness: What influences
jurors' judgments about forensic science testimony? \emph{Psychology,
Public Policy, and Law}, \emph{22}(4), 401--413.
doi:\href{https://doi.org/10.1037/law0000103}{10.1037/law0000103}

\hypertarget{ref-Kois2017}{}
Kois, L., Wellbeloved-Stone, J. M., Chauhan, P., \& Warren, J. I.
(2017). Combined evaluations of competency to stand trial and mental
state at the time of the offense: An overlooked methodological
consideration? \emph{Law and Human Behavior}, \emph{41}(3), 217--229.
doi:\href{https://doi.org/10.1037/lhb0000236}{10.1037/lhb0000236}

\hypertarget{ref-Koning2012}{}
Koning, I. M., Eijnden, R. J. J. M. van den, Verdurmen, J. E. E.,
Engels, R. C. M. E., \& Vollebergh, W. A. M. (2012). Developmental
alcohol-specific parenting profiles in adolescence and their
relationships with adolescents' alcohol use. \emph{Journal of Youth and
Adolescence}, \emph{41}(11), 1502--1511.
doi:\href{https://doi.org/10.1007/s10964-012-9772-9}{10.1007/s10964-012-9772-9}

\hypertarget{ref-VanderKooy-Hofland2012}{}
Kooy-Hofland, V. A. C. van der, Kooy, J. van der, Bus, A. G.,
IJzendoorn, M. H. van, \& Bonsel, G. J. (2012). Differential
susceptibility to early literacy intervention in children with mild
perinatal adversities: Short- and long-term effects of a randomized
control trial. \emph{Journal of Educational Psychology}, \emph{104}(2),
337--349. doi:\href{https://doi.org/10.1037/a0026984}{10.1037/a0026984}

\hypertarget{ref-Korjoukov2012}{}
Korjoukov, I., Jeurissen, D., Kloosterman, N. A., Verhoeven, J. E.,
Scholte, H. S., \& Roelfsema, P. R. (2012). The time course of
perceptual grouping in natural scenes. \emph{Psychological Science},
\emph{23}(12), 1482--1489.
doi:\href{https://doi.org/10.1177/0956797612443832}{10.1177/0956797612443832}

\hypertarget{ref-Korpipaa2017}{}
Korpipää, H., Koponen, T., Aro, M., Tolvanen, A., Aunola, K., Poikkeus,
A.-M., \ldots{} Nurmi, J.-E. (2017). Covariation between reading and
arithmetic skills from Grade 1 to Grade 7. \emph{Contemporary
Educational Psychology}, \emph{51}, 131--140.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.06.005}{10.1016/j.cedpsych.2017.06.005}

\hypertarget{ref-Kosinski2013}{}
Kosinski, M., Wang, Y., Lakkaraju, H., \& Leskovec, J. (2016). Mining
big data to extract patterns and predict real-life outcomes.
\emph{Psychological Methods}, \emph{21}(4), 493--506.
doi:\href{https://doi.org/10.1037/met0000105}{10.1037/met0000105}

\hypertarget{ref-Kostons2017}{}
Kostons, D., \& Koning, B. B. de. (2017). Does visualization affect
monitoring accuracy, restudy choice, and comprehension scores of
students in primary education? \emph{Contemporary Educational
Psychology}, \emph{51}, 1--10.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.05.001}{10.1016/j.cedpsych.2017.05.001}

\hypertarget{ref-Kowalski2017}{}
Kowalski, A., \& Huang, Y. T. (2017). Predicting and priming thematic
roles: Flexible use of verbal and nonverbal cues during relative clause
comprehension. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{43}(9), 1341--1351.
doi:\href{https://doi.org/10.1037/xlm0000389}{10.1037/xlm0000389}

\hypertarget{ref-Kober2017}{}
Köber, C., \& Habermas, T. (2017). How stable is the personal past?
Stability of most important autobiographical memories and life
narratives across eight years in a life span sample. \emph{Journal of
Personality and Social Psychology}, \emph{113}(4), 608--626.
doi:\href{https://doi.org/10.1037/pspp0000145}{10.1037/pspp0000145}

\hypertarget{ref-Kraus2012}{}
Kraus, F., Ahearne, M., Lam, S. K., \& Wieseke, J. (2012). Toward a
contingency framework of interpersonal influence in organizational
identification diffusion. \emph{Organizational Behavior and Human
Decision Processes}, \emph{118}(2), 162--178.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.03.010}{10.1016/j.obhdp.2012.03.010}

\hypertarget{ref-Krinski2017}{}
Krinski, K., Machado, D. G. S., Lirani, L. S., DaSilva, S. G., Costa, E.
C., Hardcastle, S. J., \& Elsangedy, H. M. (2017). Let's walk outdoors!
Self-paced walking outdoors improves future intention to exercise in
women with obesity. \emph{Journal of Sport and Exercise Psychology},
\emph{39}(2), 145--157.
doi:\href{https://doi.org/10.1123/jsep.2016-0220}{10.1123/jsep.2016-0220}

\hypertarget{ref-Kubiak2017a}{}
Kubiak, S. P., Brenner, H. J., Bybee, D., Campbell, R., Cummings, C. E.,
Darcy, K. M., \ldots{} Goodman-Williams, R. (2017a). Do sexually
victimized female prisoners perceive justice in litigation process and
outcomes? \emph{Psychology, Public Policy, and Law}, \emph{23}(1),
39--52.
doi:\href{https://doi.org/10.1037/law0000100}{10.1037/law0000100}

\hypertarget{ref-Kubiak2017}{}
Kubiak, S. P., Brenner, H. J., Bybee, D., Campbell, R., Cummings, C. E.,
Darcy, K. M., \ldots{} Goodman-Williams, R. (2017b). Sexual misconduct
in prison: What factors affect whether incarcerated women will report
abuses committed by prison staff? \emph{Law and Human Behavior},
\emph{41}(4), 361--374.
doi:\href{https://doi.org/10.1037/lhb0000239}{10.1037/lhb0000239}

\hypertarget{ref-Kuha2015}{}
Kuha, J., \& Moustaki, I. (2015). Nonequivalence of measurement in
latent variable modeling of multigroup data: A sensitivity analysis.
\emph{Psychological Methods}, \emph{20}(4), 523--536.
doi:\href{https://doi.org/10.1037/met0000031}{10.1037/met0000031}

\hypertarget{ref-Kunde2012}{}
Kunde, W., Augst, S., \& Kleinsorge, T. (2012). Adaptation to
(non)valent task disturbance. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{12}(4), 644--660.
doi:\href{https://doi.org/10.3758/s13415-012-0116-8}{10.3758/s13415-012-0116-8}

\hypertarget{ref-Kuperman2012}{}
Kuperman, V., Stadthagen-Gonzalez, H., \& Brysbaert, M. (2012).
Age-of-acquisition ratings for 30,000 English words. \emph{Behavior
Research Methods}, \emph{44}(4), 978--990.
doi:\href{https://doi.org/10.3758/s13428-012-0210-4}{10.3758/s13428-012-0210-4}

\hypertarget{ref-Kusev2012}{}
Kusev, P., Tsaneva-Atanasova, K., Schaik, P. van, \& Chater, N. (2012).
Modeling judgment of sequentially presented categories using weighting
and sampling without replacement. \emph{Behavior Research Methods},
\emph{44}(4), 1129--1134.
doi:\href{https://doi.org/10.3758/s13428-012-0218-9}{10.3758/s13428-012-0218-9}

\hypertarget{ref-Kushlev2012}{}
Kushlev, K., Dunn, E. W., \& Ashton-James, C. E. (2012). Does affluence
impoverish the experience of parenting? \emph{Journal of Experimental
Social Psychology}, \emph{48}(6), 1381--1384.
doi:\href{https://doi.org/10.1016/j.jesp.2012.06.001}{10.1016/j.jesp.2012.06.001}

\hypertarget{ref-Kuwabara2012}{}
Kuwabara, M., \& Smith, L. B. (2012). Cross-cultural differences in
cognitive development: Attention to relations and objects. \emph{Journal
of Experimental Child Psychology}, \emph{113}(1), 20--35.
doi:\href{https://doi.org/10.1016/j.jecp.2012.04.009}{10.1016/j.jecp.2012.04.009}

\hypertarget{ref-Ladd2017}{}
Ladd, G. W., Ettekal, I., \& Kochenderfer-Ladd, B. (2017). Peer
victimization trajectories from kindergarten through high school:
Differential pathways for children's school engagement and achievement?
\emph{Journal of Educational Psychology}, \emph{109}(6), 826--841.
doi:\href{https://doi.org/10.1037/edu0000177}{10.1037/edu0000177}

\hypertarget{ref-Lages2017}{}
Lages, M., Boyle, S. C., \& Jenkins, R. (2017). Illusory increases in
font size improve letter recognition. \emph{Psychological Science},
\emph{28}(8), 1180--1188.
doi:\href{https://doi.org/10.1177/0956797617705391}{10.1177/0956797617705391}

\hypertarget{ref-Lam2012}{}
Lam, C. B., Solmeyer, A. R., \& McHale, S. M. (2012). Sibling
relationships and empathy across the transition to adolescence.
\emph{Journal of Youth and Adolescence}, \emph{41}(12), 1657--1670.
doi:\href{https://doi.org/10.1007/s10964-012-9781-8}{10.1007/s10964-012-9781-8}

\hypertarget{ref-Landau2012}{}
Landau, M. J., Sullivan, D., Keefer, L. A., Rothschild, Z. K., \& Osman,
M. R. (2012). Subjectivity uncertainty theory of objectification:
Compensating for uncertainty about how to positively relate to others by
downplaying their subjective attributes. \emph{Journal of Experimental
Social Psychology}, \emph{48}(6), 1234--1246.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.003}{10.1016/j.jesp.2012.05.003}

\hypertarget{ref-Landers2016}{}
Landers, R. N., Brusso, R. C., Cavanaugh, K. J., \& Collmus, A. B.
(2016). A primer on theory-driven web scraping: Automatic extraction of
big data from the Internet for use in psychological research.
\emph{Psychological Methods}, \emph{21}(4), 475--492.
doi:\href{https://doi.org/10.1037/met0000081}{10.1037/met0000081}

\hypertarget{ref-Landy2017}{}
Landy, J. F., Walco, D. K., \& Bartels, D. M. (2017). What's wrong with
using steroids? Exploring whether and why people oppose the use of
performance enhancing drugs. \emph{Journal of Personality and Social
Psychology}, \emph{113}(3), 377--392.
doi:\href{https://doi.org/10.1037/pspa0000089}{10.1037/pspa0000089}

\hypertarget{ref-Lane2012}{}
Lane, T. A., Moore, D. M., Batchelor, J., Brew, B. J., \& Cysique, L. A.
(2012). Facial emotional processing in HIV infection: Relation to
neurocognitive and neuropsychiatric status. \emph{Neuropsychology},
\emph{26}(6), 713--722.
doi:\href{https://doi.org/10.1037/a0029964}{10.1037/a0029964}

\hypertarget{ref-LanguageandReadingResearchConsortium2017}{}
Language and Reading Research Consortium, \& Logan, J. (2017). Pressure
points in reading comprehension: A quantile multiple regression
analysis. \emph{Journal of Educational Psychology}, \emph{109}(4),
451--464.
doi:\href{https://doi.org/10.1037/edu0000150}{10.1037/edu0000150}

\hypertarget{ref-Lannin2017}{}
Lannin, D. G., Vogel, D. L., \& Heath, P. J. (2017). Can reflecting on
personal values online increase positive beliefs about counseling?
\emph{Journal of Counseling Psychology}, \emph{64}(3), 261--268.
doi:\href{https://doi.org/10.1037/cou0000201}{10.1037/cou0000201}

\hypertarget{ref-Lapate2017}{}
Lapate, R. C., Samaha, J., Rokers, B., Hamzah, H., Postle, B. R., \&
Davidson, R. J. (2017). Inhibition of lateral prefrontal cortex produces
emotionally biased first impressions: A Transcranial Magnetic
Stimulation and Electroencephalography study. \emph{Psychological
Science}, \emph{28}(7), 942--953.
doi:\href{https://doi.org/10.1177/0956797617699837}{10.1177/0956797617699837}

\hypertarget{ref-Larco2012}{}
Larco, N., Steiner, B., Stockard, J., \& West, A. (2012).
Pedestrian-friendly environments and active travel for residents of
multifamily housing. \emph{Environment and Behavior}, \emph{44}(3),
303--333.
doi:\href{https://doi.org/10.1177/0013916511402061}{10.1177/0013916511402061}

\hypertarget{ref-Larsen2012}{}
Larsen, J. K., Vermulst, A. A., Eisinga, R., English, T., Gross, J. J.,
Hofman, E., \ldots{} Engels, R. C. M. E. (2012). Social coping by
masking? Parental support and peer victimization as mediators of the
relationship between depressive symptoms and expressive suppression in
adolescents. \emph{Journal of Youth and Adolescence}, \emph{41}(12),
1628--1642.
doi:\href{https://doi.org/10.1007/s10964-012-9782-7}{10.1007/s10964-012-9782-7}

\hypertarget{ref-Laska2013}{}
Laska, K. M., Smith, T. L., Wislocki, A. P., Minami, T., \& Wampold, B.
E. (2013). Uniformity of evidence-based treatments in practice?
Therapist effects in the delivery of cognitive processing therapy for
PTSD. \emph{Journal of Counseling Psychology}, \emph{60}(1), 31--41.
doi:\href{https://doi.org/10.1037/a0031294}{10.1037/a0031294}

\hypertarget{ref-Latta2011}{}
Latta, R. E., \& Goodman, L. a. (2011). Intervening in partner violence
against women. \emph{The Counseling Psychologist}, \emph{39}(7),
973--1023.
doi:\href{https://doi.org/10.1177/0011000011398504}{10.1177/0011000011398504}

\hypertarget{ref-Lau2017}{}
Lau, A., Barnett, M., Stadnick, N., Saifan, D., Regan, J., Wiltsey
Stirman, S., \ldots{} Brookman-Frazee, L. (2017). Therapist report of
adaptations to delivery of evidence-based practices within a
system-driven reform of publicly funded children's mental health
services. \emph{Journal of Consulting and Clinical Psychology},
\emph{85}(7), 664--675.
doi:\href{https://doi.org/10.1037/ccp0000215}{10.1037/ccp0000215}

\hypertarget{ref-Lavis2017}{}
Lavis, T., \& Brewer, N. (2017). Effects of a proven error on
evaluations of witness testimony. \emph{Law and Human Behavior},
\emph{41}(3), 314--323.
doi:\href{https://doi.org/10.1037/lhb0000217}{10.1037/lhb0000217}

\hypertarget{ref-Lawing2017}{}
Lawing, K., Childs, K. K., Frick, P. J., \& Vincent, G. (2017). Use of
structured professional judgment by probation officers to assess risk
for recidivism in adolescent offenders. \emph{Psychological Assessment},
\emph{29}(6), 652--663.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/pas0000414}{http://dx.doi.org/10.1037/pas0000414}

\hypertarget{ref-Lawrence2016}{}
Lawrence, S. M., Harrison, C. K., \& Bukstein, S. (2016). What is this
``White'' in the white male student-athlete?: White students'
perceptions of academic and athletic success on campus. \emph{Sociology
of Sport Journal}, \emph{33}(4), 334--346.
doi:\href{https://doi.org/10.1123/ssj.2015-0139}{10.1123/ssj.2015-0139}

\hypertarget{ref-Leander2017}{}
Leander, N. P., \& Chartrand, T. L. (2017). On thwarted goals and
displaced aggression: A compensatory competence model. \emph{Journal of
Experimental Social Psychology}, \emph{72}, 88--100.
doi:\href{https://doi.org/10.1016/j.jesp.2017.04.010}{10.1016/j.jesp.2017.04.010}

\hypertarget{ref-Lebeau2016}{}
Lebeau, J.-C., Liu, S., Sáenz-Moncaleano, C., Sanduvete-Chaves, S.,
Chacón-Moscoso, S., Becker, B. J., \& Tenenbaum, G. (2016). Quiet eye
and performance in sport: A meta-analysis. \emph{Journal of Sport and
Exercise Psychology}, \emph{38}(5), 441--457.
doi:\href{https://doi.org/10.1123/jsep.2015-0123}{10.1123/jsep.2015-0123}

\hypertarget{ref-Leder2012}{}
Leder, H., Bär, S., \& Topolinski, S. (2012). Covert painting
simulations influence aesthetic appreciation of artworks.
\emph{Psychological Science}, \emph{23}(12), 1479--1481.
doi:\href{https://doi.org/10.1177/0956797612452866}{10.1177/0956797612452866}

\hypertarget{ref-Lee2012b}{}
Lee, A. F., Li, N.-C., Lamade, R., Schuler, A., \& Prentky, R. A.
(2012). Predicting hands-on child sexual offenses among possessors of
Internet child pornography. \emph{Psychology, Public Policy, and Law},
\emph{18}(4), 644--672.
doi:\href{https://doi.org/10.1037/a0027517}{10.1037/a0027517}

\hypertarget{ref-Lee2017}{}
Lee, A. J., \& Ames, D. R. (2017). ``I can't pay more'' versus ``It's
not worth more'': Divergent effects of constraint and disparagement
rationales in negotiations. \emph{Organizational Behavior and Human
Decision Processes}, \emph{141}, 16--28.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.05.002}{10.1016/j.obhdp.2017.05.002}

\hypertarget{ref-Lee2011}{}
Lee, D.-g., \& Park, H.-j. (2011). Cross-cultural validity of the Frost
multidimensional perfectionism scale in Korea. \emph{The Counseling
Psychologist}, \emph{39}(2), 320--345.
doi:\href{https://doi.org/10.1177/0011000010365910}{10.1177/0011000010365910}

\hypertarget{ref-Lee2012}{}
Lee, S. W. S., \& Schwarz, N. (2012). Bidirectionality, mediation, and
moderation of metaphorical effects: The embodiment of social suspicion
and fishy smells. \emph{Journal of Personality and Social Psychology},
\emph{103}(5), 737--749.
doi:\href{https://doi.org/10.1037/a0029708}{10.1037/a0029708}

\hypertarget{ref-Lee2012a}{}
Lee, T., Crawford, J. D., Henry, J. D., Trollor, J. N., Kochan, N. A.,
Wright, M. J., \ldots{} Sachdev, P. S. (2012). Mediating effects of
processing speed and executive functions in age-related differences in
episodic memory performance: A cross-validation study.
\emph{Neuropsychology}, \emph{26}(6), 776--784.
doi:\href{https://doi.org/10.1037/a0030053}{10.1037/a0030053}

\hypertarget{ref-VanLeeuwen2012}{}
Leeuwen, F. van, Park, J. H., \& Penton-Voak, I. S. (2012). Another
fundamental social category? Spontaneous categorization of people who
uphold or violate moral norms. \emph{Journal of Experimental Social
Psychology}, \emph{48}(6), 1385--1388.
doi:\href{https://doi.org/10.1016/j.jesp.2012.06.004}{10.1016/j.jesp.2012.06.004}

\hypertarget{ref-Lefevor2017}{}
Lefevor, G. T., Janis, R. A., \& Park, S. Y. (2017). Religious and
sexual identities: An intersectional, longitudinal examination of change
in therapy. \emph{The Counseling Psychologist}, \emph{45}(3), 387--413.
doi:\href{https://doi.org/10.1177/0011000017702721}{10.1177/0011000017702721}

\hypertarget{ref-Legault2012}{}
Legault, L., Al-Khindi, T., \& Inzlicht, M. (2012). Preserving integrity
in the face of performance threat. \emph{Psychological Science},
\emph{23}(12), 1455--1460.
doi:\href{https://doi.org/10.1177/0956797612448483}{10.1177/0956797612448483}

\hypertarget{ref-Leikas2012}{}
Leikas, S., Lönnqvist, J.-E., \& Verkasalo, M. (2012). Persons,
situations, and behaviors: Consistency and variability of different
behaviors in four interpersonal situations. \emph{Journal of Personality
and Social Psychology}, \emph{103}(6), 1007--1022.
doi:\href{https://doi.org/10.1037/a0030385}{10.1037/a0030385}

\hypertarget{ref-Leith2012}{}
Leith, J. E., \& Stein, C. H. (2012). The role of personal loss in the
caregiving experiences of well siblings of adults with serious mental
illness. \emph{Journal of Clinical Psychology}, \emph{68}(10),
1075--1088.
doi:\href{https://doi.org/10.1002/jclp.21881}{10.1002/jclp.21881}

\hypertarget{ref-Lelkes2012}{}
Lelkes, Y., Krosnick, J. A., Marx, D. M., Judd, C. M., \& Park, B.
(2012). Complete anonymity compromises the accuracy of self-reports.
\emph{Journal of Experimental Social Psychology}, \emph{48}(6),
1291--1299.
doi:\href{https://doi.org/10.1016/j.jesp.2012.07.002}{10.1016/j.jesp.2012.07.002}

\hypertarget{ref-Lemay2012}{}
Lemay, E. P., Overall, N. C., \& Clark, M. S. (2012). Experiences and
interpersonal consequences of hurt feelings and anger. \emph{Journal of
Personality and Social Psychology}, \emph{103}(6), 982--1006.
doi:\href{https://doi.org/10.1037/a0030064}{10.1037/a0030064}

\hypertarget{ref-Lemhofer2012}{}
Lemhöfer, K., \& Broersma, M. (2012). Introducing LexTALE: A quick and
valid Lexical Test for Advanced Learners of English. \emph{Behavior
Research Methods}, \emph{44}(2), 325--343.
doi:\href{https://doi.org/10.3758/s13428-011-0146-0}{10.3758/s13428-011-0146-0}

\hypertarget{ref-Lerkkanen2012}{}
Lerkkanen, M.-K., Kiuru, N., Pakarinen, E., Viljaranta, J., Poikkeus,
A.-M., Rasku-Puttonen, H., \ldots{} Nurmi, J.-E. (2012). The role of
teaching practices in the development of children's interest in reading
and mathematics in kindergarten. \emph{Contemporary Educational
Psychology}, \emph{37}(4), 266--279.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.03.004}{10.1016/j.cedpsych.2011.03.004}

\hypertarget{ref-Leslie2012}{}
Leslie, S. J., \& Gelman, S. A. (2012). Quantified statements are
recalled as generics: Evidence from preschool children and adults.
\emph{Cognitive Psychology}, \emph{64}(3), 186--214.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.12.001}{10.1016/j.cogpsych.2011.12.001}

\hypertarget{ref-Levashina2012}{}
Levashina, J., Morgeson, F. P., \& Campoin, M. A. (2012). Tell me some
more: Exploring how verbal ability and item verifiability influence
responses to biodata questions in a high-stakes selection context.
\emph{Personnel Psychology}, \emph{65}(2), 359--383.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01245.x}{10.1111/j.1744-6570.2012.01245.x}

\hypertarget{ref-Leveau2012}{}
Leveau, N., Jhean-Larose, S., Denhière, G., \& Nguyen, B.-L. (2012).
Validating an interlingual metanorm for emotional analysis of texts.
\emph{Behavior Research Methods}, \emph{44}(4), 1007--1014.
doi:\href{https://doi.org/10.3758/s13428-012-0208-y}{10.3758/s13428-012-0208-y}

\hypertarget{ref-Levenson2012}{}
Levenson, J. C., Wallace, M. L., Fournier, J. C., Rucci, P., \& Frank,
E. (2012). The role of personality pathology in depression treatment
outcome with psychotherapy and pharmacotherapy. \emph{Journal of
Consulting and Clinical Psychology}, \emph{80}(5), 719--729.
doi:\href{https://doi.org/10.1037/a0029396}{10.1037/a0029396}

\hypertarget{ref-Levenson2012a}{}
Levenson, J. S., Sandler, J. C., \& Freeman, N. J. (2012).
Failure-to-register laws and public safety: An examination of risk
factors and sex offense recidivism. \emph{Law and Human Behavior},
\emph{36}(6), 555--565.
doi:\href{https://doi.org/10.1037/b0000002}{10.1037/b0000002}

\hypertarget{ref-Leversen2012}{}
Leversen, I., Danielsen, A. G., Birkeland, M. S., \& Samdal, O. (2012).
Basic psychological need satisfaction in leisure activities and
adolescents' life satisfaction. \emph{Journal of Youth and Adolescence},
\emph{41}(12), 1588--1599.
doi:\href{https://doi.org/10.1007/s10964-012-9776-5}{10.1007/s10964-012-9776-5}

\hypertarget{ref-Levine2012}{}
Levine, L. J., Lench, H. C., Kaplan, R. L., \& Safer, M. A. (2012).
Accuracy and artifact: Reexamining the intensity bias in affective
forecasting. \emph{Journal of Personality and Social Psychology},
\emph{103}(4), 584--605.
doi:\href{https://doi.org/10.1037/a0029544}{10.1037/a0029544}

\hypertarget{ref-Levy-Gigi2012}{}
Levy-Gigi, E., Kéri, S., Myers, C. E., Lencovsky, Z., Sharvit-Benbaji,
H., Orr, S. P., \ldots{} Gluck, M. A. (2012). Individuals with
posttraumatic stress disorder show a selective deficit in generalization
of associative learning. \emph{Neuropsychology}, \emph{26}(6), 758--767.
doi:\href{https://doi.org/10.1037/a0029361}{10.1037/a0029361}

\hypertarget{ref-Lewin2012}{}
Lewin, A. B., Peris, T. S., De Nadai, A. S., McCracken, J. T., \&
Piacentini, J. (2012). Agreement between therapists, parents, patients,
and independent evaluators on clinical improvement in pediatric
obsessive-compulsive disorder. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(6), 1103--1107.
doi:\href{https://doi.org/10.1037/a0029991}{10.1037/a0029991}

\hypertarget{ref-Lewis2017}{}
Lewis, R. W., \& Farkas, G. (2017). Using an opportunity-propensity
framework to estimate individual-, classroom-, and school-level
predictors of middle school science achievement. \emph{Contemporary
Educational Psychology}, \emph{51}, 185--197.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.08.003}{10.1016/j.cedpsych.2017.08.003}

\hypertarget{ref-Leygue2017}{}
Leygue, C., Ferguson, E., \& Spence, A. (2017). Saving energy in the
workplace: Why, and for whom? \emph{Journal of Environmental
Psychology}, \emph{53}, 50--62.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.06.006}{10.1016/j.jenvp.2017.06.006}

\hypertarget{ref-Leykin2017a}{}
Leykin, Y., Dunn, L. B., \& Muñoz, R. F. (2017). The effect of
depression on the decision to join a clinical trial. \emph{Journal of
Consulting and Clinical Psychology}, \emph{85}(7), 751--756.
doi:\href{https://doi.org/10.1037/ccp0000212}{10.1037/ccp0000212}

\hypertarget{ref-Li2012a}{}
Li, T., McBride-Chang, C., Wong, A., \& Shu, H. (2012). Longitudinal
predictors of spelling and reading comprehension in Chinese as an L1 and
English as an L2 in Hong Kong Chinese children. \emph{Journal of
Educational Psychology}, \emph{104}(2), 286--301.
doi:\href{https://doi.org/10.1037/a0026445}{10.1037/a0026445}

\hypertarget{ref-Li2012}{}
Li, X., Zhao, W., \& Pollatsek, A. (2012). Dividing lines at the word
boundary position helps reading in Chinese. \emph{Psychonomic Bulletin
\& Review}, \emph{19}(5), 929--934.
doi:\href{https://doi.org/10.3758/s13423-012-0270-6}{10.3758/s13423-012-0270-6}

\hypertarget{ref-Liao2016}{}
Liao, H.-Y., Hong, Y.-y., \& Rounds, J. (2016). Perception of subtle
racism: The role of group status and legitimizing ideologies. \emph{The
Counseling Psychologist}, \emph{44}(2), 237--266.
doi:\href{https://doi.org/10.1177/0011000015625329}{10.1177/0011000015625329}

\hypertarget{ref-Liao2017}{}
Liao, H.-y., Spanierman, L. B., Harlow, A. J., \& Neville, H. A. (2017).
Do parents matter? Examination of white college students' intergroup
experiences and attitudes. \emph{The Counseling Psychologist},
\emph{45}(2), 193--212.
doi:\href{https://doi.org/10.1177/0011000017694337}{10.1177/0011000017694337}

\hypertarget{ref-Libon2012}{}
Libon, D. J., McMillan, C., Avants, B., Boller, A., Morgan, B.,
Burkholder, L., \ldots{} Grossman, M. (2012). Deficits in concept
formation in amyotrophic lateral sclerosis. \emph{Neuropsychology},
\emph{26}(4), 422--429.
doi:\href{https://doi.org/10.1037/a0028668}{10.1037/a0028668}

\hypertarget{ref-Liechty2016}{}
Liechty, T., Willfong, F., \& Sveinson, K. (2016). Embodied experiences
of empowerment among female tackle football players. \emph{Sociology of
Sport Journal}, \emph{33}(4), 305--316.
doi:\href{https://doi.org/10.1123/ssj.2015-0149}{10.1123/ssj.2015-0149}

\hypertarget{ref-Lin2012}{}
Lin, Y.-J., \& Israel, T. (2012). A computer-based intervention to
reduce internalized heterosexism in men. \emph{Journal of Counseling
Psychology}, \emph{59}(3), 458--464.
doi:\href{https://doi.org/10.1037/a0028282}{10.1037/a0028282}

\hypertarget{ref-Lin2012a}{}
Lin, Z., \& He, S. (2012). Emergent filling in induced by motion
integration reveals a high-level mechanism in filling in.
\emph{Psychological Science}, \emph{23}(12), 1534--1541.
doi:\href{https://doi.org/10.1177/0956797612446348}{10.1177/0956797612446348}

\hypertarget{ref-Linting2007}{}
Linting, M., Meulman, J. J., Groenen, P. J. F., \& Koojj, A. J. van der.
(2007). Nonlinear principal components analysis: Introduction and
application. \emph{Psychological Methods}, \emph{12}(3), 336--358.
doi:\href{https://doi.org/10.1037/1082-989X.12.3.336}{10.1037/1082-989X.12.3.336}

\hypertarget{ref-Lipowski2017}{}
Lipowski, S., Ariel, R., Tauber, S. K., \& Dunlosky, J. (2017).
Children's agenda-based regulation: The effects of prior performance and
reward on elementary school children's study choices. \emph{Journal of
Experimental Child Psychology}, \emph{164}, 55--67.
doi:\href{https://doi.org/10.1016/j.jecp.2017.06.015}{10.1016/j.jecp.2017.06.015}

\hypertarget{ref-Litalien2017a}{}
Litalien, D., Morin, A. J., \& McInerney, D. M. (2017). Generalizability
of achievement goal profiles across five cultural groups: More
similarities than differences. \emph{Contemporary Educational
Psychology}, \emph{51}, 267--283.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.08.008}{10.1016/j.cedpsych.2017.08.008}

\hypertarget{ref-Litalien2017}{}
Litalien, D., Morin, A. J., Gagné, M., Vallerand, R. J., Losier, G. F.,
\& Ryan, R. M. (2017). Evidence of a continuum structure of academic
self-determination: A two-study test using a bifactor-ESEM
representation of academic motivation. \emph{Contemporary Educational
Psychology}, \emph{51}, 67--82.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.06.010}{10.1016/j.cedpsych.2017.06.010}

\hypertarget{ref-Liu2017a}{}
Liu, C., \& Georgiou, G. K. (2017). Cognitive and environmental
correlates of rapid automatized naming in Chinese kindergarten children.
\emph{Journal of Educational Psychology}, \emph{109}(4), 465--476.
doi:\href{https://doi.org/10.1037/edu0000151}{10.1037/edu0000151}

\hypertarget{ref-Liu2012a}{}
Liu, K., \& Fox Tree, J. E. (2012). Hedges enhance memory but inhibit
retelling. \emph{Psychonomic Bulletin \& Review}, \emph{19}(5),
892--898.
doi:\href{https://doi.org/10.3758/s13423-012-0275-1}{10.3758/s13423-012-0275-1}

\hypertarget{ref-Liu2017}{}
Liu, L., \& Kager, R. (2017). Statistical learning of speech sounds is
most robust during the period of perceptual attunement. \emph{Journal of
Experimental Child Psychology}, \emph{164}, 192--208.
doi:\href{https://doi.org/10.1016/j.jecp.2017.05.013}{10.1016/j.jecp.2017.05.013}

\hypertarget{ref-Liu2012}{}
Liu, P., \& Pell, M. D. (2012). Recognizing vocal emotions in Mandarin
Chinese: A validated database of Chinese vocal emotional stimuli.
\emph{Behavior Research Methods}, \emph{44}(4), 1042--1051.
doi:\href{https://doi.org/10.3758/s13428-012-0203-3}{10.3758/s13428-012-0203-3}

\hypertarget{ref-Liu2016a}{}
Liu, S., Zhou, Y., Palumbo, R., \& Wang, J.-L. (2016). Dynamical
correlation: A new method for quantifying synchrony with multivariate
intensive longitudinal data. \emph{Psychological Methods}, \emph{21}(3),
291--308.
doi:\href{https://doi.org/10.1037/met0000071}{10.1037/met0000071}

\hypertarget{ref-Liu2016c}{}
Liu, T., Wong, Y. J., \& Tsai, P.-C. (2016). Conditional mediation
models of intersecting identities among female Asian international
students. \emph{The Counseling Psychologist}, \emph{44}(3), 411--441.
doi:\href{https://doi.org/10.1177/0011000016637200}{10.1177/0011000016637200}

\hypertarget{ref-Liu2017b}{}
Liu, Y., Millsap, R. E., West, S. G., Tein, J.-Y. Y., Tanaka, R., \&
Grimm, K. J. (2017). Testing measurement invariance in longitudinal data
with ordered-categorical measures. \emph{Psychological Methods},
\emph{22}(3), 486--506.
doi:\href{https://doi.org/10.1037/met0000075}{10.1037/met0000075}

\hypertarget{ref-Liu2018}{}
Liu, Y., Su, Y., Xu, G., \& Pei, M. (2018). When do you know what you
know? The emergence of memory monitoring. \emph{Journal of Experimental
Child Psychology}, \emph{166}, 34--48.
doi:\href{https://doi.org/10.1016/j.jecp.2017.06.014}{10.1016/j.jecp.2017.06.014}

\hypertarget{ref-Liverant2012}{}
Liverant, G. I., Suvak, M. K., Pineles, S. L., \& Resick, P. A. (2012).
Changes in posttraumatic stress disorder and depressive symptoms during
cognitive processing therapy: Evidence for concurrent change.
\emph{Journal of Consulting and Clinical Psychology}, \emph{80}(6),
957--967. doi:\href{https://doi.org/10.1037/a0030485}{10.1037/a0030485}

\hypertarget{ref-Lloyd2017}{}
Lloyd, E. P., Hugenberg, K., McConnell, A. R., Kunstman, J. W., \&
Deska, J. C. (2017). Black and white Lies: Race-based biases in
deception judgments. \emph{Psychological Science}, \emph{28}(8),
1125--1136.
doi:\href{https://doi.org/10.1177/0956797617705399}{10.1177/0956797617705399}

\hypertarget{ref-Locke}{}
Locke, K. D., Craig, T., Baik, K.-D., \& Gohil, K. (2012). Binds and
bounds of communion: Effects of interpersonal values on assumed
similarity of self and others. \emph{Journal of Personality and Social
Psychology}, \emph{103}(5), 879--897.
doi:\href{https://doi.org/10.1037/a0029422}{10.1037/a0029422}

\hypertarget{ref-Locke2017}{}
Locke, K. D., Sayegh, L., Penberthy, J. K., Weber, C., Haentjens, K., \&
Turecki, G. (2017). Interpersonal circumplex profiles of persistent
depression: Goals, self-efficacy, problems, And effects Of group
therapy. \emph{Journal of Clinical Psychology}, \emph{73}(6), 595--611.
doi:\href{https://doi.org/10.1002/jclp.22343}{10.1002/jclp.22343}

\hypertarget{ref-Lombrozo2012}{}
Lombrozo, T., \& Rehder, B. (2012). Functions in biological kind
classification. \emph{Cognitive Psychology}, \emph{65}(4), 457--485.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.06.002}{10.1016/j.cogpsych.2012.06.002}

\hypertarget{ref-London2017}{}
London, K., Hall, A. K., \& Lytle, N. E. (2017). Does it help, hurt, or
something else? The effect of a something else response alternative on
children's performance on forced-choice questions. \emph{Psychology,
Public Policy, and Law}, \emph{23}(3), 281--289.
doi:\href{https://doi.org/10.1037/law0000129}{10.1037/law0000129}

\hypertarget{ref-Long2012}{}
Long, Y., \& Baran, P. K. (2012). Does intelligibility affect place
legibility? Understanding the relationship between objective and
subjective evaluations of the urban environment. \emph{Environment and
Behavior}, \emph{44}(5), 616--640.
doi:\href{https://doi.org/10.1177/0013916511402059}{10.1177/0013916511402059}

\hypertarget{ref-Lou2017}{}
Lou, Y., Liu, Y., Kaakinen, J. K., \& Li, X. (2017). Using support
vector machines to identify literacy skills: Evidence from eye
movements. \emph{Behavior Research Methods}, \emph{49}(3), 887--895.
doi:\href{https://doi.org/10.3758/s13428-016-0748-7}{10.3758/s13428-016-0748-7}

\hypertarget{ref-Lount2017}{}
Lount, R. B., Pettit, N. C., \& Doyle, S. P. (2017). Motivating
underdogs and favorites. \emph{Organizational Behavior and Human
Decision Processes}, \emph{141}, 82--93.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.06.003}{10.1016/j.obhdp.2017.06.003}

\hypertarget{ref-Love2017}{}
Love, A., Gonzalez-Sobrino, B., \& Hughey, M. W. (2017). Excessive
celebration? The racialization of recruiting commitments on college
football internet message boards. \emph{Sociology of Sport Journal},
\emph{34}(3), 235--247.
doi:\href{https://doi.org/10.1123/ssj.2016-0033}{10.1123/ssj.2016-0033}

\hypertarget{ref-Lopez-Perez2017}{}
López-Pérez, B., Howells, L., \& Gummerum, M. (2017). Cruel to be kind:
Factors underlying altruistic efforts to worsen another person's mood.
\emph{Psychological Science}, \emph{28}(7), 862--871.
doi:\href{https://doi.org/10.1177/0956797617696312}{10.1177/0956797617696312}

\hypertarget{ref-Lopez-Romero2012}{}
López-Romero, L., Romero, E., \& Luengo, M. Á. (2012). Disentanglingthe
role of psychopathic traits and externalizing behaviour in predicting
conduct problems from childhood to adolescence. \emph{Journal of Youth
and Adolescence}, \emph{41}(11), 1397--1408.
doi:\href{https://doi.org/10.1007/s10964-012-9800-9}{10.1007/s10964-012-9800-9}

\hypertarget{ref-Losch2017}{}
Lösch, T., Lüdtke, O., Robitzsch, A., Kelava, A., Nagengast, B., \&
Trautwein, U. (2017). A well-rounded view: Using an interpersonal
approach to predict achievement by academic self-concept and peer
ratings of competence. \emph{Contemporary Educational Psychology},
\emph{51}, 198--208.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.07.003}{10.1016/j.cedpsych.2017.07.003}

\hypertarget{ref-Lu2017}{}
Lu, J. G., Akinola, M., \& Mason, M. F. (2017). ``Switching on''
creativity: Task switching can increase creativity by reducing cognitive
fixation. \emph{Organizational Behavior and Human Decision Processes},
\emph{139}, 63--75.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.01.005}{10.1016/j.obhdp.2017.01.005}

\hypertarget{ref-Lu2012}{}
Lu, Y., \& Zimring, C. (2012). Can intensive care staff see their
patients? An improved visibility analysis methodology. \emph{Environment
and Behavior}, \emph{44}(6), 861--876.
doi:\href{https://doi.org/10.1177/0013916511405314}{10.1177/0013916511405314}

\hypertarget{ref-Luan2017}{}
Luan, S., \& Reb, J. (2017). Fast-and-frugal trees as noncompensatory
models of performance-based personnel decisions. \emph{Organizational
Behavior and Human Decision Processes}, \emph{141}, 29--42.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.05.003}{10.1016/j.obhdp.2017.05.003}

\hypertarget{ref-Lund2017}{}
Lund, S., \& Söderström, T. (2017). To see or not to see: Talent
identification in the Swedish Football Association. \emph{Sociology of
Sport Journal}, \emph{34}(3), 248--258.
doi:\href{https://doi.org/10.1123/ssj.2016-0144}{10.1123/ssj.2016-0144}

\hypertarget{ref-Lundqvist2017}{}
Lundqvist, D., Svärd, J., Michelgård Palmquist, Å., Fischer, H., \&
Svenningsson, P. (2017). Patients with Parkinson's Disease display a
dopamine therapy related negative bias and an enlarged range in
emotional responses to facial emotional stimuli. \emph{Neuropsychology},
\emph{31}(6), 605--612.
doi:\href{https://doi.org/10.1037/neu0000371}{10.1037/neu0000371}

\hypertarget{ref-Lusk2017}{}
Lusk, B. R., Carr, A. R., Ranson, V. A., \& Felmingham, K. L. (2017).
Women in the midluteal phase of the menstrual cycle have difficulty
suppressing the processing of negative emotional stimuli: An
event-related potential study. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{17}(4), 886--903.
doi:\href{https://doi.org/10.3758/s13415-017-0520-1}{10.3758/s13415-017-0520-1}

\hypertarget{ref-Lussier2011}{}
Lussier, P., \& Davies, G. (2011). A person-oriented perspective on
sexual offenders, offending trajectories, and risk of recidivism: A new
challenge for policymakers, risk assessors, and actuarial prediction?
\emph{Psychology, Public Policy, and Law}, \emph{17}(4), 530--561.
doi:\href{https://doi.org/10.1037/a0024388}{10.1037/a0024388}

\hypertarget{ref-Lutz2017}{}
Lutz, J., \& Fiske, A. (2017). Perceived burdensomeness in older and
younger aults: Evaluation of the psychometric properties of the
interpersonal needs questionnaire. \emph{Journal of Clinical
Psychology}, \emph{73}(9), 1179--1195.
doi:\href{https://doi.org/10.1002/jclp.22415}{10.1002/jclp.22415}

\hypertarget{ref-Luyckx2017}{}
Luyckx, K., Duriez, B., Green, L. M., \& Negru-Subtirica, O. (2017).
Identity processes and intrinsic and extrinsic goal pursuits:
Directionality of effects in college students. \emph{Journal of Youth
and Adolescence}, \emph{46}(8), 1758--1771.
doi:\href{https://doi.org/10.1007/s10964-016-0626-8}{10.1007/s10964-016-0626-8}

\hypertarget{ref-Ludtke2011}{}
Lüdtke, O., Marsh, H. W., Robitzsch, A., \& Trautwein, U. (2011). A 2 ×
2 taxonomy of multilevel latent contextual models: Accuracy--bias
trade-offs in full and partial error correction models.
\emph{Psychological Methods}, \emph{16}(4), 444--467.
doi:\href{https://doi.org/10.1037/a0024376}{10.1037/a0024376}

\hypertarget{ref-Ludtke2008}{}
Lüdtke, O., Marsh, H. W., Robitzsch, A., Trautwein, U., Asparouhov, T.,
\& Muthén, B. (2008). The multilevel latent covariate model: A new, more
reliable approach to group-level effects in contextual studies.
\emph{Psychological Methods}, \emph{13}(3), 203--229.
doi:\href{https://doi.org/10.1037/a0012869}{10.1037/a0012869}

\hypertarget{ref-Lymeus2017}{}
Lymeus, F., Lundgren, T., \& Hartig, T. (2017). Attentional effort of
beginning mindfulness training is offset with practice directed toward
images of natural scenery. \emph{Environment and Behavior},
\emph{49}(5), 536--559.
doi:\href{https://doi.org/10.1177/0013916516657390}{10.1177/0013916516657390}

\hypertarget{ref-Ma2017}{}
Ma, A., \& Kay, A. C. (2017). Compensatory control and ambiguity
intolerance. \emph{Organizational Behavior and Human Decision
Processes}, \emph{140}, 46--61.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.04.001}{10.1016/j.obhdp.2017.04.001}

\hypertarget{ref-Ma-Kellams2012}{}
Ma-Kellams, C., \& Blascovich, J. (2012). Enjoying life in the face of
death: East--West differences in responses to mortality salience.
\emph{Journal of Personality and Social Psychology}, \emph{103}(5),
773--786. doi:\href{https://doi.org/10.1037/a0029366}{10.1037/a0029366}

\hypertarget{ref-Macarthur2017}{}
MacArthur, P. J., Angelini, J. R., Billings, A. C., \& Smith, L. R.
(2017). The thin line between masculinity and skate: Primetime
narratives of male figure skaters on the CBC and NBC 2014 winter olympic
broadcasts. \emph{Sociology of Sport Journal}, \emph{34}(1), 46--58.
doi:\href{https://doi.org/10.1123/ssj.2016-0052}{10.1123/ssj.2016-0052}

\hypertarget{ref-MacchiCassia2012}{}
Macchi Cassia, V., Pisacane, A., \& Gava, L. (2012). No own-age bias in
3-year-old children: More evidence for the role of early experience in
building face-processing biases. \emph{Journal of Experimental Child
Psychology}, \emph{113}(3), 372--382.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.014}{10.1016/j.jecp.2012.06.014}

\hypertarget{ref-MacDonald2017a}{}
MacDonald, D. E., McFarlane, T. L., Dionne, M. M., David, L., \&
Olmsted, M. P. (2017). Rapid response to intensive treatment for bulimia
nervosa and purging disorder: A randomized controlled trial of a CBT
intervention to facilitate early behavior change. \emph{Journal of
Consulting and Clinical Psychology}, \emph{85}(9), 896--908.
doi:\href{https://doi.org/10.1037/ccp0000221}{10.1037/ccp0000221}

\hypertarget{ref-MacDonald2017}{}
MacDonald, K., Yurovsky, D., \& Frank, M. C. (2017). Social cues
modulate the representations underlying cross-situational learning.
\emph{Cognitive Psychology}, \emph{94}, 67--84.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.02.003}{10.1016/j.cogpsych.2017.02.003}

\hypertarget{ref-Mace2012}{}
Macé, A.-L., Ergis, A.-M., \& Caza, N. (2012). The effect of response
modality on immediate serial recall in dementia of the Alzheimer type.
\emph{Neuropsychology}, \emph{26}(5), 613--623.
doi:\href{https://doi.org/10.1037/a0028796}{10.1037/a0028796}

\hypertarget{ref-Mackenzie2011}{}
Mackenzie, S. B., Podsakoff, P. M., \& Podsakoff, N. P. (2011).
Challenge-oriented organizational citizenship behaviors and
organizational effectiveness: Do challenge-oriented behaviors really
have an impact on the organization's bottom line? \emph{Personnel
Psychology}, \emph{64}(3), 559--592.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01219.x}{10.1111/j.1744-6570.2011.01219.x}

\hypertarget{ref-MacLeod2017}{}
MacLeod, J., Stewart, B. M., Newman, A. J., \& Arnell, K. M. (2017). Do
emotion-induced blindness and the attentional blink share underlying
mechanisms? An event-related potential study of emotionally-arousing
words. \emph{Cognitive, Affective, \& Behavioral Neuroscience},
\emph{17}(3), 592--611.
doi:\href{https://doi.org/10.3758/s13415-017-0499-7}{10.3758/s13415-017-0499-7}

\hypertarget{ref-Madjar2011}{}
Madjar, N., Kaplan, A., \& Weinstock, M. (2011). Clarifying
mastery-avoidance goals in high school: Distinguishing between
intrapersonal and task-based standards of competence. \emph{Contemporary
Educational Psychology}, \emph{36}(4), 268--279.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.03.003}{10.1016/j.cedpsych.2011.03.003}

\hypertarget{ref-Madon2017}{}
Madon, S., Guyll, M., Yang, Y., Smalarz, L., Marschall, J., \& Lannin,
D. G. (2017). A biphasic process of resistance among suspects: The
mobilization and decline of self-regulatory resources. \emph{Law and
Human Behavior}, \emph{41}(2), 159--172.
doi:\href{https://doi.org/10.1037/lhb0000221}{10.1037/lhb0000221}

\hypertarget{ref-Madon2013}{}
Madon, S., Yang, Y., Smalarz, L., Guyll, M., \& Scherr, K. C. (2013).
How factors present during the immediate interrogation situation produce
short-sighted confession decisions. \emph{Law and Human Behavior},
\emph{37}(1), 60--74.
doi:\href{https://doi.org/10.1037/lhb0000011}{10.1037/lhb0000011}

\hypertarget{ref-Maguen2017}{}
Maguen, S., Burkman, K., Madden, E., Dinh, J., Bosch, J., Keyser, J.,
\ldots{} Neylan, T. C. (2017). Impact of killing in war: A randomized,
controlled pilot trial. \emph{Journal of Clinical Psychology},
\emph{73}(9), 997--1012.
doi:\href{https://doi.org/10.1002/jclp.22471}{10.1002/jclp.22471}

\hypertarget{ref-Mahdjoubi2012}{}
Mahdjoubi, L., \& Akplotsyi, R. (2012). The impact of sensory learning
modalities on children's sensitivity to sensory cues in the perception
of their school environment. \emph{Journal of Environmental Psychology},
\emph{32}(3), 208--215.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.02.002}{10.1016/j.jenvp.2012.02.002}

\hypertarget{ref-Malmberg2012}{}
Malmberg, M., Kleinjan, M., Vermulst, A. A., Overbeek, G., Monshouwer,
K., Lammers, J., \& Engels, R. C. M. E. (2012). Do substance use risk
personality dimensions predict the onset of substance use in early
adolescence? A variable- and person-centered approach. \emph{Journal of
Youth and Adolescence}, \emph{41}(11), 1512--1525.
doi:\href{https://doi.org/10.1007/s10964-012-9775-6}{10.1007/s10964-012-9775-6}

\hypertarget{ref-Maltby2012}{}
Maltby, J., Wood, A. M., Vlaev, I., Taylor, M. J., \& Brown, G. D.
(2012). Contextual effects on the perceived health benefits of exercise:
The exercise rank hypothesis. \emph{Journal of Sport and Exercise
Psychology}, \emph{34}(6), 828--841.
doi:\href{https://doi.org/10.1123/jsep.34.6.828}{10.1123/jsep.34.6.828}

\hypertarget{ref-Mandeville2016}{}
Mandeville, A., Halbesleben, J., \& Whitman, M. (2016). Misalignment and
misperception in preferences to utilize family-friendly benefits:
Implications for benefit utilization and work--family conflict.
\emph{Personnel Psychology}, \emph{69}(4), 895--929.
doi:\href{https://doi.org/10.1111/peps.12124}{10.1111/peps.12124}

\hypertarget{ref-Mann2012}{}
Mann, A., Moeller, K., Pixner, S., Kaufmann, L., \& Nuerk, H. C. (2012).
On the development of Arabic three-digit number processing in primary
school children. \emph{Journal of Experimental Child Psychology},
\emph{113}(4), 594--601.
doi:\href{https://doi.org/10.1016/j.jecp.2012.08.002}{10.1016/j.jecp.2012.08.002}

\hypertarget{ref-Manne2012}{}
Manne, S. L., Kashy, D. A., Rubin, S., Hernandez, E., \& Bergman, C.
(2012). Therapist and patient perceptions of alliance and progress in
psychological therapy for women diagnosed with gynecological cancers.
\emph{Journal of Consulting and Clinical Psychology}, \emph{80}(5),
800--810. doi:\href{https://doi.org/10.1037/a0029158}{10.1037/a0029158}

\hypertarget{ref-Mansour2012}{}
Mansour, J. K., Beaudry, J. L., Bertrand, M. I., Kalmet, N., Melsom, E.
I., \& Lindsay, R. C. L. (2012). Impact of disguise on identification
decisions and confidence with simultaneous and sequential lineups.
\emph{Law and Human Behavior}, \emph{36}(6), 513--526.
doi:\href{https://doi.org/10.1037/h0093937}{10.1037/h0093937}

\hypertarget{ref-Marcet2016}{}
Marcet, A., \& Perea, M. (2017). Is nevtral NEUTRAL? Visual similarity
effects in the early phases of written-word recognition.
\emph{Psychonomic Bulletin \& Review}, \emph{24}(4), 1180--1185.
doi:\href{https://doi.org/10.3758/s13423-016-1180-9}{10.3758/s13423-016-1180-9}

\hypertarget{ref-Marcus2017}{}
Marcus, B., Weigelt, O., Hergert, J., Gurt, J., \& Gelléri, P. (2017).
The use of snowball sampling for multi source organizational research:
Some cause for concern. \emph{Personnel Psychology}, \emph{70}(3),
635--673.
doi:\href{https://doi.org/10.1111/peps.12169}{10.1111/peps.12169}

\hypertarget{ref-Marmarosh2012}{}
Marmarosh, C. L., \& Kivlighan, D. M. (2012). Relationships among client
and counselor agreement about the working alliance, session evaluations,
and change in client symptoms using response surface analysis.
\emph{Journal of Counseling Psychology}, \emph{59}(3), 352--367.
doi:\href{https://doi.org/10.1037/a0028907}{10.1037/a0028907}

\hypertarget{ref-Marrero2017}{}
Marrero, H., Urrutia, M., Beltrán, D., Gámez, E., \& Díaz, J. M. (2017).
Understanding approach and avoidance in verbal descriptions of everyday
actions: An ERP study. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{17}(3), 612--624.
doi:\href{https://doi.org/10.3758/s13415-017-0500-5}{10.3758/s13415-017-0500-5}

\hypertarget{ref-Marshall2017}{}
Marshall, A. D., Feinberg, M. E., Jones, D. E., \& Chote, D. R. (2017).
The Children, Intimate Relationships, and Conflictual Life Events
(CIRCLE) interview for simultaneous measurement of intimate partner and
parent to child aggression. \emph{Psychological Assessment},
\emph{29}(8), 978--989.
doi:\href{https://doi.org/10.1037/pas0000393}{10.1037/pas0000393}

\hypertarget{ref-Martin2017}{}
Martin, A. E., \& Phillips, K. W. (2017). What ``blindness'' to gender
differences helps women see and do: Implications for confidence, agency,
and action in male-dominated environments. \emph{Organizational Behavior
and Human Decision Processes}, \emph{142}, 28--44.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.07.004}{10.1016/j.obhdp.2017.07.004}

\hypertarget{ref-Martin2012}{}
Martin, A. J. (2012). The role of personal best (PB) goals in the
achievement and behavioral engagement of students with ADHD and students
without ADHD. \emph{Contemporary Educational Psychology}, \emph{37}(2),
91--105.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.01.002}{10.1016/j.cedpsych.2012.01.002}

\hypertarget{ref-Martins2012}{}
Martins, A., \& Calheiros, M. M. (2012). Construction of a
Self-Complexity Scale for Adolescents. \emph{Psychological Assessment},
\emph{24}(4), 973--982.
doi:\href{https://doi.org/10.1037/a0028582}{10.1037/a0028582}

\hypertarget{ref-Marty2012}{}
Marty, M. A., Segal, D. L., Coolidge, F. L., \& Klebe, K. J. (2012).
Analysis of the psychometric properties of the interpersonal needs
questionnaire (INQ) among community-dwelling older adults. \emph{Journal
of Clinical Psychology}, \emph{68}(9), 1008--1018.
doi:\href{https://doi.org/10.1002/jclp.21877}{10.1002/jclp.21877}

\hypertarget{ref-Mathot2017}{}
Mathôt, S., Grainger, J., \& Strijkers, K. (2017). Pupillary responses
to words that convey a sense of brightness or darkness.
\emph{Psychological Science}, \emph{28}(8), 1116--1124.
doi:\href{https://doi.org/10.1177/0956797617702699}{10.1177/0956797617702699}

\hypertarget{ref-Matosic2016}{}
Matosic, D., Ntoumanis, N., Boardley, I. D., Stenling, A., \& Sedikides,
C. (2016). Linking narcissism, motivation, and doping attitudes in
sport: A multilevel investigation involving coaches and athletes.
\emph{Journal of Sport and Exercise Psychology}, \emph{38}(6), 556--566.
doi:\href{https://doi.org/10.1123/jsep.2016-0141}{10.1123/jsep.2016-0141}

\hypertarget{ref-Matthies2012}{}
Matthies, E., Selge, S., \& Kl??ckner, C. A. (2012). The role of
parental behaviour for the development of behaviour specific
environmental norms - The example of recycling and re-use behaviour.
\emph{Journal of Environmental Psychology}, \emph{32}(3), 277--284.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.04.003}{10.1016/j.jenvp.2012.04.003}

\hypertarget{ref-Mattson2012}{}
Mattson, C., Powers, B., Halfaker, D., Akeson, S., \& Ben-Porath, Y.
(2012). Predicting drug court treatment completion using the MMPI-2-RF.
\emph{Psychological Assessment}, \emph{24}(4), 937--943.
doi:\href{https://doi.org/10.1037/a0028267}{10.1037/a0028267}

\hypertarget{ref-Mawritz2012}{}
Mawritz, M. B., Mayer, D. M., Hoobler, J. M., Wayne, S. J., \& Marinova,
S. V. (2012). A trickle-down model of abusive supervision.
\emph{Personnel Psychology}, \emph{65}(2), 325--357.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01246.x}{10.1111/j.1744-6570.2012.01246.x}

\hypertarget{ref-May2012}{}
May, C., Owens, M., \& Einstein, G. O. (2012). The impact of emotion on
prospective memory and monitoring: No pain, big gain. \emph{Psychonomic
Bulletin \& Review}, \emph{19}(6), 1165--1171.
doi:\href{https://doi.org/10.3758/s13423-012-0301-3}{10.3758/s13423-012-0301-3}

\hypertarget{ref-May2009}{}
May, R. A. B. (2009). The good and bad of it all: Professional black
male basketball players as role models for young black male basketball
players. \emph{Sociology of Sport Journal}, \emph{26}(3), 443--461.
doi:\href{https://doi.org/10.1123/ssj.26.3.443}{10.1123/ssj.26.3.443}

\hypertarget{ref-Maynard2012}{}
Maynard, B. R., Salas-Wright, C. P., Vaughn, M. G., \& Peters, K. E.
(2012). Who are truant youth? Examining distinctive profiles of truant
youth using latent profile analysis. \emph{Journal of Youth and
Adolescence}, \emph{41}(12), 1671--1684.
doi:\href{https://doi.org/10.1007/s10964-012-9788-1}{10.1007/s10964-012-9788-1}

\hypertarget{ref-McArdle2009}{}
McArdle, J. J., Grimm, K. J., Hamagami, F., Bowles, R. P., \& Meredith,
W. (2009). Modeling life-span growth curves of cognition using
longitudinal data with multiple samples and changing scales of
measurement. \emph{Psychological Methods}, \emph{14}(2), 126--149.
doi:\href{https://doi.org/10.1037/a0015857}{10.1037/a0015857}

\hypertarget{ref-McCabe2012}{}
McCabe, K. O., \& Fleeson, W. (2012). What is extraversion for?
Integrating trait and motivational perspectives and identifying the
purpose of extraversion. \emph{Psychological Science}, \emph{23}(12),
1498--1505.
doi:\href{https://doi.org/10.1177/0956797612444904}{10.1177/0956797612444904}

\hypertarget{ref-McCarthy2017}{}
McCarthy, J. M., Bauer, T. N., Truxillo, D. M., Campion, M. C., Van
Iddekinge, C. H., \& Campion, M. A. (2017). Using pre-test explanations
to improve test-taker reactions: Testing a set of ``wise''
interventions. \emph{Organizational Behavior and Human Decision
Processes}, \emph{141}, 43--56.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.04.002}{10.1016/j.obhdp.2017.04.002}

\hypertarget{ref-McClintock2017}{}
McClintock, A. S., Perlman, M. R., McCarrick, S. M., Anderson, T., \&
Himawan, L. (2017). Enhancing psychotherapy process with common factors
feedback: A randomized, clinical trial. \emph{Journal of Counseling
Psychology}, \emph{64}(3), 247--260.
doi:\href{https://doi.org/10.1037/cou0000188}{10.1037/cou0000188}

\hypertarget{ref-McDavid2017}{}
McDavid, L., McDonough, M. H., Blankenship, B. T., \& LeBreton, J. M.
(2017). A test of basic psychological needs theory in a
physical-activity-based program for underserved youth. \emph{Journal of
Sport and Exercise Psychology}, \emph{39}(1), 29--42.
doi:\href{https://doi.org/10.1123/jsep.2016-0038}{10.1123/jsep.2016-0038}

\hypertarget{ref-McDermott2013}{}
McDermott, R. C., \& Lopez, F. G. (2013). College men's intimate partner
violence attitudes: Contributions of adult attachment and gender role
stress. \emph{Journal of Counseling Psychology}, \emph{60}(1), 127--136.
doi:\href{https://doi.org/10.1037/a0030353}{10.1037/a0030353}

\hypertarget{ref-McDermott2017}{}
McDermott, R. C., Cheng, H.-L., Wong, Y. J., Booth, N., Jones, Z., \&
Sevig, T. (2017). Hope for help-seeking: A positive psychology
perspective of psychological help-seeking intentions. \emph{The
Counseling Psychologist}, \emph{45}(2), 237--265.
doi:\href{https://doi.org/10.1177/0011000017693398}{10.1177/0011000017693398}

\hypertarget{ref-McGrath2009}{}
McGrath, S. a, \& Chananie-Hill, R. a. (2009). ``Big freaky-looking
women'': Normalizing gender transgression through bodybuilding.
\emph{Sociology of Sport Journal}, \emph{26}(2), 235--254.
doi:\href{https://doi.org/10.1123/ssj.26.2.235}{10.1123/ssj.26.2.235}

\hypertarget{ref-McLawsen2012}{}
McLawsen, J. E., Scalora, M. J., \& Darrow, C. (2012). Civilly committed
sex offenders: A description and interstate comparison of populations.
\emph{Psychology, Public Policy, and Law}, \emph{18}(3), 453--476.
doi:\href{https://doi.org/10.1037/a0026116}{10.1037/a0026116}

\hypertarget{ref-McManus2012}{}
McManus, F., Surawy, C., Muse, K., Vazquez-Montes, M., \& Williams, J.
M. G. (2012). A randomized clinical trial of mindfulness-based cognitive
therapy versus unrestricted services for health anxiety
(hypochondriasis). \emph{Journal of Consulting and Clinical Psychology},
\emph{80}(5), 817--828.
doi:\href{https://doi.org/10.1037/a0028782}{10.1037/a0028782}

\hypertarget{ref-McNeil2012}{}
McNeil, N. M., Chesney, D. L., Matthews, P. G., Fyfe, E. R., Petersen,
L. A., Dunwiddie, A. E., \& Wheeler, M. C. (2012). It pays to be
organized: Organizing arithmetic practice around equivalent values
facilitates understanding of math equivalence. \emph{Journal of
Educational Psychology}, \emph{104}(4), 1109--1121.
doi:\href{https://doi.org/10.1037/a0028997}{10.1037/a0028997}

\hypertarget{ref-McNulty2017}{}
McNulty, J. K., Olson, M. A., Jones, R. E., \& Acosta, L. M. (2017).
Automatic associations between one's partner and one's affect as the
proximal mechanism of change in relationship satisfaction: Evidence from
evaluative conditioning. \emph{Psychological Science}, \emph{28}(8),
1031--1040.
doi:\href{https://doi.org/10.1177/0956797617702014}{10.1177/0956797617702014}

\hypertarget{ref-Meade2012}{}
Meade, A. W., \& Craig, S. B. (2012). Identifying careless responses in
survey data. \emph{Psychological Methods}, \emph{17}(3), 437--455.
doi:\href{https://doi.org/10.1037/a0028085}{10.1037/a0028085}

\hypertarget{ref-Meder2017}{}
Meder, B., \& Mayrhofer, R. (2017). Diagnostic causal reasoning with
verbal information. \emph{Cognitive Psychology}, \emph{96}, 54--84.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.05.002}{10.1016/j.cogpsych.2017.05.002}

\hypertarget{ref-Meier2012}{}
Meier, H. E., \& Leinwather, M. (2012). Women as ``armchair audience''?
Evidence from German national team football. \emph{Sociology of Sport
Journal}, \emph{29}(3), 365--384.
doi:\href{https://doi.org/10.1123/ssj.29.3.365}{10.1123/ssj.29.3.365}

\hypertarget{ref-Meinzer2012}{}
Meinzer, M. C., Pettit, J. W., Leventhal, A. M., \& Hill, R. M. (2012).
Explaining the covariance between attention-deficit hyperactivity
disorder symptoms and depressive symptoms: The role of hedonic
responsivity. \emph{Journal of Clinical Psychology}, \emph{68}(10),
1111--1121.
doi:\href{https://doi.org/10.1002/jclp.21884}{10.1002/jclp.21884}

\hypertarget{ref-Meisel2017}{}
Meisel, S. N., \& Colder, C. R. (2017). Social goals impact adolescent
substance use through influencing adolescents' connectedness to their
schools. \emph{Journal of Youth and Adolescence}, \emph{46}(9),
2015--2027.
doi:\href{https://doi.org/10.1007/s10964-017-0655-y}{10.1007/s10964-017-0655-y}

\hypertarget{ref-Melas2012}{}
Melas, C. D., Zampetakis, L. A., Dimopoulou, A., \& Moustakis, V.
(2012). Evaluating the properties of the Evidence-Based Practice
Attitude Scale (EBPAS) in health care. \emph{Psychological Assessment},
\emph{24}(4), 867--876.
doi:\href{https://doi.org/10.1037/a0027445}{10.1037/a0027445}

\hypertarget{ref-Meldrum2017}{}
Meldrum, R. C., \& Barnes, J. C. (2017). Unstructured socializing with
peers and delinquent behavior: A genetically informed analysis.
\emph{Journal of Youth and Adolescence}, \emph{46}(9), 1968--1981.
doi:\href{https://doi.org/10.1007/s10964-017-0680-x}{10.1007/s10964-017-0680-x}

\hypertarget{ref-Meleady2017}{}
Meleady, R., \& Crisp, R. J. (2017). Redefining climate change inaction
as temporal intergroup bias: Temporally adapted interventions for
reducing prejudice may help elicit environmental protection.
\emph{Journal of Environmental Psychology}, \emph{53}, 206--212.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.08.005}{10.1016/j.jenvp.2017.08.005}

\hypertarget{ref-Mennesson2012}{}
Mennesson, C. (2012). Gender regimes and habitus: An avenue for
analyzing gender building in sports contexts. \emph{Sociology of Sport
Journal}, \emph{29}(1), 4--21.
doi:\href{https://doi.org/10.1123/ssj.29.1.4}{10.1123/ssj.29.1.4}

\hypertarget{ref-Mercer2011}{}
Mercer, S. H., Zeigler-Hill, V., Wallace, M., \& Hayes, D. M. (2011).
Development and initial validation of the Inventory of Microaggressions
Against Black Individuals. \emph{Journal of Counseling Psychology},
\emph{58}(4), 457--469.
doi:\href{https://doi.org/10.1037/a0024937}{10.1037/a0024937}

\hypertarget{ref-Methot2016}{}
Methot, J. R., Lepine, J. A., Podsakoff, N. P., \& Christian, J. S.
(2016). Are workplace friendships a mixed blessing? Exploring tradeoffs
of multiplex relationships and their associations with job performance.
\emph{Personnel Psychology}, \emph{69}(2), 311--355.
doi:\href{https://doi.org/10.1111/peps.12109}{10.1111/peps.12109}

\hypertarget{ref-VanderMeulen2017}{}
Meulen, M. van der, Veldhuis, J., Braams, B. R., Peters, S., Konijn, E.
A., \& Crone, E. A. (2017). Brain activation upon ideal-body media
exposure and peer feedback in late adolescent girls. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, 712--723.
doi:\href{https://doi.org/10.3758/s13415-017-0507-y}{10.3758/s13415-017-0507-y}

\hypertarget{ref-Meuret2012}{}
Meuret, A. E., Seidel, A., Rosenfield, B., Hofmann, S. G., \&
Rosenfield, D. (2012). Does fear reactivity during exposure predict
panic symptom reduction? \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(5), 773--785.
doi:\href{https://doi.org/10.1037/a0028032}{10.1037/a0028032}

\hypertarget{ref-Meuwissen2017}{}
Meuwissen, A. S., Anderson, J. E., \& Zelazo, P. D. (2017). The creation
and validation of the developmental emotional faces stimulus set.
\emph{Behavior Research Methods}, \emph{49}(3), 960--966.
doi:\href{https://doi.org/10.3758/s13428-016-0756-7}{10.3758/s13428-016-0756-7}

\hypertarget{ref-Michaelides2017}{}
Michaelides, C. S., \& Avraamides, M. N. (2017). Developmental changes
in the mental transformation of spatial arrays. \emph{Journal of
Experimental Child Psychology}, \emph{164}, 152--162.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.013}{10.1016/j.jecp.2017.07.013}

\hypertarget{ref-Michaowski2016}{}
Michałowski, J. M., Droździel, D., Matuszewski, J., Koziejowski, W.,
Jednoróg, K., \& Marchewka, A. (2017). The Set of Fear Inducing Pictures
(SFIP): Development and validation in fearful and nonfearful
individuals. \emph{Behavior Research Methods}, \emph{49}(4), 1407--1419.
doi:\href{https://doi.org/10.3758/s13428-016-0797-y}{10.3758/s13428-016-0797-y}

\hypertarget{ref-Middlebrooks2017}{}
Middlebrooks, C. D., Kerr, T., \& Castel, A. D. (2017). Selectively
distracted: Divided attention and memory for important information.
\emph{Psychological Science}, \emph{28}(8), 1103--1115.
doi:\href{https://doi.org/10.1177/0956797617702502}{10.1177/0956797617702502}

\hypertarget{ref-Miguel2017}{}
Miguel, F. K., Giromini, L., Colombarolli, M. S., Zuanazzi, A. C., \&
Zennaro, A. (2017). A Brazilian investigation of the 36- and 16-item
difficulties in emotion regulation scales. \emph{Journal of Clinical
Psychology}, \emph{73}(9), 1146--1159.
doi:\href{https://doi.org/10.1002/jclp.22404}{10.1002/jclp.22404}

\hypertarget{ref-Miles2012}{}
Miles, E. W., \& Clenney, E. F. (2012). Extremely difficult negotiator
goals: Do they follow the predictions of goal-setting theory?
\emph{Organizational Behavior and Human Decision Processes},
\emph{118}(2), 108--115.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.02.001}{10.1016/j.obhdp.2012.02.001}

\hypertarget{ref-Milfont2012}{}
Milfont, T. L., \& Sibley, C. G. (2012). The big five personality traits
and environmental engagement: Associations at the individual and
societal level. \emph{Journal of Environmental Psychology},
\emph{32}(2), 187--195.
doi:\href{https://doi.org/10.1016/j.jenvp.2011.12.006}{10.1016/j.jenvp.2011.12.006}

\hypertarget{ref-Milkman2012}{}
Milkman, K. L. (2012). Unsure what the future will bring? You may
overindulge: Uncertainty increases the appeal of wants over shoulds.
\emph{Organizational Behavior and Human Decision Processes},
\emph{119}(2), 163--176.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.07.003}{10.1016/j.obhdp.2012.07.003}

\hypertarget{ref-Millar2017}{}
Millar, P. R., Balota, D. A., Maddox, G. B., Duchek, J. M.,
Aschenbrenner, A. J., Fagan, A. M., \ldots{} Morris, J. C. (2017).
Process dissociation analyses of memory changes in healthy aging,
preclinical, and very mild Alzheimer disease: Evidence for isolated
recollection deficits. \emph{Neuropsychology}, \emph{31}(7), 708--723.
doi:\href{https://doi.org/10.1037/neu0000352}{10.1037/neu0000352}

\hypertarget{ref-Miller2017}{}
Miller, A. B., Eisenlohr-Moul, T., Giletta, M., Hastings, P. D.,
Rudolph, K. D., Nock, M. K., \& Prinstein, M. J. (2017). A within-person
approach to risk for suicidal ideation and suicidal behavior: Examining
the roles of depression, stress, and abuse exposure. \emph{Journal of
Consulting and Clinical Psychology}, \emph{85}(7), 712--722.
doi:\href{https://doi.org/10.1037/ccp0000210}{10.1037/ccp0000210}

\hypertarget{ref-Miller2012a}{}
Miller, J. D., Few, L. R., Seibert, L. A., Watts, A., Zeichner, A., \&
Lynam, D. R. (2012). An examination of the Dirty Dozen measure of
psychopathy: A cautionary tale about the costs of brief measures.
\emph{Psychological Assessment}, \emph{24}(4), 1048--1053.
doi:\href{https://doi.org/10.1037/a0028583}{10.1037/a0028583}

\hypertarget{ref-Miller2017a}{}
Miller, J. G., Akiyama, H., \& Kapadia, S. (2017). Cultural variation in
communal versus exchange norms: Implications for social support.
\emph{Journal of Personality and Social Psychology}, \emph{113}(1),
81--94.
doi:\href{https://doi.org/10.1037/pspi0000091}{10.1037/pspi0000091}

\hypertarget{ref-Miller2009}{}
Miller, K. E., \& Hoffman, J. H. (2009). Mental well-being and
sport-related identities in college students. \emph{Sociology of Sport
Journal}, \emph{26}(2), 335--356.
doi:\href{https://doi.org/10.1123/ssj.26.2.335}{10.1123/ssj.26.2.335}

\hypertarget{ref-Miller2002}{}
Miller, K. E., Barnes, G. M., Sabo, D., Melnick, M. J., \& Farrell, M.
P. (2002). A comparison of health risk behavior in adolescent users of
anabolic-androgenic steroids, by gender and athlete status.
\emph{Sociology of Sport Journal}, \emph{19}(4), 385--402.
doi:\href{https://doi.org/10.1123/ssj.19.4.385}{10.1123/ssj.19.4.385}

\hypertarget{ref-Miller2012}{}
Miller, L. M., \& Roodenrys, S. (2012). Serial recall, word frequency,
and mixed lists: The influence of item arrangement. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{38}(6),
1731--1740.
doi:\href{https://doi.org/10.1037/a0028470}{10.1037/a0028470}

\hypertarget{ref-Miller2016}{}
Miller, P. J., Lubke, G. H., McArtor, D. B., \& Bergeman, C. S. (2016).
Finding structure in data using multivariate tree boosting.
\emph{Psychological Methods}, \emph{21}(4), 583--602.
doi:\href{https://doi.org/10.1037/met0000087}{10.1037/met0000087}

\hypertarget{ref-Misra2012}{}
Misra, S., \& Stokols, D. (2012). Psychological and health outcomes of
perceived information overload. \emph{Environment and Behavior},
\emph{44}(6), 737--759.
doi:\href{https://doi.org/10.1177/0013916511404408}{10.1177/0013916511404408}

\hypertarget{ref-Mohr2013}{}
Mohr, J. J., Selterman, D., \& Fassinger, R. E. (2013). Romantic
attachment and relationship functioning in same-sex couples.
\emph{Journal of Counseling Psychology}, \emph{60}(1), 72--82.
doi:\href{https://doi.org/10.1037/a0030994}{10.1037/a0030994}

\hypertarget{ref-Mokros2010}{}
Mokros, A., Stadtland, C., Osterheider, M., \& Nedopil, N. (2010).
Assessment of risk for violent recidivism through multivariate bayesian
classification. \emph{Psychology, Public Policy, and Law}, \emph{16}(4),
418--450. doi:\href{https://doi.org/10.1037/a0021312}{10.1037/a0021312}

\hypertarget{ref-Molinsky2012}{}
Molinsky, A. L., Grant, A. M., \& Margolis, J. D. (2012). The bedside
manner of homo economicus: How and why priming an economic schema
reduces compassion. \emph{Organizational Behavior and Human Decision
Processes}, \emph{119}(1), 27--37.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.05.001}{10.1016/j.obhdp.2012.05.001}

\hypertarget{ref-Molouki2017}{}
Molouki, S., \& Bartels, D. M. (2017). Personal change and the
continuity of the self. \emph{Cognitive Psychology}, \emph{93}, 1--17.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.11.006}{10.1016/j.cogpsych.2016.11.006}

\hypertarget{ref-Monti2012}{}
Monti, F., Agostini, F., Dellabartola, S., Neri, E., Bozicevic, L., \&
Pocecco, M. (2012). Pictorial intervention in a pediatric hospital
environment: Effects on parental affective perception of the unit.
\emph{Journal of Environmental Psychology}, \emph{32}(3), 216--224.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.03.001}{10.1016/j.jenvp.2012.03.001}

\hypertarget{ref-DeMontigny2012}{}
Montigny, L. de, Ling, R., \& Zacharias, J. (2012). The effects of
weather on walking rates in nine cities. \emph{Environment and
Behavior}, \emph{44}(6), 821--840.
doi:\href{https://doi.org/10.1177/0013916511409033}{10.1177/0013916511409033}

\hypertarget{ref-Montoya2017}{}
Montoya, A. K., \& Hayes, A. F. (2017). Two-condition within-participant
statistical mediation analysis: A path-analytic framework.
\emph{Psychological Methods}, \emph{22}(1), 6--27.
doi:\href{https://doi.org/10.1037/met0000086}{10.1037/met0000086}

\hypertarget{ref-Moore2012}{}
Moore, C., Detert, J. R., Klebe Treviño, L., Baker, V. L., \& Mayer, D.
M. (2012). Why employees do bad things: Moral disengagement and
unethical organizational behavior. \emph{Personnel Psychology},
\emph{65}(1), 1--48.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01237.x}{10.1111/j.1744-6570.2011.01237.x}

\hypertarget{ref-Morgan2016}{}
Morgan, G. B., Wells, K. E., Andretta, J. R., \& McKay, M. T. (2016).
Temporal attitudes profile transition among adolescents: A longitudinal
examination using mover-stayer latent transition analysis.
\emph{Psychological Assessment}, \emph{29}(7), 890--901.
doi:\href{https://doi.org/10.1037/pas0000383}{10.1037/pas0000383}

\hypertarget{ref-Morita2012}{}
Morita, T., Slaughter, V., Katayama, N., Kitazaki, M., Kakigi, R., \&
Itakura, S. (2012). Infant and adult perceptions of possible and
impossible body movements: An eye-tracking study. \emph{Journal of
Experimental Child Psychology}, \emph{113}(3), 401--414.
doi:\href{https://doi.org/10.1016/j.jecp.2012.07.003}{10.1016/j.jecp.2012.07.003}

\hypertarget{ref-Mosewich2011}{}
Mosewich, A. D., Kowalski, K. C., Sabiston, C. M., Sedgwick, W. a, \&
Tracy, J. L. (2011). Self-compassion: A potential resource for young
women athletes. \emph{Journal of Sport and Exercise Psychology},
\emph{33}(1), 103--123.
doi:\href{https://doi.org/10.1123/jsep.33.1.103}{10.1123/jsep.33.1.103}

\hypertarget{ref-Mossman2012}{}
Mossman, D., Wygant, D. B., \& Gervais, R. O. (2012). Estimating the
accuracy of neurocognitive effort measures in the absence of a ``gold
standard''. \emph{Psychological Assessment}, \emph{24}(4), 815--822.
doi:\href{https://doi.org/10.1037/a0028195}{10.1037/a0028195}

\hypertarget{ref-Motyl2017}{}
Motyl, M., Demos, A. P., Carsel, T. S., Hanson, B. E., Melton, Z. J.,
Mueller, A. B., \ldots{} Skitka, L. J. (2017). The state of social and
personality science: Rotten to the core, not so bad, getting better, or
getting worse? \emph{Journal of Personality and Social Psychology},
\emph{113}(1), 34--58.
doi:\href{https://doi.org/10.1037/pspa0000084}{10.1037/pspa0000084}

\hypertarget{ref-Mourshed2012}{}
Mourshed, M., \& Zhao, Y. (2012). Healthcare providers' perception of
design factors related to physical environments in hospitals.
\emph{Journal of Environmental Psychology}, \emph{32}(4), 362--370.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.06.004}{10.1016/j.jenvp.2012.06.004}

\hypertarget{ref-Mowle2016}{}
Mowle, E. N., Kelley, S. E., Edens, J. F., Donnellan, M. B., Smith, S.
T., Wygant, D. B., \& Sellbom, M. (2016). Development of an Inconsistent
Responding Scale for the Triarchic Psychopathy Measure.
\emph{Psychological Assessment}, \emph{29}(8), 990--1000.
doi:\href{https://doi.org/10.1037/pas0000395}{10.1037/pas0000395}

\hypertarget{ref-Muehlenkamp2017}{}
Muehlenkamp, J. J., Brausch, A. M., \& Washburn, J. J. (2017). How much
is enough? Examining frequency criteria for NSSI disorder in adolescent
inpatients. \emph{Journal of Consulting and Clinical Psychology},
\emph{85}(6), 611--619.
doi:\href{https://doi.org/10.1037/ccp0000209}{10.1037/ccp0000209}

\hypertarget{ref-Muenks2017}{}
Muenks, K., Wigfield, A., Yang, J. S., \& O'Neal, C. R. (2017). How true
is grit? Assessing its relations to high school and college students'
personality characteristics, self-regulation, engagement, and
achievement. \emph{Journal of Educational Psychology}, \emph{109}(5),
599--620.
doi:\href{https://doi.org/10.1037/edu0000153}{10.1037/edu0000153}

\hypertarget{ref-Mundt2017}{}
Mundt, M. P., Antonaccio, O. P., French, M. T., \& Zakletskaia, L. I.
(2017). The role of adolescent friendship group integration and cohesion
in weapon-related violent crime as a young adult. \emph{Journal of Youth
and Adolescence}, \emph{46}(8), 1643--1660.
doi:\href{https://doi.org/10.1007/s10964-017-0631-6}{10.1007/s10964-017-0631-6}

\hypertarget{ref-Murphy2017}{}
Murphy, P. K., Greene, J. A., Firetto, C. M., Li, M., Lobczowski, N. G.,
Duke, R. F., \ldots{} Croninger, R. M. (2017). Exploring the influence
of homogeneous versus heterogeneous grouping on students' text-based
discussions and comprehension. \emph{Contemporary Educational
Psychology}, \emph{51}, 336--355.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.09.003}{10.1016/j.cedpsych.2017.09.003}

\hypertarget{ref-Murphy2012}{}
Murphy, S., Velzen, J. van, \& Fockert, J. W. de. (2012). The role of
perceptual load in action affordance by ignored objects.
\emph{Psychonomic Bulletin \& Review}, \emph{19}(6), 1122--1127.
doi:\href{https://doi.org/10.3758/s13423-012-0299-6}{10.3758/s13423-012-0299-6}

\hypertarget{ref-Murtagh2012}{}
Murtagh, N., Gatersleben, B., \& Uzzell, D. (2012). Self-identity threat
and resistance to change: Evidence from regular travel behaviour.
\emph{Journal of Environmental Psychology}, \emph{32}(4), 318--326.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.05.008}{10.1016/j.jenvp.2012.05.008}

\hypertarget{ref-Musto2016}{}
Musto, M., \& McGann, P. (2016). Strike a Pose! The Femininity Effect in
Collegiate Women's Sport. \emph{Sociology of Sport Journal},
\emph{33}(2), 101--112.
doi:\href{https://doi.org/10.1123/ssj.2015-0034}{10.1123/ssj.2015-0034}

\hypertarget{ref-Muthen2012}{}
Muthén, B., \& Asparouhov, T. (2012). Bayesian structural equation
modeling: A more flexible representation of substantive theory.
\emph{Psychological Methods}, \emph{17}(3), 313--335.
doi:\href{https://doi.org/10.1037/a0026802}{10.1037/a0026802}

\hypertarget{ref-Nadal2011}{}
Nadal, K. L. (2011). The Racial and Ethnic Microaggressions Scale
(REMS): Construction, reliability, and validity. \emph{Journal of
Counseling Psychology}, \emph{58}(4), 470--480.
doi:\href{https://doi.org/10.1037/a0025193}{10.1037/a0025193}

\hypertarget{ref-Nahari2017}{}
Nahari, G. (2017). Top-down processes in interpersonal reality
monitoring assessments. \emph{Psychology, Public Policy, and Law},
\emph{23}(2), 232--242.
doi:\href{https://doi.org/10.1037/law0000110}{10.1037/law0000110}

\hypertarget{ref-Nahum-Shani2012a}{}
Nahum-Shani, I., Qian, M., Almirall, D., Pelham, W. E., Gnagy, B.,
Fabiano, G. A., \ldots{} Murphy, S. A. (2012a). Experimental design and
primary data analysis methods for comparing adaptive interventions.
\emph{Psychological Methods}, \emph{17}(4), 457--477.
doi:\href{https://doi.org/10.1037/a0029372}{10.1037/a0029372}

\hypertarget{ref-Nahum-Shani2012}{}
Nahum-Shani, I., Qian, M., Almirall, D., Pelham, W. E., Gnagy, B.,
Fabiano, G. A., \ldots{} Murphy, S. A. (2012b). Q-learning: A data
analysis method for constructing adaptive interventions.
\emph{Psychological Methods}, \emph{17}(4), 478--494.
doi:\href{https://doi.org/10.1037/a0029373}{10.1037/a0029373}

\hypertarget{ref-Nakamura2016}{}
Nakamura, Y. (2016). Rethinking identity politics: The multiple
attachments of an 'exclusive' sport organization. \emph{Sociology of
Sport Journal}, \emph{33}(2), 146--155.
doi:\href{https://doi.org/10.1123/ssj.2015-0062}{10.1123/ssj.2015-0062}

\hypertarget{ref-Naragon-Gainey2017}{}
Naragon-Gainey, K., \& DeMarree, K. G. (2017). Structure and validity of
measures of decentering and defusion. \emph{Psychological Assessment},
\emph{29}(7), 935--954.
doi:\href{https://doi.org/10.1037/pas0000405}{10.1037/pas0000405}

\hypertarget{ref-Naragon-Gainey2012}{}
Naragon-Gainey, K., Simpson, T. L., Moore, S. A., Varra, A. A., \&
Kaysen, D. L. (2012). The correspondence of daily and retrospective PTSD
reports among female victims of sexual assault. \emph{Psychological
Assessment}, \emph{24}(4), 1041--1047.
doi:\href{https://doi.org/10.1037/a0028518}{10.1037/a0028518}

\hypertarget{ref-Neal2017}{}
Neal, J. W., Durbin, C. E., Gornik, A. E., \& Lo, S. L. (2017).
Codevelopment of preschoolers' temperament traits and social play
networks over an entire school year. \emph{Journal of Personality and
Social Psychology}, \emph{113}(4), 627--640.
doi:\href{https://doi.org/10.1037/pspp0000135}{10.1037/pspp0000135}

\hypertarget{ref-Needham2017}{}
Needham, A. W., Wiesen, S. E., Hejazi, J. N., Libertus, K., \&
Christopher, C. (2017). Characteristics of brief sticky mittens training
that lead to increases in object exploration. \emph{Journal of
Experimental Child Psychology}, \emph{164}, 209--224.
doi:\href{https://doi.org/10.1016/j.jecp.2017.04.009}{10.1016/j.jecp.2017.04.009}

\hypertarget{ref-Nel2012}{}
Nel, P. W., Pezzolesi, C., \& Stott, D. J. (2012). How did we learn
best? A retrospective survey of clinical psychology training in the
United Kingdom. \emph{Journal of Clinical Psychology}, \emph{68}(9),
1058--1073.
doi:\href{https://doi.org/10.1002/jclp.21882}{10.1002/jclp.21882}

\hypertarget{ref-Nestler}{}
Nestler, S., Egloff, B., Küfner, A. C. P., \& Back, M. D. (2012). An
integrative lens model approach to bias and accuracy in human
inferences: Hindsight effects and knowledge updating in personality
judgments. \emph{Journal of Personality and Social Psychology},
\emph{103}(4), 689--717.
doi:\href{https://doi.org/10.1037/a0029461}{10.1037/a0029461}

\hypertarget{ref-Neuenschwander2012}{}
Neuenschwander, R., Röthlisberger, M., Cimeli, P., \& Roebers, C. M.
(2012). How do different aspects of self-regulation predict successful
adaptation to school? \emph{Journal of Experimental Child Psychology},
\emph{113}(3), 353--371.
doi:\href{https://doi.org/10.1016/j.jecp.2012.07.004}{10.1016/j.jecp.2012.07.004}

\hypertarget{ref-Newark2017}{}
Newark, D. A., Bohns, V. K., \& Flynn, F. J. (2017). A helping hand is
hard at work: Help-seekers? Underestimation of helpers' effort.
\emph{Organizational Behavior and Human Decision Processes}, \emph{139},
18--29.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.01.001}{10.1016/j.obhdp.2017.01.001}

\hypertarget{ref-Ng2016}{}
Ng, T. W. (2016). Embedding employees early on: The importance of
workplace respect. \emph{Personnel Psychology}, \emph{69}(3), 599--633.
doi:\href{https://doi.org/10.1111/peps.12117}{10.1111/peps.12117}

\hypertarget{ref-Ng2017}{}
Ng, V., Cao, M., Marsh, H. W., Tay, L., \& Seligman, M. E. P. (2016).
The Factor Structure of the Values in Action Inventory of Strengths
(VIA-IS): An Item-Level Exploratory Structural Equation Modeling (ESEM)
Bifactor Analysis. \emph{Psychological Assessment}, \emph{29}(8),
1053--1058.
doi:\href{https://doi.org/10.1037/pas0000396}{10.1037/pas0000396}

\hypertarget{ref-Nicholls2012}{}
Nicholls, M. E. R., Johnston, D. W., \& Shields, M. A. (2012). Adverse
birth factors predict cognitive ability, but not hand preference.
\emph{Neuropsychology}, \emph{26}(5), 578--587.
doi:\href{https://doi.org/10.1037/a0029151}{10.1037/a0029151}

\hypertarget{ref-Nichols2012}{}
Nichols, E. B., \& Loper, A. B. (2012). Incarceration in the household:
Academic outcomes of adolescents with an incarcerated household member.
\emph{Journal of Youth and Adolescence}, \emph{41}(11), 1455--1471.
doi:\href{https://doi.org/10.1007/s10964-012-9780-9}{10.1007/s10964-012-9780-9}

\hypertarget{ref-Nicolai2017}{}
Nicolai, S., Zerach, G., \& Solomon, Z. (2017). The roles of fathers'
posttraumatic stress symptoms and adult offspring's differentiation of
the self in the intergenerational transmission of captivity trauma.
\emph{Journal of Clinical Psychology}, \emph{73}(7), 848--863.
doi:\href{https://doi.org/10.1002/jclp.22377}{10.1002/jclp.22377}

\hypertarget{ref-Nieri2016}{}
Nieri, T., \& Hughes, E. (2016). All about having fun: Women's
experience of zumba fitness. \emph{Sociology of Sport Journal},
\emph{33}(2), 135--145.
doi:\href{https://doi.org/10.1123/ssj.2015-0071}{10.1123/ssj.2015-0071}

\hypertarget{ref-Nieuwenhuis2017}{}
Nieuwenhuis, J., Ham, M. van, Yu, R., Branje, S., Meeus, W., \&
Hooimeijer, P. (2017). Being poorer than the rest of the neighborhood:
Relative deprivation and problem behavior of youth. \emph{Journal of
Youth and Adolescence}, \emph{46}(9), 1891--1904.
doi:\href{https://doi.org/10.1007/s10964-017-0668-6}{10.1007/s10964-017-0668-6}

\hypertarget{ref-Nijdam-Jones2017}{}
Nijdam-Jones, A., Rivera, D., Rosenfeld, B., \& Arango-Lasprilla, J. C.
(2017). A cross-cultural analysis of the Test of Memory Malingering
among Latin American Spanish-speaking adults. \emph{Law and Human
Behavior}, \emph{41}(5), 422--428.
doi:\href{https://doi.org/10.1037/lhb0000250}{10.1037/lhb0000250}

\hypertarget{ref-Nilsson2017}{}
Nilsson, J., Lebedev, A. V., Rydström, A., \& Lövdén, M. (2017).
Direct-Current stimulation does little to improve the outcome of working
memory training in older adults. \emph{Psychological Science},
\emph{28}(7), 907--920.
doi:\href{https://doi.org/10.1177/0956797617698139}{10.1177/0956797617698139}

\hypertarget{ref-Nishimoto2012}{}
Nishimoto, T., Ueda, T., Miyawaki, K., Une, Y., \& Takahashi, M. (2012).
The role of imagery-related properties in picture naming: A newly
standardized set of 360 pictures for Japanese. \emph{Behavior Research
Methods}, \emph{44}(4), 934--945.
doi:\href{https://doi.org/10.3758/s13428-011-0176-7}{10.3758/s13428-011-0176-7}

\hypertarget{ref-Nixon2010}{}
Nixon, H. L. (2010). Sport sociology, NASSS, and undergraduate education
in the united states: A social network perspective for developing the
field. \emph{Sociology of Sport Journal}, \emph{27}(1), 76--88.
doi:\href{https://doi.org/10.1123/ssj.27.1.76}{10.1123/ssj.27.1.76}

\hypertarget{ref-Nordfjuxe6rn2017}{}
Nordfjærn, T., \& Zavareh, M. F. (2017). Does the value-belief-norm
theory predict acceptance of disincentives to driving and active mode
choice preferences for children's school travels among Chinese parents?
\emph{Journal of Environmental Psychology}, \emph{53}, 31--39.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.06.005}{10.1016/j.jenvp.2017.06.005}

\hypertarget{ref-Nysse-Carris2011}{}
Nysse-Carris, K. L., Bottoms, B. L., \& Salerno, J. M. (2011). Experts'
and novices' abilities to detect children's high-stakes lies of
omission. \emph{Psychology, Public Policy, and Law}, \emph{17}(1),
76--98. doi:\href{https://doi.org/10.1037/a0022136}{10.1037/a0022136}

\hypertarget{ref-Nystrom2017}{}
Nyström, M., Niehorster, D. C., Cornelissen, T., \& Garde, H. (2017).
Real-time sharing of gaze data between multiple eye
trackers--evaluation, tools, and advice. \emph{Behavior Research
Methods}, \emph{49}(4), 1310--1322.
doi:\href{https://doi.org/10.3758/s13428-016-0806-1}{10.3758/s13428-016-0806-1}

\hypertarget{ref-Oberski2015}{}
Oberski, D. L., Hagenaars, J. A. P., \& Saris, W. E. (2015). The latent
class multitrait-multimethod model. \emph{Psychological Methods},
\emph{20}(4), 422--443.
doi:\href{https://doi.org/10.1037/a0039783}{10.1037/a0039783}

\hypertarget{ref-Obsuth2017}{}
Obsuth, I., Murray, A. L., Malti, T., Sulger, P., Ribeaud, D., \&
Eisner, M. (2017). A non-bipartite propensity score analysis of the
effects of teacher--student relationships on adolescent problem and
prosocial behavior. \emph{Journal of Youth and Adolescence},
\emph{46}(8), 1661--1687.
doi:\href{https://doi.org/10.1007/s10964-016-0534-y}{10.1007/s10964-016-0534-y}

\hypertarget{ref-Oishi2012}{}
Oishi, S., \& Kesebir, S. (2012). Optimal social-networking strategy is
a function of socioeconomic conditions. \emph{Psychological Science},
\emph{23}(12), 1542--1548.
doi:\href{https://doi.org/10.1177/0956797612446708}{10.1177/0956797612446708}

\hypertarget{ref-Ojala2012}{}
Ojala, M. (2012). How do children cope with global climate change?
Coping strategies, engagement, and well-being. \emph{Journal of
Environmental Psychology}, \emph{32}(3), 225--233.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.02.004}{10.1016/j.jenvp.2012.02.004}

\hypertarget{ref-Ojalehto2017}{}
Ojalehto, bethany l., Medin, D. L., \& García, S. G. (2017). Grounding
principles for inferring agency: Two cultural perspectives.
\emph{Cognitive Psychology}, \emph{95}, 50--78.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.04.001}{10.1016/j.cogpsych.2017.04.001}

\hypertarget{ref-Okun2017}{}
Okun, L., Chang, D. F., Kanhai, G., Dunn, J., \& Easley, H. (2017).
Inverting the power dynamic: The process of first sessions of
psychotherapy with therapists of color and non-Latino white patients.
\emph{Journal of Counseling Psychology}, \emph{64}(4), 443--452.
doi:\href{https://doi.org/10.1037/cou0000223}{10.1037/cou0000223}

\hypertarget{ref-Olver2012}{}
Olver, M. E., Stockdale, K. C., \& Wong, S. C. P. (2012). Short and
long-term prediction of recidivism using the youth level of service/case
management inventory in a sample of serious young offenders. \emph{Law
and Human Behavior}, \emph{36}(4), 331--344.
doi:\href{https://doi.org/10.1037/h0093927}{10.1037/h0093927}

\hypertarget{ref-Oreg2011}{}
Oreg, S., \& Berson, Y. (2011). Leadership and employees' reactions to
change: The role of leaders' personal attributes and transformational
leadership style. \emph{Personnel Psychology}, \emph{64}(3), 627--659.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01221.x}{10.1111/j.1744-6570.2011.01221.x}

\hypertarget{ref-Ort2017}{}
Ort, E., Fahrenfort, J. J., \& Olivers, C. N. L. (2017). Lack of free
choice reveals the cost of having to search for more than one object.
\emph{Psychological Science}, \emph{28}(8), 1137--1147.
doi:\href{https://doi.org/10.1177/0956797617705667}{10.1177/0956797617705667}

\hypertarget{ref-Oshio2012}{}
Oshio, T., \& Urakawa, K. (2012). Neighbourhood satisfaction, self-rated
health, and psychological attributes: A multilevel analysis in Japan.
\emph{Journal of Environmental Psychology}, \emph{32}(4), 410--417.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.07.003}{10.1016/j.jenvp.2012.07.003}

\hypertarget{ref-Osman2012}{}
Osman, A., Wong, J. L., Bagge, C. L., Freedenthal, S., Gutierrez, P. M.,
\& Lozano, G. (2012). The Depression Anxiety Stress Scales-21 (DASS-21):
Further examination of dimensions, scale reliability, and correlates.
\emph{Journal of Clinical Psychology}, \emph{68}(12), 1322--1338.
doi:\href{https://doi.org/10.1002/jclp.21908}{10.1002/jclp.21908}

\hypertarget{ref-Ostarek2017}{}
Ostarek, M., \& Huettig, F. (2017). A task-dependent causal role for
low-level visual processes in spoken word comprehension. \emph{Journal
of Experimental Psychology: Learning, Memory, and Cognition},
\emph{43}(8), 1215--1224.
doi:\href{https://doi.org/10.1037/xlm0000375}{10.1037/xlm0000375}

\hypertarget{ref-Owen2010}{}
Owen, J., Tao, K., \& Rodolfa, E. (2010). Microaggressions and women in
short-term psychotherapy: Initial evidence. \emph{The Counseling
Psychologist}, \emph{38}(7), 923--946.
doi:\href{https://doi.org/10.1177/0011000010376093}{10.1177/0011000010376093}

\hypertarget{ref-Owens2017a}{}
Owens, E. B., Zalecki, C., Gillette, P., \& Hinshaw, S. P. (2017). Girls
with childhood ADHD as adults: Cross-domain outcomes by diagnostic
persistence. \emph{Journal of Consulting and Clinical Psychology},
\emph{85}(7), 723--736.
doi:\href{https://doi.org/10.1037/ccp0000217}{10.1037/ccp0000217}

\hypertarget{ref-Ozechowski2007}{}
Ozechowski, T. J., Turner, C. W., \& Hops, H. (2007). Mixed-effects
logistic regression for estimating transitional probabilities in
sequentially coded observational data. \emph{Psychological Methods},
\emph{12}(3), 317--335.
doi:\href{https://doi.org/10.1037/1082-989X.12.3.317}{10.1037/1082-989X.12.3.317}

\hypertarget{ref-OBoyle2012}{}
O'Boyle, E., \& Aguinis, H. (2012). The best and the rest: Revisiting
the norm of normality of individual performance. \emph{Personnel
Psychology}, \emph{65}(1), 79--119.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01239.x}{10.1111/j.1744-6570.2011.01239.x}

\hypertarget{ref-OBrien2012}{}
O'Brien, L. T., Major, B., \& Simon, S. (2012). Why did you choose that
person over me? Ingroup rejection and attributions to discrimination.
\emph{Journal of Experimental Social Psychology}, \emph{48}(6),
1225--1233.
doi:\href{https://doi.org/10.1016/j.jesp.2012.04.007}{10.1016/j.jesp.2012.04.007}

\hypertarget{ref-Pachur2012}{}
Pachur, T., \& Olsson, H. (2012). Type of learning task impacts
performance and strategy selection in decision making. \emph{Cognitive
Psychology}, \emph{65}(2), 207--240.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.03.003}{10.1016/j.cogpsych.2012.03.003}

\hypertarget{ref-Pachur2017}{}
Pachur, T., Suter, R. S., \& Hertwig, R. (2017). How the twain can meet:
Prospect theory and models of heuristics in risky choice.
\emph{Cognitive Psychology}, \emph{93}, 44--73.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.01.001}{10.1016/j.cogpsych.2017.01.001}

\hypertarget{ref-Palmer2012}{}
Palmer, M. a., Brewer, N., \& Weber, N. (2012). The information gained
from witnesses' responses to an initial ``blank'' lineup. \emph{Law and
Human Behavior}, \emph{36}(5), 439--447.
doi:\href{https://doi.org/10.1037/h0093939}{10.1037/h0093939}

\hypertarget{ref-Paluck2012}{}
Paluck, E. L., \& Shepherd, H. (2012). The salience of social referents:
A field experiment on collective norms and harassment behavior in a
school social network. \emph{Journal of Personality and Social
Psychology}, \emph{103}(6), 899--915.
doi:\href{https://doi.org/10.1037/a0030015}{10.1037/a0030015}

\hypertarget{ref-Pansky2012}{}
Pansky, A. (2012). Inoculation against forgetting: Advantages of
immediate versus delayed initial testing due to superior verbatim
accessibility. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{38}(6), 1792--1800.
doi:\href{https://doi.org/10.1037/a0028460}{10.1037/a0028460}

\hypertarget{ref-Papadopoulos2012}{}
Papadopoulos, T. C., Kendeou, P., \& Spanoudis, G. (2012). Investigating
the factor structure and measurement invariance of phonological
abilities in a sufficiently transparent language. \emph{Journal of
Educational Psychology}, \emph{104}(2), 321--336.
doi:\href{https://doi.org/10.1037/a0026446}{10.1037/a0026446}

\hypertarget{ref-Papesh2012}{}
Papesh, M. H., \& Goldinger, S. D. (2012). Memory in motion: Movement
dynamics reveal memory strength. \emph{Psychonomic Bulletin \& Review},
\emph{19}(5), 906--913.
doi:\href{https://doi.org/10.3758/s13423-012-0281-3}{10.3758/s13423-012-0281-3}

\hypertarget{ref-Park2012}{}
Park, G., Moon, E., Kim, D.-W., \& Lee, S.-H. (2012). Individual
differences in cardiac vagal tone are associated with differential
neural responses to facial expressions at different spatial frequencies:
An ERP and sLORETA study. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{12}(4), 777--793.
doi:\href{https://doi.org/10.3758/s13415-012-0111-0}{10.3758/s13415-012-0111-0}

\hypertarget{ref-Park2012a}{}
Park, I. J., \& Kim, P. Y. (2012). The role of self-construals in the
link between anger regulation and externalizing problems in Korean
American adolescents: Testing a moderated mediation model. \emph{Journal
of Clinical Psychology}, \emph{68}(12), 1339--1359.
doi:\href{https://doi.org/10.1002/jclp.21878}{10.1002/jclp.21878}

\hypertarget{ref-Park2017}{}
Park, T. Y., Kim, S., \& Sung, L. K. (2017). Fair pay dispersion: A
regulatory focus theory view. \emph{Organizational Behavior and Human
Decision Processes}, \emph{142}, 1--11.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.07.003}{10.1016/j.obhdp.2017.07.003}

\hypertarget{ref-Park2017a}{}
Park, Y., \& Casasola, M. (2017). The impact of object type on the
spatial analogies in Korean preschoolers. \emph{Cognitive Psychology},
\emph{94}, 53--66.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.02.001}{10.1016/j.cogpsych.2017.02.001}

\hypertarget{ref-Parker2018}{}
Parker, L., Monteith, M., Moss-Racusin, C., \& Van Camp, A. (2018).
Promoting concern about gender bias with evidence-based confrontation.
\emph{Journal of Experimental Social Psychology}, \emph{74}, 8--23.
doi:\href{https://doi.org/10.1016/j.jesp.2017.07.009}{10.1016/j.jesp.2017.07.009}

\hypertarget{ref-Parong2017}{}
Parong, J., Mayer, R. E., Fiorella, L., MacNamara, A., Homer, B. D., \&
Plass, J. L. (2017). Learning executive function skills by playing
focused video games. \emph{Contemporary Educational Psychology},
\emph{51}, 141--151.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.07.002}{10.1016/j.cedpsych.2017.07.002}

\hypertarget{ref-Parry2012}{}
Parry, D., Chinnasamy, C., \& Micklewright, D. (2012). Optic flow
influences perceived exertion during cycling. \emph{Journal of Sport and
Exercise Psychology}, \emph{34}(4), 444--456.
doi:\href{https://doi.org/10.1123/jsep.34.4.444}{10.1123/jsep.34.4.444}

\hypertarget{ref-Parsons2012}{}
Parsons, N. L., \& Stern, M. J. (2012). There's no dying in baseball:
Cultural valorization, collective memory, and induction into the
baseball hall of fame. \emph{Sociology of Sport Journal}, \emph{29}(1),
62--88.
doi:\href{https://doi.org/10.1123/ssj.29.1.62}{10.1123/ssj.29.1.62}

\hypertarget{ref-Parthasarathy2017}{}
Parthasarathy, V., Frazier, D. T., Bettcher, B. M., Jastrzab, L., Chao,
L., Reed, B., \ldots{} Kramer, J. H. (2017). Triglycerides are
negatively correlated with cognitive function in nondemented aging
adults. \emph{Neuropsychology}, \emph{31}(6), 682--688.
doi:\href{https://doi.org/10.1037/neu0000335}{10.1037/neu0000335}

\hypertarget{ref-Parvaz2012}{}
Parvaz, M. A., MacNamara, A., Goldstein, R. Z., \& Hajcak, G. (2012).
Event-related induced frontal alpha as a marker of lateral prefrontal
cortex activation during cognitive reappraisal. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, \emph{12}(4), 730--740.
doi:\href{https://doi.org/10.3758/s13415-012-0107-9}{10.3758/s13415-012-0107-9}

\hypertarget{ref-Paulick2017}{}
Paulick, I., Großschedl, J., Harms, U., \& Möller, J. (2017). How
teachers perceive their expertise: The role of dimensional and social
comparisons. \emph{Contemporary Educational Psychology}, \emph{51},
114--122.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.06.007}{10.1016/j.cedpsych.2017.06.007}

\hypertarget{ref-Paundra2017}{}
Paundra, J., Rook, L., Dalen, J. van, \& Ketter, W. (2017). Preferences
for car sharing services: Effects of instrumental attributes and
psychological ownership. \emph{Journal of Environmental Psychology},
\emph{53}, 121--130.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.07.003}{10.1016/j.jenvp.2017.07.003}

\hypertarget{ref-DelaPena2012}{}
Peña, C. M. de la, Friedlander, M. L., Escudero, V., \& Heatherington,
L. (2012). How do therapists ally with adolescents in family therapy? An
examination of relational control communication in early sessions.
\emph{Journal of Counseling Psychology}, \emph{59}(3), 339--351.
doi:\href{https://doi.org/10.1037/a0028063}{10.1037/a0028063}

\hypertarget{ref-Perea2012}{}
Perea, M., Gatt, A., Moret-Tatay, C., \& Fabri, R. (2012). Are all
Semitic languages immune to letter transpositions? The case of Maltese.
\emph{Psychonomic Bulletin \& Review}, \emph{19}(5), 942--947.
doi:\href{https://doi.org/10.3758/s13423-012-0273-3}{10.3758/s13423-012-0273-3}

\hypertarget{ref-Perez-Lopez2017}{}
Perez-Lopez, R., Aragonés, J. I., \& Amérigo, M. (2017). Primary spaces
and their cues as facilitators of personal and social inferences.
\emph{Journal of Environmental Psychology}, \emph{53}, 157--167.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.07.008}{10.1016/j.jenvp.2017.07.008}

\hypertarget{ref-Perfect2012}{}
Perfect, T. J., \& Weber, N. (2012). How should witnesses regulate the
accuracy of their identification decisions: One step forward, two steps
back? \emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{38}(6), 1810--1818.
doi:\href{https://doi.org/10.1037/a0028461}{10.1037/a0028461}

\hypertarget{ref-Perrault2017}{}
Perrault, R. T., Vincent, G. M., \& Guy, L. S. (2017). Are risk
assessments racially biased?: Field study of the SAVRY and YLS / CMI in
probation. \emph{Psychological Assessment}, \emph{29}(6), 664--678.
doi:\href{https://doi.org/10.1037/pas0000445}{10.1037/pas0000445}

\hypertarget{ref-Perri2012}{}
Perri, R., Zannino, G., Caltagirone, C., \& Carlesimo, G. A. (2012).
Alzheimer's disease and semantic deficits: A feature-listing study.
\emph{Neuropsychology}, \emph{26}(5), 652--663.
doi:\href{https://doi.org/10.1037/a0029302}{10.1037/a0029302}

\hypertarget{ref-Perry2012}{}
Perry, J. C., \& Calhoun-Butts, C. (2012). A qualitative study of urban
Hispanic youth in an after-school program. \emph{The Counseling
Psychologist}, \emph{40}(4), 477--519.
doi:\href{https://doi.org/10.1177/0011000011414733}{10.1177/0011000011414733}

\hypertarget{ref-Peters2013}{}
Peters, C. S., Lampinen, J. M., \& Malesky, L. A. (2013). A trap for the
unwary: Jury decision making in cases involving the entrapment defense.
\emph{Law and Human Behavior}, \emph{37}(1), 45--53.
doi:\href{https://doi.org/10.1037/lhb0000007}{10.1037/lhb0000007}

\hypertarget{ref-Peterson2012}{}
Peterson, D. J., \& Mulligan, N. W. (2012). A negative effect of
repetition in episodic memory. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{38}(6), 1786--1791.
doi:\href{https://doi.org/10.1037/a0028220}{10.1037/a0028220}

\hypertarget{ref-Peterson2017}{}
Peterson, D. J., \& Naveh-benjamin, M. (2017). The role of attention in
item-item binding in visual working memory. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{43}(9),
1403--1414.
doi:\href{https://doi.org/10.1037/xlm0000386}{10.1037/xlm0000386}

\hypertarget{ref-Peterson2012a}{}
Peterson, S. J., Galvin, B. M., \& Lange, D. (2012). Ceo servant
leadership: Exploring executive characteristics and firm performance.
\emph{Personnel Psychology}, \emph{65}(3), 565--596.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01253.x}{10.1111/j.1744-6570.2012.01253.x}

\hypertarget{ref-Pezdek2012}{}
Pezdek, K., O'Brien, M., \& Wasson, C. (2012). Cross-race (but not
same-race) face identification is impaired by presenting faces in a
group rather than individually. \emph{Law and Human Behavior},
\emph{36}(6), 488--495.
doi:\href{https://doi.org/10.1037/h0093933}{10.1037/h0093933}

\hypertarget{ref-Piasta2012}{}
Piasta, S. B., Petscher, Y., \& Justice, L. M. (2012). How many letters
should preschoolers in public programs know? The diagnostic efficiency
of various preschool letter-naming benchmarks for predicting first-grade
literacy achievement. \emph{Journal of Educational Psychology},
\emph{104}(4), 945--958.
doi:\href{https://doi.org/10.1037/a0027757}{10.1037/a0027757}

\hypertarget{ref-Pickel2013}{}
Pickel, K. L., Warner, T. C., Miller, T. J., \& Barnes, Z. T. (2013).
Conceptualizing defendants as minorities leads mock jurors to make
biased evaluations in retracted confession cases. \emph{Psychology,
Public Policy, and Law}, \emph{19}(1), 56--69.
doi:\href{https://doi.org/10.1037/a0029308}{10.1037/a0029308}

\hypertarget{ref-Pierce2017}{}
Pierce, B. H., Gallo, D. A., \& McCain, J. L. (2017). Reduced
interference from memory testing: a postretrieval monitoring account.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(7), 1063--1072.
doi:\href{https://doi.org/10.1037/xlm0000377}{10.1037/xlm0000377}

\hypertarget{ref-Piff2012}{}
Piff, P. K., Stancato, D. M., Martinez, A. G., Kraus, M. W., \& Keltner,
D. (2012). Class, chaos, and the construction of community.
\emph{Journal of Personality and Social Psychology}, \emph{103}(6),
949--962. doi:\href{https://doi.org/10.1037/a0029673}{10.1037/a0029673}

\hypertarget{ref-Piquero2012}{}
Piquero, A. R., Farrington, D. P., Fontaine, N. M. G., Vincent, G.,
Coid, J., \& Ullrich, S. (2012). Childhood risk, offending trajectories,
and psychopathy at age 48 years in the Cambridge Study in Delinquent
Development. \emph{Psychology, Public Policy, and Law}, \emph{18}(4),
577--598. doi:\href{https://doi.org/10.1037/a0027061}{10.1037/a0027061}

\hypertarget{ref-Pisani2012}{}
Pisani, A. R., Schmeelk-Cone, K., Gunzler, D., Petrova, M., Goldston, D.
B., Tu, X., \& Wyman, P. A. (2012). Associations between suicidal high
school students' help-seeking and their attitudes and perceptions of
social environment. \emph{Journal of Youth and Adolescence},
\emph{41}(10), 1312--1324.
doi:\href{https://doi.org/10.1007/s10964-012-9766-7}{10.1007/s10964-012-9766-7}

\hypertarget{ref-Pistorello2012}{}
Pistorello, J., Fruzzetti, A. E., MacLane, C., Gallop, R., \& Iverson,
K. M. (2012). Dialectical behavior therapy (DBT) applied to college
students: A randomized clinical trial. \emph{Journal of Consulting and
Clinical Psychology}, \emph{80}(6), 982--994.
doi:\href{https://doi.org/10.1037/a0029096}{10.1037/a0029096}

\hypertarget{ref-Plessow2012}{}
Plessow, F., Schade, S., Kirschbaum, C., \& Fischer, R. (2012). Better
not to deal with two tasks at the same time when stressed? Acute
psychosocial stress reduces task shielding in dual-task performance.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{12}(3),
557--570.
doi:\href{https://doi.org/10.3758/s13415-012-0098-6}{10.3758/s13415-012-0098-6}

\hypertarget{ref-Plonsky2017}{}
Plonsky, O., \& Erev, I. (2017). Learning in settings with partial
feedback and the wavy recency effect of rare events. \emph{Cognitive
Psychology}, \emph{93}, 18--43.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.01.002}{10.1016/j.cogpsych.2017.01.002}

\hypertarget{ref-Pluta2017}{}
Pluta, A., Gawron, N., Sobańska, M., Wójcik, A. D., \& Łojek, E. (2017).
The nature of the relationship between neurocognition and theory of mind
impairments in stroke patients. \emph{Neuropsychology}, \emph{31}(6),
666--681.
doi:\href{https://doi.org/10.1037/neu0000379}{10.1037/neu0000379}

\hypertarget{ref-Poarch2012}{}
Poarch, G. J., \& Hell, J. G. van. (2012). Executive functions and
inhibitory control in multilingual children: Evidence from
second-language learners, bilinguals, and trilinguals. \emph{Journal of
Experimental Child Psychology}, \emph{113}(4), 535--551.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.013}{10.1016/j.jecp.2012.06.013}

\hypertarget{ref-Pohl2012}{}
Pohl, R. F., \& Hilbig, B. E. (2012). The role of subjective linear
orders in probabilistic inferences. \emph{Psychonomic Bulletin \&
Review}, \emph{19}(6), 1178--1186.
doi:\href{https://doi.org/10.3758/s13423-012-0289-8}{10.3758/s13423-012-0289-8}

\hypertarget{ref-Pohler2016}{}
Pohler, D., \& Schmidt, J. A. (2016). Does pay-for-performance strain
the employment relationship? The effect of manager bonus eligibility on
nonmanagement employee turnover. \emph{Personnel Psychology},
\emph{69}(2), 395--429.
doi:\href{https://doi.org/10.1111/peps.12106}{10.1111/peps.12106}

\hypertarget{ref-VandePolP2012}{}
Pol, P. K. van de, Kavussanu, M., \& Ring, C. (2012). The effects of
training and competition on achievement goals, motivational responses,
and performance in a golf-putting task. \emph{Journal of Sport and
Exercise Psychology}, \emph{34}(6), 787--807.
doi:\href{https://doi.org/10.1123/jsep.34.6.787}{10.1123/jsep.34.6.787}

\hypertarget{ref-Polman2012}{}
Polman, E. (2012). Self-other decision making and loss aversion.
\emph{Organizational Behavior and Human Decision Processes},
\emph{119}(2), 141--150.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.06.005}{10.1016/j.obhdp.2012.06.005}

\hypertarget{ref-Polman2012a}{}
Polman, E., \& Russo, J. E. (2012). Commitment to a developing
preference and predecisional distortion of information.
\emph{Organizational Behavior and Human Decision Processes},
\emph{119}(1), 78--88.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.05.004}{10.1016/j.obhdp.2012.05.004}

\hypertarget{ref-Pontifex2012}{}
Pontifex, M. B., Scudder, M. R., Drollette, E. S., \& Hillman, C. H.
(2012). Fit and vigilant: The relationship between poorer aerobic
fitness and failures in sustained attention during preadolescence.
\emph{Neuropsychology}, \emph{26}(4), 407--413.
doi:\href{https://doi.org/10.1037/a0028795}{10.1037/a0028795}

\hypertarget{ref-Pornpattananangkul2017}{}
Pornpattananangkul, N., Nadig, A., Heidinger, S., Walden, K., \&
Nusslock, R. (2017). Elevated outcome-anticipation and
outcome-evaluation ERPs associated with a greater preference for
larger-but-delayed rewards. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{17}(3), 625--641.
doi:\href{https://doi.org/10.3758/s13415-017-0501-4}{10.3758/s13415-017-0501-4}

\hypertarget{ref-Porter2016}{}
Porter, C. M., Woo, S. E., \& Campion, M. A. (2016). Internal and
external networking differentially predict turnover through job
embeddedness and job offers. \emph{Personnel Psychology}, \emph{69}(3),
635--672.
doi:\href{https://doi.org/10.1111/peps.12121}{10.1111/peps.12121}

\hypertarget{ref-Poteat2011}{}
Poteat, V. P., Mereish, E. H., DiGiovanni, C. D., \& Koenig, B. W.
(2011). The effects of general and homophobic victimization on
adolescents' psychosocial and educational concerns: The importance of
intersecting identities and parent support. \emph{Journal of Counseling
Psychology}, \emph{58}(4), 597--609.
doi:\href{https://doi.org/10.1037/a0025095}{10.1037/a0025095}

\hypertarget{ref-Poteat2012}{}
Poteat, V. P., O'Dwyer, L. M., \& Mereish, E. H. (2012). Changes in how
students use and are called homophobic epithets over time: Patterns
predicted by gender, bullying, and victimization status. \emph{Journal
of Educational Psychology}, \emph{104}(2), 393--406.
doi:\href{https://doi.org/10.1037/a0026437}{10.1037/a0026437}

\hypertarget{ref-Potts2012}{}
Potts, R., \& Shanks, D. R. (2012). Can testing immunize memories
against interference? \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{38}(6), 1780--1785.
doi:\href{https://doi.org/10.1037/a0028218}{10.1037/a0028218}

\hypertarget{ref-Poulin2012}{}
Poulin, F., \& Denault, A.-S. (2012). Other-sex friendships as a
mediator between parental monitoring and substance use in girls and
boys. \emph{Journal of Youth and Adolescence}, \emph{41}(11),
1488--1501.
doi:\href{https://doi.org/10.1007/s10964-012-9770-y}{10.1007/s10964-012-9770-y}

\hypertarget{ref-Pratte2012}{}
Pratte, M. S., \& Rouder, J. N. (2012). Assessing the dissociability of
recollection and familiarity in recognition memory. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{38}(6),
1591--1607.
doi:\href{https://doi.org/10.1037/a0028144}{10.1037/a0028144}

\hypertarget{ref-Preacher2011}{}
Preacher, K. J., \& Kelley, K. (2011). Effect size measures for
mediation models: Quantitative strategies for communicating indirect
effects. \emph{Psychological Methods}, \emph{16}(2), 93--115.
doi:\href{https://doi.org/10.1037/a0022658}{10.1037/a0022658}

\hypertarget{ref-Preacher2015}{}
Preacher, K. J., Zhang, Z., \& Zyphur, M. J. (2015). Multilevel
structural equation models for assessing moderation within and across
levels of analysis. \emph{Psychological Methods}, \emph{20}(4), 1--17.
doi:\href{https://doi.org/10.1037/met0000052}{10.1037/met0000052}

\hypertarget{ref-Preston2012}{}
Preston, J. L., \& Ritter, R. S. (2012). Cleanliness and godliness:
Mutual association between two kinds of personal purity. \emph{Journal
of Experimental Social Psychology}, \emph{48}(6), 1365--1368.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.015}{10.1016/j.jesp.2012.05.015}

\hypertarget{ref-Principe2012}{}
Principe, G. F., Cherson, M., DiPuppo, J., \& Schindewolf, E. (2012).
Children's natural conversations following exposure to a rumor: Linkages
to later false reports. \emph{Journal of Experimental Child Psychology},
\emph{113}(3), 383--400.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.006}{10.1016/j.jecp.2012.06.006}

\hypertarget{ref-Pringle2009}{}
Pringle, R. (2009). Defamiliarizing heavy-contact sports: A critical
examination of rugby, discipline, and pleasure. \emph{Sociology of Sport
Journal}, \emph{26}(2), 211--234.
doi:\href{https://doi.org/10.1123/ssj.26.2.211}{10.1123/ssj.26.2.211}

\hypertarget{ref-Pruitt2010}{}
Pruitt, N. T., Johnson, A. J., Catlin, L., \& Knox, S. (2010).
Influences on women counseling psychology associate professors'
decisions regarding pursuit of full professorship. \emph{The Counseling
Psychologist}, \emph{38}(8), 1139--1173.
doi:\href{https://doi.org/10.1177/0011000010377666}{10.1177/0011000010377666}

\hypertarget{ref-Purdy2011}{}
Purdy, L. G., \& Jones, R. L. (2011). Choppy waters: Elite rowers'
perceptions of coaching. \emph{Sociology of Sport Journal},
\emph{28}(3), 329--346.
doi:\href{https://doi.org/10.1123/ssj.28.3.329}{10.1123/ssj.28.3.329}

\hypertarget{ref-Puspitasari2017a}{}
Puspitasari, A. J., Kanter, J. W., Busch, A. M., Leonard, R., Dunsiger,
S., Cahill, S., \ldots{} Koerner, K. (2017). A randomized controlled
trial of an online, modular, active learning training program for
behavioral activation for depression. \emph{Journal of Consulting and
Clinical Psychology}, \emph{85}(8), 814--825.
doi:\href{https://doi.org/10.1037/ccp0000223}{10.1037/ccp0000223}

\hypertarget{ref-PytlikZillig2011}{}
PytlikZillig, L. M., Horn, C. A., Bruning, R., Bell, S., Liu, X.,
Siwatu, K. O., \ldots{} Carlson, D. (2011). Face-to-face versus
computer-mediated discussion of teaching cases: Impacts on preservice
teachers' engagement, critical analyses, and self-efficacy.
\emph{Contemporary Educational Psychology}, \emph{36}(4), 302--312.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.07.002}{10.1016/j.cedpsych.2011.07.002}

\hypertarget{ref-Qi2017}{}
Qi, S., Li, Y., Tang, X., Zeng, Q., Diao, L., Li, X., \ldots{} Hu, W.
(2017). The temporal dynamics of detached versus positive reappraisal:
An ERP study. \emph{Cognitive, Affective and Behavioral Neuroscience},
1--12.
doi:\href{https://doi.org/10.3758/s13415-016-0494-4}{10.3758/s13415-016-0494-4}

\hypertarget{ref-Quade2017}{}
Quade, M. J., Greenbaum, R. L., \& Petrenko, O. V. (2017). ``I don't
want to be near you, unless\ldots{}'': The interactive effect of
unethical behavior and performance onto relationship conflict and
workplace ostracism. \emph{Personnel Psychology}, \emph{70}(3),
675--709.
doi:\href{https://doi.org/10.1111/peps.12164}{10.1111/peps.12164}

\hypertarget{ref-Quek2012}{}
Quek, L.-H., Sofronoff, K., Sheffield, J., White, A., \& Kelly, A.
(2012). Co-occurring anger in young people with Asperger's Syndrome.
\emph{Journal of Clinical Psychology}, \emph{68}(10), 1142--1148.
doi:\href{https://doi.org/10.1002/jclp.21888}{10.1002/jclp.21888}

\hypertarget{ref-Quested2011}{}
Quested, E., Bosch, J. A., Burns, V. E., Cumming, J., Ntoumanis, N., \&
Duda, J. L. (2011). Basic psychological need satisfaction,
stress-related appraisals, and dancers' cortisol and anxiety responses.
\emph{Journal of Sport and Exercise Psychology}, \emph{33}(6), 828--846.
doi:\href{https://doi.org/10.1123/jsep.33.6.828}{10.1123/jsep.33.6.828}

\hypertarget{ref-Quinlivan2011}{}
Quinlivan, D. S., Neuschatz, J. S., Douglass, A. B., Wells, G. L., \&
Wetmore, S. A. (2012). The effect of post-identification feedback,
delay, and suspicion on accurate eyewitnesses. \emph{Law and Human
Behavior}, \emph{36}(3), 206--214.
doi:\href{https://doi.org/10.1037/h0093970}{10.1037/h0093970}

\hypertarget{ref-Racz2017}{}
Racz, S. J., Putnick, D. L., Suwalsky, J. T. D., Hendricks, C., \&
Bornstein, M. H. (2017). Cognitive abilities, social adaptation, and
externalizing behavior problems in childhood and adolescence: Specific
cascade effects across development. \emph{Journal of Youth and
Adolescence}, \emph{46}(8), 1688--1701.
doi:\href{https://doi.org/10.1007/s10964-016-0602-3}{10.1007/s10964-016-0602-3}

\hypertarget{ref-Raghuram2017}{}
Raghuram, S., Gajendran, R. S., Liu, X., \& Somaya, D. (2017).
Boundaryless LMX: Examining LMX's impact on external career outcomes and
alumni goodwill. \emph{Personnel Psychology}, \emph{70}(2), 399--428.
doi:\href{https://doi.org/10.1111/peps.12143}{10.1111/peps.12143}

\hypertarget{ref-Ragins2017}{}
Ragins, B. R., Ehrhardt, K., Lyness, K. S., Murphy, D. D., \& Capman, J.
F. (2017). Anchoring relationships at work: High-quality mentors and
other supportive work relationships as buffers to ambient racial
discrimination. \emph{Personnel Psychology}, \emph{70}(1), 211--256.
doi:\href{https://doi.org/10.1111/peps.12144}{10.1111/peps.12144}

\hypertarget{ref-Ragins2012}{}
Ragins, B. R., Gonzalez, J. A., Ehrhardt, K., \& Singh, R. (2012).
Crossing the threshold: the spillover of community racial diversity and
diversity climate to the workplace. \emph{Personnel Psychology},
\emph{65}(4), 755--787.
doi:\href{https://doi.org/10.1111/peps.12001}{10.1111/peps.12001}

\hypertarget{ref-Raimo2017}{}
Raimo, S., Trojano, L., Pappacena, S., Alaia, R., Spitaleri, D., Grossi,
D., \ldots{} Vanvitelli ', L. (2017). Neuropsychological correlates of
theory of mind deficits in patients with multiple sclerosis.
\emph{Neuropsychology}, \emph{31}(7), 811--821.
doi:\href{https://doi.org/10.1037/neu0000372}{10.1037/neu0000372}

\hypertarget{ref-Rajsic2017}{}
Rajsic, J., Swan, G., Wilson, D. E., \& Pratt, J. (2017). Accessibility
limits recall from visual working memory. \emph{Journal of Experimental
Psychology: Learning, Memory, and Cognition}, \emph{43}(9), 1415--1431.
doi:\href{https://doi.org/10.1037/xlm0000387}{10.1037/xlm0000387}

\hypertarget{ref-Ramirez2017}{}
Ramirez, G., McDonough, I. M., \& Jin, L. (2017). Classroom stress
promotes motivated forgetting of mathematics knowledge. \emph{Journal of
Educational Psychology}, \emph{109}(6), 812--825.
doi:\href{https://doi.org/10.1037/edu0000170}{10.1037/edu0000170}

\hypertarget{ref-Ramos2012}{}
Ramos, T., Garcia-Marques, L., Hamilton, D. L., Ferreira, M., \& Van
Acker, K. (2012). What I infer depends on who you are: The influence of
stereotypes on trait and situational spontaneous inferences.
\emph{Journal of Experimental Social Psychology}, \emph{48}(6),
1247--1256.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.009}{10.1016/j.jesp.2012.05.009}

\hypertarget{ref-Ramscar2017}{}
Ramscar, M., Sun, C. C., Hendrix, P., \& Baayen, H. (2017). The
mismeasurement of mind: Life-span changes in Paired-Associate-Learning
Scores reflect the ``cost'' of learning, not cognitive decline.
\emph{Psychological Science}, \emph{28}(8), 1171--1179.
doi:\href{https://doi.org/10.1177/0956797617706393}{10.1177/0956797617706393}

\hypertarget{ref-Rankin-Wright2016}{}
Rankin-Wright, A. J., Hylton, K., \& Norman, L. (2016). Off-colour
landscape: Framing race equality in sport coaching. \emph{Sociology of
Sport Journal}, \emph{33}(4), 357--368.
doi:\href{https://doi.org/10.1123/ssj.2015-0174}{10.1123/ssj.2015-0174}

\hypertarget{ref-Rappaport2017}{}
Rappaport, L. M., Moskowitz, D. S., \& D'Antono, B. (2017). Depression
symptoms moderate the association between emotion and communal behavior.
\emph{Journal of Counseling Psychology}, \emph{64}(3), 269--279.
doi:\href{https://doi.org/10.1037/cou0000194}{10.1037/cou0000194}

\hypertarget{ref-Rat-Fischer2012}{}
Rat-Fischer, L., O'Regan, J. K., \& Fagard, J. (2012). The emergence of
tool use during the second year of life. \emph{Journal of Experimental
Child Psychology}, \emph{113}(3), 440--446.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.001}{10.1016/j.jecp.2012.06.001}

\hypertarget{ref-Ratcliff2012}{}
Ratcliff, N. J., Bernstein, M. J., Cundiff, J. L., \& Vescio, T. K.
(2012). Seeing wrath from the top (through stratified lenses):
Perceivers high in social dominance orientation show superior anger
identification for high-status individuals. \emph{Journal of
Experimental Social Psychology}, \emph{48}(6), 1373--1376.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.016}{10.1016/j.jesp.2012.05.016}

\hypertarget{ref-Rattan2012}{}
Rattan, A., Savani, K., Naidu, N. V. R., \& Dweck, C. S. (2012). Can
everyone become highly intelligent? Cultural differences in and societal
consequences of beliefs about the universal potential for intelligence.
\emph{Journal of Personality and Social Psychology}, \emph{103}(5),
787--803. doi:\href{https://doi.org/10.1037/a0029263}{10.1037/a0029263}

\hypertarget{ref-Read2012}{}
Read, D., \& Scholten, M. (2012). Tradeoffs between sequences: Weighing
accumulated outcomes against outcome-adjusted delays. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{38}(6),
1675--1688.
doi:\href{https://doi.org/10.1037/a0028216}{10.1037/a0028216}

\hypertarget{ref-Redlich2012}{}
Redlich, A. D., \& Summers, A. (2012). Voluntary, knowing, and
intelligent pleas: Understanding the plea inquiry. \emph{Psychology,
Public Policy, and Law}, \emph{18}(4), 626--643.
doi:\href{https://doi.org/10.1037/a0026066}{10.1037/a0026066}

\hypertarget{ref-Redlich2011}{}
Redlich, A. D., Kulish, R., \& Steadman, H. J. (2011). Comparing true
and false confessions among persons with serious mental illness.
\emph{Psychology, Public Policy, and Law}, \emph{17}(3), 394--418.
doi:\href{https://doi.org/10.1037/a0022918}{10.1037/a0022918}

\hypertarget{ref-Reeve2011}{}
Reeve, J., \& Tseng, C. M. (2011). Agency as a fourth aspect of
students' engagement during learning activities. \emph{Contemporary
Educational Psychology}, \emph{36}(4), 257--267.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.05.002}{10.1016/j.cedpsych.2011.05.002}

\hypertarget{ref-Reidy2012}{}
Reidy, T. J., Sorensen, J. R., \& Cunningham, M. D. (2012). Community
violence to prison assault: A test of the behavioral continuity
hypothesis. \emph{Law and Human Behavior}, \emph{36}(4), 356--363.
doi:\href{https://doi.org/10.1037/h0093934}{10.1037/h0093934}

\hypertarget{ref-Reingold2012}{}
Reingold, E. M., Reichle, E. D., Glaholt, M. G., \& Sheridan, H. (2012).
Direct lexical control of eye movements in reading: Evidence from a
survival analysis of fixation durations. \emph{Cognitive Psychology},
\emph{65}(2), 177--206.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.03.001}{10.1016/j.cogpsych.2012.03.001}

\hypertarget{ref-Renfrow2016}{}
Renfrow, D. G., Wissick, T. L., \& Guard, C. M. (2016). (Re)Defining the
situation when football fans rush the field. \emph{Sociology of Sport
Journal}, \emph{33}(3), 250--261.
doi:\href{https://doi.org/10.1123/ssj.2015-0107}{10.1123/ssj.2015-0107}

\hypertarget{ref-Renkewitz2012}{}
Renkewitz, F., \& Jahn, G. (2012). Memory indexing: A novel method for
tracing memory processes in complex cognitive tasks. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{38}(6),
1622--1639.
doi:\href{https://doi.org/10.1037/a0028073}{10.1037/a0028073}

\hypertarget{ref-Resendes2012}{}
Resendes, J., \& Lecci, L. (2012). Comparing the MMPI-2 scale scores of
parents involved in parental competency and child custody assessments.
\emph{Psychological Assessment}, \emph{24}(4), 1054--1059.
doi:\href{https://doi.org/10.1037/a0028585}{10.1037/a0028585}

\hypertarget{ref-Resnik2017}{}
Resnik, L., Ekerholm, S., Johnson, E. E., Ellison, M. L., \& O'Toole, T.
P. (2017). Which homeless veterans benefit from a peer mentor and how?
\emph{Journal of Clinical Psychology}, \emph{73}(9), 1027--1047.
doi:\href{https://doi.org/10.1002/jclp.22407}{10.1002/jclp.22407}

\hypertarget{ref-Retnowati2017}{}
Retnowati, E., Ayres, P., \& Sweller, J. (2017). Can collaborative
learning improve the effectiveness of worked examples in learning
mathematics? \emph{Journal of Educational Psychology}, \emph{109}(5),
666--679.
doi:\href{https://doi.org/10.1037/edu0000167}{10.1037/edu0000167}

\hypertarget{ref-Rettenberger2017}{}
Rettenberger, M., Rice, M. E., Harris, G. T., \& Eher, R. (2017).
Actuarial risk assessment of sexual offenders: The psychometric
properties of the Sex Offender Risk Appraisal Guide (SORAG).
\emph{Psychological Assessment}, \emph{29}(6), 624--638.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/pas0000390}{http://dx.doi.org/10.1037/pas0000390}

\hypertarget{ref-Reyes2017}{}
Reyes, H. L. M., Foshee, V. A., Chen, M. S., \& Ennett, S. T. (2017).
Patterns of dating violence victimization and perpetration among Latino
youth. \emph{Journal of Youth and Adolescence}, \emph{46}(8),
1727--1742.
doi:\href{https://doi.org/10.1007/s10964-016-0621-0}{10.1007/s10964-016-0621-0}

\hypertarget{ref-Reynolds2017}{}
Reynolds, G. O., Hanna, K. K., Neargarder, S., \& Cronin-Golomb, A.
(2017). The relation of anxiety and cognition in Parkinson's Disease.
\emph{Neuropsychology}, \emph{31}(6), 596--604.
doi:\href{https://doi.org/10.1037/neu0000353}{10.1037/neu0000353}

\hypertarget{ref-Reynolds2012}{}
Reynolds, M., Mulatti, C., \& Besner, D. (2012). Reading nonwords aloud:
evidence for dynamic control in skilled readers. \emph{Psychonomic
Bulletin \& Review}, \emph{19}(6), 1135--1141.
doi:\href{https://doi.org/10.3758/s13423-012-0290-2}{10.3758/s13423-012-0290-2}

\hypertarget{ref-Reznik2017}{}
Reznik, S. J., Nusslock, R., Pornpattananangkul, N., Abramson, L. Y.,
Coan, J. A., \& Harmon-Jones, E. (2017). Laboratory-induced learned
helplessness attenuates approach motivation as indexed by posterior
versus frontal theta activity. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, 904--916.
doi:\href{https://doi.org/10.3758/s13415-017-0521-0}{10.3758/s13415-017-0521-0}

\hypertarget{ref-Reznitskaya2012}{}
Reznitskaya, A., Glina, M., Carolan, B., Michaud, O., Rogers, J., \&
Sequeira, L. (2012). Examining transfer effects from dialogic
discussions to new tasks and contexts. \emph{Contemporary Educational
Psychology}, \emph{37}(4), 288--306.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.02.003}{10.1016/j.cedpsych.2012.02.003}

\hypertarget{ref-Rice2012}{}
Rice, K. G., Choi, C.-C., Zhang, Y., Morero, Y. I., \& Anderson, D.
(2012). Self-critical perfectionism, acculturative stress, and
depression among international students. \emph{The Counseling
Psychologist}, \emph{40}(4), 575--600.
doi:\href{https://doi.org/10.1177/0011000011427061}{10.1177/0011000011427061}

\hypertarget{ref-Rich2012}{}
Rich, Y., \& Schachter, E. P. (2012). High school identity climate and
student identity development. \emph{Contemporary Educational
Psychology}, \emph{37}(3), 218--228.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.06.002}{10.1016/j.cedpsych.2011.06.002}

\hypertarget{ref-Richetin2012}{}
Richetin, J., Perugini, M., Conner, M., Adjali, I., Hurling, R.,
Sengupta, A., \& Greetham, D. (2012). To reduce and not to reduce
resource consumption? That is two questions. \emph{Journal of
Environmental Psychology}, \emph{32}(2), 112--122.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.01.003}{10.1016/j.jenvp.2012.01.003}

\hypertarget{ref-Richtberg2017}{}
Richtberg, S., Jakob, M., Höfling, V., \& Weck, F. (2017). Patient
characteristics and patient behavior as predictors of outcome in
cognitive therapy and exposure therapy for hypochondriasis.
\emph{Journal of Clinical Psychology}, \emph{73}(6), 612--625.
doi:\href{https://doi.org/10.1002/jclp.22356}{10.1002/jclp.22356}

\hypertarget{ref-Riciputi2016}{}
Riciputi, S., McDonough, M. H., \& Ullrich-French, S. (2016).
Participant perceptions of character concepts in a physical
activity--based positive youth development program. \emph{Journal of
Sport and Exercise Psychology}, \emph{38}(5), 481--492.
doi:\href{https://doi.org/10.1123/jsep.2016-0061}{10.1123/jsep.2016-0061}

\hypertarget{ref-Riem2017}{}
Riem, M. M. E., Van Ijzendoorn, M. H., Parsons, C. E., Young, K. S., De
Carli, P., Kringelbach, M. L., \& Bakermans-Kranenburg, M. J. (2017).
Experimental manipulation of infant temperament affects amygdala
functional connectivity. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, 858--868.
doi:\href{https://doi.org/10.3758/s13415-017-0518-8}{10.3758/s13415-017-0518-8}

\hypertarget{ref-Rieth2017}{}
Rieth, C. A., \& Huber, D. E. (2017). Comparing different kinds of words
and word-word relations to test an habituation model of priming.
\emph{Cognitive Psychology}, \emph{95}, 79--104.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.04.002}{10.1016/j.cogpsych.2017.04.002}

\hypertarget{ref-Ries2012}{}
Riès, S., Legou, T., Burle, B., Alario, F.-X., \& Malfait, N. (2012).
Why does picture naming take longer than word reading? The contribution
of articulatory processes. \emph{Psychonomic Bulletin \& Review},
\emph{19}(5), 955--961.
doi:\href{https://doi.org/10.3758/s13423-012-0287-x}{10.3758/s13423-012-0287-x}

\hypertarget{ref-Riggs2017}{}
Riggs, A. E., Alibali, M. W., \& Kalish, C. W. (2017). Does it matter
how Molly does it? Person-presentation of strategies and transfer in
mathematics. \emph{Contemporary Educational Psychology}, \emph{51},
315--320.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.09.001}{10.1016/j.cedpsych.2017.09.001}

\hypertarget{ref-Rindal2017}{}
Rindal, E. J., Chrobak, Q. M., Zaragoza, M. S., \& Weihing, C. A.
(2017). Mechanisms of eyewitness suggestibility: tests of the
explanatory role hypothesis. \emph{Psychonomic Bulletin \& Review},
\emph{24}(5), 1413--1425.
doi:\href{https://doi.org/10.3758/s13423-016-1201-8}{10.3758/s13423-016-1201-8}

\hypertarget{ref-Rink2012}{}
Rink, F., Ryan, M. K., \& Stoker, J. I. (2012). Influence in times of
crisis. \emph{Psychological Science}, \emph{23}(11), 1306--1313.
doi:\href{https://doi.org/10.1177/0956797612453115}{10.1177/0956797612453115}

\hypertarget{ref-Rios2012}{}
Rios, K., Wheeler, S. C., \& Miller, D. T. (2012). Compensatory
nonconformity: Self-uncertainty and low implicit self-esteem increase
adoption and expression of minority opinions. \emph{Journal of
Experimental Social Psychology}, \emph{48}(6), 1300--1309.
doi:\href{https://doi.org/10.1016/j.jesp.2012.07.005}{10.1016/j.jesp.2012.07.005}

\hypertarget{ref-Riva2012}{}
Riva, P., Romero Lauro, L. J., DeWall, C. N., \& Bushman, B. J. (2012).
Buffer the pain away. \emph{Psychological Science}, \emph{23}(12),
1473--1475.
doi:\href{https://doi.org/10.1177/0956797612450894}{10.1177/0956797612450894}

\hypertarget{ref-Riva2017}{}
Riva, V., Cantiani, C., Dionne, G., Marini, A., Mascheretti, S.,
Molteni, M., \& Marino, C. (2017). Working memory mediates the effects
of gestational age at birth on expressive language development in
children. \emph{Neuropsychology}, \emph{31}(5), 475--485.
doi:\href{https://doi.org/10.1037/neu0000376}{10.1037/neu0000376}

\hypertarget{ref-Ro2017}{}
Ro, M., Brauer, M., Kuntz, K., Shukla, R., \& Bensch, I. (2017). Making
cool choices for sustainability: Testing the effectiveness of a
game-based approach to promoting pro-environmental behaviors.
\emph{Journal of Environmental Psychology}, \emph{53}, 20--30.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.06.007}{10.1016/j.jenvp.2017.06.007}

\hypertarget{ref-Roberts2012}{}
Roberts, W., Milich, R., \& Fillmore, M. T. (2012). Constraints on
information processing capacity in adults with ADHD.
\emph{Neuropsychology}, \emph{26}(6), 695--703.
doi:\href{https://doi.org/10.1037/a0030296}{10.1037/a0030296}

\hypertarget{ref-Robinson2017a}{}
Robinson, J. S., Page-Gould, E., \& Plaks, J. E. (2017). I appreciate
your effort: Asymmetric effects of actors' exertion on observers'
consequentialist versus deontological judgments. \emph{Journal of
Experimental Social Psychology}, \emph{73}, 50--64.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.005}{10.1016/j.jesp.2017.06.005}

\hypertarget{ref-Robinson2017}{}
Robinson, K. A., Ranellucci, J., Lee, Y.-k., Wormington, S. V., Roseth,
C. J., \& Linnenbrink-Garcia, L. (2017). Affective profiles and academic
success in a college science course. \emph{Contemporary Educational
Psychology}, \emph{51}, 209--221.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.08.004}{10.1016/j.cedpsych.2017.08.004}

\hypertarget{ref-Rocklage2017}{}
Rocklage, M. D., Pietri, E. S., \& Fazio, R. H. (2017). The weighting of
positive vs. negative valence and its impact on the formation of social
relationships. \emph{Journal of Experimental Social Psychology},
\emph{73}, 65--75.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.011}{10.1016/j.jesp.2017.06.011}

\hypertarget{ref-Rodeheffer2012}{}
Rodeheffer, C. D., Hill, S. E., \& Lord, C. G. (2012). Does this
recession make me look black? The effect of resource scarcity on the
categorization of biracial faces. \emph{Psychological Science},
\emph{23}(12), 1476--1478.
doi:\href{https://doi.org/10.1177/0956797612450892}{10.1177/0956797612450892}

\hypertarget{ref-Rodell2017}{}
Rodell, J. B., Colquitt, J. A., \& Baer, M. D. (2017). Is adhering to
justice rules enough? The role of charismatic qualities in perceptions
of supervisors' overall fairness. \emph{Organizational Behavior and
Human Decision Processes}, \emph{140}, 14--28.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.03.001}{10.1016/j.obhdp.2017.03.001}

\hypertarget{ref-Rodriguez2016}{}
Rodriguez, A., Reise, S. P., \& Haviland, M. G. (2016). Evaluating
bifactor models: Calculating and interpreting statistical indices.
\emph{Psychological Methods}, \emph{21}(2), 137--150.
doi:\href{https://doi.org/10.1037/met0000045}{10.1037/met0000045}

\hypertarget{ref-Roese2017}{}
Roese, N. J., Smallman, R., \& Epstude, K. (2017). Do episodic
counterfactual thoughts focus on controllable action?: The role of
self-initiation. \emph{Journal of Experimental Social Psychology},
\emph{73}, 14--23.
doi:\href{https://doi.org/10.1016/j.jesp.2017.05.006}{10.1016/j.jesp.2017.05.006}

\hypertarget{ref-Rogers2016}{}
Rogers, C. S. (2017). Semantic priming, not repetition priming, is to
blame for false hearing. \emph{Psychonomic Bulletin \& Review},
\emph{24}(4), 1194--1204.
doi:\href{https://doi.org/10.3758/s13423-016-1185-4}{10.3758/s13423-016-1185-4}

\hypertarget{ref-Rogge2017}{}
Rogge, R. D., Fincham, F. D., Crasta, D., \& Maniaci, M. R. (2016).
Positive and Negative Evaluation of Relationships: Development and
Validation of the Positive--Negative Relationship Quality (PN-RQ) Scale.
\emph{Psychological Assessment}, \emph{29}(8), 1028--1043.
doi:\href{https://doi.org/10.1037/pas0000392}{10.1037/pas0000392}

\hypertarget{ref-Rolison2012}{}
Rolison, J. J., Evans, J. S. B., Dennis, I., \& Walsh, C. R. (2012).
Dual-processes in learning and judgment: Evidence from the multiple cue
probability learning paradigm. \emph{Organizational Behavior and Human
Decision Processes}, \emph{118}(2), 189--202.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.03.003}{10.1016/j.obhdp.2012.03.003}

\hypertarget{ref-Rollings2017}{}
Rollings, K. A., \& Wells, N. M. (2017). Effects of floor plan openness
on eating behaviors. \emph{Environment and Behavior}, \emph{49}(6),
663--684.
doi:\href{https://doi.org/10.1177/0013916516661822}{10.1177/0013916516661822}

\hypertarget{ref-Rom2018}{}
Rom, S. C., \& Conway, P. (2018). The strategic moral self:
Self-presentation shapes moral dilemma judgments. \emph{Journal of
Experimental Social Psychology}, \emph{74}, 24--37.
doi:\href{https://doi.org/10.1016/j.jesp.2017.08.003}{10.1016/j.jesp.2017.08.003}

\hypertarget{ref-Romano2017}{}
Romano, M., Arambasic, J., \& Peters, L. (2017). Therapist and client
interactions in motivational interviewing for social anxiety disorder.
\emph{Journal of Clinical Psychology}, \emph{73}(7), 829--847.
doi:\href{https://doi.org/10.1002/jclp.22405}{10.1002/jclp.22405}

\hypertarget{ref-Ronchi2012}{}
Ronchi, R., Algeri, L., Chiapella, L., Spada, M. S., \& Vallar, G.
(2012). Spatial neglect and perseveration in visuomotor exploration.
\emph{Neuropsychology}, \emph{26}(5), 588--603.
doi:\href{https://doi.org/10.1037/a0029216}{10.1037/a0029216}

\hypertarget{ref-Roper2012}{}
Roper, Z. J. J., \& Vecera, S. P. (2012). Searching for two things at
once: Establishment of multiple attentional control settings on a
trial-by-trial basis. \emph{Psychonomic Bulletin \& Review},
\emph{19}(6), 1114--1121.
doi:\href{https://doi.org/10.3758/s13423-012-0297-8}{10.3758/s13423-012-0297-8}

\hypertarget{ref-Rosenfeld2017}{}
Rosenfeld, B., Foellmi, M., Khadivi, A., Wijetunga, C., Howe, J.,
Nijdam-Jones, A., \ldots{} Rotter, M. (2017). Determining when to
conduct a violence risk assessment: Development and initial validation
of the Fordham Risk Screening Tool (FRST). \emph{Law and Human
Behavior}, \emph{41}(4), 325--332.
doi:\href{https://doi.org/10.1037/lhb0000247}{10.1037/lhb0000247}

\hypertarget{ref-Ross2012}{}
Ross, S., \& Allen, N. (2012). Examining the convergent validity of
shared mental model measures. \emph{Behavior Research Methods},
\emph{44}(4), 1052--1062.
doi:\href{https://doi.org/10.3758/s13428-012-0201-5}{10.3758/s13428-012-0201-5}

\hypertarget{ref-Rossano2012}{}
Rossano, F., Carpenter, M., \& Tomasello, M. (2012). One-year-old
infants follow others' voice direction. \emph{Psychological Science},
\emph{23}(11), 1298--1302.
doi:\href{https://doi.org/10.1177/0956797612450032}{10.1177/0956797612450032}

\hypertarget{ref-Rottman2012}{}
Rottman, B. M., \& Keil, F. C. (2012). Causal structure learning over
time: Observations and interventions. \emph{Cognitive Psychology},
\emph{64}(1-2), 93--125.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.10.003}{10.1016/j.cogpsych.2011.10.003}

\hypertarget{ref-Roer2016}{}
Röer, J. P., Körner, U., Buchner, A., \& Bell, R. (2017). Semantic
priming by irrelevant speech. \emph{Psychonomic Bulletin \& Review},
\emph{24}(4), 1205--1210.
doi:\href{https://doi.org/10.3758/s13423-016-1186-3}{10.3758/s13423-016-1186-3}

\hypertarget{ref-Rubio-Fernandez2016}{}
Rubio-Fernández, P. (2017). The director task: A test of Theory-of-Mind
use or selective attention? \emph{Psychonomic Bulletin \& Review},
\emph{24}(4), 1121--1128.
doi:\href{https://doi.org/10.3758/s13423-016-1190-7}{10.3758/s13423-016-1190-7}

\hypertarget{ref-Ruiz-Alfonso2017}{}
Ruiz-Alfonso, Z., \& León, J. (2017). Passion for math: Relationships
between teachers' emphasis on class contents usefulness, motivation and
grades. \emph{Contemporary Educational Psychology}, \emph{51}, 284--292.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.08.010}{10.1016/j.cedpsych.2017.08.010}

\hypertarget{ref-Rummel2017}{}
Rummel, J., Smeekens, B. A., \& Kane, M. J. (2017). Dealing with
prospective memory demands while performing an ongoing task: Shared
processing, increased on-task focus, or both? \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{43}(7),
1047--1062.
doi:\href{https://doi.org/10.1037/xlm0000359}{10.1037/xlm0000359}

\hypertarget{ref-Russo2017}{}
Russo, N., Kates, W. R., \& Wyble, B. (2017). Developmental changes in
feature detection across time: Evidence from the attentional blink.
\emph{Journal of Experimental Child Psychology}, \emph{164}, 32--44.
doi:\href{https://doi.org/10.1016/j.jecp.2017.06.013}{10.1016/j.jecp.2017.06.013}

\hypertarget{ref-Rutherford2017}{}
Rutherford, T., Long, J. J., \& Farkas, G. (2017). Teacher value for
professional development, self-efficacy, and student outcomes within a
digital mathematics intervention. \emph{Contemporary Educational
Psychology}, \emph{51}, 22--36.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.05.005}{10.1016/j.cedpsych.2017.05.005}

\hypertarget{ref-Ruva2017}{}
Ruva, C. L., \& Guenther, C. C. (2017). Keep your bias to yourself: How
deliberating with differently biased others affects mock-jurors' guilt
decisions, perceptions of the defendant, memories, and evidence
interpretation. \emph{Law and Human Behavior}, \emph{41}(5), 478--493.
doi:\href{https://doi.org/10.1037/lhb0000256}{10.1037/lhb0000256}

\hypertarget{ref-Ryan2012}{}
Ryan, A. M., \& Shim, S. S. (2012). Changes in help seeking from peers
during early adolescence: Associations with changes in achievement and
perceptions of teachers. \emph{Journal of Educational Psychology},
\emph{104}(4), 1122--1134.
doi:\href{https://doi.org/10.1037/a0027696}{10.1037/a0027696}

\hypertarget{ref-Sachdeva2017}{}
Sachdeva, S. (2017). The influence of sacred beliefs in environmental
risk perception and attitudes. \emph{Environment and Behavior},
\emph{49}(5), 583--600.
doi:\href{https://doi.org/10.1177/0013916516649413}{10.1177/0013916516649413}

\hypertarget{ref-Safai2016}{}
Safai, P., Johnson, J., \& Bryans, J. (2016). The absence of resistance
training? Exploring the politics of health in high performance youth
triathlon. \emph{Sociology of Sport Journal}, \emph{33}(4), 269--281.
doi:\href{https://doi.org/10.1123/ssj.2016-0053}{10.1123/ssj.2016-0053}

\hypertarget{ref-Salahuddin2011}{}
Salahuddin, N. M., \& O'Brien, K. M. (2011). Challenges and resilience
in the lives of urban, multiracial adults: An instrument development
study. \emph{Journal of Counseling Psychology}, \emph{58}(4), 494--507.
doi:\href{https://doi.org/10.1037/a0024633}{10.1037/a0024633}

\hypertarget{ref-Salas-Wright2012}{}
Salas-Wright, C. P., Vaughn, M. G., Hodge, D. R., \& Perron, B. E.
(2012). Religiosity profiles of American youth in relation to substance
use, violence, and delinquency. \emph{Journal of Youth and Adolescence},
\emph{41}(12), 1560--1575.
doi:\href{https://doi.org/10.1007/s10964-012-9761-z}{10.1007/s10964-012-9761-z}

\hypertarget{ref-Salazar2017}{}
Salazar, R. D., Ren, X., Ellis, T. D., Toraif, N., Barthelemy, O. J.,
Neargarder, S., \& Cronin-Golomb, A. (2017). Dual tasking in Parkinson's
Disease: Cognitive consequences while walking. \emph{Neuropsychology},
\emph{31}(6), 613--623.
doi:\href{https://doi.org/10.1037/neu0000331}{10.1037/neu0000331}

\hypertarget{ref-Salerno2017}{}
Salerno, J. M. (2017). Seeing red: Disgust reactions to gruesome
photographs in color (but not in black and white) increase convictions.
\emph{Psychology, Public Policy, and Law}, \emph{23}(3), 336--350.
doi:\href{https://doi.org/10.1037/law0000122}{10.1037/law0000122}

\hypertarget{ref-Samara2017}{}
Samara, A., Smith, K., Brown, H., \& Wonnacott, E. (2017). Acquiring
variation in an artificial language: Children and adults are sensitive
to socially conditioned linguistic variation. \emph{Cognitive
Psychology}, \emph{94}, 85--114.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.02.004}{10.1016/j.cogpsych.2017.02.004}

\hypertarget{ref-Sanchez2016}{}
Sanchez, L. (2017). 'Every time they ride, I pray:' Parents' management
of daughters' horseback riding risks. \emph{Sociology of Sport Journal},
\emph{34}(3), 259--269.
doi:\href{https://doi.org/10.1123/ssj.2016-0111}{10.1123/ssj.2016-0111}

\hypertarget{ref-Sanders2012}{}
Sanders, M. A., Shirk, S. D., Burgin, C. J., \& Martin, L. L. (2012).
The gargle effect. \emph{Psychological Science}, \emph{23}(12),
1470--1472.
doi:\href{https://doi.org/10.1177/0956797612450034}{10.1177/0956797612450034}

\hypertarget{ref-Sanderson2015}{}
Sanderson, J., \& Gramlich, K. (2015). ``You go girl!'': Twitter and
conversations about sport culture and gender. \emph{Sociology of Sport
Journal}, \emph{33}(2), 113--123.
doi:\href{https://doi.org/10.1123/ssj.2015-0048}{10.1123/ssj.2015-0048}

\hypertarget{ref-Sandvik2017}{}
Sandvik, M. R., Strandbu, Å., \& Loland, S. (2017). Talking doping: A
frame analysis of communication about doping among talented, young,
Norwegian road cyclists. \emph{Sociology of Sport Journal},
\emph{34}(2), 195--204.
doi:\href{https://doi.org/10.1123/ssj.2016-0073}{10.1123/ssj.2016-0073}

\hypertarget{ref-Santos2012}{}
Santos, A. S., Garcia-Marques, L., Mackie, D. M., Ferreira, M. B.,
Payne, B. K., \& Moreira, S. (2012). Implicit open-mindedness: Evidence
for and limits on stereotype malleability. \emph{Journal of Experimental
Social Psychology}, \emph{48}(6), 1257--1266.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.013}{10.1016/j.jesp.2012.05.013}

\hypertarget{ref-Santos2017}{}
Santos, C. E., Goldstein, A. L., \& Tracey, T. J. G. (2017). Development
and evaluation of the gender expression attitudes towards transgender
clients scale. \emph{The Counseling Psychologist}, \emph{45}(3),
353--386.
doi:\href{https://doi.org/10.1177/0011000017702966}{10.1177/0011000017702966}

\hypertarget{ref-Sapieja2011}{}
Sapieja, K. M., Dunn, J. G., \& Holt, N. L. (2011). Perfectionism and
perceptions of parenting styles in male youth soccer. \emph{Journal of
Sport and Exercise Psychology}, \emph{33}(1), 20--39.
doi:\href{https://doi.org/10.1123/jsep.33.1.20}{10.1123/jsep.33.1.20}

\hypertarget{ref-Sathyan2012}{}
Sathyan, T., Shuttleworth, R., Hedley, M., \& Davids, K. (2012).
Validity and reliability of a radio positioning system for tracking
athletes in indoor and outdoor team sports. \emph{Behavior Research
Methods}, \emph{44}(4), 1108--1114.
doi:\href{https://doi.org/10.3758/s13428-012-0192-2}{10.3758/s13428-012-0192-2}

\hypertarget{ref-Sauer2017}{}
Sauer, J. D., Palmer, M. A., \& Brewer, N. (2017). Mock-Juror
Evaluations of Traditional and Ratings-Based Eyewitness Identification
Evidence. \emph{Law and Human Behavior}, \emph{41}(4), 375--384.
doi:\href{https://doi.org/10.1037/lhb0000235}{10.1037/lhb0000235}

\hypertarget{ref-Sauerland2012}{}
Sauerland, M., Sagana, A., \& Sporer, S. L. (2012). Assessing
nonchoosers' eyewitness identification accuracy from photographic
showups by using confidence and response times. \emph{Law and Human
Behavior}, \emph{36}(5), 394--403.
doi:\href{https://doi.org/10.1037/h0093926}{10.1037/h0093926}

\hypertarget{ref-Savani2017}{}
Savani, K., \& Job, V. (2017). Reverse ego-depletion: Acts of
self-control can improve subsequent performance in Indian cultural
contexts. \emph{Journal of Personality and Social Psychology},
\emph{113}(4), 589--607.
doi:\href{https://doi.org/10.1037/pspi0000099}{10.1037/pspi0000099}

\hypertarget{ref-Savine2012}{}
Savine, A. C., \& Braver, T. S. (2012). RETRACTED ARTICLE: Local and
global effects of motivation on cognitive control. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, \emph{12}(4), 692--718.
doi:\href{https://doi.org/10.3758/s13415-012-0113-y}{10.3758/s13415-012-0113-y}

\hypertarget{ref-Scannell2017}{}
Scannell, L., \& Gifford, R. (2017). Place attachment enhances
psychological need satisfaction. \emph{Environment and Behavior},
\emph{49}(4), 359--389.
doi:\href{https://doi.org/10.1177/0013916516637648}{10.1177/0013916516637648}

\hypertarget{ref-Schacht2017a}{}
Schacht, R. L., Brooner, R. K., King, V. L., Kidorf, M. S., \& Peirce,
J. M. (2017). Incentivizing attendance to prolonged exposure for PTSD
with opioid use disorder patients: A randomized controlled trial.
\emph{Journal of Consulting and Clinical Psychology}, \emph{85}(7),
689--701.
doi:\href{https://doi.org/10.1037/ccp0000208}{10.1037/ccp0000208}

\hypertarget{ref-Schaumberg2017}{}
Schaumberg, R. L., \& Mullen, E. (2017). From incidental harms to moral
elevation: The positive effect of experiencing unintentional,
uncontrollable, and unavoidable harms on perceived moral character.
\emph{Journal of Experimental Social Psychology}, \emph{73}, 86--96.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.016}{10.1016/j.jesp.2017.06.016}

\hypertarget{ref-Schenke2017}{}
Schenke, K., Nguyen, T., Watts, T. W., Sarama, J., \& Clements, D. H.
(2017). Differential effects of the classroom on African American and
non-African American's mathematics achievement. \emph{Journal of
Educational Psychology}, \emph{109}(6), 794--811.
doi:\href{https://doi.org/10.1037/edu0000165}{10.1037/edu0000165}

\hypertarget{ref-Scherer2016}{}
Scherer, J., Koch, J., \& Holt, N. L. (2016). The uses of an inner-city
sport-for-development program: Dispatches from the (real) creative
class. \emph{Sociology of Sport Journal}, \emph{33}(3), 185--198.
doi:\href{https://doi.org/10.1123/ssj.2015-0145}{10.1123/ssj.2015-0145}

\hypertarget{ref-Schmidt2017}{}
Schmidt, M. F., Gonzalez-Cabrera, I., \& Tomasello, M. (2017).
Children's developing metaethical judgments. \emph{Journal of
Experimental Child Psychology}, \emph{164}, 163--177.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.008}{10.1016/j.jecp.2017.07.008}

\hypertarget{ref-Schmidt2017a}{}
Schmidt, N. B., Norr, A. M., Allan, N. P., Raines, A. M., \& Capron, D.
W. (2017). A randomized clinical trial targeting anxiety sensitivity for
patients with suicidal ideation. \emph{Journal of Consulting and
Clinical Psychology}, \emph{85}(6), 596--610.
doi:\href{https://doi.org/10.1037/ccp0000195}{10.1037/ccp0000195}

\hypertarget{ref-Schmittat2016}{}
Schmittat, S. M., \& Englich, B. (2016). If you judge, investigate!
Responsibility reduces confirmatory information processing in legal
experts. \emph{Psychology, Public Policy, and Law}, \emph{22}(4),
386--400.
doi:\href{https://doi.org/10.1037/law0000097}{10.1037/law0000097}

\hypertarget{ref-Schmitter-Edgecombe2012}{}
Schmitter-Edgecombe, M., McAlister, C., \& Weakley, A. (2012).
Naturalistic assessment of everyday functioning in individuals with mild
cognitive impairment: the day-out task. \emph{Neuropsychology},
\emph{26}(5), 631--41.
doi:\href{https://doi.org/10.1037/a0029352}{10.1037/a0029352}

\hypertarget{ref-Schneider2012}{}
Schneider, D. W., \& Anderson, J. R. (2012). Modeling fan effects on the
time course of associative recognition. \emph{Cognitive Psychology},
\emph{64}(3), 127--160.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.11.001}{10.1016/j.cogpsych.2011.11.001}

\hypertarget{ref-Schnotz2017}{}
Schnotz, W., Wagner, I., Ullrich, M., Horz, H., \& McElvany, N. (2017).
Development of students' text-picture integration and reading competence
across grades 5--7 in a three-tier secondary school system: A
longitudinal study. \emph{Contemporary Educational Psychology},
\emph{51}, 152--169.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.06.003}{10.1016/j.cedpsych.2017.06.003}

\hypertarget{ref-Schock2012}{}
Schock, J., Cortese, M. J., \& Khanna, M. M. (2012). Imageability
estimates for 3,000 disyllabic words. \emph{Behavior Research Methods},
\emph{44}(2), 374--379.
doi:\href{https://doi.org/10.3758/s13428-011-0162-0}{10.3758/s13428-011-0162-0}

\hypertarget{ref-Schock2012a}{}
Schock, J., Cortese, M. J., Khanna, M. M., \& Toppi, S. (2012). Age of
acquisition estimates for 3,000 disyllabic words. \emph{Behavior
Research Methods}, \emph{44}(4), 971--977.
doi:\href{https://doi.org/10.3758/s13428-012-0209-x}{10.3758/s13428-012-0209-x}

\hypertarget{ref-Scholz2017}{}
Scholz, A., Krems, J. F., \& Jahn, G. (2017). Watching diagnoses
develop: Eye movements reveal symptom processing during diagnostic
reasoning. \emph{Psychonomic Bulletin \& Review}, \emph{24}(5),
1398--1412.
doi:\href{https://doi.org/10.3758/s13423-017-1294-8}{10.3758/s13423-017-1294-8}

\hypertarget{ref-SchreiberCompo2017}{}
Schreiber Compo, N., Carol, R. N., Evans, J. R., Pimentel, P., Holness,
H., Nichols-Lopez, K., \ldots{} Furton, K. G. (2017). Witness memory and
alcohol: The effects of state-dependent recall. \emph{Law and Human
Behavior}, \emph{41}(2), 202--215.
doi:\href{https://doi.org/10.1037/lhb0000224}{10.1037/lhb0000224}

\hypertarget{ref-Schriber2016}{}
Schriber, R. A., Chung, J. M., Sorensen, K. S., \& Robins, R. W. (2016).
Dispositional contempt: A first look at the contemptuous person.
\emph{Journal of Personality and Social Psychology}, \emph{00}(00), 00.
doi:\href{https://doi.org/10.1037/pspp0000101}{10.1037/pspp0000101}

\hypertarget{ref-Schroder2012}{}
Schroder, H. S., Moran, T. P., Moser, J. S., \& Altmann, E. M. (2012).
When the rules are reversed: Action-monitoring consequences of reversing
stimulus--response mappings. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{12}(4), 629--643.
doi:\href{https://doi.org/10.3758/s13415-012-0105-y}{10.3758/s13415-012-0105-y}

\hypertarget{ref-Schroder2012a}{}
Schröder, A., Gemballa, T., Ruppin, S., \& Wartenburger, I. (2012).
German norms for semantic typicality, age of acquisition, and concept
familiarity. \emph{Behavior Research Methods}, \emph{44}(2), 380--394.
doi:\href{https://doi.org/10.3758/s13428-011-0164-y}{10.3758/s13428-011-0164-y}

\hypertarget{ref-Schry2012}{}
Schry, A. R., Roberson-Nay, R., \& White, S. W. (2012). Measuring social
anxiety in college students: A comprehensive evaluation of the
psychometric properties of the SPAI-23. \emph{Psychological Assessment},
\emph{24}(4), 846--854.
doi:\href{https://doi.org/10.1037/a0027398}{10.1037/a0027398}

\hypertarget{ref-Schutte2017}{}
Schutte, I., Kenemans, J. L., \& Schutter, D. J. L. G. (2017).
Resting-state theta/beta EEG ratio is associated with reward- and
punishment-related reversal learning. \emph{Cognitive, Affective, \&
Behavioral Neuroscience}, \emph{17}(4), 754--763.
doi:\href{https://doi.org/10.3758/s13415-017-0510-3}{10.3758/s13415-017-0510-3}

\hypertarget{ref-Schuurman2016}{}
Schuurman, N. K., Ferrer, E., Boer-Sonnenschein, M. de, \& Hamaker, E.
L. (2016). How to compare cross-lagged associations in a multilevel
autoregressive model. \emph{Psychological Methods}, \emph{21}(2),
206--221.
doi:\href{https://doi.org/10.1037/met0000062}{10.1037/met0000062}

\hypertarget{ref-Schwartz}{}
Schwartz, S. H., Cieciuch, J., Vecchione, M., Davidov, E., Fischer, R.,
Beierlein, C., \ldots{} Konty, M. (2012). Refining the theory of basic
individual values. \emph{Journal of Personality and Social Psychology},
\emph{103}(4), 663--688.
doi:\href{https://doi.org/10.1037/a0029393}{10.1037/a0029393}

\hypertarget{ref-Schweitzer2011}{}
Schweitzer, N. J., Saks, M. J., Murphy, E. R., Roskies, A. L.,
Sinnott-Armstrong, W., \& Gaudet, L. M. (2011). Neuroimages as evidence
in a mens rea defense: No impact. \emph{Psychology, Public Policy, and
Law}, \emph{17}(3), 357--393.
doi:\href{https://doi.org/10.1037/a0023581}{10.1037/a0023581}

\hypertarget{ref-Schwinger2012}{}
Schwinger, M., \& Wild, E. (2012). Prevalence, stability, and
functionality of achievement goal profiles in mathematics from third to
seventh grade. \emph{Contemporary Educational Psychology}, \emph{37}(1),
1--13.
doi:\href{https://doi.org/10.1016/j.cedpsych.2011.08.001}{10.1016/j.cedpsych.2011.08.001}

\hypertarget{ref-Scurich2012}{}
Scurich, N., Monahan, J., \& John, R. S. (2012). Innumeracy and
unpacking: Bridging the nomothetic/idiographic divide in violence risk
assessment. \emph{Law and Human Behavior}, \emph{36}(6), 548--554.
doi:\href{https://doi.org/10.1037/h0093994}{10.1037/h0093994}

\hypertarget{ref-Searston2016}{}
Searston, R. A., \& Tangen, J. M. (2017). The style of a stranger:
Identification expertise generalizes to coarser level categories.
\emph{Psychonomic Bulletin \& Review}, \emph{24}(4), 1324--1329.
doi:\href{https://doi.org/10.3758/s13423-016-1211-6}{10.3758/s13423-016-1211-6}

\hypertarget{ref-Seebauer2017}{}
Seebauer, S., Fleiß, J., \& Schweighart, M. (2017). A household is not a
person: consistency of pro-environmental behavior in adult couples and
the accuracy of proxy-reports. \emph{Environment and Behavior},
\emph{49}(6), 603--637.
doi:\href{https://doi.org/10.1177/0013916516663796}{10.1177/0013916516663796}

\hypertarget{ref-Segal2017}{}
Segal, D., Shalev, L., \& Mashal, N. (2017). Attenuated hemispheric
asymmetry in metaphor processing among adults with ADHD.
\emph{Neuropsychology}, \emph{31}(6), 636--647.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/neu0000370}{http://dx.doi.org/10.1037/neu0000370}

\hypertarget{ref-Seibert2017}{}
Seibert, S. E., Sargent, L. D., Kraimer, M. L., \& Kiazad, K. (2017).
Linking developmental experiences to leader effectiveness and
promotability: The mediating role of leadership self-efficacy and mentor
network. \emph{Personnel Psychology}, \emph{70}(2), 357--397.
doi:\href{https://doi.org/10.1111/peps.12145}{10.1111/peps.12145}

\hypertarget{ref-Selmeczy2017}{}
Selmeczy, D., \& Dobbins, I. (2017). Ignoring memory hints: The stubborn
influence of environmental cues on recognition memory. \emph{Journal of
Experimental Psychology: Learning Memory and Cognition}, \emph{1}(2),
1448--1469.
doi:\href{https://doi.org/10.1037/xlm0000383}{10.1037/xlm0000383}

\hypertarget{ref-Semmelmann2017}{}
Semmelmann, K., \& Weigelt, S. (2017). Online psychophysics: Reaction
time effects in cognitive experiments. \emph{Behavior Research Methods},
\emph{49}(4), 1241--1260.
doi:\href{https://doi.org/10.3758/s13428-016-0783-4}{10.3758/s13428-016-0783-4}

\hypertarget{ref-Sense2013}{}
Sense, F., Morey, C. C., Prince, M., Heathcote, A., \& Morey, R. D.
(2017). Opportunity for verbalization does not improve visual change
detection performance: A state-trace analysis. \emph{Behavior Research
Methods}, \emph{49}(3), 853--862.
doi:\href{https://doi.org/10.3758/s13428-016-0741-1}{10.3758/s13428-016-0741-1}

\hypertarget{ref-Sentse2017}{}
Sentse, M., Kretschmer, T., Haan, A. de, \& Prinzie, P. (2017). Conduct
problem trajectories between age 4 and 17 and their association with
behavioral adjustment in emerging adulthood. \emph{Journal of Youth and
Adolescence}, \emph{46}(8), 1633--1642.
doi:\href{https://doi.org/10.1007/s10964-016-0476-4}{10.1007/s10964-016-0476-4}

\hypertarget{ref-Seo2012}{}
Seo, M.-G., Taylor, M. S., Hill, N. S., Zhang, X., Tesluk, P. E., \&
Lorinkova, N. M. (2012). The role of affect and leadership during
organizational change. \emph{Personnel Psychology}, \emph{65}(1),
121--165.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01240.x}{10.1111/j.1744-6570.2011.01240.x}

\hypertarget{ref-Seo2010}{}
Seo, Y. S. (2010). Individualism, collectivism, client expression, and
counselor effectiveness among south Korean international students.
\emph{The Counseling Psychologist}, \emph{38}(6), 824--847.
doi:\href{https://doi.org/10.1177/0011000009359947}{10.1177/0011000009359947}

\hypertarget{ref-Serrien2012}{}
Serrien, D. J., Sovijärvi-Spapé, M. M., \& Farnsworth, B. (2012).
Bimanual control processes and the role of handedness.
\emph{Neuropsychology}, \emph{26}(6), 802--807.
doi:\href{https://doi.org/10.1037/a0030154}{10.1037/a0030154}

\hypertarget{ref-Seto2017}{}
Seto, M. C., \& Eke, A. W. (2017). Correlates of admitted sexual
interest in children among individuals convicted of child pornography
offenses. \emph{Law and Human Behavior}, \emph{41}(3), 305--313.
doi:\href{https://doi.org/10.1037/lhb0000240}{10.1037/lhb0000240}

\hypertarget{ref-Seto2012}{}
Seto, M. C., Wood, J. M., Babchishin, K. M., \& Flynn, S. (2012). Online
solicitation offenders are different from child pornography offenders
and lower risk contact sexual offenders. \emph{Law and Human Behavior},
\emph{36}(4), 320--330.
doi:\href{https://doi.org/10.1037/h0093925}{10.1037/h0093925}

\hypertarget{ref-Sexton2017}{}
Sexton, N. J., \& Cooper, R. P. (2017). Task inhibition, conflict, and
the n-2 repetition cost: A combined computational and empirical
approach. \emph{Cognitive Psychology}, \emph{94}, 1--25.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.01.003}{10.1016/j.cogpsych.2017.01.003}

\hypertarget{ref-Shadish2011}{}
Shadish, W. R., Galindo, R., Wong, V. C., Steiner, P. M., \& Cook, T. D.
(2011). A randomized experiment comparing random and cutoff-based
assignment. \emph{Psychological Methods}, \emph{16}(2), 179--191.
doi:\href{https://doi.org/10.1037/a0023345}{10.1037/a0023345}

\hypertarget{ref-Shakib2011}{}
Shakib, S., Veliz, P., Dunbar, M. D., \& Sabo, D. (2011). Athletics as a
source for social status among youth: Examining variation by gender,
race/ethnicity, and socioeconomic status. \emph{Sociology of Sport
Journal}, \emph{28}(3), 303--328.
doi:\href{https://doi.org/10.1123/ssj.28.3.303}{10.1123/ssj.28.3.303}

\hypertarget{ref-Shaw2017}{}
Shaw, T., Campbell, M., Runions, K., \& Zubrick, S. R. (2017).
Properties of the DASS-21 in an Australian community adolescent
population. \emph{Journal of Clinical Psychology}, \emph{73}(7),
879--892.
doi:\href{https://doi.org/10.1002/jclp.22376}{10.1002/jclp.22376}

\hypertarget{ref-Shea2017}{}
Shea, M., Wong, Y. J., Nguyen, K. K., \& Baghdasarian, S. (2017).
College women's subjective femininity stress, gender solidarity, and
psychological help-seeking intentions. \emph{The Counseling
Psychologist}, \emph{45}(3), 438--461.
doi:\href{https://doi.org/10.1177/0011000017701820}{10.1177/0011000017701820}

\hypertarget{ref-Sheeber2012}{}
Sheeber, L. B., Seeley, J. R., Feil, E. G., Davis, B., Sorensen, E.,
Kosty, D. B., \& Lewinsohn, P. M. (2012). Development and pilot
evaluation of an Internet-facilitated cognitive-behavioral intervention
for maternal depression. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(5), 739--749.
doi:\href{https://doi.org/10.1037/a0028820}{10.1037/a0028820}

\hypertarget{ref-Shen2017}{}
Shen, L., \& Hsee, C. K. (2017). Numerical nudging: Using an
accelerating score to enhance performance. \emph{Psychological Science},
\emph{28}(8), 1077--1086.
doi:\href{https://doi.org/10.1177/0956797617700497}{10.1177/0956797617700497}

\hypertarget{ref-Shen-Miller2012}{}
Shen-Miller, D. S., Forrest, L., \& Burt, M. (2012). Contextual
influences on faculty diversity conceptualizations when working with
trainee competence problems. \emph{The Counseling Psychologist},
\emph{40}(8), 1181--1219.
doi:\href{https://doi.org/10.1177/0011000011431832}{10.1177/0011000011431832}

\hypertarget{ref-Sheremata2016}{}
Sheremata, S. L., \& Shomstein, S. (2017). Task set induces dynamic
reallocation of resources in visual short-term memory. \emph{Psychonomic
Bulletin \& Review}, \emph{24}(4), 1113--1120.
doi:\href{https://doi.org/10.3758/s13423-016-1181-8}{10.3758/s13423-016-1181-8}

\hypertarget{ref-Sherman2012}{}
Sherman, G. D., Haidt, J., \& Clore, G. L. (2012). The faintest speck of
dirt. \emph{Psychological Science}, \emph{23}(12), 1506--1514.
doi:\href{https://doi.org/10.1177/0956797612445318}{10.1177/0956797612445318}

\hypertarget{ref-Sherry2013}{}
Sherry, S. B., Mackinnon, S. P., Macneil, M. A., \& Fitzpatrick, S.
(2013). Discrepancies confer vulnerability to depressive symptoms: A
three-wave longitudinal study. \emph{Journal of Counseling Psychology},
\emph{60}(1), 112--126.
doi:\href{https://doi.org/10.1037/a0030439}{10.1037/a0030439}

\hypertarget{ref-Shigemoto2017}{}
Shigemoto, Y., Low, B., Borowa, D., \& Robitschek, C. (2017). Function
of personal growth initiative on posttraumatic growth, posttraumatic
stress, and depression over and above adaptive and maladaptive
rumination. \emph{Journal of Clinical Psychology}, \emph{73}(9),
1126--1145.
doi:\href{https://doi.org/10.1002/jclp.22423}{10.1002/jclp.22423}

\hypertarget{ref-Shin2016}{}
Shin, R. Q., Smith, L. C., Welch, J. C., \& Ezeofor, I. (2016). Is
Allison more likely than Lakisha to receive a callback from counseling
professionals? A racism audit study. \emph{The Counseling Psychologist},
\emph{44}(8), 1187--1211.
doi:\href{https://doi.org/10.1177/0011000016668814}{10.1177/0011000016668814}

\hypertarget{ref-Shiyko2017}{}
Shiyko, M. P., Perkins, S., \& Caldwell, L. (2017). Feasibility and
adherence paradigm to ecological momentary assessments in urban minority
youth. \emph{Psychological Assessment}, \emph{29}(7), 926--934.
doi:\href{https://doi.org/10.1037/pas0000386}{10.1037/pas0000386}

\hypertarget{ref-Shrout2017}{}
Shrout, P. E., \& Yip-Bannicq, M. (2017). Inferences about competing
measures based on patterns of binary significance tests are
questionable. \emph{Psychological Methods}, \emph{22}(1), 84--93.
doi:\href{https://doi.org/10.1037/met0000109}{10.1037/met0000109}

\hypertarget{ref-Shulman2017}{}
Shulman, S., Seiffge-Krenke, I., \& Walsh, S. D. (2017). Is sexual
activity during adolescence good for future romantic relationships?
\emph{Journal of Youth and Adolescence}, \emph{46}(9), 1867--1877.
doi:\href{https://doi.org/10.1007/s10964-017-0699-z}{10.1007/s10964-017-0699-z}

\hypertarget{ref-Sibley2012}{}
Sibley, M. H., Pelham, W. E., Molina, B. S. G., Gnagy, E. M., Waxmonsky,
J. G., Waschbusch, D. A., \ldots{} Kuriyan, A. B. (2012). When
diagnosing ADHD in young adults emphasize informant reports, DSM items,
and impairment. \emph{Journal of Consulting and Clinical Psychology},
\emph{80}(6), 1052--1061.
doi:\href{https://doi.org/10.1037/a0029098}{10.1037/a0029098}

\hypertarget{ref-Siddique2012}{}
Siddique, J., Chung, J. Y., Brown, C. H., \& Miranda, J. (2012).
Comparative effectiveness of medication versus cognitive-behavioral
therapy in a randomized controlled trial of low-income young minority
women with depression. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(6), 995--1006.
doi:\href{https://doi.org/10.1037/a0030452}{10.1037/a0030452}

\hypertarget{ref-Sigelman2012}{}
Sigelman, C. K. (2012). Rich man, poor man: Developmental differences in
attributions and perceptions. \emph{Journal of Experimental Child
Psychology}, \emph{113}(3), 415--429.
doi:\href{https://doi.org/10.1016/j.jecp.2012.06.011}{10.1016/j.jecp.2012.06.011}

\hypertarget{ref-Silinskas2017}{}
Silinskas, G., Pakarinen, E., Lerkkanen, M.-K., Poikkeus, A.-M., \&
Nurmi, J.-E. (2017). Classroom interaction and literacy activities in
kindergarten: Longitudinal links to Grade 1 readers at risk and not at
risk of reading difficulties. \emph{Contemporary Educational
Psychology}, \emph{51}, 321--335.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.09.002}{10.1016/j.cedpsych.2017.09.002}

\hypertarget{ref-DaSilva2017}{}
Silva, A. N. da, Vasco, A. B., \& Watson, J. C. (2017). Alexithymia and
emotional processing: A mediation model. \emph{Journal of Clinical
Psychology}, \emph{73}(9), 1196--1205.
doi:\href{https://doi.org/10.1002/jclp.22422}{10.1002/jclp.22422}

\hypertarget{ref-Silva2017b}{}
Silva, K., Patrianakos, J., Chein, J., \& Steinberg, L. (2017). Joint
effects of peer presence and fatigue on risk and reward processing in
late adolescence. \emph{Journal of Youth and Adolescence}, \emph{46}(9),
1878--1890.
doi:\href{https://doi.org/10.1007/s10964-017-0690-8}{10.1007/s10964-017-0690-8}

\hypertarget{ref-Silva2017a}{}
Silva, N. D., Dillon, F. R., Verdejo, T. R., Sanchez, M., \& De La Rosa,
M. (2017). Acculturative stress, psychological distress, and religious
coping among Latina young adult immigrants. \emph{The Counseling
Psychologist}, \emph{45}(2), 213--236.
doi:\href{https://doi.org/10.1177/0011000017692111}{10.1177/0011000017692111}

\hypertarget{ref-Silva2017}{}
Silva, S., Inácio, F., Folia, V., \& Petersson, K. M. (2017). Eye
movements in implicit artificial grammar learning. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{43}(9),
1387--1402.
doi:\href{https://doi.org/10.1037/xlm0000350}{10.1037/xlm0000350}

\hypertarget{ref-Silver2017}{}
Silver, J. R., \& Silver, E. (2017). Why are conservatives more punitive
than liberals? A moral foundations approach. \emph{Law and Human
Behavior}, \emph{41}(3), 258--272.
doi:\href{https://doi.org/10.1037/lhb0000232}{10.1037/lhb0000232}

\hypertarget{ref-Simms2018}{}
Simms, N. K., Frausel, R. R., \& Richland, L. E. (2018). Working memory
predicts children's analogical reasoning. \emph{Journal of Experimental
Child Psychology}, \emph{166}, 160--177.
doi:\href{https://doi.org/10.1016/j.jecp.2017.08.005}{10.1016/j.jecp.2017.08.005}

\hypertarget{ref-Sinai2012}{}
Sinai, M., Kaplan, A., \& Flum, H. (2012). Promoting identity
exploration within the school curriculum: A design-based study in a
Junior High literature lesson in Israel. \emph{Contemporary Educational
Psychology}, \emph{37}(3), 195--205.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.01.006}{10.1016/j.cedpsych.2012.01.006}

\hypertarget{ref-Sirna2016}{}
Sirna, K. M. (2016). Road cycling over forty: Fitness, friends, and
fondos. \emph{Sociology of Sport Journal}, \emph{33}(3), 230--239.
doi:\href{https://doi.org/10.1123/ssj.2015-0138}{10.1123/ssj.2015-0138}

\hypertarget{ref-Sitzmann2017}{}
Sitzmann, T., \& Bell, B. S. (2017). The dynamic effects of subconscious
goal pursuit on resource allocation, task performance, and goal
abandonment. \emph{Organizational Behavior and Human Decision
Processes}, \emph{138}, 1--14.
doi:\href{https://doi.org/10.1016/j.obhdp.2016.11.001}{10.1016/j.obhdp.2016.11.001}

\hypertarget{ref-Skopp2012a}{}
Skopp, N. A., Bush, N. E., Vogel, D. L., Wade, N. G., Sirotin, A. P.,
Mccann, R. A., \& Metzger-Abamukong, M. J. (2012a). Development and
initial testing of a measure of public and self-stigma in the military.
\emph{Journal of Clinical Psychology}, \emph{68}(9), 1036--1047.
doi:\href{https://doi.org/10.1002/jclp.21889}{10.1002/jclp.21889}

\hypertarget{ref-Skopp2012}{}
Skopp, N. A., Swanson, R., Luxton, D. D., Reger, M. A., Trofimovich, L.,
First, M., \ldots{} Gahm, G. A. (2012b). An examination of the
diagnostic efficiency of post-deployment mental health screens.
\emph{Journal of Clinical Psychology}, \emph{68}(12), 1253--1265.
doi:\href{https://doi.org/10.1002/jclp.21887}{10.1002/jclp.21887}

\hypertarget{ref-Slater2017}{}
Slater, A., Halliwell, E., Jarman, H., \& Gaskin, E. (2017). More than
just child's play?: An experimental investigation of the impact of an
appearance-focused internet game on body image and career aspirations of
young girls. \emph{Journal of Youth and Adolescence}, \emph{46}(9),
2047--2059.
doi:\href{https://doi.org/10.1007/s10964-017-0659-7}{10.1007/s10964-017-0659-7}

\hypertarget{ref-Sleep2016}{}
Sleep, C. E., Sellbom, M., Campbell, W. K., \& Miller, J. D. (2016).
Narcissism and response validity: Do individuals with narcissistic
features underreport psychopathology? \emph{Psychological Assessment},
\emph{October 31}(8), 1--6.
doi:\href{https://doi.org/http://dx.doi.org/10.1037/pas0000413}{http://dx.doi.org/10.1037/pas0000413}

\hypertarget{ref-Slepian2017}{}
Slepian, M. L., Chun, J. S., \& Mason, M. F. (2017). The experience of
secrecy. \emph{Journal of Personality and Social Psychology},
\emph{113}(1), 1--33.
doi:\href{https://doi.org/10.1037/pspa0000085}{10.1037/pspa0000085}

\hypertarget{ref-Sluss2012}{}
Sluss, D. M., \& Thompson, B. S. (2012). Socializing the newcomer: The
mediating role of leader-member exchange. \emph{Organizational Behavior
and Human Decision Processes}, \emph{119}(1), 114--125.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.05.005}{10.1016/j.obhdp.2012.05.005}

\hypertarget{ref-Smalls2017}{}
Smalls, B. L., Gregory, C. M., Zoller, J. S., \& Egede, L. E. (2017).
Conceptualizing the effect of community and neighborhood factors on Type
2 Diabetes health outcomes. \emph{Environment and Behavior},
\emph{49}(5), 560--582.
doi:\href{https://doi.org/10.1177/0013916516652440}{10.1177/0013916516652440}

\hypertarget{ref-Smith2011a}{}
Smith, A. L., Ntoumanis, N., Duda, J. L., \& Vansteenkiste, M. (2011).
Goal striving, coping, and well-being: A prospective investigation of
the self-concordance model in sport. \emph{Journal of Sport and Exercise
Psychology}, \emph{33}(1), 124--145.
doi:\href{https://doi.org/10.1123/jsep.33.1.124}{10.1123/jsep.33.1.124}

\hypertarget{ref-Smith2011}{}
Smith, J. C. S., Vogel, D. L., Madon, S., \& Edwards, S. R. (2011). The
power of touch: Nonverbal communication within married dyads. \emph{The
Counseling Psychologist}, \emph{39}(5), 764--787.
doi:\href{https://doi.org/10.1177/0011000010385849}{10.1177/0011000010385849}

\hypertarget{ref-Smith2012b}{}
Smith, J. R., Louis, W. R., Terry, D. J., Greenaway, K. H., Clarke, M.
R., \& Cheng, X. (2012a). Congruent or conflicted? The impact of
injunctive and descriptive norms on environmental intentions.
\emph{Journal of Environmental Psychology}, \emph{32}(4), 353--361.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.06.001}{10.1016/j.jenvp.2012.06.001}

\hypertarget{ref-Smith2012a}{}
Smith, M. M., Mills, J. A., Epping, E. A., Westervelt, H. J., \&
Paulsen, J. S. (2012). Depressive symptom severity is related to poorer
cognitive performance in prodromal Huntington disease.
\emph{Neuropsychology}, \emph{26}(5), 664--669.
doi:\href{https://doi.org/10.1037/a0029218}{10.1037/a0029218}

\hypertarget{ref-Smith2012}{}
Smith, N. G., Keller, B. K., Mollen, D., Bledsoe, M. L., Buhin, L.,
Edwards, L. M., \ldots{} Yakushko, O. (2012b). Voices of early career
psychologists in division 17, the Society of Counseling Psychology.
\emph{The Counseling Psychologist}, \emph{40}(6), 794--825.
doi:\href{https://doi.org/10.1177/0011000011417145}{10.1177/0011000011417145}

\hypertarget{ref-Smith2017}{}
Smith, N., Kinnafick, F., Cooley, S. J., \& Sandal, G. M. (2017).
Reported growth following mountaineering expeditions: The role of
personality and perceived stress. \emph{Environment and Behavior},
\emph{49}(8), 933--955.
doi:\href{https://doi.org/10.1177/0013916516670447}{10.1177/0013916516670447}

\hypertarget{ref-Snedeker2012}{}
Snedeker, J., Geren, J., \& Shafto, C. L. (2012). Disentangling the
effects of cognitive development and linguistic expertise: A
longitudinal study of the acquisition of English in
internationally-adopted children. \emph{Cognitive Psychology},
\emph{65}(1), 39--76.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.01.004}{10.1016/j.cogpsych.2012.01.004}

\hypertarget{ref-Socia2016}{}
Socia, K. M., \& Harris, A. J. (2016). Evaluating public perceptions of
the risk presented by registered sex offenders: Evidence of crime
control theater? \emph{Psychology, Public Policy, and Law},
\emph{22}(4), 375--385.
doi:\href{https://doi.org/10.1037/law0000081}{10.1037/law0000081}

\hypertarget{ref-Soltanlou2017}{}
Soltanlou, M., Artemenko, C., Dresler, T., Haeussinger, F. B.,
Fallgatter, A. J., Ehlis, A.-C., \& Nuerk, H.-C. (2017). Increased
arithmetic complexity is associated with domain-general but not
domain-specific magnitude processing in children: A simultaneous
fNIRS-EEG study. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, 724--736.
doi:\href{https://doi.org/10.3758/s13415-017-0508-x}{10.3758/s13415-017-0508-x}

\hypertarget{ref-Sonnentag2012}{}
Sonnentag, S., \& Grant, A. M. (2012). Doing good at work feels good at
home, but not right away: When and why perceived prosocial impact
predicts positive affect. \emph{Personnel Psychology}, \emph{65}(3),
495--530.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01251.x}{10.1111/j.1744-6570.2012.01251.x}

\hypertarget{ref-Sparks2017}{}
Sparks, C., Lonsdale, C., Dimmock, J., \& Jackson, B. (2017). An
Intervention to improve teachers' interpersonally involving
instructional practices in high school physical education: Implications
for student relatedness support and in-class experiences. \emph{Journal
of Sport and Exercise Psychology}, \emph{39}(2), 120--133.
doi:\href{https://doi.org/10.1123/jsep.2016-0198}{10.1123/jsep.2016-0198}

\hypertarget{ref-Spinath2012}{}
Spinath, B., \& Steinmayr, R. (2012). The roles of competence beliefs
and goal orientations for change in intrinsic motivation. \emph{Journal
of Educational Psychology}, \emph{104}(4), 1135--1148.
doi:\href{https://doi.org/10.1037/a0028115}{10.1037/a0028115}

\hypertarget{ref-Spitz2012}{}
Spitz, G., Ponsford, J. L., Rudzki, D., \& Maller, J. J. (2012).
Association between cognitive performance and functional outcome
following traumatic brain injury: A longitudinal multilevel examination.
\emph{Neuropsychology}, \emph{26}(5), 604--612.
doi:\href{https://doi.org/10.1037/a0029239}{10.1037/a0029239}

\hypertarget{ref-Sporrel2017}{}
Sporrel, K., Caljouw, S. R., \& Withagen, R. (2017). Children prefer a
nonstandardized to a standardized jumping stone configuration: Playing
time and judgments. \emph{Journal of Environmental Psychology},
\emph{53}, 131--137.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.07.006}{10.1016/j.jenvp.2017.07.006}

\hypertarget{ref-Spranger2012}{}
Spranger, J. L., Colarelli, S. M., Dimotakis, N., Jacob, A. C., \&
Arvey, R. D. (2012). Effects of kin density within family-owned
businesses. \emph{Organizational Behavior and Human Decision Processes},
\emph{119}(2), 151--162.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.07.001}{10.1016/j.obhdp.2012.07.001}

\hypertarget{ref-Staats2012}{}
Staats, B. R., Milkman, K. L., \& Fox, C. R. (2012). The team scaling
fallacy: Underestimating the declining efficiency of larger teams.
\emph{Organizational Behavior and Human Decision Processes},
\emph{118}(2), 132--142.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.03.002}{10.1016/j.obhdp.2012.03.002}

\hypertarget{ref-Staiano2012}{}
Staiano, A. E., Baker, C. M., \& Calvert, S. L. (2012). Dietary digital
diaries. \emph{Environment and Behavior}, \emph{44}(5), 695--712.
doi:\href{https://doi.org/10.1177/0013916511403623}{10.1177/0013916511403623}

\hypertarget{ref-Stallen2012}{}
Stallen, M., De Dreu, C. K. W., Shalvi, S., Smidts, A., \& Sanfey, A. G.
(2012). The herding hormone. \emph{Psychological Science},
\emph{23}(11), 1288--1292.
doi:\href{https://doi.org/10.1177/0956797612446026}{10.1177/0956797612446026}

\hypertarget{ref-Stanley2016}{}
Stanley, C., \& Byrne, M. D. (2016). Comparing vector-based and Bayesian
memory models using large-scale datasets: User-generated hashtag and tag
prediction on Twitter and Stack Overflow. \emph{Psychological Methods},
\emph{21}(4), 542--565.
doi:\href{https://doi.org/10.1037/met0000098}{10.1037/met0000098}

\hypertarget{ref-Stanton2017}{}
Stanton, S. C. E., Campbell, L., \& Pink, J. C. (2017). Benefits of
positive relationship experiences for avoidantly attached individuals.
\emph{Journal of Personality and Social Psychology}, \emph{113}(4),
568--588.
doi:\href{https://doi.org/10.1037/pspi0000098}{10.1037/pspi0000098}

\hypertarget{ref-Steenbergen2012}{}
Steenbergen, P., Buitenweg, J. R., Trojan, J., Heide, E. M. van der,
Heuvel, T. van den, Flor, H., \& Veltink, P. H. (2012). A system for
inducing concurrent tactile and nociceptive sensations at the same site
using electrocutaneous stimulation. \emph{Behavior Research Methods},
\emph{44}(4), 924--933.
doi:\href{https://doi.org/10.3758/s13428-012-0216-y}{10.3758/s13428-012-0216-y}

\hypertarget{ref-Stefanelli2017}{}
Stefanelli, A., \& Seidl, R. (2017). Opinions on contested energy
infrastructures: An empirically based simulation approach. \emph{Journal
of Environmental Psychology}, \emph{52}, 204--217.
doi:\href{https://doi.org/10.1016/j.jenvp.2016.06.003}{10.1016/j.jenvp.2016.06.003}

\hypertarget{ref-Stein2012}{}
Stein, G. L., Gonzalez, L. M., \& Huq, N. (2012). Cultural stressors and
the hopelessness model of depressive symptoms in Latino adolescents.
\emph{Journal of Youth and Adolescence}, \emph{41}(10), 1339--1349.
doi:\href{https://doi.org/10.1007/s10964-012-9765-8}{10.1007/s10964-012-9765-8}

\hypertarget{ref-Steiner2012}{}
Steiner, E. T., \& Ashcraft, M. H. (2012). Three brief assessments of
math achievement. \emph{Behavior Research Methods}, \emph{44}(4),
1101--1107.
doi:\href{https://doi.org/10.3758/s13428-011-0185-6}{10.3758/s13428-011-0185-6}

\hypertarget{ref-Steiner2010}{}
Steiner, P. M., Cook, T. D., Shadish, W. R., \& Clark, M. H. (2010). The
importance of covariate selection in controlling for selection bias in
observational studies. \emph{Psychological Methods}, \emph{15}(3),
250--267. doi:\href{https://doi.org/10.1037/a0018719}{10.1037/a0018719}

\hypertarget{ref-Stenling2016}{}
Stenling, A., \& Tafvelin, S. (2016). Transfer of training after an
organizational intervention in Swedish sports clubs: a
self-determination theory perspective. \emph{Journal of Sport and
Exercise Psychology}, \emph{38}(5), 493--504.
doi:\href{https://doi.org/10.1123/jsep.2016-0084}{10.1123/jsep.2016-0084}

\hypertarget{ref-Stephens2012}{}
Stephens, N. M., Townsend, S. S. M., Markus, H. R., \& Phillips, L. T.
(2012). A cultural mismatch: Independent cultural norms produce greater
increases in cortisol and more negative emotions among first-generation
college students. \emph{Journal of Experimental Social Psychology},
\emph{48}(6), 1389--1393.
doi:\href{https://doi.org/10.1016/j.jesp.2012.07.008}{10.1016/j.jesp.2012.07.008}

\hypertarget{ref-Stephens2017a}{}
Stephens, S., Cantor, J. M., Goodwill, A. M., \& Seto, M. C. (2017).
Multiple indicators of sexual interest in prepubescent or pubescent
children as predictors of sexual recidivism. \emph{Journal of Consulting
and Clinical Psychology}, \emph{85}(6), 585--595.
doi:\href{https://doi.org/10.1037/ccp0000194}{10.1037/ccp0000194}

\hypertarget{ref-Sticca2017}{}
Sticca, F., Goetz, T., Nett, U. E., Hubbard, K., \& Haag, L. (2017).
Short- and long-term effects of over-reporting of grades on academic
self-concept and achievement. \emph{Journal of Educational Psychology},
\emph{109}(6), 842--854.
doi:\href{https://doi.org/10.1037/edu0000174}{10.1037/edu0000174}

\hypertarget{ref-Stice2017a}{}
Stice, E., Rohde, P., Shaw, H., \& Gau, J. M. (2017). Clinician-led,
peer-led, and internet-delivered dissonance-based eating disorder
prevention programs: Acute effectiveness of these delivery modalities.
\emph{Journal of Consulting and Clinical Psychology}, \emph{85}(9),
883--895.
doi:\href{https://doi.org/10.1037/ccp0000211}{10.1037/ccp0000211}

\hypertarget{ref-Stites2017}{}
Stites, M. C., Payne, B. R., \& Federmeier, K. D. (2017). Getting ahead
of yourself: Parafoveal word expectancy modulates the N400 during
sentence reading. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{17}(3), 475--490.
doi:\href{https://doi.org/10.3758/s13415-016-0492-6}{10.3758/s13415-016-0492-6}

\hypertarget{ref-Stocco2012}{}
Stocco, A., Lebiere, C., O'Reilly, R. C., \& Anderson, J. R. (2012).
Distinct contributions of the caudate nucleus, rostral prefrontal
cortex, and parietal cortex to the execution of instructed tasks.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{12}(4),
611--628.
doi:\href{https://doi.org/10.3758/s13415-012-0117-7}{10.3758/s13415-012-0117-7}

\hypertarget{ref-Stolzenberg2017}{}
Stolzenberg, S. N., McWilliams, K., \& Lyon, T. D. (2017). Spatial
language, question type, and young children's ability to describe
clothing: Legal and developmental implications. \emph{Law and Human
Behavior}, \emph{41}(4), 398--409.
doi:\href{https://doi.org/10.1037/lhb0000237}{10.1037/lhb0000237}

\hypertarget{ref-Strunk2012}{}
Strunk, D. R., Cooper, A. A., Ryan, E. T., DeRubeis, R. J., \& Hollon,
S. D. (2012). The process of change in cognitive therapy for depression
when combined with antidepressant medication: Predictors of early
intersession symptom gains. \emph{Journal of Consulting and Clinical
Psychology}, \emph{80}(5), 730--738.
doi:\href{https://doi.org/10.1037/a0029281}{10.1037/a0029281}

\hypertarget{ref-Stupnisky2012}{}
Stupnisky, R. H., Perry, R. P., Hall, N. C., \& Guay, F. (2012).
Examining perceived control level and instability as predictors of
first-year college students' academic achievement. \emph{Contemporary
Educational Psychology}, \emph{37}(2), 81--90.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.01.001}{10.1016/j.cedpsych.2012.01.001}

\hypertarget{ref-Sugiyama2012}{}
Sugiyama, T., Okely, A. D., Masters, J. M., \& Moore, G. T. (2012).
Attributes of child care centers and outdoor play areas associated with
preschoolers' physical activity and sedentary behavior.
\emph{Environment and Behavior}, \emph{44}(3), 334--349.
doi:\href{https://doi.org/10.1177/0013916510393276}{10.1177/0013916510393276}

\hypertarget{ref-Sui2016}{}
Sui, Y., Wang, H., Kirkman, B. L., \& Li, N. (2016). Understanding the
curvilinear relationships between LMX differentiation and team
coordination and performance. \emph{Personnel Psychology}, \emph{69}(3),
559--597.
doi:\href{https://doi.org/10.1111/peps.12115}{10.1111/peps.12115}

\hypertarget{ref-Sullivan2012}{}
Sullivan, D., Landau, M. J., Kay, A. C., \& Rothschild, Z. K. (2012).
Collectivism and the meaning of suffering. \emph{Journal of Personality
and Social Psychology}, \emph{103}(6), 1023--1039.
doi:\href{https://doi.org/10.1037/a0030382}{10.1037/a0030382}

\hypertarget{ref-Sumanth2011}{}
Sumanth, J. J., \& Cable, D. M. (2011). Status and organizational entry:
How organizational and individual status affect justice perceptions of
hiring systems. \emph{Personnel Psychology}, \emph{64}(4), 963--1000.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01233.x}{10.1111/j.1744-6570.2011.01233.x}

\hypertarget{ref-Sun2016}{}
Sun, G., Zhang, L., Vine, S. J., \& Wilson, M. R. (2016). The quiet eye
provides preplanning and online control support for interceptive task
performance. \emph{Journal of Sport and Exercise Psychology},
\emph{38}(5), 458--469.
doi:\href{https://doi.org/10.1123/jsep.2016-0012}{10.1123/jsep.2016-0012}

\hypertarget{ref-Sunderland2017}{}
Sunderland, M., Slade, T., Krueger, R. F., Markon, K. E., Patrick, C.
J., \& Kramer, M. D. (2017). Efficiently measuring dimensions of the
externalizing spectrum model: Development of the Externalizing Spectrum
Inventory-Computerized Adaptive Test (ESI-CAT). \emph{Psychological
Assessment}, \emph{29}(7), 868--880.
doi:\href{https://doi.org/10.1037/pas0000384}{10.1037/pas0000384}

\hypertarget{ref-Sutter2012}{}
Sutter, C., Zöllig, J., Allemand, M., \& Martin, M. (2012). Sleep
quality and cognitive function in healthy old age: The moderating role
of subclinical depression. \emph{Neuropsychology}, \emph{26}(6),
768--775. doi:\href{https://doi.org/10.1037/a0030033}{10.1037/a0030033}

\hypertarget{ref-Sutton2012}{}
Sutton, J. E., Twyman, A. D., Joanisse, M. F., \& Newcombe, N. S.
(2012). Geometry three ways: An fMRI investigation of geometric
information processing during reorientation. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{38}(6),
1530--1541.
doi:\href{https://doi.org/10.1037/a0028456}{10.1037/a0028456}

\hypertarget{ref-Swanson2012}{}
Swanson, H. L., Orosco, M. J., \& Lussier, C. M. (2012). Cognition and
literacy in English language learners at risk for reading disabilities.
\emph{Journal of Educational Psychology}, \emph{104}(2), 302--320.
doi:\href{https://doi.org/10.1037/a0026225}{10.1037/a0026225}

\hypertarget{ref-Sweet2017}{}
Sweet, D. M., Meissner, C. A., \& Atkinson, D. J. (2017). Assessing law
enforcement performance in behavior-based threat detection tasks
involving a concealed weapon or device. \emph{Law and Human Behavior},
\emph{41}(5), 411--421.
doi:\href{https://doi.org/10.1037/lhb0000243}{10.1037/lhb0000243}

\hypertarget{ref-Switzer2017}{}
Switzer, D., \& Vedlitz, A. (2017). Green colored lenses: Worldviews and
motivated reasoning in the case of local water scarcity.
\emph{Environment and Behavior}, \emph{49}(7), 719--744.
doi:\href{https://doi.org/10.1177/0013916516669391}{10.1177/0013916516669391}

\hypertarget{ref-Szojka2017}{}
Szojka, Z. A., Andrews, S. J., Lamb, M. E., Stolzenberg, S. N., \& Lyon,
T. D. (2017). Challenging the credibility of alleged victims of child
sexual abuse in Scottish courts. \emph{Psychology, Public Policy, and
Law}, \emph{23}(2), 200--210.
doi:\href{https://doi.org/10.1037/law0000117}{10.1037/law0000117}

\hypertarget{ref-Szto2016}{}
Szto, C. (2016). \#LOL at multiculturalism: Reactions to hockey night in
Canada Punjabi from the twitterverse. \emph{Sociology of Sport Journal},
\emph{33}(3), 208--218.
doi:\href{https://doi.org/10.1123/ssj.2015-0160}{10.1123/ssj.2015-0160}

\hypertarget{ref-Szymanski2011}{}
Szymanski, D. M., \& Obiri, O. (2011). Do religious coping styles
moderate or mediate the external and internalized racism-distress links?
\emph{Counseling Psychologist}, \emph{39}(3), 438--462.
doi:\href{https://doi.org/10.1177/0011000010378895}{10.1177/0011000010378895}

\hypertarget{ref-Szymanski2010}{}
Szymanski, D. M., \& Sung, M. R. (2010). Minority stress and
psychological distress among Asian American sexual minority persons
1\(\Psi\)7. \emph{The Counseling Psychologist}, \emph{38}(6), 848--872.
doi:\href{https://doi.org/10.1177/0011000010366167}{10.1177/0011000010366167}

\hypertarget{ref-Szymanski2017}{}
Szymanski, D. M., Mikorski, R., \& Carretta, R. F. (2017). Heterosexism
and LGB positive identity: roles of coping and personal growth
initiative. \emph{The Counseling Psychologist}, \emph{45}(2), 294--319.
doi:\href{https://doi.org/10.1177/0011000017697195}{10.1177/0011000017697195}

\hypertarget{ref-Tadmor2012}{}
Tadmor, C. T., Hong, Y.-y., Chao, M. M., Wiruchnipawan, F., \& Wang, W.
(2012). Multicultural experiences reduce intergroup bias through
epistemic unfreezing. \emph{Journal of Personality and Social
Psychology}, \emph{103}(5), 750--772.
doi:\href{https://doi.org/10.1037/a0029719}{10.1037/a0029719}

\hypertarget{ref-Tajrobehkar2016}{}
Tajrobehkar, B. (2016). Flirting with the judges: Bikini fitness
competitors' negotiations of femininity in bodybuilding competitions.
\emph{Sociology of Sport Journal}, \emph{33}(4), 294--304.
doi:\href{https://doi.org/10.1123/ssj.2015-0152}{10.1123/ssj.2015-0152}

\hypertarget{ref-Takahashi2012}{}
Takahashi, N. (2012). Japanese children's understanding of notational
systems. \emph{Journal of Experimental Child Psychology}, \emph{113}(4),
457--468.
doi:\href{https://doi.org/10.1016/j.jecp.2012.07.008}{10.1016/j.jecp.2012.07.008}

\hypertarget{ref-Takano2017}{}
Takano, K., Ueno, M., Moriya, J., Mori, M., Nishiguchi, Y., \& Raes, F.
(2017). Unraveling the linguistic nature of specific autobiographical
memories using a computerized classification algorithm. \emph{Behavior
Research Methods}, \emph{49}(3), 835--852.
doi:\href{https://doi.org/10.3758/s13428-016-0753-x}{10.3758/s13428-016-0753-x}

\hypertarget{ref-Takeuchi2012}{}
Takeuchi, R., Chen, Z., \& Cheung, S. Y. (2012). Applying uncertainty
management theory to employee voice behavior: An integrative
investigation. \emph{Personnel Psychology}, \emph{65}(2), 283--323.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01247.x}{10.1111/j.1744-6570.2012.01247.x}

\hypertarget{ref-Tamminen2016}{}
Tamminen, K. A., Gaudreau, P., McEwen, C. E., \& Crocker, P. R. (2016).
Interpersonal Emotion Regulation Among Adolescent Athletes: A Bayesian
Multilevel Model Predicting Sport Enjoyment and Commitment.
\emph{Journal of Sport and Exercise Psychology}, \emph{38}(6), 541--555.
doi:\href{https://doi.org/10.1123/jsep.2015-0189}{10.1123/jsep.2015-0189}

\hypertarget{ref-Tang2017}{}
Tang, S., Morewedge, C. M., Larrick, R. P., \& Klein, J. G. (2017).
Disloyalty aversion: Greater reluctance to bet against close others than
the self. \emph{Organizational Behavior and Human Decision Processes},
\emph{140}, 1--13.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.02.001}{10.1016/j.obhdp.2017.02.001}

\hypertarget{ref-Tangirala2012}{}
Tangirala, S., \& Ramanujam, R. (2012). Ask and you shall hear (but not
always): Examining the relationship between manager consultation and
employee voice. \emph{Personnel Psychology}, \emph{65}(2), 251--282.
doi:\href{https://doi.org/10.1111/j.1744-6570.2012.01248.x}{10.1111/j.1744-6570.2012.01248.x}

\hypertarget{ref-Tanner2012}{}
Tanner, M. A., Gray, J. J., \& Haaga, D. A. (2012). Association of
cotherapy supervision with client outcomes, attrition, and trainee
effectiveness in a psychotherapy training clinic. \emph{Journal of
Clinical Psychology}, \emph{68}(12), 1241--1252.
doi:\href{https://doi.org/10.1002/jclp.21902}{10.1002/jclp.21902}

\hypertarget{ref-Tardiff2017}{}
Tardiff, N., Bascandziev, I., Sandor, K., Carey, S., \& Zaitchik, D.
(2017). Some consequences of normal aging for generating conceptual
explanations: A case study of vitalist biology. \emph{Cognitive
Psychology}, \emph{95}, 145--163.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.04.004}{10.1016/j.cogpsych.2017.04.004}

\hypertarget{ref-Taylor2012}{}
Taylor, E. G., \& Ahn, W. K. (2012). Causal imprinting in causal
structure learning. \emph{Cognitive Psychology}, \emph{65}(3), 381--413.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.07.001}{10.1016/j.cogpsych.2012.07.001}

\hypertarget{ref-Thibodeau2017}{}
Thibodeau, P. H., Crow, L., \& Flusberg, S. J. (2017). The metaphor
police: A case study of the role of metaphor in explanation.
\emph{Psychonomic Bulletin \& Review}, \emph{24}(5), 1375--1386.
doi:\href{https://doi.org/10.3758/s13423-016-1192-5}{10.3758/s13423-016-1192-5}

\hypertarget{ref-Thiruchselvam2012}{}
Thiruchselvam, R., Hajcak, G., \& Gross, J. J. (2012). Looking inward.
\emph{Psychological Science}, \emph{23}(12), 1461--1466.
doi:\href{https://doi.org/10.1177/0956797612449838}{10.1177/0956797612449838}

\hypertarget{ref-Thoman2012}{}
Thoman, D. B., Sansone, C., Fraughton, T., \& Pasupathi, M. (2012). How
students socially evaluate interest: Peer responsiveness influences
evaluation and maintenance of interest. \emph{Contemporary Educational
Psychology}, \emph{37}(4), 254--265.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.04.001}{10.1016/j.cedpsych.2012.04.001}

\hypertarget{ref-Thomas2013}{}
Thomas, K. J., Loughran, T. A., \& Piquero, A. R. (2013). Do individual
characteristics explain variation in sanction risk updating among
serious juvenile offenders? Advancing the logic of differential
deterrence. \emph{Law and Human Behavior}, \emph{37}(1), 10--21.
doi:\href{https://doi.org/10.1037/h0093990}{10.1037/h0093990}

\hypertarget{ref-Thompson2011}{}
Thompson, M. N., \& Subich, L. M. (2011). Social status identity:
Antecedents and vocational outcomes. \emph{The Counseling Psychologist},
\emph{39}(5), 735--763.
doi:\href{https://doi.org/10.1177/0011000010389828}{10.1177/0011000010389828}

\hypertarget{ref-Thompson2012}{}
Thompson, R. L., Vinson, D. P., Woll, B., \& Vigliocco, G. (2012). The
road to language learning is iconic. \emph{Psychological Science},
\emph{23}(12), 1443--1448.
doi:\href{https://doi.org/10.1177/0956797612459763}{10.1177/0956797612459763}

\hypertarget{ref-Thompson2011a}{}
Thompson, V. A., Prowse Turner, J. A., \& Pennycook, G. (2011).
Intuition, reason, and metacognition. \emph{Cognitive Psychology},
\emph{63}(3), 107--140.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.06.001}{10.1016/j.cogpsych.2011.06.001}

\hypertarget{ref-Thrash2017}{}
Thrash, T. M., Maruskin, L. A., Moldovan, E. G., Oleynick, V. C., \&
Belzak, W. C. (2017). Writer--reader contagion of inspiration and
related states: Conditional process analyses within a cross-classified
writer × reader framework. \emph{Journal of Personality and Social
Psychology}, \emph{113}(3), 466--491.
doi:\href{https://doi.org/10.1037/pspp0000094}{10.1037/pspp0000094}

\hypertarget{ref-Tifferet2017}{}
Tifferet, S., \& Vilnai-Yavetz, I. (2017). Phytophilia and service
atmospherics: The effect of indoor plants on consumers.
\emph{Environment and Behavior}, \emph{49}(7), 814--844.
doi:\href{https://doi.org/10.1177/0013916516669390}{10.1177/0013916516669390}

\hypertarget{ref-Tillman2017}{}
Tillman, K. A., Marghetis, T., Barner, D., \& Srinivasan, M. (2017).
Today is tomorrow's yesterday: Children's acquisition of deictic time
words. \emph{Cognitive Psychology}, \emph{92}, 87--100.
doi:\href{https://doi.org/10.1016/j.cogpsych.2016.10.003}{10.1016/j.cogpsych.2016.10.003}

\hypertarget{ref-Tobler2012}{}
Tobler, C., Visschers, V. H. M., \& Siegrist, M. (2012). Addressing
climate change: Determinants of consumers' willingness to act and to
support policy measures. \emph{Journal of Environmental Psychology},
\emph{32}(3), 197--207.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.02.001}{10.1016/j.jenvp.2012.02.001}

\hypertarget{ref-Todd2012}{}
Todd, A. R., \& Galinsky, A. D. (2012). The reciprocal link between
multiculturalism and perspective-taking: How ideological and
self-regulatory approaches to managing diversity reinforce each other.
\emph{Journal of Experimental Social Psychology}, \emph{48}(6),
1394--1398.
doi:\href{https://doi.org/10.1016/j.jesp.2012.07.007}{10.1016/j.jesp.2012.07.007}

\hypertarget{ref-Todd2011a}{}
Todd, N. R., \& Abrams, E. M. (2011). White dialectics: A new framework
for theory, research, and practice with white students 1\(\psi\)7.
\emph{The Counseling Psychologist}, \emph{39}(3), 353--395.
doi:\href{https://doi.org/10.1177/0011000010377665}{10.1177/0011000010377665}

\hypertarget{ref-Toet2012}{}
Toet, A., \& Schaik, M. G. van. (2012). Effects of signals of disorder
on fear of crime in real and virtual environments. \emph{Journal of
Environmental Psychology}, \emph{32}(3), 260--276.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.04.001}{10.1016/j.jenvp.2012.04.001}

\hypertarget{ref-Tolar2012}{}
Tolar, T. D., Fuchs, L., Cirino, P. T., Fuchs, D., Hamlett, C. L., \&
Fletcher, J. M. (2012). Predicting development of mathematical word
problem solving across the intermediate grades. \emph{Journal of
Educational Psychology}, \emph{104}(4), 1083--1093.
doi:\href{https://doi.org/10.1037/a0029020}{10.1037/a0029020}

\hypertarget{ref-Tomlin2017}{}
Tomlin, D., Nedic, A., Prentice, D. A., Holmes, P., \& Cohen, J. D.
(2017). The integration of social influence and reward: Computational
approaches and neural evidence. \emph{Cognitive, Affective, \&
Behavioral Neuroscience}, \emph{17}(4), 784--808.
doi:\href{https://doi.org/10.3758/s13415-017-0512-1}{10.3758/s13415-017-0512-1}

\hypertarget{ref-Tonidandel2009}{}
Tonidandel, S., LeBreton, J. M., \& Johnson, J. W. (2009). Determining
the statistical significance of relative weights. \emph{Psychological
Methods}, \emph{14}(4), 387--399.
doi:\href{https://doi.org/10.1037/a0017735}{10.1037/a0017735}

\hypertarget{ref-Tonkin2012}{}
Tonkin, M., Howells, K., Ferguson, E., Clark, A., Newberry, M., \&
Schalast, N. (2012). Lost in translation? Psychometric properties and
construct validity of the English Essen Climate Evaluation Schema
(EssenCES) social climate questionnaire. \emph{Psychological
Assessment}, \emph{24}(3), 573--580.
doi:\href{https://doi.org/10.1037/a0026267}{10.1037/a0026267}

\hypertarget{ref-Tormala2012}{}
Tormala, Z. L., Jia, J. S., \& Norton, M. I. (2012). The preference for
potential. \emph{Journal of Personality and Social Psychology},
\emph{103}(4), 567--583.
doi:\href{https://doi.org/10.1037/a0029227}{10.1037/a0029227}

\hypertarget{ref-Towfigh2011}{}
Towfigh, E., \& Glöckner, A. (2011). GAME OVER: Empirical support for
soccer bets regulation. \emph{Psychology, Public Policy, and Law},
\emph{17}(3), 475--506.
doi:\href{https://doi.org/10.1037/a0023402}{10.1037/a0023402}

\hypertarget{ref-Toyama2017}{}
Toyama, A., Katahira, K., \& Ohira, H. (2017). A simple computational
algorithm of model-based choice preference. \emph{Cognitive, Affective,
\& Behavioral Neuroscience}, \emph{17}(4), 764--783.
doi:\href{https://doi.org/10.3758/s13415-017-0511-2}{10.3758/s13415-017-0511-2}

\hypertarget{ref-Treble-barna2017}{}
Treble-Barna, A., Schultz, H., Minich, N., Taylor, H. G., Yeates, K. O.,
Stancin, T., \& Wade, S. L. (2017). Long-term classroom functioning and
its association with neuropsychological and academic performance
following traumatic brain injury during early childhood.
\emph{Neuropsychology}, \emph{31}(5), 486--498.
doi:\href{https://doi.org/10.1037/neu0000325}{10.1037/neu0000325}

\hypertarget{ref-Triana2017}{}
Triana, M. D. C., Richard, O. C., \& Yücel, İ. (2017). Status
incongruence and supervisor gender as moderators of the transformational
leadership to subordinate affective organizational commitment
relationship. \emph{Personnel Psychology}, \emph{70}(2), 429--467.
doi:\href{https://doi.org/10.1111/peps.12154}{10.1111/peps.12154}

\hypertarget{ref-Troister2012}{}
Troister, T., \& Holden, R. R. (2012). A two-year prospective study of
psychache and its relationship to suicidality among high-risk
undergraduates. \emph{Journal of Clinical Psychology}, \emph{68}(9),
1019--1027.
doi:\href{https://doi.org/10.1002/jclp.21869}{10.1002/jclp.21869}

\hypertarget{ref-Trueblood2012}{}
Trueblood, J. S. (2012). Multialternative context effects obtained using
an inference task. \emph{Psychonomic Bulletin \& Review}, \emph{19}(5),
962--968.
doi:\href{https://doi.org/10.3758/s13423-012-0288-9}{10.3758/s13423-012-0288-9}

\hypertarget{ref-Truelove2012}{}
Truelove, H. B., \& Parks, C. (2012). Perceptions of behaviors that
cause and mitigate global warming and intentions to perform these
behaviors. \emph{Journal of Environmental Psychology}, \emph{32}(3),
246--259.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.04.002}{10.1016/j.jenvp.2012.04.002}

\hypertarget{ref-Tse2017}{}
Tse, C.-S., Yap, M. J., Chan, Y.-L., Sze, W. P., Shaoul, C., \& Lin, D.
(2017). The Chinese Lexicon Project: A megastudy of lexical decision
performance for 25,000+ traditional Chinese two-character compound
words. \emph{Behavior Research Methods}, \emph{49}(4), 1503--1519.
doi:\href{https://doi.org/10.3758/s13428-016-0810-5}{10.3758/s13428-016-0810-5}

\hypertarget{ref-Tucker2001}{}
Tucker, L. W., \& Parks, J. B. (2001). Effects of gender and sport type
on intercollegiate athletes' perceptions of the legitimacy of aggressive
behaviors in sport. \emph{Sociology of Sport Journal}, \emph{18}(4),
403--413.
doi:\href{https://doi.org/10.1123/ssj.18.4.403}{10.1123/ssj.18.4.403}

\hypertarget{ref-Tuliao2016}{}
Tuliao, A. P., Velasquez, P. A. E., Bello, A. M., \& Pinson, M. J. T.
(2016). Intent to seek counseling among Filipinos. \emph{The Counseling
Psychologist}, \emph{44}(3), 353--382.
doi:\href{https://doi.org/10.1177/0011000015627197}{10.1177/0011000015627197}

\hypertarget{ref-Tylka2013}{}
Tylka, T. L., \& Kroon Van Diest, A. M. (2013). The Intuitive Eating
Scale--2: Item refinement and psychometric evaluation with college women
and men. \emph{Journal of Counseling Psychology}, \emph{60}(1),
137--153. doi:\href{https://doi.org/10.1037/a0030893}{10.1037/a0030893}

\hypertarget{ref-Ullan2012}{}
Ullán, A. M., Belver, M. H., Fernández, E., Serrano, I., Delgado, J., \&
Herrero, C. (2012). Hospital designs for patients of different ages.
\emph{Environment and Behavior}, \emph{44}(5), 668--694.
doi:\href{https://doi.org/10.1177/0013916511403802}{10.1177/0013916511403802}

\hypertarget{ref-Ulset2017}{}
Ulset, V., Vitaro, F., Brendgen, M., Bekkhus, M., \& Borge, A. I.
(2017). Time spent outdoors during preschool: Links with children's
cognitive and behavioral development. \emph{Journal of Environmental
Psychology}, \emph{52}, 69--80.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.05.007}{10.1016/j.jenvp.2017.05.007}

\hypertarget{ref-Umemoto2017}{}
Umemoto, A., HajiHosseini, A., Yates, M. E., \& Holroyd, C. B. (2017).
Reward-based contextual learning supported by anterior cingulate cortex.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{17}(3),
642--651.
doi:\href{https://doi.org/10.3758/s13415-017-0502-3}{10.3758/s13415-017-0502-3}

\hypertarget{ref-Undorf2016}{}
Undorf, M., \& Zander, T. (2017). Intuition and metacognition: The
effect of semantic coherence on judgments of learning. \emph{Psychonomic
Bulletin \& Review}, \emph{24}(4), 1217--1224.
doi:\href{https://doi.org/10.3758/s13423-016-1189-0}{10.3758/s13423-016-1189-0}

\hypertarget{ref-Ung2017}{}
Ung, J. E., Dozier, M. E., Bratiotis, C., \& Ayers, C. R. (2017). An
exploratory investigation of animal hoarding symptoms in a sample of
adults diagnosed with hoarding disorder. \emph{Journal of Clinical
Psychology}, \emph{73}(9), 1114--1125.
doi:\href{https://doi.org/10.1002/jclp.22417}{10.1002/jclp.22417}

\hypertarget{ref-Unkelbach2012}{}
Unkelbach, C., Ostheimer, V., Fasold, F., \& Memmert, D. (2012). A
calibration explanation of serial position effects in evaluative
judgments. \emph{Organizational Behavior and Human Decision Processes},
\emph{119}(1), 103--113.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.06.004}{10.1016/j.obhdp.2012.06.004}

\hypertarget{ref-Unsworth2012}{}
Unsworth, N., McMillan, B. D., Brewer, G. A., \& Spillers, G. J. (2012).
Everyday attention failures: An individual differences investigation.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{38}(6), 1765--1772.
doi:\href{https://doi.org/10.1037/a0028075}{10.1037/a0028075}

\hypertarget{ref-Uren2017}{}
Uren, J., Cotton, S. M., Killackey, E., Saling, M. M., \& Allott, K.
(2017). Cognitive clusters in first-episode psychosis: Overlap with
healthy controls and relationship to concurrent and prospective symptoms
and functioning. \emph{Neuropsychology}, \emph{31}(7), 787--797.
doi:\href{https://doi.org/10.1037/neu0000367}{10.1037/neu0000367}

\hypertarget{ref-Vadasy2012}{}
Vadasy, P. F., \& Sanders, E. A. (2012). Two-year follow-up of a
kindergarten phonics intervention for English learners and native
English speakers: Contextualizing treatment impacts by classroom
literacy instruction. \emph{Journal of Educational Psychology},
\emph{104}(4), 987--1005.
doi:\href{https://doi.org/10.1037/a0028163}{10.1037/a0028163}

\hypertarget{ref-Vaid2017}{}
Vaid, U., \& Evans, G. W. (2017). Housing quality and health: An
evaluation of slum rehabilitation in India. \emph{Environment and
Behavior}, \emph{49}(7), 771--790.
doi:\href{https://doi.org/10.1177/0013916516667975}{10.1177/0013916516667975}

\hypertarget{ref-Valdez2011}{}
Valdez, C. R., Dvorscek, M. J., Budge, S. L., \& Esmond, S. (2011).
Provider perspectives about Latino patients: Determinants of care and
implications for treatment. \emph{The Counseling Psychologist},
\emph{39}(4), 497--526.
doi:\href{https://doi.org/10.1177/0011000010385012}{10.1177/0011000010385012}

\hypertarget{ref-Valentin2012}{}
Valentin, D., \& Chanquoy, L. (2012). Olfactory categorization: A
developmental study. \emph{Journal of Experimental Child Psychology},
\emph{113}(3), 337--352.
doi:\href{https://doi.org/10.1016/j.jecp.2012.05.007}{10.1016/j.jecp.2012.05.007}

\hypertarget{ref-DeValk2016}{}
Valk, J. M. de, Wnuk, E., Huisman, J. L. A., \& Majid, A. (2017).
Odor--color associations differ with verbal descriptors for odors: A
comparison of three linguistically diverse groups. \emph{Psychonomic
Bulletin \& Review}, \emph{24}(4), 1171--1179.
doi:\href{https://doi.org/10.3758/s13423-016-1179-2}{10.3758/s13423-016-1179-2}

\hypertarget{ref-VandeVondervoort2017}{}
Van de Vondervoort, J. W., \& Hamlin, J. K. (2017). Preschoolers' social
and moral judgments of third-party helpers and hinderers align with
infants' social evaluations. \emph{Journal of Experimental Child
Psychology}, \emph{164}, 136--151.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.004}{10.1016/j.jecp.2017.07.004}

\hypertarget{ref-VandenBroeck2012}{}
Van den Broeck, W., \& Geudens, A. (2012). Old and new ways to study
characteristics of reading disability: The case of the nonword-reading
deficit. \emph{Cognitive Psychology}, \emph{65}(3), 414--456.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.06.003}{10.1016/j.cogpsych.2012.06.003}

\hypertarget{ref-Darby2017}{}
Van der Meij, N., Darby, P., \& Liston, K. (2017). ``The downfall of a
man is not the end of his life'': Navigating involuntary immobility in
Ghanaian football stretching the field. \emph{Sociology of Sport
Journal}, \emph{34}(2), 183--194.
doi:\href{https://doi.org/10.1123/ssj.2016-0101}{10.1123/ssj.2016-0101}

\hypertarget{ref-VanIttersum2012}{}
Van Ittersum, K., \& Pennings, J. M. E. (2012). Attribute-value
functions as global interpretations of attribute importance.
\emph{Organizational Behavior and Human Decision Processes},
\emph{119}(1), 89--102.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.04.002}{10.1016/j.obhdp.2012.04.002}

\hypertarget{ref-VanRompay2012}{}
{\{}van Rompay\}, T. J. L., Tanja-Dijkstra, K., Verhoeven, J. W. M., \&
\{van Es\}, A. F. (2012). On store design and consumer motivation.
\emph{Environment and Behavior}, \emph{44}(6), 800--820.
doi:\href{https://doi.org/10.1177/0013916511407309}{10.1177/0013916511407309}

\hypertarget{ref-VanDaalen2017}{}
VanDaalen, R. A., \& Santos, C. E. (2017). Racism and sociopolitical
engagement among lesbian, gay, and bisexual racial/ethnic minority
adults. \emph{The Counseling Psychologist}, \emph{45}(3), 414--437.
doi:\href{https://doi.org/10.1177/0011000017699529}{10.1177/0011000017699529}

\hypertarget{ref-Vanderveen2012}{}
Vanderveen, J. W., Reddy, L. F., Veilleux, J. C., January, A. M., \&
Dilillo, D. (2012). Clinical PhD graduate student views of their
scientist-practitioner training. \emph{Journal of Clinical Psychology},
\emph{68}(9), 1048--1057.
doi:\href{https://doi.org/10.1002/jclp.21883}{10.1002/jclp.21883}

\hypertarget{ref-Vandierendonck2012}{}
Vandierendonck, A., Demanet, J., Liefooghe, B., \& Verbruggen, F.
(2012). A chain-retrieval model for voluntary task switching.
\emph{Cognitive Psychology}, \emph{65}(2), 241--283.
doi:\href{https://doi.org/10.1016/j.cogpsych.2012.04.003}{10.1016/j.cogpsych.2012.04.003}

\hypertarget{ref-Vatterott2012}{}
Vatterott, D. B., \& Vecera, S. P. (2012). Experience-dependent
attentional tuning of distractor rejection. \emph{Psychonomic Bulletin
\& Review}, \emph{19}(5), 871--878.
doi:\href{https://doi.org/10.3758/s13423-012-0280-4}{10.3758/s13423-012-0280-4}

\hypertarget{ref-Vaughn2012}{}
Vaughn, K. E., \& Rawson, K. A. (2012). When is guessing incorrectly
better than studying for enhancing memory? \emph{Psychonomic Bulletin \&
Review}, \emph{19}(5), 899--905.
doi:\href{https://doi.org/10.3758/s13423-012-0276-0}{10.3758/s13423-012-0276-0}

\hypertarget{ref-Velez2012}{}
Velez, B. L., \& Moradi, B. (2012). Workplace support, discrimination,
and person--organization fit: Tests of the theory of work adjustment
with LGB individuals. \emph{Journal of Counseling Psychology},
\emph{59}(3), 399--407.
doi:\href{https://doi.org/10.1037/a0028326}{10.1037/a0028326}

\hypertarget{ref-Velez2016}{}
Velez, B. L., \& Moradi, B. (2016). A moderated mediation test of
minority stress. \emph{The Counseling Psychologist}, \emph{44}(8),
1132--1157.
doi:\href{https://doi.org/10.1177/0011000016665467}{10.1177/0011000016665467}

\hypertarget{ref-Venables2012}{}
Venables, D., Pidgeon, N. F., Parkhill, K. A., Henwood, K. L., \&
Simmons, P. (2012). Living with nuclear power: Sense of place,
proximity, and risk perceptions in local host communities. \emph{Journal
of Environmental Psychology}, \emph{32}(4), 371--383.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.06.003}{10.1016/j.jenvp.2012.06.003}

\hypertarget{ref-Vendetti2012}{}
Vendetti, M., Knowlton, B. J., \& Holyoak, K. J. (2012). The impact of
semantic distance and induced stress on analogical reasoning: A
neurocomputational account. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, \emph{12}(4), 804--812.
doi:\href{https://doi.org/10.3758/s13415-012-0103-0}{10.3758/s13415-012-0103-0}

\hypertarget{ref-Vergara-Martinez2017}{}
Vergara-Martínez, M., Comesaña, M., \& Perea, M. (2017). The ERP
signature of the contextual diversity effect in visual word recognition.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{17}(3),
461--474.
doi:\href{https://doi.org/10.3758/s13415-016-0491-7}{10.3758/s13415-016-0491-7}

\hypertarget{ref-Viana2012}{}
Viana, A. G., \& Gratz, K. L. (2012). The role of anxiety sensitivity,
behavioral inhibition, and cognitive biases in anxiety symptoms:
Structural equation modeling of direct and indirect pathways.
\emph{Journal of Clinical Psychology}, \emph{68}(10), 1122--1141.
doi:\href{https://doi.org/10.1002/jclp.21890}{10.1002/jclp.21890}

\hypertarget{ref-Viljoen2017}{}
Viljoen, J. L., Shaffer, C. S., Gray, A. L., \& Douglas, K. S. (2017).
Are adolescent risk assessment tools sensitive to change? A framework
and examination of the SAVRY and the YLS/CMI. \emph{Law and Human
Behavior}, \emph{41}(3), 244--257.
doi:\href{https://doi.org/10.1037/lhb0000238}{10.1037/lhb0000238}

\hypertarget{ref-Vincent2012}{}
Vincent, G. M., Paiva-Salisbury, M. L., Cook, N. E., Guy, L. S., \&
Perrault, R. T. (2012). Impact of risk/needs assessment on juvenile
probation officers' decision making: Importance of implementation.
\emph{Psychology, Public Policy, and Law}, \emph{18}(4), 549--576.
doi:\href{https://doi.org/10.1037/a0027186}{10.1037/a0027186}

\hypertarget{ref-Vissers2017}{}
Vissers, W., Keijsers, G. P., Kampman, M., Hendriks, G.-J., Rijnders,
P., \& Hutschemaekers, G. J. (2017). Symptom reduction without
remoralization: A randomized, waiting-list controlled study aimed at
separating two beneficial psychotherapy outcome effects. \emph{Journal
of Clinical Psychology}, \emph{73}(7), 785--796.
doi:\href{https://doi.org/10.1002/jclp.22380}{10.1002/jclp.22380}

\hypertarget{ref-Vitaro2012}{}
Vitaro, F., Boivin, M., Brendgen, M., Girard, A., \& Dionne, G. (2012).
Social experiences in kindergarten and academic achievement in grade 1:
A monozygotic twin difference study. \emph{Journal of Educational
Psychology}, \emph{104}(2), 366--380.
doi:\href{https://doi.org/10.1037/a0026879}{10.1037/a0026879}

\hypertarget{ref-Vlaev2017}{}
Vlaev, I., Crockett, M. J., Clark, L., Müller, U., \& Robbins, T. W.
(2017). Serotonin enhances the impact of health information on food
choice. \emph{Cognitive, Affective, \& Behavioral Neuroscience},
\emph{17}(3), 542--553.
doi:\href{https://doi.org/10.3758/s13415-016-0496-2}{10.3758/s13415-016-0496-2}

\hypertarget{ref-Voelkle2012}{}
Voelkle, M. C., Oud, J. H. L., Davidov, E., \& Schmidt, P. (2012). An
SEM approach to continuous time modeling of panel data: Relating
authoritarianism and anomia. \emph{Psychological Methods}, \emph{17}(2),
176--192. doi:\href{https://doi.org/10.1037/a0027543}{10.1037/a0027543}

\hypertarget{ref-Vogel2010}{}
Vogel, D. L., Shechtman, Z., \& Wade, N. G. (2010). The Role of public
and self-stigma in predicting attitudes toward group counseling.
\emph{The Counseling Psychologist}, \emph{38}(7), 904--922.
doi:\href{https://doi.org/10.1177/0011000010368297}{10.1177/0011000010368297}

\hypertarget{ref-Vogel2017}{}
Vogel, D. L., Strass, H. A., Heath, P. J., Al-Darmaki, F. R., Armstrong,
P. I., Baptista, M. N., \ldots{} Zlati, A. (2017). Stigma of seeking
psychological services: Examining college students across ten
countries/regions. \emph{The Counseling Psychologist}, \emph{45}(2),
170--192.
doi:\href{https://doi.org/10.1177/0011000016671411}{10.1177/0011000016671411}

\hypertarget{ref-Vollet2017}{}
Vollet, J. W., Kindermann, T. A., \& Skinner, E. A. (2017). In peer
matters, teachers matter: Peer group influences on students' engagement
depend on teacher involvement. \emph{Journal of Educational Psychology},
\emph{109}(5), 635--652.
doi:\href{https://doi.org/10.1037/edu0000172}{10.1037/edu0000172}

\hypertarget{ref-VonHolzen2012}{}
Von Holzen, K., \& Mani, N. (2012). Language nonselective lexical access
in bilingual toddlers. \emph{Journal of Experimental Child Psychology},
\emph{113}(4), 569--586.
doi:\href{https://doi.org/10.1016/j.jecp.2012.08.001}{10.1016/j.jecp.2012.08.001}

\hypertarget{ref-Voss2017}{}
Voss, T., Wagner, W., Klusmann, U., Trautwein, U., \& Kunter, M. (2017).
Changes in beginning teachers' classroom management knowledge and
emotional exhaustion during the induction phase. \emph{Contemporary
Educational Psychology}, \emph{51}, 170--184.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.08.002}{10.1016/j.cedpsych.2017.08.002}

\hypertarget{ref-Vrij2012}{}
Vrij, A., Mann, S., Jundi, S., Hope, L., \& Leal, S. (2012). Can I take
your picture? Undercover interviewing to detect deception.
\emph{Psychology, Public Policy, and Law}, \emph{18}(2), 231--244.
doi:\href{https://doi.org/10.1037/a0025670}{10.1037/a0025670}

\hypertarget{ref-Wachi2017}{}
Wachi, T., Kuraishi, H., Watanabe, K., Otsuka, Y., Yokota, K., \& Lamb,
M. E. (2017). Police officers' ability to detect lies within a deception
paradigm. \emph{Psychology, Public Policy, and Law}, \emph{23}(3),
301--311.
doi:\href{https://doi.org/10.1037/law0000124}{10.1037/law0000124}

\hypertarget{ref-Waiyavutti2012}{}
Waiyavutti, C., Johnson, W., \& Deary, I. J. (2012). Do personality
scale items function differently in people with high and low IQ?
\emph{Psychological Assessment}, \emph{24}(3), 545--555.
doi:\href{https://doi.org/10.1037/a0026266}{10.1037/a0026266}

\hypertarget{ref-Wakslak2012}{}
Wakslak, C. J. (2012). The experience of cognitive dissonance in
important and trivial domains: A Construal-Level Theory approach.
\emph{Journal of Experimental Social Psychology}, \emph{48}(6),
1361--1364.
doi:\href{https://doi.org/10.1016/j.jesp.2012.05.011}{10.1016/j.jesp.2012.05.011}

\hypertarget{ref-Walk2005}{}
Walk, S. R., \& Wiersma, L. D. (2005). Construct validity of the risk,
pain, and injury questionnaire. \emph{Sociology of Sport Journal},
\emph{22}(4), 433--446.
doi:\href{https://doi.org/10.1123/ssj.22.4.433}{10.1123/ssj.22.4.433}

\hypertarget{ref-Walters2012}{}
Walters, G. D. (2012a). Psychopathy and crime: Testing the incremental
validity of PCL-R-measured psychopathy as a predictor of general and
violent recidivism. \emph{Law and Human Behavior}, \emph{36}(5),
404--412. doi:\href{https://doi.org/10.1037/h0093928}{10.1037/h0093928}

\hypertarget{ref-Walters2012a}{}
Walters, G. D. (2012b). Substance abuse and criminal thinking: Testing
the countervailing, mediation, and specificity hypotheses. \emph{Law and
Human Behavior}, \emph{36}(6), 506--512.
doi:\href{https://doi.org/10.1037/h0093936}{10.1037/h0093936}

\hypertarget{ref-Wang2016}{}
Wang, B., Yan, C., Wang, Z., Olivers, C. N. L., \& Theeuwes, J. (2017).
Adverse orienting effects on visual working memory encoding and
maintenance. \emph{Psychonomic Bulletin \& Review}, \emph{24}(4),
1261--1267.
doi:\href{https://doi.org/10.3758/s13423-016-1205-4}{10.3758/s13423-016-1205-4}

\hypertarget{ref-Wang2016a}{}
Wang, H.-C., Savage, G., Gaskell, M. G., Paulin, T., Robidoux, S., \&
Castles, A. (2017). Bedding down new words: Sleep promotes the emergence
of lexical competition in visual word recognition. \emph{Psychonomic
Bulletin \& Review}, \emph{24}(4), 1186--1193.
doi:\href{https://doi.org/10.3758/s13423-016-1182-7}{10.3758/s13423-016-1182-7}

\hypertarget{ref-Wang2016b}{}
Wang, J. C., Morin, A. J., Ryan, R. M., \& Liu, W. (2016). Students'
motivational profiles in the physical education context. \emph{Journal
of Sport and Exercise Psychology}, \emph{38}(6), 612--630.
doi:\href{https://doi.org/10.1123/jsep.2016-0153}{10.1123/jsep.2016-0153}

\hypertarget{ref-Wang2012a}{}
Wang, K. T., Heppner, P. P., Fu, C.-C., Zhao, R., Li, F., \& Chuang,
C.-C. (2012). Profiles of acculturative adjustment patterns among
Chinese international students. \emph{Journal of Counseling Psychology},
\emph{59}(3), 424--436.
doi:\href{https://doi.org/10.1037/a0028532}{10.1037/a0028532}

\hypertarget{ref-Wang2012b}{}
Wang, L., Northcraft, G. B., \& Van Kleef, G. A. (2012). Beyond
negotiated outcomes: The hidden costs of anger expression in dyadic
negotiation. \emph{Organizational Behavior and Human Decision
Processes}, \emph{119}(1), 54--63.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.05.002}{10.1016/j.obhdp.2012.05.002}

\hypertarget{ref-Wang2017}{}
Wang, M.-T., Chow, A., \& Amemiya, J. (2017). Who wants to play? Sport
motivation trajectories, sport participation, and the development of
depressive symptoms. \emph{Journal of Youth and Adolescence},
\emph{46}(9), 1982--1998.
doi:\href{https://doi.org/10.1007/s10964-017-0649-9}{10.1007/s10964-017-0649-9}

\hypertarget{ref-Wang2012}{}
Wang, Q., Chan, H.-W., \& Lin, L. (2012). Antecedents of Chinese
parents' autonomy support and psychological control: the interplay
between parents' self-development socialization goals and adolescents'
school performance. \emph{Journal of Youth and Adolescence},
\emph{41}(11), 1442--1454.
doi:\href{https://doi.org/10.1007/s10964-012-9760-0}{10.1007/s10964-012-9760-0}

\hypertarget{ref-Wang2012c}{}
Wang, W.-c., \& Yonelinas, A. P. (2012). Familiarity is related to
conceptual implicit memory: An examination of individual differences.
\emph{Psychonomic Bulletin \& Review}, \emph{19}(6), 1154--1164.
doi:\href{https://doi.org/10.3758/s13423-012-0298-7}{10.3758/s13423-012-0298-7}

\hypertarget{ref-Warburton2017}{}
Warburton, V. E. (2017). Peer and teacher influences on the motivational
climate in physical education: A longitudinal perspective on achievement
goal adoption. \emph{Contemporary Educational Psychology}, \emph{51},
303--314.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.08.001}{10.1016/j.cedpsych.2017.08.001}

\hypertarget{ref-Ward2008}{}
Ward, R. E. (2008). Athletic expenditures and the academic mission of
American schools: a group-level analysis. \emph{Sociology of Sport
Journal}, \emph{25}(4), 560--578.
doi:\href{https://doi.org/10.1123/ssj.25.4.560}{10.1123/ssj.25.4.560}

\hypertarget{ref-Watkins2017}{}
Watkins, S. L., Mincey, S. K., Vogt, J., \& Sweeney, S. P. (2017). Is
planting equitable? An examination of the spatial distribution of
nonprofit urban tree-planting programs by canopy cover, income, race,
and ethnicity. \emph{Environment and Behavior}, \emph{49}(4), 452--482.
doi:\href{https://doi.org/10.1177/0013916516636423}{10.1177/0013916516636423}

\hypertarget{ref-Watson2013}{}
Watson, A. C., \& Angell, B. (2013). The role of stigma and uncertainty
in moderating the effect of procedural justice on cooperation and
resistance in police encounters with persons with mental illnesses.
\emph{Psychology, Public Policy, and Law}, \emph{19}(1), 30--39.
doi:\href{https://doi.org/10.1037/a0027931}{10.1037/a0027931}

\hypertarget{ref-Watson2016}{}
Watson, L. B., Velez, B. L., Brownfield, J., \& Flores, M. J. (2016).
Minority stress and bisexual women's disordered eating. \emph{The
Counseling Psychologist}, \emph{44}(8), 1158--1186.
doi:\href{https://doi.org/10.1177/0011000016669233}{10.1177/0011000016669233}

\hypertarget{ref-Wayne2017}{}
Wayne, J. H., Butts, M. M., Casper, W. J., \& Allen, T. D. (2017). In
search of balance: A conceptual and empirical integration of multiple
meanings of work--family balance. \emph{Personnel Psychology},
\emph{70}(1), 167--210.
doi:\href{https://doi.org/10.1111/peps.12132}{10.1111/peps.12132}

\hypertarget{ref-Weeks2016}{}
Weeks, J. C., \& Hasher, L. (2017). Divided attention reduces resistance
to distraction at encoding but not retrieval. \emph{Psychonomic Bulletin
\& Review}, \emph{24}(4), 1268--1273.
doi:\href{https://doi.org/10.3758/s13423-016-1210-7}{10.3758/s13423-016-1210-7}

\hypertarget{ref-Weems2012}{}
Weems, C. F., Scott, B. G., Banks, D. M., \& Graham, R. A. (2012). Is TV
traumatic for all youths? The role of preexisting posttraumatic-stress
symptoms in the link between disaster coverage and stress.
\emph{Psychological Science}, \emph{23}(11), 1293--1297.
doi:\href{https://doi.org/10.1177/0956797612446952}{10.1177/0956797612446952}

\hypertarget{ref-Wei2012}{}
Wei, M., Tsai, P.-C., Chao, R. C.-L., Du, Y., \& Lin, S.-P. (2012).
Advisory working alliance, perceived English proficiency, and
acculturative stress. \emph{Journal of Counseling Psychology},
\emph{59}(3), 437--448.
doi:\href{https://doi.org/10.1037/a0028617}{10.1037/a0028617}

\hypertarget{ref-Weijters2010}{}
Weijters, B., Geuens, M., \& Schillewaert, N. (2010). The stability of
individual response styles. \emph{Psychological Methods}, \emph{15}(1),
96--110. doi:\href{https://doi.org/10.1037/a0018721}{10.1037/a0018721}

\hypertarget{ref-Weinberg2012}{}
Weinberg, A., Luhmann, C. C., Bress, J. N., \& Hajcak, G. (2012). Better
late than never? The effect of feedback delay on ERP indices of reward
processing. \emph{Cognitive, Affective, \& Behavioral Neuroscience},
\emph{12}(4), 671--677.
doi:\href{https://doi.org/10.3758/s13415-012-0104-z}{10.3758/s13415-012-0104-z}

\hypertarget{ref-Weiss2017}{}
Weiss, R. A., \& Rosenfeld, B. (2017). Identifying feigning in
trauma-exposed African immigrants. \emph{Psychological Assessment},
\emph{29}(7), 881--889.
doi:\href{https://doi.org/10.1037/pas0000381}{10.1037/pas0000381}

\hypertarget{ref-Welbourne2017}{}
Welbourne, T. M., \& Paterson, T. A. (2017). Advancing a richer view of
identity at work: The role-based identity scale. \emph{Personnel
Psychology}, \emph{70}(2), 315--356.
doi:\href{https://doi.org/10.1111/peps.12150}{10.1111/peps.12150}

\hypertarget{ref-VanWell2012}{}
Well, S. van, Visser, R. M., Scholte, H. S., \& Kindt, M. (2012). Neural
substrates of individual differences in human fear learning: Evidence
from concurrent fMRI, fear-potentiated startle, and US-expectancy data.
\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{12}(3),
499--512.
doi:\href{https://doi.org/10.3758/s13415-012-0089-7}{10.3758/s13415-012-0089-7}

\hypertarget{ref-Wells2012}{}
Wells, J. C., \& Baldwin, E. D. (2012). Historic preservation,
significance, and age value: A comparative phenomenology of historic
Charleston and the nearby new-urbanist community of I'On. \emph{Journal
of Environmental Psychology}, \emph{32}(4), 384--400.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.06.002}{10.1016/j.jenvp.2012.06.002}

\hypertarget{ref-Welsh2012}{}
Welsh, M. B., \& Navarro, D. J. (2012). Seeing is believing: Priors,
trust, and base rate neglect. \emph{Organizational Behavior and Human
Decision Processes}, \emph{119}(1), 1--14.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.04.001}{10.1016/j.obhdp.2012.04.001}

\hypertarget{ref-Wen2016}{}
Wen, Y., \& Heuven, W. J. B. van. (2016). Chinese translation norms for
1429 English words. \emph{Behavior Research Methods}, (June 2016),
1006--1019.
doi:\href{https://doi.org/10.3758/s13428-016-0761-x}{10.3758/s13428-016-0761-x}

\hypertarget{ref-Wenzel2017}{}
Wenzel, M., Anvari, F., Vel-Palumbo, M. de, \& Bury, S. M. (2017).
Collective apology, hope, and forgiveness. \emph{Journal of Experimental
Social Psychology}, \emph{72}, 75--87.
doi:\href{https://doi.org/10.1016/j.jesp.2017.05.003}{10.1016/j.jesp.2017.05.003}

\hypertarget{ref-Werner2012}{}
Werner, C. M., Cook, S., Colby, J., \& Lim, H. J. (2012). ``Lights out''
in university classrooms: Brief group discussion can change behavior.
\emph{Journal of Environmental Psychology}, \emph{32}(4), 418--426.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.07.001}{10.1016/j.jenvp.2012.07.001}

\hypertarget{ref-Westbrook2017}{}
Westbrook, J., \& Berenbaum, H. (2017). Emotional awareness moderates
the relationship between childhood abuse and borderline personality
disorder symptom factors. \emph{Journal of Clinical Psychology},
\emph{73}(7), 910--921.
doi:\href{https://doi.org/10.1002/jclp.22389}{10.1002/jclp.22389}

\hypertarget{ref-Westley2017}{}
Westley, A., Kohút, Z., \& Rueschemeyer, S.-A. (2017). ``I know
something you don't know'': Discourse and social context effects on the
N400 in adolescents. \emph{Journal of Experimental Child Psychology},
\emph{164}, 45--54.
doi:\href{https://doi.org/10.1016/j.jecp.2017.06.016}{10.1016/j.jecp.2017.06.016}

\hypertarget{ref-Whiffen2017}{}
Whiffen, J. W., \& Karpicke, J. D. (2017). The role of episodic context
in retrieval practice effects. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{43}(7), 1036--1046.
doi:\href{https://doi.org/10.1037/xlm0000379}{10.1037/xlm0000379}

\hypertarget{ref-White2011}{}
White, C. N., Ratcliff, R., \& Starns, J. J. (2011). Diffusion models of
the flanker task: Discrete versus gradual attentional selection.
\emph{Cognitive Psychology}, \emph{63}(4), 210--238.
doi:\href{https://doi.org/10.1016/j.cogpsych.2011.08.001}{10.1016/j.cogpsych.2011.08.001}

\hypertarget{ref-White2017}{}
White, L. J., Alexander, A., \& Greenfield, D. B. (2017). The
relationship between executive functioning and language: Examining
vocabulary, syntax, and language learning in preschoolers attending Head
Start. \emph{Journal of Experimental Child Psychology}, \emph{164},
16--31.
doi:\href{https://doi.org/10.1016/j.jecp.2017.06.010}{10.1016/j.jecp.2017.06.010}

\hypertarget{ref-White2017a}{}
White, M. H., \& Crandall, C. S. (2017). Freedom of racist speech: Ego
and expressive threats. \emph{Journal of Personality and Social
Psychology}, \emph{113}(3), 413--429.
doi:\href{https://doi.org/10.1037/pspi0000095}{10.1037/pspi0000095}

\hypertarget{ref-White2012}{}
White, P., \& McTeer, W. (2012). Socioeconomic status and sport
participation at different developmental stages during childhood and
youth: multivariate analyses using Canadian national survey data.
\emph{Sociology of Sport Journal}, \emph{29}(2), 186--209.
doi:\href{https://doi.org/10.1123/ssj.29.2.186}{10.1123/ssj.29.2.186}

\hypertarget{ref-Whitman2012}{}
Whitman, J. C., \& Woodward, T. S. (2012). Self-selection bias in
hypothesis comparison. \emph{Organizational Behavior and Human Decision
Processes}, \emph{118}(2), 216--225.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.02.002}{10.1016/j.obhdp.2012.02.002}

\hypertarget{ref-Whitmer2012a}{}
Whitmer, A. J., \& Banich, M. T. (2012). Brain activity related to the
ability to inhibit previous task sets: an fMRI study. \emph{Cognitive,
Affective, \& Behavioral Neuroscience}, \emph{12}(4), 661--670.
doi:\href{https://doi.org/10.3758/s13415-012-0118-6}{10.3758/s13415-012-0118-6}

\hypertarget{ref-Whitmer2012}{}
Whitmer, A. J., \& Gotlib, I. H. (2012). Depressive rumination and the
C957T polymorphism of the DRD2 gene. \emph{Cognitive, Affective, \&
Behavioral Neuroscience}, \emph{12}(4), 741--747.
doi:\href{https://doi.org/10.3758/s13415-012-0112-z}{10.3758/s13415-012-0112-z}

\hypertarget{ref-Wickrama2012}{}
Wickrama, K. A. S., Simons, L. G., \& Baltimore, D. (2012). The
influence of ethnicity and adverse life experiences during adolescence
on young adult socioeconomic attainment: The moderating role of
education. \emph{Journal of Youth and Adolescence}, \emph{41}(11),
1472--1487.
doi:\href{https://doi.org/10.1007/s10964-012-9764-9}{10.1007/s10964-012-9764-9}

\hypertarget{ref-Widaman2012}{}
Widaman, K. F., Helm, J. L., Castro-Schilo, L., Pluess, M., Stallings,
M. C., \& Belsky, J. (2012). Distinguishing ordinal and disordinal
interactions. \emph{Psychological Methods}, \emph{17}(4), 615--622.
doi:\href{https://doi.org/10.1037/a0030003}{10.1037/a0030003}

\hypertarget{ref-Wiener2012}{}
Wiener, R. L., Bennett, S., Cheloha, C., \& Nicholson, N. (2012). Gender
policing: Harassment judgments when men target other men.
\emph{Psychology, Public Policy, and Law}, \emph{18}(2), 245--267.
doi:\href{https://doi.org/10.1037/a0025904}{10.1037/a0025904}

\hypertarget{ref-Wiese2017}{}
Wiese, H., Komes, J., Tüttenberg, S., Leidinger, J., \& Schweinberger,
S. R. (2017). Age-related differences in face recognition: neural
correlates of repetition and semantic priming in young and older adults.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(8), 1254--1273.
doi:\href{https://doi.org/10.1037/xlm0000380}{10.1037/xlm0000380}

\hypertarget{ref-Wijekumar2017}{}
Wijekumar, K. K., Meyer, B. J. F., \& Lei, P. (2017). Web-based text
structure strategy instruction improves seventh graders' content area
reading comprehension. \emph{Journal of Educational Psychology},
\emph{109}(6), 741--760.
doi:\href{https://doi.org/10.1037/edu0000168}{10.1037/edu0000168}

\hypertarget{ref-Wilkerson2012}{}
Wilkerson, A., Carlson, N. E., Yen, I. H., \& Michael, Y. L. (2012).
Neighborhood physical features and relationships with neighbors.
\emph{Environment and Behavior}, \emph{44}(5), 595--615.
doi:\href{https://doi.org/10.1177/0013916511402058}{10.1177/0013916511402058}

\hypertarget{ref-Williams2017}{}
Williams, K. R., \& Stansfield, R. (2017). Disentangling the risk
assessment and intimate partner violence relation: Estimating mediating
and moderating effects. \emph{Law and Human Behavior}, \emph{41}(4),
344--353.
doi:\href{https://doi.org/10.1037/lhb0000249}{10.1037/lhb0000249}

\hypertarget{ref-Williams2012}{}
Williams, S. E., Cumming, J., Ntoumanis, N., Nordin-Bates, S. M.,
Ramsey, R., \& Hall, C. (2012). Further validation and development of
the movement imagery questionnaire. \emph{Journal of Sport and Exercise
Psychology}, \emph{34}(5), 621--646.
doi:\href{https://doi.org/10.1123/jsep.34.5.621}{10.1123/jsep.34.5.621}

\hypertarget{ref-Wilson2017a}{}
Wilson, J. P., Hugenberg, K., \& Rule, N. O. (2017). Racial bias in
judgments of physical size and formidability: From size to threat.
\emph{Journal of Personality and Social Psychology}, \emph{113}(1),
59--80.
doi:\href{https://doi.org/10.1037/pspi0000092}{10.1037/pspi0000092}

\hypertarget{ref-Wilson2018}{}
Wilson, J. P., Young, S. G., Rule, N. O., \& Hugenberg, K. (2018).
Configural processing and social judgments: Face inversion particularly
disrupts inferences of human-relevant traits. \emph{Journal of
Experimental Social Psychology}, \emph{74}, 1--7.
doi:\href{https://doi.org/10.1016/j.jesp.2017.07.007}{10.1016/j.jesp.2017.07.007}

\hypertarget{ref-Wilson2017}{}
Wilson, L. C., Miller, K. E., Leheney, E. K., Ballman, A. D., \& Scarpa,
A. (2017). Examining the psychological effect of rape acknowledgment:
The interaction of acknowledgment status and ambivalent sexism.
\emph{Journal of Clinical Psychology}, \emph{73}(7), 864--878.
doi:\href{https://doi.org/10.1002/jclp.22379}{10.1002/jclp.22379}

\hypertarget{ref-Wilson2012}{}
Wilson, S., \& Durbin, C. E. (2012). The Laboratory Parenting Assessment
Battery: Development and preliminary validation of an observational
parenting rating system. \emph{Psychological Assessment}, \emph{24}(4),
823--832. doi:\href{https://doi.org/10.1037/a0028352}{10.1037/a0028352}

\hypertarget{ref-Wiltermuth2017}{}
Wiltermuth, S. S., Vincent, L. C., \& Gino, F. (2017). Creativity in
unethical behavior attenuates condemnation and breeds social contagion
when transgressions seem to create little harm. \emph{Organizational
Behavior and Human Decision Processes}, \emph{139}, 106--126.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.01.006}{10.1016/j.obhdp.2017.01.006}

\hypertarget{ref-Witzel2012}{}
Witzel, N. O., \& Forster, K. I. (2012). How L2 words are stored: The
episodic L2 hypothesis. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{38}(6), 1608--1621.
doi:\href{https://doi.org/10.1037/a0028072}{10.1037/a0028072}

\hypertarget{ref-Wolitzky-Taylor2012}{}
Wolitzky-Taylor, K. B., Arch, J. J., Rosenfield, D., \& Craske, M. G.
(2012). Moderators and non-specific predictors of treatment outcome for
anxiety disorders: A comparison of cognitive behavioral therapy to
acceptance and commitment therapy. \emph{Journal of Consulting and
Clinical Psychology}, \emph{80}(5), 786--799.
doi:\href{https://doi.org/10.1037/a0029418}{10.1037/a0029418}

\hypertarget{ref-Wolsiefer2017}{}
Wolsiefer, K., Westfall, J., \& Judd, C. M. (2017). Modeling stimulus
variation in three common implicit attitude tasks. \emph{Behavior
Research Methods}, \emph{49}(4), 1193--1209.
doi:\href{https://doi.org/10.3758/s13428-016-0779-0}{10.3758/s13428-016-0779-0}

\hypertarget{ref-Woltz2012}{}
Woltz, D. J., Gardner, M. K., Kircher, J. C., \& Burrow-Sanchez, J. J.
(2012). Relationship between perceived and actual frequency represented
by common rating scale labels. \emph{Psychological Assessment},
\emph{24}(4), 995--1007.
doi:\href{https://doi.org/10.1037/a0028693}{10.1037/a0028693}

\hypertarget{ref-Wong2013}{}
Wong, C. C. Y., \& Mak, W. W. S. (2013). Differentiating the role of
three self-compassion components in buffering cognitive-personality
vulnerability to depression among Chinese in Hong Kong. \emph{Journal of
Counseling Psychology}, \emph{60}(1), 162--169.
doi:\href{https://doi.org/10.1037/a0030451}{10.1037/a0030451}

\hypertarget{ref-Wong2017}{}
Wong, T. T.-Y. (2017). The unique and shared contributions of arithmetic
operation understanding and numerical magnitude representation to
children's mathematics achievement. \emph{Journal of Experimental Child
Psychology}, \emph{164}, 68--86.
doi:\href{https://doi.org/10.1016/j.jecp.2017.07.007}{10.1016/j.jecp.2017.07.007}

\hypertarget{ref-Wong2017a}{}
Wong, T. T.-Y., \& Ho, C. S.-H. (2017). Component processes in
arithmetic word-problem solving and their correlates. \emph{Journal of
Educational Psychology}, \emph{109}(4), 520--531.
doi:\href{https://doi.org/10.1037/edu0000149}{10.1037/edu0000149}

\hypertarget{ref-Wood2016}{}
Wood, Z. C., \& Garn, A. C. (2016). Leveling the playing field?
Perspectives and observations of coed intramural flag football
modifications. \emph{Sociology of Sport Journal}, \emph{33}(3),
240--249.
doi:\href{https://doi.org/10.1123/ssj.2015-0095}{10.1123/ssj.2015-0095}

\hypertarget{ref-Woodcock}{}
Woodcock, A., Hernandez, P. R., Estrada, M., \& Schultz, P. W. (2012).
The consequences of chronic stereotype threat: Domain disidentification
and abandonment. \emph{Journal of Personality and Social Psychology},
\emph{103}(4), 635--646.
doi:\href{https://doi.org/10.1037/a0029120}{10.1037/a0029120}

\hypertarget{ref-Worthy2012}{}
Worthy, D. A., Otto, A. R., \& Maddox, W. T. (2012). Working-memory load
and temporal myopia in dynamic decision making. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{38}(6),
1640--1658.
doi:\href{https://doi.org/10.1037/a0028146}{10.1037/a0028146}

\hypertarget{ref-Wu2016}{}
Wu, C. M., Meder, B., Filimon, F., \& Nelson, J. D. (2017). Asking
better questions: How presentation formats influence information search.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{43}(8), 1274--1297.
doi:\href{https://doi.org/10.1037/xlm0000374}{10.1037/xlm0000374}

\hypertarget{ref-Wu2012a}{}
Wu, D.-A., Shimojo, S., Wang, S. W., \& Camerer, C. F. (2012). Shared
visual attention reduces hindsight bias. \emph{Psychological Science},
\emph{23}(12), 1524--1533.
doi:\href{https://doi.org/10.1177/0956797612447817}{10.1177/0956797612447817}

\hypertarget{ref-Wu2012}{}
Wu, E. K. Y., \& Mak, W. W. S. (2012). Acculturation process and
distress: Mediating roles of sociocultural adaptation and acculturative
stress. \emph{The Counseling Psychologist}, \emph{40}(1), 66--92.
doi:\href{https://doi.org/10.1177/0011000011410893}{10.1177/0011000011410893}

\hypertarget{ref-Wyles2017}{}
Wyles, K. J., Pahl, S., Holland, M., \& Thompson, R. C. (2017). Can
beach cleans do more than clean-up litter? Comparing beach cleans to
other coastal activities. \emph{Environment and Behavior}, \emph{49}(5),
509--535.
doi:\href{https://doi.org/10.1177/0013916516649412}{10.1177/0013916516649412}

\hypertarget{ref-Wylie2017}{}
Wylie, G. R., Genova, H. M., DeLuca, J., \& Dobryakova, E. (2017). The
relationship between outcome prediction and cognitive fatigue: A
convergence of paradigms. \emph{Cognitive, Affective, \& Behavioral
Neuroscience}, 838--849.
doi:\href{https://doi.org/10.3758/s13415-017-0515-y}{10.3758/s13415-017-0515-y}

\hypertarget{ref-Wynveen2012}{}
Wynveen, C. J., Kyle, G. T., \& Sutton, S. G. (2012). Natural area
visitors' place meaning and place attachment ascribed to a marine
setting. \emph{Journal of Environmental Psychology}, \emph{32}(4),
287--296.
doi:\href{https://doi.org/10.1016/j.jenvp.2012.05.001}{10.1016/j.jenvp.2012.05.001}

\hypertarget{ref-Xiao2017}{}
Xiao, H., Castonguay, L. G., Janis, R. A., Youn, S. J., Hayes, J. A., \&
Locke, B. D. (2017). Therapist effects on dropout from a college
counseling center practice research network. \emph{Journal of Counseling
Psychology}, \emph{64}(4), 424--431.
doi:\href{https://doi.org/10.1037/cou0000208}{10.1037/cou0000208}

\hypertarget{ref-Xiao2012}{}
Xiao, W., \& Treiman, R. (2012). Iconicity of simple Chinese characters.
\emph{Behavior Research Methods}, \emph{44}(4), 954--960.
doi:\href{https://doi.org/10.3758/s13428-012-0191-3}{10.3758/s13428-012-0191-3}

\hypertarget{ref-Xu2017}{}
Xu, H., \& Tracey, T. J. G. (2017). Development of an abbreviated career
indecision profile-65 using item response theory: The CIP-Short.
\emph{Journal of Counseling Psychology}, \emph{64}(2), 222--232.
doi:\href{https://doi.org/10.1037/cou0000182}{10.1037/cou0000182}

\hypertarget{ref-Xu2017a}{}
Xu, Y., Malt, B. C., \& Srinivasan, M. (2017). Evolution of word
meanings through metaphorical mapping: Systematicity over the past
millennium. \emph{Cognitive Psychology}, \emph{96}, 41--53.
doi:\href{https://doi.org/10.1016/j.cogpsych.2017.05.005}{10.1016/j.cogpsych.2017.05.005}

\hypertarget{ref-Yamaguchi2017}{}
Yamaguchi, M., \& Logan, G. D. (2016). Pushing typists back on the
learning curve: Memory chunking in the hierarchical control of skilled
typewriting. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{42}(12), 1919--1936.
doi:\href{https://doi.org/10.1037/xlm0000288}{10.1037/xlm0000288}

\hypertarget{ref-Yang2017}{}
Yang, C., Potts, R., \& Shanks, D. R. (2017). Metacognitive unawareness
of the errorful generation benefit and its effects on self-regulated
learning. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{43}(7), 1073--1092.
doi:\href{https://doi.org/10.1037/xlm0000363}{10.1037/xlm0000363}

\hypertarget{ref-Yang2012}{}
Yang, J., Staub, A., Li, N., Wang, S., \& Rayner, K. (2012).
Plausibility effects when reading one- and two-character words in
Chinese: Evidence from eye movements. \emph{Journal of Experimental
Psychology: Learning, Memory, and Cognition}, \emph{38}(6), 1801--1809.
doi:\href{https://doi.org/10.1037/a0028478}{10.1037/a0028478}

\hypertarget{ref-Yao2017}{}
Yao, Z., Wu, J., Zhang, Y., \& Wang, Z. (2017). Norms of valence,
arousal, concreteness, familiarity, imageability, and context
availability for 1,100 Chinese words. \emph{Behavior Research Methods},
\emph{49}(4), 1374--1385.
doi:\href{https://doi.org/10.3758/s13428-016-0793-2}{10.3758/s13428-016-0793-2}

\hypertarget{ref-Yeager2012}{}
Yeager, D. S., Bundick, M. J., \& Johnson, R. (2012). The role of future
work goal motives in adolescent identity development: A longitudinal
mixed-methods investigation. \emph{Contemporary Educational Psychology},
\emph{37}(3), 206--217.
doi:\href{https://doi.org/10.1016/j.cedpsych.2012.01.004}{10.1016/j.cedpsych.2012.01.004}

\hypertarget{ref-Young2012}{}
Young, D. L., Goodie, A. S., Hall, D. B., \& Wu, E. (2012). Decision
making under time pressure, modeled in a prospect theory framework.
\emph{Organizational Behavior and Human Decision Processes},
\emph{118}(2), 179--188.
doi:\href{https://doi.org/10.1016/j.obhdp.2012.03.005}{10.1016/j.obhdp.2012.03.005}

\hypertarget{ref-Young2016}{}
Young, K. S., Parsons, C. E., LeBeau, R. T., Tabak, B. A., Sewart, A.
R., Stein, A., \ldots{} Craske, M. G. (2017). Sensing emotion in voices:
Negativity bias and gender differences in a validation study of the
Oxford Vocal (`OxVoc') sounds database. \emph{Psychological Assessment},
\emph{29}(8), 967--977.
doi:\href{https://doi.org/10.1037/pas0000382}{10.1037/pas0000382}

\hypertarget{ref-Yu2016}{}
Yu, N.-Y., Van Gemmert, A. W. A., \& Chang, S.-H. (2016).
Characterization of graphomotor functions in individuals with
Parkinson's disease and essential tremor. \emph{Behavior Research
Methods}, \emph{35}(2), 795--806.
doi:\href{https://doi.org/10.3758/s13428-016-0752-y}{10.3758/s13428-016-0752-y}

\hypertarget{ref-Yu-HsinLiao2012}{}
Yu-Hsin Liao, K., Wei, M., Russell, D. W., \& Abraham, W. T. (2012).
Experiential self-focus writing as a facilitator of processing an
interpersonal hurt. \emph{Journal of Clinical Psychology},
\emph{68}(10), 1089--1110.
doi:\href{https://doi.org/10.1002/jclp.21886}{10.1002/jclp.21886}

\hypertarget{ref-Yuan2010}{}
Yuan, K.-H., \& Hayashi, K. (2010). Fitting data to model: Structural
equation modeling diagnosis using two scatter plots. \emph{Psychological
Methods}, \emph{15}(4), 335--351.
doi:\href{https://doi.org/10.1037/a0020140}{10.1037/a0020140}

\hypertarget{ref-Zanini2016}{}
Zanini, C., Benavides-Varela, S., Lorusso, R., \& Franzon, F. (2017).
Mass is more: The conceiving of (un)countability and its encoding into
language in 5-year-old-children. \emph{Psychonomic Bulletin \& Review},
\emph{24}(4), 1330--1340.
doi:\href{https://doi.org/10.3758/s13423-016-1187-2}{10.3758/s13423-016-1187-2}

\hypertarget{ref-Zapolski2017}{}
Zapolski, T. C. B., Fisher, S., Banks, D. E., Hensel, D. J., \&
Barnes-Najor, J. (2017). Examining the protective effect of ethnic
identity on drug attitudes and use among a diverse youth population.
\emph{Journal of Youth and Adolescence}, \emph{46}(8), 1702--1715.
doi:\href{https://doi.org/10.1007/s10964-016-0605-0}{10.1007/s10964-016-0605-0}

\hypertarget{ref-Zebel2017}{}
Zebel, S., Schreurs, W., \& Ufkes, E. G. (2017). Crime seriousness and
participation in restorative justice: The role of time elapsed since the
offense. \emph{Law and Human Behavior}, \emph{41}(4), 385--397.
doi:\href{https://doi.org/10.1037/lhb0000242}{10.1037/lhb0000242}

\hypertarget{ref-Zee2017}{}
Zee, M., Jong, P. F. de, \& Koomen, H. M. (2017). From externalizing
student behavior to student-specific teacher self-efficacy: The role of
teacher-perceived conflict and closeness in the student--teacher
relationship. \emph{Contemporary Educational Psychology}, \emph{51},
37--50.
doi:\href{https://doi.org/10.1016/j.cedpsych.2017.06.009}{10.1016/j.cedpsych.2017.06.009}

\hypertarget{ref-Zeinoun2017}{}
Zeinoun, P., Daouk-Öyry, L., Choueiri, L., \& Vijver, F. J. R. van de.
(2017). A mixed-methods study of personality conceptions in the Levant:
Jordan, Lebanon, Syria, and the West Bank. \emph{Journal of Personality
and Social Psychology}, \emph{113}(3), 453--465.
doi:\href{https://doi.org/10.1037/pspp0000148}{10.1037/pspp0000148}

\hypertarget{ref-Zentall2012}{}
Zentall, S. R., \& Morris, B. J. (2012). A critical eye: Praise directed
toward traits increases children's eye fixations on errors and decreases
motivation. \emph{Psychonomic Bulletin \& Review}, \emph{19}(6),
1073--1077.
doi:\href{https://doi.org/10.3758/s13423-012-0294-y}{10.3758/s13423-012-0294-y}

\hypertarget{ref-Zerella2017}{}
Zerella, S., Treuer, K. von, \& Albrecht, S. L. (2017). The influence of
office layout features on employee perception of organizational culture.
\emph{Journal of Environmental Psychology}, \emph{54}(Supplement C),
1--10.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.08.004}{10.1016/j.jenvp.2017.08.004}

\hypertarget{ref-Zestcott2016}{}
Zestcott, C. A., Lifshin, U., Helm, P., \& Greenberg, J. (2016). He
dies, he scores: Evidence that reminders of death motivate improved
performance in basketball. \emph{Journal of Sport and Exercise
Psychology}, \emph{38}(5), 470--480.
doi:\href{https://doi.org/10.1123/jsep.2016-0025}{10.1123/jsep.2016-0025}

\hypertarget{ref-Zhan2016}{}
Zhan, Y., Wang, M., \& Shi, J. (2016). Interpersonal process of
emotional labor: The role of negative and positive customer treatment.
\emph{Personnel Psychology}, \emph{69}(3), 525--557.
doi:\href{https://doi.org/10.1111/peps.12114}{10.1111/peps.12114}

\hypertarget{ref-Zhang2012a}{}
Zhang, J., Lamis, D. A., \& Yuanyuan, K. (2012). Measuring Chinese
psychological traits and social support with Western developed
instruments in psychological autopsy studies. \emph{Journal of Clinical
Psychology}, \emph{68}(12), 1313--1321.
doi:\href{https://doi.org/10.1002/jclp.21907}{10.1002/jclp.21907}

\hypertarget{ref-Zhang2012}{}
Zhang, Z., Waldman, D. A., \& Wang, Z. (2012). A multilevel
investigation of leader- member exchange, informal leader emergence, and
individual and team performance. \emph{Personnel Psychology},
\emph{65}(1), 49--78.
doi:\href{https://doi.org/10.1111/j.1744-6570.2011.01238.x}{10.1111/j.1744-6570.2011.01238.x}

\hypertarget{ref-Zhao2017}{}
Zhao, M., \& B?lthoff, I. (2017). Holistic processing of static and
moving faces. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{43}(7), 1020--1035.
doi:\href{https://doi.org/10.1037/xlm0000368}{10.1037/xlm0000368}

\hypertarget{ref-Zhou2012}{}
Zhou, N., Lam, S.-F., \& Chan, K. C. (2012). The Chinese classroom
paradox: A cross-cultural comparison of teacher controlling behaviors.
\emph{Journal of Educational Psychology}, \emph{104}(4), 1162--1174.
doi:\href{https://doi.org/10.1037/a0027609}{10.1037/a0027609}

\hypertarget{ref-Zhu2017}{}
Zhu, Y., Ritter, S., Müller, B., \& Dijksterhuis, A. (2017). Creativity:
Intuitive processing outperforms deliberative processing in creative
idea selection. \emph{Journal of Experimental Social Psychology},
\emph{73}, 180--188.
doi:\href{https://doi.org/10.1016/j.jesp.2017.06.009}{10.1016/j.jesp.2017.06.009}

\hypertarget{ref-Zijlstra2017}{}
Zijlstra, E., Hagedoorn, M., Krijnen, W. P., Schans, C. P. van der, \&
Mobach, M. P. (2017). Motion nature projection reduces patient's
psycho-physiological anxiety during CT imaging. \emph{Journal of
Environmental Psychology}, \emph{53}, 168--176.
doi:\href{https://doi.org/10.1016/j.jenvp.2017.07.010}{10.1016/j.jenvp.2017.07.010}

\hypertarget{ref-Zimmerman2017}{}
Zimmerman, G. M., \& Kushner, M. (2017). Examining the contemporaneous,
short-term, and long-term effects of secondary exposure to violence on
adolescent substance use. \emph{Journal of Youth and Adolescence},
\emph{46}(9), 1933--1952.
doi:\href{https://doi.org/10.1007/s10964-017-0694-4}{10.1007/s10964-017-0694-4}

\hypertarget{ref-Zingoni2017}{}
Zingoni, M., \& Byron, K. (2017). How beliefs about the self influence
perceptions of negative feedback and subsequent effort and learning.
\emph{Organizational Behavior and Human Decision Processes}, \emph{139},
50--62.
doi:\href{https://doi.org/10.1016/j.obhdp.2017.01.007}{10.1016/j.obhdp.2017.01.007}

\hypertarget{ref-Zosh2012}{}
Zosh, J. M., \& Feigenson, L. (2012). Memory load affects object
individuation in 18-month-old infants. \emph{Journal of Experimental
Child Psychology}, \emph{113}(3), 322--336.
doi:\href{https://doi.org/10.1016/j.jecp.2012.07.005}{10.1016/j.jecp.2012.07.005}

\hypertarget{ref-Zottoli2016}{}
Zottoli, T. M., Daftary-Kapur, T., Winters, G. M., \& Hogan, C. (2016).
Plea discounts, time pressures, and false-guilty pleas in youth and
adults who pleaded guilty to felonies in New York City.
\emph{Psychology, Public Policy, and Law}, \emph{22}(3), 250--259.
doi:\href{https://doi.org/10.1037/law0000095}{10.1037/law0000095}

\hypertarget{ref-Zwaanswijk2016}{}
Zwaanswijk, W., Veen, V. C., Geel, M. van, Andershed, H., \& Vedder, P.
(2017). The relation between the bifactor model of the Youth
Psychopathic Traits Inventory and conduct problems in adolescence:
Variations across gender, ethnic background, and age.
\emph{Psychological Assessment}, \emph{29}(8), 1065--1070.
doi:\href{https://doi.org/10.1037/pas0000407}{10.1037/pas0000407}






\end{document}
